### 2024-12-26 main.tex
Added v1 of the paper (copied from overleaf).

\documentclass[a4paper]{article}

\usepackage{amsmath}  % extra math features
\usepackage{booktabs}  % nice tables
\usepackage[margin=25mm]{geometry}
\usepackage{graphicx} % required for inserting images
\usepackage{hyperref} % clickable hyperlinks
\usepackage{multirow}  % pandas to_latex() uses this
\usepackage{siunitx}  % use for all units
\usepackage{subcaption}  % for subfigures

% hyperref settings for better looking links
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
}

\title{
  DRAFT: v1 \\
  Vibration Characterization of Babies\\
  Transported in Strollers and Cargo Bicycles\\
  \vspace{2mm}
  \large{Prepared for VeiligheidNL}
}
\author{Gabriele Dell'Orto \and Brecht Daams \and Riender Happee \and Jason K. Moore}

\begin{document}

\maketitle

\section*{\centering Notice}
%
\textbf{This is a draft report. The values and results must be considered
preliminary and may change as the analysis is refined and rechecked.}

\section*{\centering Acknowledgements}
%
Thomas Valk and Jesper Meijerink helped design and perform the experiments.
Georgios Papaioannou and Arjo Loeve gave advice on the experimental design and
analyses.

\section{Introduction}
%
This paper reports on the vibration experienced by infants of different ages
when transported in cargo bicycles and strollers. Vibration can be related to
discomfort and might lead to negative health consequences. However, the topic is
poorly addressed in scientific literature, and only a few studies focus on the
effect of vibration on babies. To measure the actual vibration transmitted to
the babies, we equipped three strollers and two cargo bicycles with inertial
measurement units (IMU) and conducted several experiments across different road
surfaces and travelling speeds, using dummies representing the size of 0, 3, and
9 months old babies. We present analysis in the time and frequency domains,
allowing us to compare vertical accelerations at the baby-seat interface, as
recommended by ISO-2631-1. We investigate the influence of different variables
on vibration, such as type of vehicle, baby seat, travelling speed, dummy size
and mass, and road surfaces.

\section{Methods}
%
\subsection{Experimental Methodology}
%
In this section, we describe the measurement equipment used and the protocol
followed during the experimental campaign.

\subsubsection{Description of Test Equipment}
%
We conducted the experimental campaign using three different strollers, two
cargo bicycles, and two baby seats, chosen for their popularity and/or
distinctive features. The test involved three baby dummies representative of
various ages (different sizes and masses).

\paragraph{Strollers}
%
\begin{description}
  \item[Maxi-Cosi Street Plus] Among the most popular brands, this stroller comes
  with a cot configuration (0-3 months) and a baby seat option. It has large
  wheels, with only a marginal suspension system.
  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
  \item[Stokke BABYZEN YOYO 0+] It is the smallest foldable stroller on the
  market, it has only a marginal suspension system and smaller wheels compared
  to the other strollers on the market. It can be considered the ideal choice
  for holidays, being one of the few buggies that can be taken as hand
  luggage on the plane.
  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
  rented for the experiment})
  \item[Bugaboo Fox 5] It is featured by large wheels, and a suspension system
  which makes it an all-terrain stroller (according to the manufacturer). It has
  a large puncture-proof tyres and an air-permeable mattress.
  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
  website})
\end{description}

\paragraph{Cargo Bicycles}
%
\begin{description}
  \item[Urban Arrow Bicycle] This is a popular electric cargo bicycle in The
  Netherlands. This vehicle has two inline wheels which makes it roll into the
  curve like a regular bicycle. It is featured by a long frame that can carry
  loads usually placed in between the rider and the front wheel. It can fit
  various accessories, including baby seats, rain covers, etc.
  (\href{https://urbanarrow.com/}{Urban Arrow website})
  \item[Keiler Tricycle] This is a tadpole (two wheels in the front, one in the
  rear) cargo tricycle without electric assist. This vehicle will not roll in
  curves. However, differing road surface unevenness at the left and right front
  wheel will induce lateral roll and lateral acceleration in infants. We
  added masses in specific locations to simulate the presence of an electric
  motor and battery package.
 (\href{https://kashop.nl/product/keiler-bakfiets/}{Product Webpage}) 
\end{description}

\paragraph{Baby Seats}

These baby seats were mounted in the cargo bay of the two cargo bicycles.
%
\begin{description}
  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] This seat can be adapted to
    cargo bicycles with a proper fixing system (e.g. ``Urban Arrow Baby Car Seat
    Adapter''). It comes with an integrated suspension system which is part of
    the adapter.
    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi Webpage})
  \item[Melia Baby Shell]. The baby seat is meant for babies from 2 to 9 months,
    specifically designed for cargo bikes.
    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia Webpage})
\end{description}

We conducted tests using three different dummies, of various sizes and masses
according to the desired ages of 0, 3 and 9 months. We considered the use of
``crash test dummies'' which are designed and commonly used to test
child seats in cars in crash conditions. However, the nearest available body
sizes for crash test dummies were a 6-weeks Q-dummy, a 6-months Crabi dummy, and a
12-months Q-dummy. These 3 dummies are of a fundamentally different design,
hampering comparison, and do not match the desired body size. Moreover, these
child dummies have dynamic properties designed for crash conditions, and use
scaling of adult biomechanical data, rather than child data.
Testing with real children would be unethical for the most severe conditions
tested, and would create challenges in terms of reproducibility.
Hence we bought and adapted dummies available in a wide range of postures. We
bought ``reborn'' dummies from a webshop specialising in dolls and dummies
(\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). We filled the dummies
with cat litter sand to reproduce the exact weight needed for testing. Cat
litter sand indeed features smooth and round-shaped grains, which do not
damage the dummies' material (fabric and plastic). The weight and body height of
the dummies are average measures for children of exactly 0, 3 and 9 months old.
We wanted to use the measurements from Steenbekkers \cite{Steenbekkers1993}. But
the researchers provided the results only per three-month group, which did not fit our
age categories. Therefore, we decided to use the growth charts to determine the average weight
and body height at the right ages. Growth charts (`groeidiagrammen') are used by
doctors to assess the growth of babies. The average weight at 0 months and the
average body height at all three ages are derived from Dutch growth charts.
Measurements of Dutch children are used because the Dutchies are the target group of
VeiligheidNL. Dutch children are also the tallest in Europe. The average weight
of 3 and 9 months children is derived from French growth charts. French children
are the smallest in Europe. At 3 months, the weight difference is 4 ounces and
at 9 months, it is 3 ounces compared to Dutch children.  
%
\begin{description}
  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
  ``Andi Asleep'' (product code AW380008).
  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
  ``Asia - Limited Edition'' (product code 300287).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
  \item[Dummy 9 months] weight 8.90~\si{\kg}. Size 70~\si{\cm}. Dollkit 28'',
  ``Hailey'' (product code 304137).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
\end{description}

To achieve a realistic mass distribution in the body of the dummies, it is
important to fill each limb with the proper amount of sand. To do this, we
simplified the geometry of each body segment according to defined basic
geometric shapes: we assumed a sphere for the head, and cylinders for the torso,
upper arms, upper legs and lower legs, according to what was stated in
\cite{Snyder1977}. We also assumed an equal density of each limb, and we
rescaled the measurements of the limb segments reported in \cite{Snyder1977} to
match the dimensions of our dummies. In doing so, we were able to calculate the
volume of each segment, thus the mass of each limb of the dummies (assuming a
density of 1000~\si{\kg\per\cubic\meter}).

\subsubsection{Description of Measurement Equipment}
%
Linear acceleration and angular velocity was measured using five IMUs.
Specifically, we used a Consensys Shimmer3 IMU with a Consensys Base 6U.01 dock.
The Shimmer units were updated to the firmware version LogAndStream v0.11.0, and
managed via the software ConsensysBASIC v1.6.0-64bit on a Laptop Dell 7310, OS
Microsoft Windows 10. We 3D printed supports for the sensors to ensure a firm
clamp between the sensor and the bicycle/stroller tested (visible in
Figure~\ref{fig:sensors_UA}). Each vehicle was equipped with five IMUs, as
listed below. The pictures of sensors mounted on the cargo bicycle Urban Arrow
are depicted in Figure~\ref{fig:sensors_UA}. The location and orientation of the
sensors for Urban Arrow equipped with the Melia baby shell are reported in
Figure~\ref{fig:tech_drawing_UA_Melia}, both for lateral and front view.
Similarly, the Bugaboo configured to carry 0 months babies in the baby cot is
shown in Figure~\ref{fig:tech_drawing_Bugaboo0}.
%
\begin{figure}
  \centering
  \subcaptionbox{IMU on the front fork}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/FW_UA.png}}
  \subcaptionbox{IMU on the rear wheel hub}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/RW_UA.png}}
  \subcaptionbox{IMU under the cargo bay}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/BT_UA.png}}
  \subcaptionbox{IMUs on the baby seat surface}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/Maxicosi_sensors_UA.png}}
  \caption{IMU locations on the Urban Arrow cargo bicycle. The white 3D printed
  sensor supports are visible in (a) and (c).}
  \label{fig:sensors_UA}
\end{figure}
%
\begin{figure}
  \centering
  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA_Melia_lateral.PNG}}
  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_UA_Melia_front.PNG}}
  \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
  Melia baby shell. Here you can see the locations from the front and the
  lateral view. All the measurements are in \si{\mm}. You can also see the
  sensors' orientation. The reference system from which we draw the measurements
  is highlighted in red and placed on the rotational axis of the front wheel.}
  \label{fig:tech_drawing_UA_Melia}
\end{figure}
%
\begin{figure}
  \centering
  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_lateral.PNG}}
  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_front.PNG}}
  \caption{IMU locations on the Bugaboo Fox 5 stroller in the configuration for
  the 0 month baby. Here you can see the location from the front and the lateral
  view. All the measurements are in \si{\mm}. You can also see the sensors'
  orientation. The reference system from which we draw the measurements is
  highlighted in red, and placed on the rotational axis of the front wheel.}
  \label{fig:tech_drawing_Bugaboo0}
\end{figure}
%
\begin{enumerate}
  \item \textbf{Rear Wheel} The sensor was placed on the wheel hub (cargo
  bicycles) or clamped to the wheel (strollers). The purpose of this sensor is
  for a travel speed measurement. We can derive the travelling (longitudinal)
  speed according to:
  %
  \begin{align}
    v = \si{\omega} \cdot r
    \label{eq:long-speed}
  \end{align}
  %
  where \si{\omega} is the angular speed of the vehicle (from IMU gyroscope aligned with the wheel's axis) and $r$ is the radius of the wheel.
  \item \textbf{Front Wheel} The sensor was mounted on the front wheel fork (the
  caster wheel for the stroller). This is the measurement point closest to the
  ground for a non-rotating sensor. The purpose of this sensor is to measure the
  road roughness filtered out by the tyres.  
  \item \textbf{Frame} As for the cargo bicycle, the third sensor was placed
  below the frontal cargo bay, clamped to the frame. It can give us an
  understanding of the damping characteristics of the bicycle frame, together
  with an estimation of the effect of the suspension system. Regarding the
  stroller, the sensor was placed under the baby seat.
  \item \textbf{Seat Head} Sensor mounted into the baby seat, directly in
  contact with the dummy's head. It measured the vibration transmitted to the
  head contact point.
  \item \textbf{Seat Buttock} This sensor was taped into the baby seat, at the
  interface between the dummy's buttock and the baby seat. It measured the
  vibration transmitted to the dummy's buttock.
\end{enumerate}

The IMU sensors for the seat head and seat buttock were placed at the surface at
positions contacting the dummy. This matches the recommended practice in
vibration testing norms such as ISO-2631-1. This generates acceleration data
representative of the mechanical load transferred from the seat to the human
body taking into account the compliance of the seat foams. We set the sampling
frequency to 910.22~\si{\hertz} for all the sensors. The full-scale range was
16~g for the accelerometer ("WR" or "wide range" configuration on Consensys
Shimmer software), and 2000~\si{\degree\per\second} for the gyroscope. All the
tests were recorded with two GoPro cameras Hero7: one directly mounted on the
strollers/bicycles to record the relative motion dummy/seat, while the other one
was held by an experimenter walking or riding alongside the vehicle to have a
complete overview of the experiment.

\subsubsection{Description of Experimental Protocol}
%
We conducted the experimental campaign in Delft, The Netherlands along public
roads near the Delft University of Technology, Faculty of Mechanical
Engineering.
After mounting the sensors in the correct position and reaching the location
of the experiment, we turned on the sensors to start the experimental session.
Before each trial, we pushed the vehicle back and forth on level ground to mark
the beginning of the trial for time synchronizing the sensors.
For the cargo bicycle test, a single rider conducted the full experimental
campaign to be consistent across different sessions (rider mass: 59~\si{\kg};
rider height: 1.70~\si{\m}).
We gathered data from multiple trials within the same session. The tests were
conducted on six different surfaces for the strollers with the pusher manually
keeping consistent walking speed of approximately 5~\si{\kilo\meter\per\hour}
across different trials by observing a speedometer. We tested on three surface
scenarios for the cargo bicycles (at different speeds). The test combinations
are listed below.
%
\begin{itemize}
  \item \textbf{Strollers} We tried to keep speed as constant and consistent as
  possible among different trials and sessions. The experimental campaign was
  conducted using dummies of 0 months and 9 months. Some of the test surfaces
  are depicted in Figure~\ref{fig:surfaces_stroller} and all are listed below:
  \begin{itemize}
      \item Tarmac
      \item Paver bricks % Klinkers
      \item Sidewalk pavers % Stoeptegels
      \item Cobblestones 
      \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
      \item Shock. A 30x30~\si{\mm} square section aluminium bar was taped on the ground (smooth surface)
  \end{itemize}
  \item \textbf{Cargo bicycles} The experimental campaign was conducted using
  dummies of 0 months and 3 months. Regarding the Keiler tricycle, the speed was
  limited to 20~\si{\km\per\hour} for safety reasons (due to wobbling), and
  difficulties to safely keep a constant speed over 22~\si{\km\per\hour}. The test surfaces are listed below:
  \begin{itemize}
      \item Tarmac
      \item Paver bricks
      \item Shock. As mentioned before, we conducted shock test riding over a
      30x30~\si{\mm} square section aluminium bar, at three speeds: 
      \begin{itemize}
          \item Low speed scenario: 5~\si{\km\per\hour}
          \item Medium speed scenario: 12~\si{\km\per\hour}
          \item High speed scenario: 20~\si{\km\per\hour} for the Keiler
          tricycle, 25~\si{\km\per\hour} for the Urban Arrow cargo bicycle.
      \end{itemize}
  \end{itemize}
  \item \textbf{Baby seats} Both were tested on each cargo bicycle using the
  same mounting systems.
  \begin{itemize}
      \item Maxi-Cosi X Joolz Pebble Pro i-Size car seat, it can be adapted to
      cargo bicycles with a proper fixing system ("Urban Arrow Baby Car Seat
      Adapter"). It comes with an integrated suspension system (part of the
      adapter). 
      \item Melia baby shell. The baby seat is meant for babies from 2 to 9
      months, specifically designed for cargo bikes.
  \end{itemize}
\end{itemize}

\begin{figure}
  \centering
  \subcaptionbox{Paver bricks}{\includegraphics[width=0.45\textwidth]{fig/Klinkers.PNG}}
  \subcaptionbox{Sidewalk slabs}{\includegraphics[width=0.45\textwidth]{fig/Aula_YOYO.PNG}}
  \subcaptionbox{Sidewalk pavers}{\includegraphics[width=0.45\textwidth]{fig/Stoeptegels_YOYO.PNG}}
  \subcaptionbox{Cobblestones}{\includegraphics[width=0.45\textwidth]{fig/Cobblestone_YOYO.PNG}}
  \caption{Different road surfaces chosen for tests with strollers.}
  \label{fig:surfaces_stroller}
\end{figure}

\subsubsection{Postures}
All tested systems provided full support of back and head and allowed usage in
lying or at least reclined postures. Nine months old babies would be able to
sit erect but will often rest their heads or may even sleep. Although sitting
upright is the best posture for children who can sit upright, a more recumbent
posture was tested because this allowed measurement of vibration at the head
(which is difficult with upright posture because the head does not always touch
the back of the seat if in an upright position). We tested all systems with
horizontal or reclined postures. The inclination angle with respect to the
ground is listed in Table~\ref{tab:baby-posture}, for each condition tested.
%
\begin{table}
  \centering
  \caption{Inclination angles of the sensors ``Seat Head'' and ``Seat Buttock'',
  per each tested configuration. We report the angles of the sensor at the
  interface between the seat and the dummies' head and buttock, taken positive
  counterclockwise. In this case, 0~\si{\degree} is defined by the ground plane.
  In other words, 0~\si{\degree} means horizontal, -90~\si{\degree} means
  vertical.}
\begin{tabular}{lllrrr}
\toprule
 &  &  & Count & \multicolumn{2}{c}{Inclination angle [deg]}  \\
Vehicle Type & Model & Dummy & Baby seat & Seat Head & Seat Buttock\\
\midrule
\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 months & Maxi-Cosi X Joolz & -41 & -2 \\
 &  & 3 months & Maxi-Cosi X Joolz & -41 & -2 \\
 &  & 3 months & Melia & 64 & -2 \\
\cline{2-6}
 & \multirow[t]{3}{*}{Tricycle} & 0 months & Maxi-Cosi X Joolz & -41 & -2 \\
 &  & 3 months & Maxi-Cosi X Joolz & -41 & -2 \\
 &  & 3 months & Melia & 64 & -2 \\
\cline{1-6} \cline{2-6}
\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street+ & 0 months & Baby cot & 0 & 0\\
\cline{2-6}
 & Maxi-Cosi Street+ & 9 months & Baby seat & 40 & -10 \\
\cline{2-6}
 & Babyzen Yoyo 0+ & 0 months & Baby cot & -12 & -12 \\
\cline{2-6}
 & Bugaboo Fox 5 & 0 months & Baby cot & 0 & 0 \\
\cline{2-6}
 & Bugaboo Fox 5 & 9 months & Baby seat & 49 & -24\\
\bottomrule
\end{tabular}
  \label{tab:baby-posture}
\end{table}

\subsection{Data Analysis Methodology}
% 
We analysed the raw data with a custom data processing pipeline hosted at
\href{https://github.com/mechmotum/baby-vibration}{github.com/mechmotum/baby-vibration}
implemented in Python 3.13.1 using the following software packages:
DynamicistToolKit 0.6.1, Matplotlib 3.9.3, NumPy 2.2.0, Pandas 2.2.3, pyyaml
6.0.2, SciPy 1.14.1, Seaborn 0.13.2, and statsmodels 0.14.4. The pipeline
generates a website at
\href{https://mechmotum.github.io/baby-vibration}{mechmotum.github.io/baby-vibration}
with an exhaustive collection of figures for examining the quality of the data
and general results for all trials. Selected tables and figures from the website
are presented and discussed in the results section of this paper.

\subsubsection{Data Preparation}
%
The raw data consists of a single CSV file per session per IMU sensor along with
meta-data for the sessions and vehicles. The CSV file contains the time series
data from IMU: linear acceleration along and angular speed about each of the
body-fixed orthogonal axes of the sensor alongside Epoch Unix timestamps. We
segment the sessions into trials representing a motion state of the vehicle:
either static level ground or being propelled over one of the surfaces of
interest at a constant speed, as depicted in Figure~\ref{fig:session} as an
example of the segmentation. We process the data per session as follows:
%
\begin{enumerate}
  \item Extract segments representing a single trial from each session time
    history, based on the manually labelled segment ``start'' and ``end'' times.
  \item Rotate the accelerometer data for each sensor from body-fixed sensor
    coordinates to body-fixed vehicle coordinates and remove the constant
    standard gravity component. This is achieved by rotating the coordinate axes
    about the sensor's body-fixed axis which has was manually aligned with the
    vehicle's pitch axis. We subtract the mean measured acceleration due to
    gravity giving linear acceleration of each sensor projected into the
    vehicle's SAE axes, named: longitudinal $x$, lateral $y$, and vertical $z$.
  \item Extract each motion trial segment and select the vehicle vertical
    component of the seat pan accelerometer.
  \item Calculate the vehicle travel speed from the angular rate of the rear
    wheel and the vehicle's wheel radius.
\end{enumerate}
%
This results in seat pan acceleration time histories of 78 trials of duration
in the range of \SIrange{5}{80}{\second} (mean: 36~\si{\second}), see
Table~\ref{tab:num-trials} for a breakdown of the trials.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session015.png}
  \caption{Vehicle speed versus time for an entire session (015) showing the
  segmented trials in the shaded grey areas. Gold horizontal lines depict the
  mean speed bounded by the standard deviation of the speed.}
  \label{fig:session}
\end{figure}
%
\begin{table}
  \centering
  \caption{Number of trials performed on each road surface and speed along with
  the mean duration and its standard deviation.}
\begin{tabular}{lllrrr}
\toprule
 &  &  & Count & \multicolumn{2}{c}{Duration [s]}  \\
Vehicle Type & Road Surface & Target Speed [km/h] &  & Mean & STD  \\
\midrule
\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Tarmac} & 12 & 6 & 58.33 & 8.56 \\
 &  & 20 & 3 & 50.42 & 7.04 \\
 &  & 25 & 3 & 44.08 & 1.60 \\
\cline{2-6}
 & \multirow[t]{3}{*}{Paver Bricks} & 12 & 6 & 54.46 & 5.95 \\
 &  & 20 & 6 & 38.68 & 5.08 \\
 &  & 25 & 3 & 33.43 & 4.25 \\
\cline{1-6} \cline{2-6}
\multirow[t]{5}{*}{Stroller} & Tarmac & 5 & 10 & 27.87 & 10.07 \\
\cline{2-6}
 & Cobblestones & 5 & 13 & 27.90 & 24.74 \\
\cline{2-6}
 & Paver Bricks & 5 & 6 & 51.47 & 21.62 \\
\cline{2-6}
 & Sidewalk Slabs & 5 & 16 & 19.59 & 6.59 \\
\cline{2-6}
 & Sidewalk Pavers & 5 & 6 & 48.94 & 19.71 \\
\cline{1-6} \cline{2-6}
 & & \textbf{Count Sum} & \textbf{78} & & \\
\bottomrule
\end{tabular}
  \label{tab:num-trials}
\end{table}

\subsubsection{Trial Analyses}
%
Figure~\ref{fig:vert-acc-example} shows an example time history of the vertical
acceleration of the seat pan during a single trial. We downsampled the time
history from the set sampling frequency of 910.22~\si{\hertz} to \(N\) samples
at a constant sample rate of 400~\si{\hertz} with linear interpolation.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session001-t2-aula-stroller-maxicosi-cot-0-SeatBotacc_ver.png}
  \caption{Seat pan vertical acceleration from session 1: Maxi-Cosi Stroller over
  the Sidewalk Slabs. Black horizontal lines indicate the \(\pm\)RMS
  boundary.}
  \label{fig:vert-acc-example}
\end{figure}

We calculated the root mean square of the downsampled vertical component of
acceleration at the seat pan for each trial using Equation~\ref{eq:rms-acc}.
This quantity gives an indicator of the average vertical acceleration
experienced at the baby's buttocks for the duration of the trial and can be seen
in Figure~\ref{fig:vert-acc-example}. RMS acceleration is the primary metric
recommended by ISO-2631-1 for evaluation of health and comfort in whole body
vibration.
%
\begin{align}
  \textrm{RMS}_{a_z} = \sqrt{\frac{1}{N}\sum_{n=1}^{N} a_z^2(t_n)}
  \label{eq:rms-acc}
\end{align}

We also calculated the frequency spectrum of the vertical acceleration time
history of each trial using the Fast Fourier Transform (FFT).
Figure~\ref{fig:freq-spectrum} gives an example of a frequency spectrum. In this
case, the primary peak frequency is identified to be 6.5~\si{\hertz} and the
frequency content is mostly contained below about 80~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session004-t0-pave-stroller-maxicosi-cot-0-SeatBotacc_ver.png}
  \caption{Seat pan vertical acceleration frequency spectrum from session 4:
  Maxi-Cosi Stroller over cobblestones. The gray curve shows the result of the
  FFT and the blue line is a smoothed version (Butterworth low pass
  forward/reverse). The orange vertical line indicates the frequency at the
  maximum amplitude of the smoothed curve. The green vertical line indicates the
  bandwidth threshold for 80\% of the area under the filtered curve.}
  \label{fig:freq-spectrum}
\end{figure}

\section{Results}
%
\subsection{Effect of Speed}
%
We tested the two cargo bicycles at three different target speeds: 12, 20, and
25~\si{\kilo\meter\per\hour}. Figure~\ref{fig:compare-bicycle-speed} shows the
variation in vertical RMS acceleration across the tested speeds. Accelerations
experienced when riding over the paver bricks are always larger than riding over
tarmac at the same speed, with the paver bricks having about a 5\(\times\)
increase in magnitude over tarmac. Over paver bricks, the RMS acceleration
increases by 1.7\(\times\) when increasing the speed from
\SIrange{12}{25}{\kilo\meter\per\hour}. The effect of speed while over tarmac is
less drastic but also increases over the speed range.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-speed-compare.png}
  \caption{Seat pan vertical acceleration RMS versus speed for all cargo bicycle
  trials. Shaded regions represent the 95\% confidence intervals from a simple
  linear regression.}
  \label{fig:compare-bicycle-speed}
\end{figure}

\subsection{Effect of Baby Size}
%
We tested dummy babies representing ages 0~months (3.5~\si{\kilo\gram}),
3~months (5.9~\si{\kilo\gram}), and 9~months (8.9~\si{\kilo\gram}).
Figure~\ref{fig:compare-baby-mass} shows the vertical RMS acceleration for each
trial for the strollers and the bicycles, comparing the baby size. There are
larger accelerations experienced in the bicycle versus the stroller, mostly
attributed to the different testing speeds. When comparing the vertical RMS
acceleration values within each vehicle type there are no obvious differences
due to baby size, i.e. each baby size experiences a similar range of
acceleration magnitudes.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
  \caption{Seat pan vertical RMS acceleration grouped by baby age (and thus size
  \& mass) for all trials with colour indicating the mean speed of the
  trial.}
  \label{fig:compare-baby-mass}
\end{figure}

\subsection{Effect of Road Surface}
%
Figure~\ref{fig:compare-road-surface} shows vertical RMS acceleration from
trials grouped into the various road surfaces we tested. All vehicles were
tested on tarmac and paver bricks but only strollers were tested on cobblestones
and sidewalks. It is notable that tarmac almost always has lower RMS
acceleration regardless of speed and vehicle type. The sidewalk slabs can have
slightly higher acceleration than cobblestones for the strollers. Paver bricks
and sidewalk pavers have a similar range of RMS acceleration for the same
5~\si{\kilo\meter\per\hour} walking speeds. Paver bricks cause relatively large
accelerations at high travel speeds in the cargo bicycles.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-road-surface-compare.png}
  \caption{Seat pan vertical RMS acceleration grouped by road surface with
  colour indicating the mean speed of the trial. The lightest colour dots are
  strollers and the rest are cargo bicycles.}
  \label{fig:compare-road-surface}
\end{figure}

\subsection{Effect of Vehicle Model}
%
We tested three models of strollers over five different road surfaces.
Figure~\ref{fig:stroller-type-compare} compares the vertical RMS accelerations
for each road surface for each of the three strollers. The Maxi-Cosi Street Plus
and Stokke BABYZEN YOYO 0+ strollers have similar mean values across trials. The
Bugaboo has a slightly lower mean, but much larger variation in the RMS values.
There may be no significant difference in the acceleration experienced in each
stroller model. All road surfaces compared to tarmac cause at least double the
RMS acceleration.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-stroller-type-compare.png}
  \caption{Mean seat pan vertical RMS acceleration per road surface for each
  stroller. Vertical lines indicate the standard deviation for categories that
  have more than one trial.} 
  \label{fig:stroller-type-compare}
\end{figure}

Figure~\ref{fig:bicycle-type-compare} compares the two cargo bicycle models we
tested. Each cargo bicycle was fitted with the same set of two baby seats (Melia
baby shell and Maxi-Cosi Pebble Pro baby seat). The two-wheel cargo bicycle
seems to deliver lower acceleration to the seat pan, but the variation in the
data is large, indicating there may be no significant difference between the two
vehicles. Both vehicles show increasing vertical RMS acceleration with speed.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-type-compare.png}
  \caption{Seat pan vertical RMS acceleration versus speed grouped by road
  surface and cargo bicycle model. Horizontal lines indicate a linear
  regression, vertical lines are the standard deviation at those speeds, and
  shaded regions show the 95\% confidence intervals for the regression.}
  \label{fig:bicycle-type-compare}
\end{figure}

\subsection{Dominant Frequency and Bandwidth}
%
Figure~\ref{fig:peak-freq-dist} shows the dominant frequency compared among road
surface types for each of the target speeds. Peak frequencies range from
\SIrange{5}{11}{\hertz} across all trials. For strollers
(5~\si{\kilo\meter\per\hour}, the median frequency increases from sidewalk
slabs, to cobblestones, to sidewalk pavers, to tarmac, to paver bricks. With the
exception of paver bricks being larger than tarmac this increase corresponds to
an increase in the size of the geometric surface features of the road.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-peak-freq-dist.png}
  \caption{Peak frequency distributions comparisons among road surfaces for each
  target speed group. The boxes bound the quartiles and indicate the median. The
  whiskers indicate the 95th perentile and circles are any outliers.}
  \label{fig:peak-freq-dist}
\end{figure}

Figure~\ref{fig:thresh-freq-dist} gives a general indication of bandwidth
distributions for each of the target speed groups. Most frequency content is
below 100~\si{\hertz} for the all trials. The median threshold frequency across
all trials is 70~\si{\hertz} which gives an idea of the bandwidth for the
vibrations of interest.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-thresh-freq-dist.png}
  \caption{Threshold frequency  (based on 80\% of the area under the filtered
  frequency spectrum) for each target speed group.}
  \label{fig:thresh-freq-dist}
\end{figure}

\subsection{Overall Comparison}
We tabulate the seat pan vertical RMS acceleration, trial duration, peak
frequency, and threshold frequency for all 52 combinations of vehicle setup,
road surface, and target speed in Table~\ref{tab:results}.
Figure~\ref{fig:compare-all} shows the vertical RMS acceleration of all trials
broken down by vehicle setup (vehicle, seat, baby age), road surface, trial
duration, and travel speed. Some additional insights can be gathered from this
figure, that are not seen in the prior figures.
%
\begin{itemize}
    \item The baby in stroller travelling at 5~\si{\kilo\meter\per\hour} over
    cobblestones and sidewalks slabs cracks can experience accelerations of
    similar magnitude to a baby in a cargo bicycle travelling at
    12~\si{\kilo\meter\per\hour} over paver bricks.
    \item A 3 month old baby in a baby shell (Melia) travelling over brick
    pavers at high speeds has lower RMS acceleration than the same baby in a car
    seat (Maxi-Cosi Pebble Pro) in the Urban Arrow and it may also be true for
    the Keiler tricycle. Switching to the baby shell in the Urban Arrow has a
    similar effect to reducing speed by 10~\si{\kilo\meter\per\hour}.
\end{itemize}

\begin{table}
  \centering
  \caption{Computed metrics for all 52 scenarios measured.}
  \label{tab:results}
  \footnotesize
\begin{tabular}{lllcccccc}
\toprule
        &            &              &        &       & Mean         &          & Mean      & Mean      \\
Vehicle & Seat, Baby & Road Surface & Target & Trial & RMS          & Mean     & Peak      & Threshold \\
        &            &              & Speed  & Count & Acceleration & Duration & Frequency & Frequency \\
        &            &              & [km/h] &       &  [m/s\(^2\)]     & [s]      & [Hz]      & [Hz]      \\
\midrule
\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 2 & 4.4 & 39.8 & 6.6 & 22.6 \\
\cline{3-9}
 &  & Paver Bricks & 5 & 1 & 2.6 & 70.5 & 10.7 & 25.1 \\
\cline{3-9}
 &  & Sidewalk Pavers & 5 & 1 & 2.9 & 51.6 & 8.2 & 119.5 \\
\cline{3-9}
 &  & Sidewalk Slabs & 5 & 3 & 4.8 & 20.0 & 5.8 & 41.8 \\
\cline{3-9}
 &  & Tarmac & 5 & 2 & 0.7 & 24.9 & 9.9 & 61.5 \\
\cline{2-9} \cline{3-9}
 & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 2.5 & 42.0 & 6.8 & 46.5 \\
\cline{3-9}
 &  & Paver Bricks & 5 & 1 & 2.3 & 66.9 & 9.7 & 57.5 \\
\cline{3-9}
 &  & Sidewalk Pavers & 5 & 1 & 1.7 & 71.3 & 7.6 & 47.4 \\
\cline{3-9}
 &  & Sidewalk Slabs & 5 & 3 & 2.4 & 23.9 & 6.0 & 47.1 \\
\cline{3-9}
 &  & Tarmac & 5 & 2 & 0.6 & 33.2 & 8.4 & 68.9 \\
\cline{1-9} \cline{2-9} \cline{3-9}
\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 1 & 4.6 & 81.7 & 6.6 & 82.3 \\
\cline{3-9}
 &  & Paver Bricks & 5 & 1 & 3.2 & 61.5 & 10.6 & 75.6 \\
\cline{3-9}
 &  & Sidewalk Pavers & 5 & 1 & 3.0 & 51.0 & 7.8 & 79.7 \\
\cline{3-9}
 &  & Sidewalk Slabs & 5 & 5 & 4.5 & 12.3 & 5.7 & 80.3 \\
\cline{3-9}
 &  & Tarmac & 5 & 2 & 0.9 & 29.4 & 10.5 & 56.5 \\
\cline{2-9} \cline{3-9}
 & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 5 & 4.2 & 12.6 & 7.8 & 65.8 \\
\cline{3-9}
 &  & Paver Bricks & 5 & 2 & 3.0 & 26.0 & 9.8 & 79.6 \\
\cline{3-9}
 &  & Sidewalk Pavers & 5 & 1 & 2.6 & 54.8 & 6.8 & 67.1 \\
\cline{3-9}
 &  & Sidewalk Slabs & 5 & 3 & 3.2 & 23.0 & 6.9 & 70.4 \\
\cline{3-9}
 &  & Tarmac & 5 & 2 & 1.0 & 33.6 & 10.2 & 70.7 \\
\cline{1-9} \cline{2-9} \cline{3-9}
\multirow[t]{12}{*}{trike} & \multirow[t]{4}{*}{maxicosi, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 7.2 & 47.6 & 8.0 & 44.9 \\
 &  &  & 20 & 1 & 11.1 & 35.3 & 6.4 & 101.6 \\
\cline{3-9}
 &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.9 & 73.7 & 8.1 & 23.8 \\
 &  &  & 20 & 1 & 2.7 & 58.4 & 6.5 & 18.8 \\
\cline{2-9} \cline{3-9}
 & \multirow[t]{4}{*}{maxicosi, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 6.8 & 57.8 & 7.9 & 72.3 \\
 &  &  & 20 & 1 & 9.8 & 42.8 & 7.1 & 87.2 \\
\cline{3-9}
 &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.5 & 55.6 & 7.6 & 31.7 \\
 &  &  & 20 & 1 & 2.1 & 47.6 & 6.2 & 19.2 \\
\cline{2-9} \cline{3-9}
 & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 5.8 & 52.6 & 8.9 & 100.5 \\
 &  &  & 20 & 1 & 10.2 & 46.0 & 6.9 & 120.9 \\
\cline{3-9}
 &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.2 & 50.8 & 7.9 & 91.1 \\
 &  &  & 20 & 1 & 1.6 & 45.2 & 8.1 & 72.8 \\
\cline{1-9} \cline{2-9} \cline{3-9}
\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 6.6 & 62.3 & 7.6 & 110.4 \\
 &  &  & 20 & 1 & 9.2 & 39.1 & 8.0 & 71.6 \\
 &  &  & 25 & 1 & 11.4 & 38.3 & 7.1 & 117.5 \\
\cline{3-9}
 &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.4 & 58.1 & 8.7 & 28.9 \\
 &  &  & 25 & 1 & 2.1 & 43.1 & 10.0 & 28.5 \\
\cline{2-9} \cline{3-9}
 & \multirow[t]{5}{*}{maxicosi, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 5.2 & 58.2 & 7.9 & 85.7 \\
 &  &  & 20 & 1 & 10.6 & 32.1 & 4.9 & 102.8 \\
 &  &  & 25 & 1 & 10.5 & 30.3 & 6.2 & 99.3 \\
\cline{3-9}
 &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.1 & 50.7 & 8.8 & 37.8 \\
 &  &  & 25 & 1 & 1.6 & 43.2 & 9.6 & 31.8 \\
\cline{2-9} \cline{3-9}
 & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 4.6 & 48.3 & 6.8 & 36.6 \\
 &  &  & 20 & 1 & 6.9 & 36.8 & 7.8 & 51.1 \\
 &  &  & 25 & 1 & 7.5 & 31.7 & 9.2 & 60.6 \\
\cline{3-9}
 &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.0 & 61.2 & 8.5 & 66.5 \\
 &  &  & 25 & 1 & 1.4 & 45.9 & 9.7 & 41.7 \\
\cline{1-9} \cline{2-9} \cline{3-9}
\multirow[t]{5}{*}{yoyo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 18.1 & 6.6 & 91.1 \\
\cline{3-9}
 &  & Paver Bricks & 5 & 1 & 2.8 & 57.8 & 9.7 & 123.9 \\
\cline{3-9}
 &  & Sidewalk Pavers & 5 & 2 & 2.6 & 32.5 & 6.5 & 98.9 \\
\cline{3-9}
 &  & Sidewalk Slabs & 5 & 2 & 4.0 & 25.7 & 5.1 & 103.8 \\
\cline{3-9}
 &  & Tarmac & 5 & 2 & 0.8 & 18.1 & 7.4 & 156.6 \\
\cline{1-9} \cline{2-9} \cline{3-9}
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/SeatBotacc_ver-compare-all.png}
  \caption{Scatter plot of the vertical RMS acceleration of all trials broken
  down by vehicle setup, trial duration, road surface, and plotted versus
  speed.}
  \label{fig:compare-all}
\end{figure}

\section{Conclusion}
%
We have presented a comprehensive set of acceleration measurements from
experiments that simulate the vibrations experienced by babies in the 0-9 month
age range during transportation via strollers and cargo bicycles. We compare the
average magnitude of vertical acceleration at the seat pan across a variety of
road surfaces and seats while moving at typical vehicle travel speeds. In this
preliminary analysis, we report on the variation among the various independent
variables, finding that average acceleration can be relatively large for some
scenarios. We only report the characterization of the accelerations experienced
by the baby and do not weigh in on whether these can cause discomfort or have
negative health consequences. There is a large gap in the literature connecting
acceleration magnitude to discomfort and/or health consequences.

We show that average acceleration can range from
\SIrange{0.5}{11.4}{\meter\per\second\squared} across all tested scenarios.
Strollers experience \SIrange{0.5}{5.3}{\meter\per\second\squared} average
acceleration for a mean walking speed of 5.2~\si{\kilo\meter\per\hour}. Cargo
bicycles experience \SIrange{1.0}{11.4}{\meter\per\second\squared} over a speed
range of \SIrange{12}{25}{\kilo\meter\per\hour}.

Travelling over a tarmac surface offers the least vibration to all vehicle types
at any speed with a maximum average acceleration of
2.7~\si{\meter\per\second\squared}. For strollers, travelling over surfaces
rougher than tarmac at normal walking speed can cause from 1.6\(\times\) to
6.6\(\times\) the accelerations experienced on tarmac with average accelerations
reaching 5.3~\si{\meter\per\second\squared}. Cobblestones and the large gaps of
the sidewalk slabs cause the largest magnitude vibrations to the baby in the
strollers. For cargo bicycles, travelling over paver bricks at the same speeds
can quadruple the magnitude of the average acceleration the baby experiences.
Travelling at the maximum allowed speed of an electric cargo bike (25
\si{\kilo\meter\per\hour}) over paver bricks causes the baby to experience
average accelerations exceeding 8~\si{\meter\per\second\squared}. The effect of
speed on vibration is higher for paver bricks than tarmac.

The size of the baby (mass and shape) has no obvious effect on the average
accelerations experienced at the seat pan body-seat interface. These vibrations
are transmitted to the baby's body and the physical properties (mass, stiffness,
damping) of the baby's body determine whether this excitation is amplified or
not and to which body segment is more affected. Tests with more realistic
dummies or real babies is necessary to know how the baby itself moves when
excited by this level of vibration. This information is not readily available in
the literature and may be hard to perform due to ethical limitations and absence
of realistic dummies.

When comparing stroller and cargo bicycle vehicle setups (vehicle, seat, baby
age) among each other, the preliminary results show no obvious differences in
the acceleration experienced by the baby other than the baby shell being better
than a baby car seat for the 3 month old baby in the cargo bike at the maximum
speeds. This may be attributed to the suspended mounting location of the baby
seat in the cargo bay versus the baby shell being mounted to the existing bench
in the cargo bay. Statistical analysis may reveal more nuance differences among
the vehicle setups.

We also investigated the dominant frequency and bandwidth of vibrations across
the various scenarios. Vibrations at frequencies between
\SIrange{4.9}{10.7}{\hertz} have the largest magnitude contribution to the
vibrations but there is frequency content of magnitudes of interest in a
bandwidth of up to 100~\si{\hertz}.

We measured four other sensors on the vehicles, all with six accelerometer and
gyroscope time histories, for a total of 30 time histories of possible interest.
This paper provides a look into the experiments via three metrics: vertical RMS
acceleration, peak frequency, and bandwidth of effectively one of the 30 time
histories. There are a variety of other metrics that can provide insight, for
example vibration dosage value and crest factor that characterize peak
accelerations or ISO 2631-1 weighted linear and rotational accelerations that
have more connection to experienced comfort. Future work will investigate these
more closely as well as shock effects and apply standard statistical models to
the data to make more definitive conclusions in the scenario comparisons.

\bibliographystyle{plain}
\bibliography{reference}

\end{document}

### 2025-01-25 src/website.py
Added comfort plots for bike and stroller, tuned figures.

@@ -1,9 +1,11 @@
+# builtin
 import datetime
 import os
 import pickle
 import pprint
 import subprocess
 
+# external dependencies
 from statsmodels.stats.multicomp import pairwise_tukeyhsd
 import matplotlib.pyplot as plt
 import numpy as np
@@ -12,6 +14,7 @@ import seaborn as sns
 import statsmodels.api as sma
 import statsmodels.formula.api as smf
 
+# local
 from functions import print_header, eval_health
 from html_templates import INDEX, H2, H4, P, IMG
 from paths import PATH_TO_REPO, PATH_TO_DATA_DIR, PATH_TO_FIG_DIR
@@ -19,11 +22,20 @@ from run import SIGNAL
 
 SIGNAL_RMS = SIGNAL + '_rms'
 SIGNAL_RMS_ISO = SIGNAL + '_rms_iso'
+SIGNAL_RMS_MAG_ISO = SIGNAL.split('_')[0] + '_rms_mag_iso'
 KPH2MPS, MPS2KPH = 1.0/3.6, 3.6
 MM2INCH = 1.0/25.4
 MAXWIDTH = 160.0  # mm (max width suitable for an A4 with 25 mm margins)
+COMFORT_BOUNDS = (
+    (0.0, 0.315, 'not uncomfortable'),
+    (0.315, 0.63, 'a little uncomfortable'),
+    (0.5, 1.0, 'fairly uncomfortable'),
+    (0.8, 1.6, 'uncomfortable'),
+    (1.25, 2.5, 'very uncomfortable'),
+    (2.0, 99.0, 'extremely uncomfortable'),
+)
 
-sns.set_theme(style='white')
+sns.set_theme(style='whitegrid')
 
 try:
     githash = subprocess.check_output([
@@ -153,85 +165,58 @@ for surf in stroller_df['Road Surface'].unique():
 
 boxp_html = []
 
+#########################################################
+# Figure: Health ISO Weighted RMS All Trials Scatter Plot
+#########################################################
 boxp_html.append(H2.format('All Trials ISO Weighted RMS Compared (Health)'))
 msg = f"""Scatter plot of the ISO 2631-1 Weighted RMS {SIGNAL} of all trials
 broken down by vehicle setup (brand, seat configuration, baby age), trial
-duration, road surface, and plotted versus speed. Red horizontal line indicate
-"above the health caution zone" from the ISO 2631-1 standard for different
[…]

### 2025-01-25 src/website.py
Added comfort labels outside of plot.

@@ -302,10 +302,16 @@ p = sns.stripplot(
     hue_order=sorted(stroller_df["Road Surface"].unique()),
     order=sorted(stroller_df["Vehicle, Seat, Baby Age"].unique()),
 )
-for low, high, note in COMFORT_BOUNDS:
-    p.axes.axhline(low, color='black')
-    p.axes.text(1.3, low + 0.05, note, fontsize=8,
-                bbox=dict(boxstyle='round,pad=0.0', color='white'))
+for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
+    p.axes.axhline(low, color='grey')
+    p.axes.annotate('→ ' + note,
+                    xy=(7.5, low),
+                    xytext=(9.6 - i*0.3, low + 0.02),
+                    color='black',
+                    fontsize=8,
+                    rotation=90,
+                    arrowprops=dict(facecolor='grey', width=2.0,
+                                    headwidth=0.0, frac=0.0))
 p.set_xticklabels(p.get_xticklabels(), rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
 p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
@@ -330,10 +336,16 @@ p = sns.scatterplot(
     hue='Road Surface',
     style="Target Speed [km/h]",
 )
-for low, high, note in COMFORT_BOUNDS:
-    p.axes.axhline(low, color='black')
-    p.axes.text(1.4, low + 0.1, note, fontsize=8,
-                bbox=dict(boxstyle='round,pad=0.0', color='white'))
+for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
+    p.axes.axhline(low, color='grey')
+    p.axes.annotate('→ ' + note,
+                    xy=(5.25, low),
+                    xytext=(7.2 - i*0.3, low + 0.02),
+                    color='black',
+                    fontsize=8,
+                    rotation=90,
+                    arrowprops=dict(facecolor='grey', width=2.0,
+                                    headwidth=0.0, frac=0.0))
 p.set_xticklabels(p.get_xticklabels(), rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
 p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')

### 2025-01-25 src/website.py
Changed comfort lines to tab:brown color.

@@ -303,14 +303,14 @@ p = sns.stripplot(
     order=sorted(stroller_df["Vehicle, Seat, Baby Age"].unique()),
 )
 for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
-    p.axes.axhline(low, color='grey')
+    p.axes.axhline(low, color='tab:brown', alpha=0.6)
     p.axes.annotate('→ ' + note,
                     xy=(7.5, low),
                     xytext=(9.6 - i*0.3, low + 0.02),
-                    color='black',
+                    color='tab:brown',
                     fontsize=8,
                     rotation=90,
-                    arrowprops=dict(facecolor='grey', width=2.0,
+                    arrowprops=dict(facecolor='tab:brown', width=2.0,
                                     headwidth=0.0, frac=0.0))
 p.set_xticklabels(p.get_xticklabels(), rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
@@ -337,14 +337,14 @@ p = sns.scatterplot(
     style="Target Speed [km/h]",
 )
 for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
-    p.axes.axhline(low, color='grey')
+    p.axes.axhline(low, color='tab:brown', alpha=0.6)
     p.axes.annotate('→ ' + note,
                     xy=(5.25, low),
                     xytext=(7.2 - i*0.3, low + 0.02),
-                    color='black',
+                    color='tab:brown',
                     fontsize=8,
                     rotation=90,
-                    arrowprops=dict(facecolor='grey', width=2.0,
+                    arrowprops=dict(facecolor='tab:brown', width=2.0,
                                     headwidth=0.0, frac=0.0))
 p.set_xticklabels(p.get_xticklabels(), rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))

### 2025-01-25 src/website.py
Changed name of trike vehicle to keiler to be consistent.

@@ -125,7 +125,7 @@ print(trial_count_df.to_latex(float_format="%0.1f"))
 f = (f"{SIGNAL_RMS_ISO} ~ "
      "Q('Mean Speed [m/s]') * "
      "C(Q('Road Surface'), Treatment('Tarmac')) + "
-     "C(Q('Vehicle, Seat, Baby Age'), Treatment('trike, maxicosi, 3 mo'))")
+     "C(Q('Vehicle, Seat, Baby Age'), Treatment('keiler, maxicosi, 3 mo'))")
 mod = smf.ols(formula=f, data=bicycle_df)
 bicycle_res = mod.fit()
 print_header("Bicycle OLS Results (Vertical ISO Weigthed RMS)")
@@ -312,7 +312,8 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
                     rotation=90,
                     arrowprops=dict(facecolor='tab:brown', width=2.0,
                                     headwidth=0.0, frac=0.0))
-p.set_xticklabels(p.get_xticklabels(), rotation=90)
+p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
+                   p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
 p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, 1.1*MAXWIDTH*MM2INCH))
@@ -346,10 +347,11 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
                     rotation=90,
                     arrowprops=dict(facecolor='tab:brown', width=2.0,
                                     headwidth=0.0, frac=0.0))
-p.set_xticklabels(p.get_xticklabels(), rotation=90)
+p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
+                   p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
 p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
-p.figure.set_size_inches((MAXWIDTH*MM2INCH, 1.2*MAXWIDTH*MM2INCH))
+p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*MM2INCH))
[…]

### 2025-01-25 src/website.py
Added crest factor plot and tuned remaining plots.

@@ -217,7 +217,8 @@ for val, note in zip((10.0, 20.0, 60.0, 240.0),
                      ('10 min', '20 min', '1 hr', '4 hr')):
     p.axes.axhline(eval_health(val)[1], color='grey')
     p.axes.text(1.15, eval_health(val)[1] + 0.05, note)
-p.set_xticklabels(p.get_xticklabels(), rotation=90)
+p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
+                   p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
 p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*MM2INCH))
@@ -248,7 +249,8 @@ for val, note in zip((10.0, 20.0, 60.0, 240.0),
     p.axes.axhline(eval_health(val)[1], color='grey')
     p.axes.text(1.1, eval_health(val)[1] + 0.15, note,
                 bbox=dict(boxstyle='round,pad=0.02', color='white'))
-p.set_xticklabels(p.get_xticklabels(), rotation=90)
+p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
+                   p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
 p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*MM2INCH))
@@ -312,6 +314,8 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
                     rotation=90,
                     arrowprops=dict(facecolor='tab:brown', width=2.0,
                                     headwidth=0.0, frac=0.0))
+p.axes.text(8.0, 3.5, 'ISO 2631-1 Adult\nPublic Transit Feelings',
+            color='tab:brown')
 p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
                    p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
@@ -331,10 +335,11 @@ boxp_html.append(
 msg = """"""
 boxp_html.append(P.format(msg))
[…]

### 2025-01-25 src/website.py
Plot baby mass on single strip plot, not broken out by vehicle. Solves the legend placement.

@@ -626,19 +626,16 @@ boxp_html.append(IMG.format('', fname) + '\n</br>')
 boxp_html.append(H2.format('Baby Mass Comparison'))
 msg = 'Compare accelerations across baby mass (age) and speed.'
 boxp_html.append(P.format(msg))
-p = sns.catplot(
+p = sns.stripplot(
     data=stats_df,
     x="Baby Age [mo]",
     y=SIGNAL_RMS_ISO,
     hue='Mean Speed [km/h]',
-    col='Vehicle Type',
-    sharex=False,
 )
-p.set_ylabels(r'Vertical Acceleration RMS [m/s$^2$]')
+p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
 fname = '{}-baby-mass-compare.png'.format(SIGNAL)
-# TODO : The legend overlaps the axes if I try to make it a fixed width.
-#p.figure.set_size_inches((MAXWIDTH*MM2INCH, 80*MM2INCH))
-#p.figure.set_layout_engine('constrained')
+p.figure.set_size_inches((MAXWIDTH*MM2INCH, 100*MM2INCH))
+p.figure.set_layout_engine('constrained')
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
 plt.clf()
 boxp_html.append(IMG.format('', fname) + '\n</br>')

### 2025-01-26 src/paths.py
Output latex tables to file instead of to STDOUT.

@@ -10,6 +10,7 @@ PATH_TO_REPO = os.path.realpath(
     os.path.join(os.path.dirname(os.path.realpath(__file__)), '..'))
 PATH_TO_DATA_DIR = os.path.join(PATH_TO_REPO, 'data')
 PATH_TO_FIG_DIR = os.path.join(PATH_TO_REPO, 'fig')
+PATH_TO_TABLE_DIR = os.path.join(PATH_TO_REPO, 'table')
 PATH_TO_BOUNDS_DIR = os.path.join(PATH_TO_FIG_DIR, 'bounds')
 PATH_TO_TIME_HIST_DIR = os.path.join(PATH_TO_FIG_DIR, 'time_hist')
 PATH_TO_SPECT_DIR = os.path.join(PATH_TO_FIG_DIR, 'spectrums')
@@ -19,6 +20,7 @@ PATH_TO_SYNC_DIR = os.path.join(PATH_TO_FIG_DIR, 'sync')
 paths_to_create = [
     PATH_TO_DATA_DIR,
     PATH_TO_FIG_DIR,
+    PATH_TO_TABLE_DIR,
     PATH_TO_BOUNDS_DIR,
     PATH_TO_TIME_HIST_DIR,
     PATH_TO_SPECT_DIR,

### 2025-01-26 src/website.py

@@ -17,7 +17,8 @@ import statsmodels.formula.api as smf
 # local
 from functions import print_header, eval_health
 from html_templates import INDEX, H2, H4, P, IMG
-from paths import PATH_TO_REPO, PATH_TO_DATA_DIR, PATH_TO_FIG_DIR
+from paths import (PATH_TO_REPO, PATH_TO_DATA_DIR, PATH_TO_FIG_DIR,
+                   PATH_TO_TABLE_DIR)
 from run import SIGNAL
 
 SIGNAL_RMS = SIGNAL + '_rms'
@@ -110,7 +111,8 @@ summary_df['Duration [s]'] = \
 summary_df['Crest Factor'] = stats_df.groupby(groups)['Crest Factor'].mean()
 print_header("Means Per Scenario")
 print(summary_df)
-print(summary_df.to_latex(float_format="%0.1f"))
+with open(os.path.join(PATH_TO_TABLE_DIR, 'summary-data-frame.tex'), 'w') as f:
+    f.write(summary_df.to_latex(float_format="%0.1f"))
 
 # Table that shows how many trials and the mean duration
 groups = ['Vehicle Type', 'Road Surface', 'Target Speed [km/h]']
@@ -120,8 +122,13 @@ trial_count_df = stats_df.groupby(groups)['Duration [s]'].agg(
        'STD': 'std'})
 print_header("Trial Counts and Duration Stats Per Scenario")
 print(trial_count_df)
-print(trial_count_df.to_latex(float_format="%0.1f"))
+with open(os.path.join(PATH_TO_TABLE_DIR,
+                       'trial-count-data-frame.tex'), 'w') as f:
+    f.write(trial_count_df.to_latex(float_format="%0.1f"))
 
+#####################################
+# Table: ISO Weighted RMS Bicycle OLS
+#####################################
 f = (f"{SIGNAL_RMS_ISO} ~ "
      "Q('Mean Speed [m/s]') * "
      "C(Q('Road Surface'), Treatment('Tarmac')) + "
@@ -130,6 +137,8 @@ mod = smf.ols(formula=f, data=bicycle_df)
 bicycle_res = mod.fit()
 print_header("Bicycle OLS Results (Vertical ISO Weigthed RMS)")
 print(bicycle_res.summary())
+with open(os.path.join(PATH_TO_TABLE_DIR, 'bicycle-ols.tex'), 'w') as f:
+    f.write(bicycle_res.summary().as_latex())
[…]

### 2025-01-26 src/website.py
Added Tukey comparison plots.

@@ -151,7 +151,14 @@ for surf in ('Tarmac', 'Paver Bricks'):
         sub_df = bicycle_df[(bicycle_df['Road Surface'] == surf) & spd_sel]
         comp_tab = pairwise_tukeyhsd(sub_df[f"{SIGNAL_RMS_ISO}"],
                                      sub_df['Vehicle, Seat, Baby Age'])
-        bicycle_comp_tables.append((surf, speed, comp_tab))
+        fig, ax = plt.subplots(layout='constrained')
+        comp_tab.plot_simultaneous(ax=ax)
+        fig.set_size_inches((MAXWIDTH*MM2INCH, 0.5*MAXWIDTH*MM2INCH))
+        fname = 'tukey-{}-bicycle-{}-{}.png'.format(SIGNAL, surf, speed)
+        fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
+        plt.clf()
+        bicycle_comp_tables.append((surf, speed, comp_tab,
+                                    IMG.format('', fname) + '\n</br>'))
         print(comp_tab)
 
 ######################################
@@ -174,7 +181,14 @@ for surf in stroller_df['Road Surface'].unique():
     sf_sel = stroller_df[stroller_df['Road Surface'] == surf]
     comp_tab = pairwise_tukeyhsd(sf_sel[f"{SIGNAL_RMS_ISO}"],
                                  sf_sel['Vehicle, Seat, Baby Age'])
-    stroller_comp_tables.append((surf, comp_tab))
+    fig, ax = plt.subplots(layout='constrained')
+    comp_tab.plot_simultaneous(ax=ax)
+    fig.set_size_inches((MAXWIDTH*MM2INCH, 0.5*MAXWIDTH*MM2INCH))
+    fname = 'tukey-{}-stroller-{}.png'.format(SIGNAL, surf)
+    fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
+    plt.clf()
+    stroller_comp_tables.append((surf, comp_tab,
+                                 IMG.format('', fname) + '\n</br>'))
     print(comp_tab)
 
 boxp_html = []
@@ -732,11 +746,12 @@ html_source = INDEX.format(
     boxp_html='\n  '.join(boxp_html),
     bicycle_stats=bicycle_res.summary().as_html(),
     stroller_stats=stroller_res.summary().as_html(),
[…]

### 2025-01-26 src/website.py
Improved labels and titles on Tukey plots.

@@ -153,7 +153,10 @@ for surf in ('Tarmac', 'Paver Bricks'):
                                      sub_df['Vehicle, Seat, Baby Age'])
         fig, ax = plt.subplots(layout='constrained')
         comp_tab.plot_simultaneous(ax=ax)
-        fig.set_size_inches((MAXWIDTH*MM2INCH, 0.5*MAXWIDTH*MM2INCH))
+        ax.set_title(f'Cargo Bicycle Tukey Comparison for\nSurface {surf} and '
+                     f'Speed {speed}')
+        ax.set_xlabel('RMS Acceleration [m/s$^2$]')
+        fig.set_size_inches((MAXWIDTH*MM2INCH, 0.4*MAXWIDTH*MM2INCH))
         fname = 'tukey-{}-bicycle-{}-{}.png'.format(SIGNAL, surf, speed)
         fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
         plt.clf()
@@ -183,7 +186,9 @@ for surf in stroller_df['Road Surface'].unique():
                                  sf_sel['Vehicle, Seat, Baby Age'])
     fig, ax = plt.subplots(layout='constrained')
     comp_tab.plot_simultaneous(ax=ax)
-    fig.set_size_inches((MAXWIDTH*MM2INCH, 0.5*MAXWIDTH*MM2INCH))
+    ax.set_title(f'Stroller Tukey Comparison for Surface {surf}')
+    ax.set_xlabel('RMS Acceleration [m/s$^2$]')
+    fig.set_size_inches((MAXWIDTH*MM2INCH, 0.4*MAXWIDTH*MM2INCH))
     fname = 'tukey-{}-stroller-{}.png'.format(SIGNAL, surf)
     fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
     plt.clf()

### 2025-01-27 src/data.py
More intervals and label placement improvement for time histories.

@@ -259,7 +259,7 @@ class Trial():
         """
         interped = self.imu_data[sig_name].interpolate(method='time')
         ax = interped.plot(ax=ax)
-        ax.xaxis.set_major_locator(mdates.SecondLocator(interval=4))
+        ax.xaxis.set_major_locator(mdates.SecondLocator(interval=2))
         ax.xaxis.set_major_formatter(mdates.DateFormatter('%H:%M:%S'))
         if 'acc' in sig_name.lower():
             too_big = interped[interped > 16.0*9.81]
@@ -267,7 +267,7 @@ class Trial():
             ax = too_big.plot(ax=ax, linestyle='', marker='o', color='red')
             ax = too_small.plot(ax=ax, linestyle='', marker='o', color='red')
         ax.figure.text(0.01, 0.01,
-                       'Duration: {:1.1f}'.format(self.calc_duration()))
+                       'Duration: {:1.1f}s'.format(self.calc_duration()))
         if show_rms or show_vdv:
             mean = self.imu_data[sig_name].mean()
         if show_rms:
@@ -279,7 +279,7 @@ class Trial():
             ax.axhline(mean + vdv, color='grey')
             ax.axhline(mean - vdv, color='grey')
         # TODO : Not the case if gyro signal is selected, e.g.
-        ax.set_ylabel('Acceleration [m/s$^2$]')
+        ax.set_ylabel('Acceleration\n[m/s$^2$]')
         ax.set_xlabel('Time [HH:MM:SS]')
         return ax
 

### 2025-01-27 src/data.py
Add grid to time series plots.

@@ -281,6 +281,7 @@ class Trial():
         # TODO : Not the case if gyro signal is selected, e.g.
         ax.set_ylabel('Acceleration\n[m/s$^2$]')
         ax.set_xlabel('Time [HH:MM:SS]')
+        ax.grid()
         return ax
 
     def calc_rms(self, sig_name):

### 2025-01-27 main.tex
Update tex and bib file to version 2 from overleaf.

@@
 
+% NOTE : Use as \si{\kph} or \si{\mps}
+\def\kph{\kilo\meter\per\hour}
+\def\mps{\meter\per\second}
+
 \title{
-  DRAFT: v1 \\
-  Vibration Characterization of Babies\\
-  Transported in Strollers and Cargo Bicycles\\
+  DRAFT: v2 \\
+  Vibration Characterisation of Strollers and\\
+  Cargo Bicycles for Transporting Infants\\
   \vspace{2mm}
@@
 }
-\author{Gabriele Dell'Orto \and Brecht Daams \and Riender Happee \and Jason K. Moore}
+% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
+\author{
+Gabriele Dell'Orto \and
+Brecht Daams \and
+Riender Happee \and
+Arjo J. Loeve \and
+Jesper Meijerink \and
+Georgios Papaioannou \and
+Thomas Valk \and
+Jason K. Moore
+}
 
@@
 %
-\textbf{This is a draft report. The values and results must be considered
-preliminary and may change as the analysis is refined and rechecked.}
-
-\section*{\centering Acknowledgements}
-%
-Thomas Valk and Jesper Meijerink helped design and perform the experiments.
-Georgios Papaioannou and Arjo Loeve gave advice on the experimental design and
-analyses.
+\textbf{This is a draft report. The values and results must be considered preliminary and may change as the analysis is refined and rechecked.}
+
+\begin{abstract}
+    TODO
+\end{abstract}
 
@@
 %
-This paper reports on the vibration experienced by infants of different ages
-when transported in cargo bicycles and strollers. Vibration can be related to
-discomfort and might lead to negative health consequences. However, the topic is
-poorly addressed in scientific literature, and only a few studies focus on the
-effect of vibration on babies. To measure the actual vibration transmitted to
-the babies, we equipped three strollers and two cargo bicycles with inertial
-measurement units (IMU) and conducted several experiments across different road
-surfaces and travelling speeds, using dummies representing the size of 0, 3, and
-9 months old babies. We present analysis in the time and frequency domains,
-allowing us to compare vertical accelerations at the baby-seat interface, as
-recommended by ISO-2631-1. We investigate the influence of different variables
-on vibration, such as type of vehicle, baby seat, travelling speed, dummy size
-and mass, and road surfaces.
+% Paragraph about motivation 
+Cycling, one of the active transportation modes is advantageous for health~\cite{Oja1998} and greatly contributes to reducing CO2 emissions, congestion, and air
+pollution ~\cite{Neves2019}.
+As a result, bikes have been widely used as a mean to deliver goods to consumers, and also for daily commuting to work and personal matters (shopping, commuting with children/infants, and others).
+Among all journeys in EU, 20-40$\%$ are by bike or on foot, with bicycle trips being most frequent in the Netherlands, Denmark and Sweden and less frequent in Finland.
+Various countries and employers provide incentives to increase the use of bikes.
+Nevertheless, there are great challenges that need to be overcome to secure the wide acceptance and use of active transportation modes.
+One of these challenges is the comfort levels experienced by riders and passengers (i.e., infants/children in cargo bikes), which is a multi-faceted aspect \cite{ayachi2015identifying} and critical for the wide acceptance and use of bikes as a daily mean of transport.
+
+% Paragraph about comfort in bikes
+Comfort on bicycles \cite{too1990biomechanics} is mostly affected by physical comfort and the impact of environmental factors (weather, route geometry and road roughness).  
+Physical comfort is related with mechanical (bicycle and components design), biomechanical (whole-body vibrations, human body dynamics and kinematics) and physiological factors (individual characteristics, e.g.
+sex, body size, weight and others).
+While there is extensive literature exploring the impact of environmental factors (i.e., irregular road surface quality, weather conditions) on cyclists' comfort \cite{Stinson2003,Hagemeister2003,ayachi2015identifying,Verhoeven2017,Teixeira2020}, there is limited work on understanding the biomechanical and physiological factors of comfort while riding a bike or being driven by a bike (infants/children on cargo bikes or trailers).
+In this paper, we will explore biomechanical comfort, by assessing the whole-body vibrations that could be experienced by transported infants, and evaluating potential health risks and discomfort that might arise.
+
+% Paragraph about transmission of vibrations
+Biomechanical comfort is mostly related to the vibrations induced by road irregularities and transmitted via the vehicle to the human body and head while being driven. 
+According to the literature, the road irregularities are a critical factor for the amplitude of the resulting vibrations experienced by the bicyclists and passengers, as the vibrations induced on the body and head are not efficiently isolated due to the lack of suspension systems in most of the bike models \cite{vasudevan2017comparison}.
+The bike design and its specific configuration can affect the sitting posture, and eventually the transmissibility of the vibrations \cite{Brand2020,Verma2016}.
+The sitting posture can also vary in case of children/infants who may be transported sitting or lying down in a different--than the bicyclist--location (e.g.
+above a wheel when in a bike seat) and in/on a different ‘seat’ (a car seat, bike seat, stroller seat or cot).
+These all influence the level of whole-body vibrations and the transmission of the vibrations from the seat to the body and head. 
+Furthermore, the amplitude of the vibrations experienced by bicyclists/passengers while biking or being transported may increase because of increased travelling speed either due to running with a stroller or due to the increased power offered by electric bikes (with and without trailers), and cargo bikes.
+The average speed of electric bikes and speed pedelecs is 19$\%$ higher (21,0 km/h) and up to 63$\%$ higher (28,1 km/h), respectively, than the average speed of conventional bicycling (SWOV, 2022, p.
+8).
+The intensity of these vibrations could become even more critical with the change of load, which could be related with age and size of the infant/children transported. 
+However, there is limited literature exploring the whole-body vibrations of infants and children being transported by bikes with trailers, cargo bikes or even cots \cite{Schwanitz2020,MalteChildComfort2022}.
+
+% Paragraph about children in bikes
+% 
+One of the research fields closely related to vibrations acting on infants during transportation is that of inflicted head injury by shaking trauma (IHI-ST) (Vester, 2019; Zandwijk, 2019; Hutchinson, 2024).
+However, there is a lack of reliable, applicable, validated injury thresholds for assessing IHI-ST risks and hardly any chance that these thresholds do apply to vibration studies.
+Similarly, even if there are significant indications that the vibration amplitude affects comfort in bikes or strollers, there are no standard assessment methods or guidelines available with regards to their design.
+ISO 2631, the international standard for assessing whole-body vibrations, was derived using datasets on motion platforms, adults as human participants and sitting postures which are adopted in passenger vehicles rather than in bikes.
+This inconsistency was captured by Gao et al. (2018), who derived different limits of comfort for adults compared to ISO-2631.
+In addition, the exposure time to the vibrations is not considered as a factor of comfort by the ISO2631, despite having a clear impact on health risks according to the European Directive (2002/44/EC, 2002).
+
+% Paragraph Potential effects of vibrations on adults
+Despite the lack of clarity with regards to comfort assessment or inflicted head injury by shaking trauma for children/infants on bikes, there are clear indications in the literature that these should be explored.
+About 36$\%$ of males and 42$\%$ of females in the total sample of 900 people (Groenendijk et al., 1992) had various complaints about comfort.
+Discomfort for both men and women occurred even during short bicycle trips (3—10 km). 
+Duarte et al.
+(2018) considered four different exposure durations and concluded that their results rejected the hypothesis that the exposure duration or the vibration dose value (VDV) by itself are important parameters on the vibration influence.
+Furthermore, cyclists can avoid or reduce shocks and uncomfortable vibrations for a short time by standing on the pedals, which can increase comfort in some situations. 
+This is an option that children sitting or lying in transportation systems do not have.
+Results from research into comfort of adult cyclists are assumed to be children sitting or lying in transportation systems, leading potentially to misinterpretations. 
+Hence, there is a need to re-focus on the impact of vibrations on infants and children health and comfort \cite{rybarczyk2020physiological} to secure the safe, comfortable and wide use of bikes.
+
+Schwanitz et al. (2020a and 2020b) measured seat pan accelerations of a child bicycle trailer with anthropomorphic children shaped sandbag dummies (baby and toddler sizes) present in the seats. 
+They report ISO 2631-1 weighted RMS vertical accelerations riding over smooth asphalt, gravel, and cobblestones. 
+Tire pressure and the number of passengers had no significant effect on vibration magnitude, but road surface and travel speed did. 
+The baby sized dummy (5 kg) experienced 20$\%$ higher vibration than the toddler sized dummy (10 kg). 
+They express that their measured values generally exceed the ISO 2631-1 occupational norms for 4-8 hour vibrational comfort of adults.
+
+Kayna-Forster (2020) measured acceleration in bicycle child trailers with human subjects aged 12 months to 6 years over asphalt and gravel terrain. 
+The bicyclists travelled at their chosen comfort speeds and averaged 12 km/h over the 20 minute ride duration.
+According to the assessment using ISO-2631 and the use of an unspecified correction, the vibrations are similar to the ones experienced in car seats in vehicles and illustrated moderate or low health risk for a 2 hour duration.
+On the other hand, the uncorrected values point to moderate and high risks, which align with subsequent studies detailed below.
+As expected, she also pointed out that cargo trailers with suspension systems did exhibit lower seat accelerations. 
+Her second study utilised a laboratory vibration excitation system, similar to Ota et al.
+(2012) to determine the impact of independent variables (terrain type, trailer type, and cushion type) to the dependent variable vibration magnitude at the interface between the trailer seat and dummy buttock of a child.
+Terrain type had the greatest influence on vibration exposure levels followed by trailer type (p<0,001). 
+Adding gel cushions did not significantly influence vibration measured at the seat/buttock interface.
+
+Whole-body vibration by means of vibration total values obtained at toddler and baby dummy in dependence on different road surfaces, load cases, tire pressures, and velocities.
+Vibration discomfort threshold value 2.0 m/s2 is indicated with a dashed line.
+(Schwanitz et al., 2020a)
+Liu (2023) developed a benchtop vibration excitation system for a unsuspended bicycle trailer capable of applying controlled and simulated road vibrations to the trailer.
+They measured IS0 2631-1 weighted RMS vertical accelerations at the seat pan ranging from 2,8 to 3,6 m/s2 for seat masses of 0 kg to 23 kg.
+Vibration increased with load at a high tire pressure (150 kPa) and had less variation at a lower pressure (75 kPa).
+They point out that these values are rated as “extremely uncomfortable” as per the 4-8 hour ISO 2631-1 occupational norms.
+Rothhämel (2023) found ISO 2631-1 weighted RMS child trailer seat pan acceleration between 1 and 5 m/s2 for speeds between 10 and 20 km/h on smooth asphalt with large tire pressure variations having small effects.
+On cobblestones this range increased to 2 to 9 m/s2 for the same speed range.
+The child trailer exhibited larger weighted RMS vibration than a tadpole configuration three-wheel cargo bicycle with the child seat between the front wheels.
+Both the trailer and cargo bicycle child seats had generally larger magnitude vibrations than experienced in an automobile seat travelling at 30 km/h on a rough road (~3 m/s2) (Gromadowski 2013).
+Rothhämel and Liu (2023) made improvements to the work by Lui (2023).
+They used the benchtop excitation device and the bicycle trailer with a 6,5 kg mass representing an infant and measured seat pan vertical acceleration at 2047 Hz sampling rate with excitation bandwidth of 17 Hz.
+They report ISO 2631-1 weighted vertical RMS ranging from 3 to 5 m/s2 for tire pressures from 50 to 400 kPa, which are higher value accelerations than reported by Liu (2023), See Figure 16.
+These values also fall into the “extremely uncomfortable” zone for the ISO 2631-1 4-8 hour occupational norms.
+
+This paper reports on the vibration induced on infants of different ages when transported in strollers and cargo bicycles. 
+Vibration can be related to discomfort and might lead to negative health consequences.  
+In fact, vibrations induced by such transportation means have brought up as alternative scenarios in court cases concerning suspicion of infant injuries inflicted by violent shaking, such as in a recent case about a twin in 2023 in the Netherlands.
+However, the topic is poorly addressed in scientific literature, and only a few studies focus on the effect of vibration on babies. 
+To measure the actual vibration transmitted to the babies, we equipped five strollers and two cargo bicycles with inertial measurement units (IMU) and conducted several experiments on different road surfaces and travel speeds,
+using dummies representing the size and mass of 0, 3, and 9 months old infants.
+We present results in the time and frequency domains,
+which allows comparing vertical accelerations at the baby-seat interface, as
+recommended by ISO-2631-1 norms for vibration discomfort. 
+We investigated the influence of different variables on vibration, such as type of vehicle, baby seat, travelling speed, dummy size and mass, and road surfaces.
 
@@
 %
-In this section, we describe the measurement equipment used and the protocol
-followed during the experimental campaign.
-
-\subsubsection{Description of Test Equipment}
-%
-We conducted the experimental campaign using three different strollers, two
-cargo bicycles, and two baby seats, chosen for their popularity and/or
-distinctive features. The test involved three baby dummies representative of
-various ages (different sizes and masses).
+\subsubsection{Test Equipment}
+%
+Vibration measurements were conducted at approximate constant speed using five
+different strollers, two cargo bicycles, and two baby seats, chosen for their
+popularity and/or distinctive features:
 
@@
   (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
-  \item[Stokke BABYZEN YOYO 0+] It is the smallest foldable stroller on the
-  market, it has only a marginal suspension system and smaller wheels compared
-  to the other strollers on the market. It can be considered the ideal choice
-  for holidays, being one of the few buggies that can be taken as hand
-  luggage on the plane.
+  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the
+  market. It has only a marginal suspension system and smaller wheels compared
+  to the other strollers on the market. 
   (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
   rented for the experiment})
-  \item[Bugaboo Fox 5] It is featured by large wheels, and a suspension system
-  which makes it an all-terrain stroller (according to the manufacturer). It has
+  \item[Bugaboo Fox 5] Featured by large wheels and a suspension system
+  that makes it an all-terrain stroller according to the manufacturer. It has
   a large puncture-proof tyres and an air-permeable mattress.
@@
 \begin{description}
-  \item[Urban Arrow Bicycle] This is a popular electric cargo bicycle in The
-  Netherlands. This vehicle has two inline wheels which makes it roll into the
-  curve like a regular bicycle. It is featured by a long frame that can carry
-  loads usually placed in between the rider and the front wheel. It can fit
-  various accessories, including baby seats, rain covers, etc.
+  \item[Urban Arrow Bicycle] A popular electric cargo bicycle in The
+  Netherlands. This vehicle has two inline wheels which makes it roll into curves like a regular bicycle. It is featured by a long frame that can carry
+  loads usually placed in between the rider and the front wheel. 
   (\href{https://urbanarrow.com/}{Urban Arrow website})
-  \item[Keiler Tricycle] This is a tadpole (two wheels in the front, one in the
-  rear) cargo tricycle without electric assist. This vehicle will not roll in
+  \item[Keiler Tricycle] A tadpole cargo tricycle (two wheels in the front, one in the
+  rear) without electric assist. This vehicle will not roll into
   curves. However, differing road surface unevenness at the left and right front
@@
 \paragraph{Baby Seats}
-
-These baby seats were mounted in the cargo bay of the two cargo bicycles.
+%
+These baby seats were mounted in the cargo bays of the two cargo bicycles.
 %
 \begin{description}
-  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] This seat can be adapted to
-    cargo bicycles with a proper fixing system (e.g. ``Urban Arrow Baby Car Seat
-    Adapter''). It comes with an integrated suspension system which is part of
-    the adapter.
+  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to
+    cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow Baby Car Seat
+    Adapter''). Comes with an integrated suspension system.
     (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi Webpage})
-  \item[Melia Baby Shell]. The baby seat is meant for babies from 2 to 9 months,
+  \item[Melia Baby Shell] Meant for babies from 2 to 9 months old,
     specifically designed for cargo bikes.
@@
 \end{description}
-
-We conducted tests using three different dummies, of various sizes and masses
-according to the desired ages of 0, 3 and 9 months. We considered the use of
-``crash test dummies'' which are designed and commonly used to test
-child seats in cars in crash conditions. However, the nearest available body
-sizes for crash test dummies were a 6-weeks Q-dummy, a 6-months Crabi dummy, and a
+%
+Appendix~\ref{app:equipment} provides figures and technical descriptions of all the strollers and cargo bicycles.
+
+The tests involved three baby dummies with sizes and weights representative of 0, 3 and 9 months old infants. We considered the use of
+``crash test dummies'' (also known as anthropomorphic test devices or ATD's) which are designed and commonly used to test
+child seats in cars crash tests. However, the nearest available body
+sizes for crash test dummies were a 6-weeks Q0-dummy, a 6-months Crabi dummy, and a
 12-months Q-dummy. These 3 dummies are of a fundamentally different design,
-hampering comparison, and do not match the desired body size. Moreover, these
-child dummies have dynamic properties designed for crash conditions, and use
-scaling of adult biomechanical data, rather than child data.
+hampering comparison, and do not match the desired body sizes. Moreover, these
+child dummies have dynamic properties designed for crash conditions, and were designed based on
+scaling of adult biomechanical data rather than child data.
 Testing with real children would be unethical for the most severe conditions
 tested, and would create challenges in terms of reproducibility.
-Hence we bought and adapted dummies available in a wide range of postures. We
-bought ``reborn'' dummies from a webshop specialising in dolls and dummies
-(\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). We filled the dummies
-with cat litter sand to reproduce the exact weight needed for testing. Cat
-litter sand indeed features smooth and round-shaped grains, which do not
-damage the dummies' material (fabric and plastic). The weight and body height of
-the dummies are average measures for children of exactly 0, 3 and 9 months old.
+Hence we bought and adapted ``reborn'' dummies available in a wide range of postures from a webshop specialising in dolls and dummies
+(\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). The dummies
+were filled with a mixture of cat litter sand and water to reproduce the exact weights needed for testing. Cat
+litter sand features smooth and round-shaped grains, which do not
+damage the dummies' materials (fabric and plastic). The weight and body height of
+the dummies were made to match the are average measures for children of 0, 3 and 9 months old.
 We wanted to use the measurements from Steenbekkers \cite{Steenbekkers1993}. But
 the researchers provided the results only per three-month group, which did not fit our
-age categories. Therefore, we decided to use the growth charts to determine the average weight
-and body height at the right ages. Growth charts (`groeidiagrammen') are used by
-doctors to assess the growth of babies. The average weight at 0 months and the
+age categories. Therefore, we decided to use the growth charts (used by clinicians to assess infant growth) to determine the average weight
+and body height at the right ages. The average weight at 0 months and the
 average body height at all three ages are derived from Dutch growth charts.
-Measurements of Dutch children are used because the Dutchies are the target group of
+Measurements of Dutch children are used because these are the target group of
 VeiligheidNL. Dutch children are also the tallest in Europe. The average weight
@@
 
-To achieve a realistic mass distribution in the body of the dummies, it is
-important to fill each limb with the proper amount of sand. To do this, we
-simplified the geometry of each body segment according to defined basic
-geometric shapes: we assumed a sphere for the head, and cylinders for the torso,
-upper arms, upper legs and lower legs, according to what was stated in
-\cite{Snyder1977}. We also assumed an equal density of each limb, and we
-rescaled the measurements of the limb segments reported in \cite{Snyder1977} to
-match the dimensions of our dummies. In doing so, we were able to calculate the
-volume of each segment, thus the mass of each limb of the dummies (assuming a
+To achieve a realistic mass distribution in the body of the dummies, each limb was filled with a proper amount of sand.
+To do this, the geometry of each body segment was simplified according to pre-defined basic geometric shapes: a sphere for the head, and cylinders for the torso,
+upper arms, upper legs and lower legs, according to \cite{Snyder1977}.
+We also assumed an equal density of each limb, and rescaled the measurements of the limb segments reported in \cite{Snyder1977} to match the dimensions of our dummies.
+In doing so, we were able to calculate the volume of each segment, and thus the mass of each limb of the dummies (assuming a
 density of 1000~\si{\kg\per\cubic\meter}).
 
-\subsubsection{Description of Measurement Equipment}
-%
-Linear acceleration and angular velocity was measured using five IMUs.
-Specifically, we used a Consensys Shimmer3 IMU with a Consensys Base 6U.01 dock.
-The Shimmer units were updated to the firmware version LogAndStream v0.11.0, and
-managed via the software ConsensysBASIC v1.6.0-64bit on a Laptop Dell 7310, OS
-Microsoft Windows 10. We 3D printed supports for the sensors to ensure a firm
+\subsubsection{Measurement Equipment}
+%
+Linear accelerations and angular velocities were measured tri-axially using Consensys Shimmer3 IMUs with a Consensys Base 6U.01 dock.
+The IMUs were updated to firmware version LogAndStream v0.11.0, and
+managed via the software ConsensysBASIC v1.6.0-64bit on a Dell 7310 laptop with
+Microsoft Windows 10. We 3D printed supports (material: PLA) for the sensors to ensure a firm
 clamp between the sensor and the bicycle/stroller tested (visible in
 Figure~\ref{fig:sensors_UA}). Each vehicle was equipped with five IMUs, as
-listed below. The pictures of sensors mounted on the cargo bicycle Urban Arrow
+listed below. The sensors mounted on the cargo bicycle Urban Arrow
 are depicted in Figure~\ref{fig:sensors_UA}. The location and orientation of the
-sensors for Urban Arrow equipped with the Melia baby shell are reported in
+sensors for Urban Arrow equipped with the Melia baby shell are shown in
 Figure~\ref{fig:tech_drawing_UA_Melia}, both for lateral and front view.
-Similarly, the Bugaboo configured to carry 0 months babies in the baby cot is
+Similarly, the Bugaboo configured to carry 0 months old infants in the baby cot is
 shown in Figure~\ref{fig:tech_drawing_Bugaboo0}.
@@
   \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA_Melia_lateral.PNG}}
-  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_UA_Melia_front.PNG}}
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_front.PNG}}
   \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
@@
   \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_lateral.PNG}}
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_lat.PNG}}
   \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_front.PNG}}
@@
 \begin{enumerate}
-  \item \textbf{Rear Wheel} The sensor was placed on the wheel hub (cargo
-  bicycles) or clamped to the wheel (strollers). The purpose of this sensor is
-  for a travel speed measurement. We can derive the travelling (longitudinal)
-  speed according to:
+  \item \textbf{Rear Wheel} This IMU was placed on the wheel hub (cargo
+  bicycles) or clamped to the wheel (strollers) for measuring the travel speed . The travelling (longitudinal)
+  speed was derived according to:
   %
   \begin{align}
-    v = \si{\omega} \cdot r
+    v = \omega \cdot r
     \label{eq:long-speed}
@@
   %
-  where \si{\omega} is the angular speed of the vehicle (from IMU gyroscope aligned with the wheel's axis) and $r$ is the radius of the wheel.
-  \item \textbf{Front Wheel} The sensor was mounted on the front wheel fork (the
-  caster wheel for the stroller). This is the measurement point closest to the
-  ground for a non-rotating sensor. The purpose of this sensor is to measure the
-  road roughness filtered out by the tyres.  
-  \item \textbf{Frame} As for the cargo bicycle, the third sensor was placed
-  below the frontal cargo bay, clamped to the frame. It can give us an
+  where \si{\omega} is the angular speed of the wheel (obtained from the IMU's gyroscope aligned with the wheel's axis) and $r$ is the radius of the wheel.
+  \item \textbf{Front Wheel} This IMU was mounted on the front wheel fork (the
+  caster wheel for the stroller). This was the non-rotating measurement point closest to the
+  ground. The purpose of this sensor was to measure the
+  road roughness filtered out only by the tyres.  
+  \item \textbf{Frame} On the cargo bicycle, an IMU was placed
+  below the frontal cargo bay, clamped to the frame. This was to provide an
   understanding of the damping characteristics of the bicycle frame, together
-  with an estimation of the effect of the suspension system. Regarding the
-  stroller, the sensor was placed under the baby seat.
-  \item \textbf{Seat Head} Sensor mounted into the baby seat, directly in
-  contact with the dummy's head. It measured the vibration transmitted to the
+  with an estimation of the effect of the suspension system. On the
+  stroller, the IMU was placed under the baby seat.
+  \item \textbf{Seat Head} IMU mounted into the baby seat, directly in
+  contact with the dummy's head. This IMU measured the vibration transmitted to the
   head contact point.
-  \item \textbf{Seat Buttock} This sensor was taped into the baby seat, at the
+  \item \textbf{Seat Buttock} This IMU was taped into the baby seat, at the
   interface between the dummy's buttock and the baby seat. It measured the
@@
 
-The IMU sensors for the seat head and seat buttock were placed at the surface at
-positions contacting the dummy. This matches the recommended practice in
+The IMUs for the seat head and seat buttock 
+positions contacting the dummy were placed according to the recommended practice in
 vibration testing norms such as ISO-2631-1. This generates acceleration data
 representative of the mechanical load transferred from the seat to the human
-body taking into account the compliance of the seat foams. We set the sampling
-frequency to 910.22~\si{\hertz} for all the sensors. The full-scale range was
-16~g for the accelerometer ("WR" or "wide range" configuration on Consensys
-Shimmer software), and 2000~\si{\degree\per\second} for the gyroscope. All the
-tests were recorded with two GoPro cameras Hero7: one directly mounted on the
-strollers/bicycles to record the relative motion dummy/seat, while the other one
+body taking into account the compliance of the seat foams and the inertia and compliance of the dummy.
+
+The target sampling
+frequency was to 910.22~\si{\hertz} for all IMUs. The full-scale range was set to
+\(\pm\)16~g for the accelerometer ("WR" or "wide range" configuration on Consensys
+Shimmer software), and \(\pm\)2000~\si{\degree\per\second} for the gyroscope. All 
+tests were recorded with two GoPro Hero7 cameras: one directly mounted on the
+strollers/bicycles to record the dummy-seat relative motion, while the other
 was held by an experimenter walking or riding alongside the vehicle to have a
@@
 
-\subsubsection{Description of Experimental Protocol}
-%
-We conducted the experimental campaign in Delft, The Netherlands along public
+\subsubsection{Experimental Protocol}
+%
+All tests were conducted in Delft, The Netherlands on public
 roads near the Delft University of Technology, Faculty of Mechanical
-Engineering.
-After mounting the sensors in the correct position and reaching the location
+Engineering. Satellite imagery and local photographs of each site are provided in Appendix~\ref{app:location}.
+After mounting the sensors and reaching the location
 of the experiment, we turned on the sensors to start the experimental session.
 Before each trial, we pushed the vehicle back and forth on level ground to mark
-the beginning of the trial for time synchronizing the sensors.
-For the cargo bicycle test, a single rider conducted the full experimental
-campaign to be consistent across different sessions (rider mass: 59~\si{\kg};
-rider height: 1.70~\si{\m}).
-We gathered data from multiple trials within the same session. The tests were
-conducted on six different surfaces for the strollers with the pusher manually
-keeping consistent walking speed of approximately 5~\si{\kilo\meter\per\hour}
-across different trials by observing a speedometer. We tested on three surface
-scenarios for the cargo bicycles (at different speeds). The test combinations
+the beginning of the trial for time-synchronizing the sensors.
+For the cargo bicycle test, a single rider conducted all test runs to be consistent across different sessions (rider mass: 59~\si{\kg};
+rider height: 1.70~\si{\m}). We tested on three types of road surfaces with the cargo bicycles and repeated those at different speeds.
+The stroller tests were conducted on six different surfaces with the pusher manually
+keeping a consistent walking speed of approximately 5~\si{\kilo\meter\per\hour}.
+In all tests, speed was controlled by the pusher or cyclist using a speedometer mounted on the stroller handle bar or the steer of the cargo bicycle.
+We gathered data from multiple trials within the same session. The test combinations
 are listed below.
@@
 \begin{itemize}
-  \item \textbf{Strollers} We tried to keep speed as constant and consistent as
-  possible among different trials and sessions. The experimental campaign was
-  conducted using dummies of 0 months and 9 months. Some of the test surfaces
-  are depicted in Figure~\ref{fig:surfaces_stroller} and all are listed below:
+  \item \textbf{Strollers}  The stroller tests were done with the dummies of 0 months and 9 months old. Some of the test surfaces
+  are shown in Figure~\ref{fig:surfaces_stroller} and all are listed below:
   \begin{itemize}
@@
       \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
-      \item Shock. A 30x30~\si{\mm} square section aluminium bar was taped on the ground (smooth surface)
+      \item Shock. A 30x30~\si{\mm} square section aluminium bar was taped to the ground (smooth surface)
   \end{itemize}
-  \item \textbf{Cargo bicycles} The experimental campaign was conducted using
-  dummies of 0 months and 3 months. Regarding the Keiler tricycle, the speed was
+  \item \textbf{Cargo bicycles} The cargo bike tests were conducted using
+  the dummies of 0 months and 3 months. With the Keiler tricycle, the speed was
   limited to 20~\si{\km\per\hour} for safety reasons (due to wobbling), and
@@
 All tested systems provided full support of back and head and allowed usage in
-lying or at least reclined postures. Nine months old babies would be able to
-sit erect but will often rest their heads or may even sleep. Although sitting
+lying or at least reclined postures. Nine months old infants would be able to
+sit erect but will often rest their heads or be asleep. Although sitting
 upright is the best posture for children who can sit upright, a more recumbent
@@
 horizontal or reclined postures. The inclination angle with respect to the
-ground is listed in Table~\ref{tab:baby-posture}, for each condition tested.
+ground is listed in Table~\ref{tab:baby-posture} for each condition tested.
 %
@@
   \centering
-  \caption{Inclination angles of the sensors ``Seat Head'' and ``Seat Buttock'',
-  per each tested configuration. We report the angles of the sensor at the
-  interface between the seat and the dummies' head and buttock, taken positive
-  counterclockwise. In this case, 0~\si{\degree} is defined by the ground plane.
+  \caption{Inclination angles of the IMUs ``Seat Head'' and ``Seat Buttock'',
+  per each tested configuration. We report the angles of the sensor at
+  the interface between the seat and the dummies' head and buttock, taken positive
+  counterclockwise. In this case, the ground plane defines 0~\si{\degree}.
   In other words, 0~\si{\degree} means horizontal, -90~\si{\degree} means
@@
 \cline{2-6}
- & Babyzen Yoyo 0+ & 0 months & Baby cot & -12 & -12 \\
+ & Babyzen YOYO 0+ & 0 months & Baby cot & -12 & -12 \\
+\cline{2-6}
+& Babyzen YOYO 0+ & 9 months & Baby seat & 45.2 & -4 \\
 \cline{2-6}
@@
 
-\subsection{Data Analysis Methodology}
-% 
-We analysed the raw data with a custom data processing pipeline hosted at
+\subsection{Data Processing Code}
+% 
+We analysed the raw data with a custom data processing pipeline. The pipeline's
+open source code is hosted at
 \href{https://github.com/mechmotum/baby-vibration}{github.com/mechmotum/baby-vibration}
@@
 with an exhaustive collection of figures for examining the quality of the data
-and general results for all trials. Selected tables and figures from the website
+and general results for all trials. Selected tables and figures from that output
 are presented and discussed in the results section of this paper.
@@
 %
-The raw data consists of a single CSV file per session per IMU sensor along with
+We define a ``session'' as a continuous data collection period from a single
+vehicle. Each section is segmented into ``trials'' corresponding to a different
+road surface or activity and each experiment is divided into subsequent,
+back-to-back ``repetitions''.
+The raw data consists of a single CSV file per session per IMU along with
 meta-data for the sessions and vehicles. The CSV file contains the time series
-data from IMU: linear acceleration along and angular speed about each of the
-body-fixed orthogonal axes of the sensor alongside Epoch Unix timestamps. We
+data from each IMU: linear acceleration along and angular speed about each of the
+body-fixed orthogonal axes of the IMU alongside Epoch Unix timestamps. We
 segment the sessions into trials representing a motion state of the vehicle:
@@
 interest at a constant speed, as depicted in Figure~\ref{fig:session} as an
-example of the segmentation. We process the data per session as follows:
+example of the segmentation. The data were processed per session as follows:
 %
 \begin{enumerate}
+  \item Calculate the vehicle travel speed during the session from the angular
+    rate of the rear wheel and the vehicle's wheel radius.
   \item Extract segments representing a single trial from each session time
     history, based on the manually labelled segment ``start'' and ``end'' times.
+  \item Split the trials with durations longer than 20~\si{\second} into
+    repitions of \SIrange{20}{40}{\second}.
   \item Rotate the accelerometer data for each sensor from body-fixed sensor
-    coordinates to body-fixed vehicle coordinates and remove the constant
+    coordinates to body-fixed vehicle coordinates and subtract the constant
     standard gravity component. This is achieved by rotating the coordinate axes
-    about the sensor's body-fixed axis which has was manually aligned with the
-    vehicle's pitch axis. We subtract the mean measured acceleration due to
+    about the sensor's body-fixed axis which was manually aligned with the
+    vehicle's pitch axis. We subtracted the mean measured acceleration due to
     gravity giving linear acceleration of each sensor projected into the
-    vehicle's SAE axes, named: longitudinal $x$, lateral $y$, and vertical $z$.
-  \item Extract each motion trial segment and select the vehicle vertical
-    component of the seat pan accelerometer.
-  \item Calculate the vehicle travel speed from the angular rate of the rear
-    wheel and the vehicle's wheel radius.
+    vehicle's SAE body-fixed axes, named: longitudinal $x$, lateral $y$, and
+    vertical $z$.
+  \item Extract each motion trial segment and select the vehicle body-fixed
+  longitudinal, lateral, and vertical component of the seat pan accelerometer.
 \end{enumerate}
 %
-This results in seat pan acceleration time histories of 78 trials of duration
-in the range of \SIrange{5}{80}{\second} (mean: 36~\si{\second}), see
-Table~\ref{tab:num-trials} for a breakdown of the trials.
+This resulted in seat pan acceleration-time recordings of 154 repetitions of durations
+in the range of \SIrange{10}{40}{\second} (mean: 25~\si{\second}), see
+Table~\ref{tab:num-trials} for a breakdown of the repititions.
 %
@@
   \caption{Vehicle speed versus time for an entire session (015) showing the
-  segmented trials in the shaded grey areas. Gold horizontal lines depict the
-  mean speed bounded by the standard deviation of the speed.}
+  trials in the shaded grey areas. Gold horizontal lines depict the mean speed
+  during the trial bounded by the standard deviation of the speed.}
   \label{fig:session}
@@
 %
+% NOTE : This table is autogenerated from the data pipeline scripts and pasted in. I move the units to a second row manually for width conservation.
 \begin{table}
   \centering
-  \caption{Number of trials performed on each road surface and speed along with
-  the mean duration and its standard deviation.}
-\begin{tabular}{lllrrr}
+  \caption{Number of repetitions performed on each road surface and speed along with
+  the mean duration in seconds and its standard deviation.}
+\begin{tabular}{llcccc}
 \toprule
- &  &  & Count & \multicolumn{2}{c}{Duration [s]}  \\
-Vehicle Type & Road Surface & Target Speed [km/h] &  & Mean & STD  \\
+ &  &  & \multicolumn{2}{c}{Repetitions}\\
+ &  & Target Speed & Count & Mean duration & STD duration \\
+Vehicle Type & Road Surface & (km/h) & (-) & (s) & (s) \\
 \midrule
-\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Tarmac} & 12 & 6 & 58.33 & 8.56 \\
- &  & 20 & 3 & 50.42 & 7.04 \\
- &  & 25 & 3 & 44.08 & 1.60 \\
-\cline{2-6}
- & \multirow[t]{3}{*}{Paver Bricks} & 12 & 6 & 54.46 & 5.95 \\
- &  & 20 & 6 & 38.68 & 5.08 \\
- &  & 25 & 3 & 33.43 & 4.25 \\
+\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 13 & 25.1 & 7.0 \\
+ &  & 20 & 8 & 28.8 & 7.6 \\
+ &  & 25 & 3 & 33.4 & 4.3 \\
+\cline{2-6}
+ & \multirow[t]{3}{*}{Tarmac} & 12 & 14 & 25.0 & 7.0 \\
+ &  & 20 & 6 & 25.2 & 7.2 \\
+ &  & 25 & 6 & 22.0 & 2.5 \\
 \cline{1-6} \cline{2-6}
-\multirow[t]{5}{*}{Stroller} & Tarmac & 5 & 10 & 27.87 & 10.07 \\
-\cline{2-6}
- & Cobblestones & 5 & 13 & 27.90 & 24.74 \\
-\cline{2-6}
- & Paver Bricks & 5 & 6 & 51.47 & 21.62 \\
-\cline{2-6}
- & Sidewalk Slabs & 5 & 16 & 19.59 & 6.59 \\
-\cline{2-6}
- & Sidewalk Pavers & 5 & 6 & 48.94 & 19.71 \\
+\multirow[t]{5}{*}{Stroller} & Cobblestones & 5 & 26 & 22.8 & 5.6 \\
+\cline{2-6}
+ & Paver Bricks & 5 & 20 & 25.0 & 7.6 \\
+\cline{2-6}
+ & Sidewalk Pavers & 5 & 19 & 25.2 & 8.2 \\
+\cline{2-6}
+ & Sidewalk Slabs & 5 & 23 & 22.8 & 3.4 \\
+\cline{2-6}
+ & Tarmac & 5 & 16 & 28.9 & 9.6 \\
 \cline{1-6} \cline{2-6}
- & & \textbf{Count Sum} & \textbf{78} & & \\
+ & & \textbf{Count Sum} & \textbf{154} & & \\
 \bottomrule
@@
 Figure~\ref{fig:vert-acc-example} shows an example time history of the vertical
-acceleration of the seat pan during a single trial. We downsampled the time
-history from the set sampling frequency of 910.22~\si{\hertz} to \(N\) samples
-at a constant sample rate of 400~\si{\hertz} with linear interpolation.
+acceleration of the seat pan during a single trial. To perform the ISO 2631-1
+recommended health and comfort analysis, we first downsampled the time history
+from the hardware-set variable sampling frequency of approximately
+910.22~\si{\hertz} to a constant sample rate of 400~\si{\hertz} using linear
+interpolation. We set any acceleration values outside of the sensor
+manufacturer's reported operating range of \(\pm\)16~g to that maximum or
+minimum, respectively, given that the larger values may be unreliable. Values
+that exceed the range are rare and only present in some of the cargo bicycle
+paver brick trials. Following the ISO 2631-1 recommendation, we low pass
+filtered the signal at \(1.5\times80~\si{\hertz}=120~\si{\hertz}\) using a
+zero-lag 2~\textsuperscript{nd} order Butterworth filter, given that the
+standard only applies to frequencies up to 80~\si{\hertz}.
 %
@@
   \centering
-  \includegraphics[width=160mm]{fig/session001-t2-aula-stroller-maxicosi-cot-0-SeatBotacc_ver.png}
-  \caption{Seat pan vertical acceleration from session 1: Maxi-Cosi Stroller over
-  the Sidewalk Slabs. Black horizontal lines indicate the \(\pm\)RMS
-  boundary.}
+  \includegraphics[width=160mm]{fig/session001-t2-aula-stroller-maxicosi-cot-0-SeatBotacc_ver-rep0.png}
+  \caption{Raw seat pan vertical acceleration versus time from session 001:
+  Maxi-Cosi Street Plus Stroller over the Sidewalk Slabs. Black horizontal lines
+  indicate the \(\pm\)root mean square (RMS) about the mean and grey horizontal
+  lines indicate the \(\pm\)vibration dose value (VDV) about the mean.}
   \label{fig:vert-acc-example}
@@
 
-We calculated the root mean square of the downsampled vertical component of
-acceleration at the seat pan for each trial using Equation~\ref{eq:rms-acc}.
-This quantity gives an indicator of the average vertical acceleration
-experienced at the baby's buttocks for the duration of the trial and can be seen
-in Figure~\ref{fig:vert-acc-example}. RMS acceleration is the primary metric
-recommended by ISO-2631-1 for evaluation of health and comfort in whole body
-vibration.
+ISO 2631-1 provides weighting filters that highlight those frequencies adults
+are most sensitive to. To apply them, we calculated the amplitude spectrum of
+the acceleration time histories of each trial using the Fast Fourier Transform
+(FFT). Figure~\ref{fig:freq-spectrum} gives an example of a raw amplitude
+spectrum along with smoothened versions of the raw and ISO 2631-1 weighted signals. In almost
+all trials, there is a single dominate peak frequency in the ISO weighted and
+smoothed spectra. For the few trials that had two or more peaks at
+approximately the same amplitude, we selected the first one as the peak frequency.
+Additionally, the area under the spectrum curve was calculated and the
+frequency below which 80\% of the amplitude content falls marked as an indicator
+of bandwidth.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/session004-t0-pave-stroller-maxicosi-cot-0-SeatBotacc_ver-rep0.png}
+  \caption{Seat pan vertical acceleration amplitude spectrum from session 004:
+  Maxi-Cosi Street Plus over cobblestones. The gray curve shows the result of
+  the FFT, the red line is a smoothed version of the FFT (zero-lag Butterworth
+  low pass), and the blue line is the smoothed ISO weighted FFT. The orange
+  vertical line indicates the frequency at the maximum amplitude of the smoothed
+  curve. The green vertical line indicates the bandwidth threshold for 80\% of
+  the area under the blue curve.}
+  \label{fig:freq-spectrum}
+\end{figure}
+
+We calculated the root mean square (RMS) over \(N\) samples of the downsampled,
+lowpass filtered, and ISO 2631-1 weighted vertical component of acceleration
+\(a_{w,z}\) at the seat pan for each trial using Equation~\ref{eq:rms-acc} to
+use for the health assessment and the RMS of the magnitude of the acceleration
+vector at the seat pan using Equation~\ref{eq:rms-acc-mag} for the comfort
+assessment, as per ISO 2631-1 guidelines. We set the ISO 2631-1 adjustment
+factor \(k\) equal to 1 for all acceleration components. This quantity gives an
+indication of the average vertical acceleration experienced at the infant's
+buttocks-seat interface for the duration of the trial and can be seen in
+Figure~\ref{fig:vert-acc-example}. RMS acceleration is the primary metric
+recommended by ISO-2631-1 for evaluation of health and comfort in adult whole
+body vibration. We also calculate the vibration dose value (VDV) of the \(M\)
+raw data vertical acceleration \(a_{z}\) samples with Equation~\ref{eq:vdv-acc}
+for Figure~\ref{fig:vert-acc-example}. Lastly, we compute the crest factor of
+the downsampled and low pass filtered vertical acceleration. All of these per
+repetition metrics are reported as mean values over the repetitions
+corresponding to a scenario in Table~\ref{tab:results} in the appendix.
 %
 \begin{align}
-  \textrm{RMS}_{a_z} = \sqrt{\frac{1}{N}\sum_{n=1}^{N} a_z^2(t_n)}
+  \textrm{RMS}_{a_{w,z}} = \sqrt{\frac{1}{N}\sum_{n=1}^{N} a_{w,z}^2(t_n)}
   \label{eq:rms-acc}
@@
 
-We also calculated the frequency spectrum of the vertical acceleration time
-history of each trial using the Fast Fourier Transform (FFT).
-Figure~\ref{fig:freq-spectrum} gives an example of a frequency spectrum. In this
-case, the primary peak frequency is identified to be 6.5~\si{\hertz} and the
-frequency content is mostly contained below about 80~\si{\hertz}.
+\begin{align}
+  \textrm{RMS}_{a_{w,xyz}} = \sqrt{\frac{1}{N}\sum_{n=1}^{N} a_{w,x}^2(t_n) + a_{w,y}^2(t_n) + a_{w,z}^2(t_n)}
+  \label{eq:rms-acc-mag}
+\end{align}
+
+\begin{align}
+  \textrm{VDV}_{a_{z}} = \sqrt{\frac{1}{M}\sum_{m=1}^{M} a_{z}^2(t_m)}
+  \label{eq:vdv-acc}
+\end{align}
+
+\begin{align}
+  \textrm{Crest Factor}_{a_{z}} =\frac{\max|a_{z}(t_m)|}{\sqrt{\frac{1}{M}\sum_{m=1}^{M} a_{z}^2(t_m)}}
+  \label{eq:vdv-acc}
+\end{align}
+
+%% TODO 
+% Explain the analyses conducted on shock test
+
+% Add statistical subsection on analysis methods
+
+\subsection{Statistical Modelling}
+%
+To determine how road surface and stroller setup predict ISO~2631-1 weighted
+vertical RMS acceleration, we fit an ordinary linear least squares model to the
+data using:
+%
+\begin{align}
+  \textrm{RMS}_{a_z} =
+  \beta_0 +
+  \beta_1 x_\textrm{Road Surface} +
+  \beta_2 x_\textrm{Stroller} +
+  \epsilon
+\end{align}
+%
+Both \(x_\textrm{Road Surface}\) and \(\beta_2 x_\textrm{Stroller}\) are
+categorical variables and we select tarmac and the Green Machine as the
+reference values when coding the categorical variables, respectively. We do not
+consider the interaction of road surface and stroller.
+
+To determine how speed, road surface, and cargo bicycle setup predict ISO~2631-1
+weighted vertical RMS acceleration, we fit an ordinary linear least squares
+model to the data using:
+%
+\begin{align}
+  \textrm{RMS}_{a_z} =
+  \kappa_0 +
+  \kappa_1 x_\textrm{Road Surface} +
+  \kappa_2 x_\textrm{Cargo Bicycle} + 
+  \kappa_3 x_\textrm{Speed} +
+  \kappa_4 x_\textrm{Road Surface} \times x_\textrm{Speed} +
+  \epsilon
+\end{align}
+%
+Both \(x_\textrm{Road Surface}\) and \(\kappa_2 x_\textrm{Cargo Bicycle}\) are
+categorical variables and \(x_\textrm{Speed}\) is a continuous variable. and we
+select tarmac and the Keiler, Maxi-Cosi seat, 0 mo infant as the
+reference values when coding the categorical variables, respectively. We do not
+consider the interaction of road surface and cargo bicycle setup, but we do
+consider the interaction of speed with road surface. We use \(p<0.05\) to
+indicate significant difference for both models.
+
+Following fitting the two statistical models, we apply Tukey's Range Test to
+compare vehicle setups among each other for the different road surfaces and
+speed ranges with \(p=0.05\) for the adjusted limit for significance.
+
+\section{Results}
+%
+\subsection{Effect of Speed with Cargo Bicycles}
+%
+Figure~\ref{fig:compare-bicycle-speed} shows the
+variation in ISO 2631-1 weighted vertical RMS acceleration across the tested
+speeds. Acceleration experienced when riding over the paver bricks were always
+larger than for tarmac at the same speed, with the paver bricks showing
+about a 4-5\(\times\) higher acceleration magnitude over tarmac. Over paver bricks, the
+RMS acceleration increased by about 1.6\(\times\) when increasing the speed from
+\SIrange{12}{25}{\kilo\meter\per\hour}. The effect of speed while cycling over tarmac was
+less drastic but also seems to show a slight increase of accelerations over the speed range.
 %
@@
   \centering
-  \includegraphics[width=160mm]{fig/session004-t0-pave-stroller-maxicosi-cot-0-SeatBotacc_ver.png}
-  \caption{Seat pan vertical acceleration frequency spectrum from session 4:
-  Maxi-Cosi Stroller over cobblestones. The gray curve shows the result of the
-  FFT and the blue line is a smoothed version (Butterworth low pass
-  forward/reverse). The orange vertical line indicates the frequency at the
-  maximum amplitude of the smoothed curve. The green vertical line indicates the
-  bandwidth threshold for 80\% of the area under the filtered curve.}
-  \label{fig:freq-spectrum}
-\end{figure}
-
-\section{Results}
-%
-\subsection{Effect of Speed}
-%
-We tested the two cargo bicycles at three different target speeds: 12, 20, and
-25~\si{\kilo\meter\per\hour}. Figure~\ref{fig:compare-bicycle-speed} shows the
-variation in vertical RMS acceleration across the tested speeds. Accelerations
-experienced when riding over the paver bricks are always larger than riding over
-tarmac at the same speed, with the paver bricks having about a 5\(\times\)
-increase in magnitude over tarmac. Over paver bricks, the RMS acceleration
-increases by 1.7\(\times\) when increasing the speed from
-\SIrange{12}{25}{\kilo\meter\per\hour}. The effect of speed while over tarmac is
-less drastic but also increases over the speed range.
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-speed-compare.png}
+  \caption{Seat pan ISO 2631-1 weighted vertical acceleration RMS versus speed
+  for all cargo bicycle repetitions. Shaded regions represent the 95\% confidence
+  intervals from a simple linear regression.}
+  \label{fig:compare-bicycle-speed}
+\end{figure}
+
+\subsection{Effect of Dummy Size}
+%
+
+Figure~\ref{fig:compare-baby-mass} shows the ISO 2631-1 weighted vertical RMS
+acceleration for each repetition for all vehicles, comparing between dummy sizes. There were
+larger accelerations <<<at the seat buttocks and head sites?>>> in the bicycle (high speeds) versus the
+stroller (low speeds), likely mostly attributed to the different testing speeds.
+When comparing the vertical RMS acceleration values between cargo bikes and strollers there are no obvious differences due to baby size, i.e. each dummy size
+experienced a similar range of acceleration magnitudes when vehicle type and and
+road surface are ignored. For the bicycles, the lightest dummy sometimes experienced 
+higher acceleration than the heavier dummy, but high and low accelerations are
+seen across the speed range tested.
 %
@@
   \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-speed-compare.png}
-  \caption{Seat pan vertical acceleration RMS versus speed for all cargo bicycle
-  trials. Shaded regions represent the 95\% confidence intervals from a simple
-  linear regression.}
-  \label{fig:compare-bicycle-speed}
-\end{figure}
-
-\subsection{Effect of Baby Size}
-%
-We tested dummy babies representing ages 0~months (3.5~\si{\kilo\gram}),
-3~months (5.9~\si{\kilo\gram}), and 9~months (8.9~\si{\kilo\gram}).
-Figure~\ref{fig:compare-baby-mass} shows the vertical RMS acceleration for each
-trial for the strollers and the bicycles, comparing the baby size. There are
-larger accelerations experienced in the bicycle versus the stroller, mostly
-attributed to the different testing speeds. When comparing the vertical RMS
-acceleration values within each vehicle type there are no obvious differences
-due to baby size, i.e. each baby size experiences a similar range of
-acceleration magnitudes.
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
+  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration grouped by
+  baby age (and thus size \& mass) for all repetitions with colour indicating the
+  mean speed of the trial. The lightest colour dots are strollers and the remaining
+  are cargo bicycles.}
+  \label{fig:compare-baby-mass}
+\end{figure}
+
+\subsection{Effect of Road Surface}
+%
+Figure~\ref{fig:compare-road-surface} shows ISO 2631-1 weighted vertical RMS
+acceleration from repetitions grouped into the various road surfaces we tested. All
+vehicles were tested on paver bricks and tarmac but only strollers were tested
+on cobblestones and sidewalks. It is notable that tarmac almost always induced lower
+RMS acceleration than other road types regardless of speed and vehicle type. The sidewalk slabs and
+cobblestones have very similar acceleration ranges for all strollers. Paver
+bricks and sidewalk pavers seem to have a similar range of RMS acceleration for
+the same 5~\si{\kilo\meter\per\hour} walking speeds. Paver bricks cause
+relatively large accelerations at high travel speeds in the cargo bicycles.
 %
@@
   \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
-  \caption{Seat pan vertical RMS acceleration grouped by baby age (and thus size
-  \& mass) for all trials with colour indicating the mean speed of the
-  trial.}
-  \label{fig:compare-baby-mass}
-\end{figure}
-
-\subsection{Effect of Road Surface}
-%
-Figure~\ref{fig:compare-road-surface} shows vertical RMS acceleration from
-trials grouped into the various road surfaces we tested. All vehicles were
-tested on tarmac and paver bricks but only strollers were tested on cobblestones
-and sidewalks. It is notable that tarmac almost always has lower RMS
-acceleration regardless of speed and vehicle type. The sidewalk slabs can have
-slightly higher acceleration than cobblestones for the strollers. Paver bricks
-and sidewalk pavers have a similar range of RMS acceleration for the same
-5~\si{\kilo\meter\per\hour} walking speeds. Paver bricks cause relatively large
-accelerations at high travel speeds in the cargo bicycles.
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-road-surface-compare.png}
+  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration grouped by
+  road surface with colour indicating the mean speed of the repetition. The lightest
+  colour dots are strollers and the rest are cargo bicycles.}
+  \label{fig:compare-road-surface}
+\end{figure}
+
+\subsection{Effect of Vehicle Model}
+%
+Figure~\ref{fig:stroller-type-compare} shows the vertical RMS accelerations for
+each road surface for each of the three strollers, lumping seat configurations
+and dummy sizes. The Maxi-Cosi Street Plus and Stokke BABYZEN YOYO 0+ strollers
+have similar mean values across repetitions. The Bugaboo has a slightly lower
+mean for cobblestones, paver bricks, and sidewalk pavers. The Green Machine
+performs better than the modern strollers on paver bricks, but similarly
+otherwise. The Old Rusty performs better than the modern strollers on all
+surfaces except tarmac. All strollers seem to experience the same acceleration
+on tarmac. There may be no significant difference in the acceleration
+experienced in each modern stroller model. All road surfaces compared to tarmac
+cause at least double the RMS acceleration.
 %
@@
   \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-road-surface-compare.png}
-  \caption{Seat pan vertical RMS acceleration grouped by road surface with
-  colour indicating the mean speed of the trial. The lightest colour dots are
-  strollers and the rest are cargo bicycles.}
-  \label{fig:compare-road-surface}
-\end{figure}
-
-\subsection{Effect of Vehicle Model}
-%
-We tested three models of strollers over five different road surfaces.
-Figure~\ref{fig:stroller-type-compare} compares the vertical RMS accelerations
-for each road surface for each of the three strollers. The Maxi-Cosi Street Plus
-and Stokke BABYZEN YOYO 0+ strollers have similar mean values across trials. The
-Bugaboo has a slightly lower mean, but much larger variation in the RMS values.
-There may be no significant difference in the acceleration experienced in each
-stroller model. All road surfaces compared to tarmac cause at least double the
-RMS acceleration.
-%
-\begin{figure}
-  \centering
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-stroller-type-compare.png}
-  \caption{Mean seat pan vertical RMS acceleration per road surface for each
-  stroller. Vertical lines indicate the standard deviation for categories that
-  have more than one trial.} 
+  \caption{Mean seat pan ISO 2631-1 weighted vertical RMS acceleration per road
+  surface for each stroller. Vertical lines indicate the standard deviation for
+  categories that have more than one repetition.} 
   \label{fig:stroller-type-compare}
@@
 tested. Each cargo bicycle was fitted with the same set of two baby seats (Melia
-baby shell and Maxi-Cosi Pebble Pro baby seat). The two-wheel cargo bicycle
-seems to deliver lower acceleration to the seat pan, but the variation in the
-data is large, indicating there may be no significant difference between the two
-vehicles. Both vehicles show increasing vertical RMS acceleration with speed.
+baby shell and Maxi-Cosi Pebble Pro baby seat). On tarmac the two-wheel cargo
+bicycle delivers lower accelerations to the seat pan, but on paver bricks the
+two vehicles show little difference in RMS accelerations. Both vehicles show
+increasing vertical RMS acceleration with speed.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-type-compare.png}
-  \caption{Seat pan vertical RMS acceleration versus speed grouped by road
-  surface and cargo bicycle model. Horizontal lines indicate a linear
-  regression, vertical lines are the standard deviation at those speeds, and
-  shaded regions show the 95\% confidence intervals for the regression.}
+  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration versus speed
+  grouped by road surface and cargo bicycle model. Horizontal lines indicate a
+  linear regression, vertical lines are the standard deviation at those speeds,
+  and shaded regions show the 95\% confidence intervals for the regression.}
   \label{fig:bicycle-type-compare}
@@
 Figure~\ref{fig:peak-freq-dist} shows the dominant frequency compared among road
-surface types for each of the target speeds. Peak frequencies range from
-\SIrange{5}{11}{\hertz} across all trials. For strollers
-(5~\si{\kilo\meter\per\hour}, the median frequency increases from sidewalk
-slabs, to cobblestones, to sidewalk pavers, to tarmac, to paver bricks. With the
-exception of paver bricks being larger than tarmac this increase corresponds to
-an increase in the size of the geometric surface features of the road.
+surface types for each of the target speeds. Peak frequencies range from about
+\SIrange{4}{11}{\hertz} across all trials. For strollers
+(5~\si{\kilo\meter\per\hour}, the median frequency increases from sidewalk slabs
+to cobblestones and sidewalk pavers and then to tarmac and paver bricks. The
+peak frequency median does not correlate sequentially with the geometric width
+of the dimension of the road surface feature. For the cargo bicycles, difference
+in peak frequency between the two road surfaces is not apparent.
 %
@@
   target speed group. The boxes bound the quartiles and indicate the median. The
-  whiskers indicate the 95th perentile and circles are any outliers.}
+  whiskers indicate the 95th percentile and circles are any outliers.}
   \label{fig:peak-freq-dist}
@@
 
-Figure~\ref{fig:thresh-freq-dist} gives a general indication of bandwidth
-distributions for each of the target speed groups. Most frequency content is
-below 100~\si{\hertz} for the all trials. The median threshold frequency across
-all trials is 70~\si{\hertz} which gives an idea of the bandwidth for the
-vibrations of interest.
+Figure~\ref{fig:thresh-freq-dist} gives a general indication of bandwidth (80\%
+of the amplitude spectrum content) distributions for each of the target speed
+groups. Most frequency content is below 45~\si{\hertz} for all trials. The
+median bandwidth across all trials is 20~\si{\hertz}.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-thresh-freq-dist.png}
-  \caption{Threshold frequency  (based on 80\% of the area under the filtered
-  frequency spectrum) for each target speed group.}
+  \caption{Bandwidth (based on 80\% of the area under the filtered \textbf{}amplitude spectrum) for each target speed group.}
   \label{fig:thresh-freq-dist}
@@
 
-\subsection{Overall Comparison}
-We tabulate the seat pan vertical RMS acceleration, trial duration, peak
-frequency, and threshold frequency for all 52 combinations of vehicle setup,
-road surface, and target speed in Table~\ref{tab:results}.
-Figure~\ref{fig:compare-all} shows the vertical RMS acceleration of all trials
-broken down by vehicle setup (vehicle, seat, baby age), road surface, trial
-duration, and travel speed. Some additional insights can be gathered from this
-figure, that are not seen in the prior figures.
-%
-\begin{itemize}
-    \item The baby in stroller travelling at 5~\si{\kilo\meter\per\hour} over
-    cobblestones and sidewalks slabs cracks can experience accelerations of
-    similar magnitude to a baby in a cargo bicycle travelling at
-    12~\si{\kilo\meter\per\hour} over paver bricks.
-    \item A 3 month old baby in a baby shell (Melia) travelling over brick
-    pavers at high speeds has lower RMS acceleration than the same baby in a car
-    seat (Maxi-Cosi Pebble Pro) in the Urban Arrow and it may also be true for
-    the Keiler tricycle. Switching to the baby shell in the Urban Arrow has a
-    similar effect to reducing speed by 10~\si{\kilo\meter\per\hour}.
-\end{itemize}
-
-\begin{table}
-  \centering
-  \caption{Computed metrics for all 52 scenarios measured.}
-  \label{tab:results}
+\subsection{Health Assessment}
+%
+Figures \ref{fig:health-stroller} and \ref{fig:health-bicycle} show the ISO
+2631-1 weighted vertical acceleration at the seat pan for all trials of the
+stroller and cargo bicycles, respectively. The horizontal lines in the figure
+correspond to the boundary of the ``health caution zone'' in the standard, which
+has a dependence on exposure duration. If acceleration values are above a given
+threshold, ISO 2631-1 states that ``health risks are likely'' for adults in
+erect seating postures for a continuous daily dose.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-rms-stroller-compare-all.png}
+  \caption{ISO 2631-1 weighted seat pan vertical RMS acceleration of all
+  stroller repetitions with colour representing road surface. The horizontal grey
+  lines with time duration indicators are the upper bound of the ISO 2631-1
+  ``health caution zone'' for adults seated erectly experiencing vibrations for
+  continuous duration in a daily dose.}
+  \label{fig:health-stroller}
+\end{figure}
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-rms-bicycle-compare-all.png}
+  \caption{ISO 2631-1 weighted seat pan vertical RMS acceleration of all cargo
+  bicycle trials with colour representing road surface and marker style
+  indicating the target speed. The horizontal grey lines with time duration
+  indicators are the upper bound of the ISO 2631-1 ``health caution zone'' for
+  adults seated erectly experiencing vibrations for continuous duration in a
+  daily dose.}
+  \label{fig:health-bicycle}
+\end{figure}
+
+For the strollers, all vibration measurements were below the health caution zone
+boundary if the daily continuous exposure is less than 10~\si{\minute}.
+Additionally, all vehicles pushed over tarmac were still below the zone if the
+daily continuous exposure is less than 4~\si{\hour}. Pushing the Bugaboo and
+Maxi-Cosi with a 0 month infant or the Stokke with a 9 month infant over
+cobblestones and sidewalk slabs may have health risks if the duration exceeds
+20~\si{\minute}. For almost all of the strollers pushing over any surface but
+tarmac exceeded the 1~\si{\hour} risk boundary. Notably the Bugaboo and Old
+Rusty with a 9 month infant fell under the 1~\si{\hour} threshold for all
+surfaces. The 0 month dummy experienced worse accelerations than the 9 month
+dummy in the Bugaboo and Maxi-Cosi, but that was opposite for the Stokke YOYO.
+Old rusty showed the least overall acceleration magnitudes.
+
+For both cargo bicycles the accelerations exceeded the 10~\si{\minute} health
+risk threshold when ridden above 20~\si{\kilo\meter\per\hour} on paver bricks
+and exceeded the 1~\si{\hour} health risk threshold when ridden more than
+1~\si{\hour} above 12~\si{\kilo\meter\per\hour} on paver bricks. All but the
+Keiler with the Maxi-Cosi seat and the 0 month dummy were under the 1~\si{\hour}
+threshold for riding on tarmac at any target speed. Only the Urban Arrow with
+the 3 month dummy is under the 4~\si{\hour} threshold when ridden at
+12~\si{\kilo\meter\per\hour}. The accelerations may be less when using the
+Meila Baby Shell seat versus the Maxi-Cosi car seat.
+
+\subsection{Comfort Assessment}
+%
+ISO~2631-1 recommends using the magnitude of the weighted seat pan acceleration
+vector for comfort assessment. Figures \ref{fig:comfort-stroller} and
+\ref{fig:comfort-bicycle} plot RMS of the acceleration magnitude along with the
+comfort indicators provided in the standard that are based on adults seated in
+public transit for an unspecified duration.
+
+When following the threshold definitions from the ISO~2631-1 guidelines, for the
+strollers, all vehicles and surfaces are at least ``a little uncomfortable''.
+The other strollers are ``fairly uncomfortable'' on tarmac. All other road
+surfaces are at least ``very uncomfortable''. The Bugaboo 9 month, Green Machine
+0 month over paver bricks and Old Rusty 9 month over paver bricks, sidewalk
+pavers, and sidewalk slabs are ``very uncomfortable'', but all other strollers
+and surfaces are ``extremely uncomfortable''.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-rms-comfort-stroller-compare-all.png}
+  \caption{ISO 2631-1 weighted seat pan magnitude RMS acceleration of all
+  stroller repetitions with colour representing road surface. The horizontal
+  brown lines with the upper bound of the ISO 2631-1 ``comfort zones'' for
+  adults seated erectly experiencing vibrations in public transit.}
+  \label{fig:comfort-stroller}
+\end{figure}
+
+Both of the two cargo bicycles ridden at any tested speed over paver bricks, as
+well as the Keiler with the Maxi-Cosi seat over tarmac at the high speeds  fall
+into the category ``extremely uncomfortable''. The other vehicle setups fall
+between ``fairly uncomfortable'' and ``very uncomfortable'' over tarmac for the
+range of speeds. The Urban Arrow with the Melia Baby Shell performs, on average,
+the best on paver bricks and tarmac.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-rms-comfort-bicycle-compare-all.png}
+  \caption{ISO 2631-1 weighted seat pan magnitude RMS acceleration of all cargo
+  bicycle repetitions with colour representing road surface and marker style
+  representing target speed. The horizontal brown lines with the upper bound of
+  the ISO 2631-1 ``comfort zones'' for adults seated erectly experiencing
+  vibrations in public transit.}
+  \label{fig:comfort-bicycle}
+\end{figure}
+
+\subsection{Shock test}
+%
+We conducted shock tests by riding the bicycle or pushing the strollers over a
+square-section bump of 30x30 mm, at different speeds. The analysis focuses on
+the maximum peak of the seat pan acceleration. Starting from the events' time
+histories (Figure \ref{fig:shock_time-history}), we identified the peak
+acceleration values for each trial, then averaged them to obtain the results
+listed in Table \ref{tab:shock} for different vehicles and configurations. There
+is a significant variation among tests, with the peaks for the bicycles
+sometimes reaching the accelerometer's full scale (16~g). While the seat pan
+accelerations for the strollers are generally lower than those experienced with
+the bicycles, the configuration (0 or 9 months) may play a large role. Strollers
+with the baby seat configuration for 9 months show much lower accelerations
+compared to the baby cot for 0 month (Bugaboo and Maxi-Cosi). Surprisingly, the
+oldest strollers (Old Rusty and Green Machine) performed very well during the
+shock test, resulting in the lowest seat pan acceleration among all the tested
+vehicles.
+Figure \ref{fig:shock_vehicle_comparison} shows the peaks of the vertical acceleration recorded at the seat pan, grouped by different vehicles, for the shock test.
+As already noted in Table \ref{tab:shock}, the old strollers Old Rusty and Green Machine show lower acceleration values.
+We do not clearly distinguish any trend with the speed for the bicycles (``keiler'' and ``urbanarrow'').
+%
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-trike-maxicosi-0-SeatBotacc_ver-rep0.png}
+  \caption{Raw seat pan vertical acceleration versus time from session 015: Keiler tricycle during the shock test.}
+  \label{fig:shock_time-history}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-shock-test-compare.png}
+  \caption{Maximum vertical acceleration recorded at the seat pan during the shock test, grouped by vehicles.
+The colour indicates the mean speed of the trial.
+The lighter the colour the lower the speed.}
+  \label{fig:shock_vehicle_comparison}
+\end{figure}
+
+\begin{table}[ht]
+  \centering
+  \caption{Maximum seat pan acceleration [m/s²] recorded for shock test, for different vehicles and baby masses.}
+  \label{tab:shock}
   \footnotesize
-\begin{tabular}{lllcccccc}
+  \begin{tabular}{lllrrrr}
     \toprule
-        &            &              &        &       & Mean         &          & Mean      & Mean      \\
-Vehicle & Seat, Baby & Road Surface & Target & Trial & RMS          & Mean     & Peak      & Threshold \\
-        &            &              & Speed  & Count & Acceleration & Duration & Frequency & Frequency \\
-        &            &              & [km/h] &       &  [m/s\(^2\)]     & [s]      & [Hz]      & [Hz]      \\
+     & &  & Target Speed & Trial Count & Max Acceleration \\
+    Vehicle Type & Model & Seat, Baby & [km/h] & & [m/s²] \\
     \midrule
-\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 2 & 4.4 & 39.8 & 6.6 & 22.6 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 1 & 2.6 & 70.5 & 10.7 & 25.1 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 1 & 2.9 & 51.6 & 8.2 & 119.5 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 3 & 4.8 & 20.0 & 5.8 & 41.8 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 0.7 & 24.9 & 9.9 & 61.5 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 2.5 & 42.0 & 6.8 & 46.5 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 1 & 2.3 & 66.9 & 9.7 & 57.5 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 1 & 1.7 & 71.3 & 7.6 & 47.4 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 3 & 2.4 & 23.9 & 6.0 & 47.1 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 0.6 & 33.2 & 8.4 & 68.9 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
-\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 1 & 4.6 & 81.7 & 6.6 & 82.3 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 1 & 3.2 & 61.5 & 10.6 & 75.6 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 1 & 3.0 & 51.0 & 7.8 & 79.7 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 5 & 4.5 & 12.3 & 5.7 & 80.3 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 0.9 & 29.4 & 10.5 & 56.5 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 5 & 4.2 & 12.6 & 7.8 & 65.8 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 2 & 3.0 & 26.0 & 9.8 & 79.6 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 1 & 2.6 & 54.8 & 6.8 & 67.1 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 3 & 3.2 & 23.0 & 6.9 & 70.4 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 1.0 & 33.6 & 10.2 & 70.7 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
-\multirow[t]{12}{*}{trike} & \multirow[t]{4}{*}{maxicosi, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 7.2 & 47.6 & 8.0 & 44.9 \\
- &  &  & 20 & 1 & 11.1 & 35.3 & 6.4 & 101.6 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.9 & 73.7 & 8.1 & 23.8 \\
- &  &  & 20 & 1 & 2.7 & 58.4 & 6.5 & 18.8 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{4}{*}{maxicosi, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 6.8 & 57.8 & 7.9 & 72.3 \\
- &  &  & 20 & 1 & 9.8 & 42.8 & 7.1 & 87.2 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.5 & 55.6 & 7.6 & 31.7 \\
- &  &  & 20 & 1 & 2.1 & 47.6 & 6.2 & 19.2 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 5.8 & 52.6 & 8.9 & 100.5 \\
- &  &  & 20 & 1 & 10.2 & 46.0 & 6.9 & 120.9 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.2 & 50.8 & 7.9 & 91.1 \\
- &  &  & 20 & 1 & 1.6 & 45.2 & 8.1 & 72.8 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
-\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 6.6 & 62.3 & 7.6 & 110.4 \\
- &  &  & 20 & 1 & 9.2 & 39.1 & 8.0 & 71.6 \\
- &  &  & 25 & 1 & 11.4 & 38.3 & 7.1 & 117.5 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.4 & 58.1 & 8.7 & 28.9 \\
- &  &  & 25 & 1 & 2.1 & 43.1 & 10.0 & 28.5 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{5}{*}{maxicosi, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 5.2 & 58.2 & 7.9 & 85.7 \\
- &  &  & 20 & 1 & 10.6 & 32.1 & 4.9 & 102.8 \\
- &  &  & 25 & 1 & 10.5 & 30.3 & 6.2 & 99.3 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.1 & 50.7 & 8.8 & 37.8 \\
- &  &  & 25 & 1 & 1.6 & 43.2 & 9.6 & 31.8 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 4.6 & 48.3 & 6.8 & 36.6 \\
- &  &  & 20 & 1 & 6.9 & 36.8 & 7.8 & 51.1 \\
- &  &  & 25 & 1 & 7.5 & 31.7 & 9.2 & 60.6 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.0 & 61.2 & 8.5 & 66.5 \\
- &  &  & 25 & 1 & 1.4 & 45.9 & 9.7 & 41.7 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
-\multirow[t]{5}{*}{yoyo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 18.1 & 6.6 & 91.1 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 1 & 2.8 & 57.8 & 9.7 & 123.9 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 2 & 2.6 & 32.5 & 6.5 & 98.9 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 2 & 4.0 & 25.7 & 5.1 & 103.8 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 0.8 & 18.1 & 7.4 & 156.6 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
+    Strollers & Bugaboo & Cot, 0 mo  & 5 & 2 & 145.599 \\
+              &         & Seat, 9 mo & 5 & 4 & 49.329 \\
+    \cline{2-6}
+              & Maxi-Cosi & Cot, 0 mo  & 5 & 2 & 131.184 \\
+              &           & Seat, 9 mo & 5 & 4 & 34.941 \\
+    \cline{2-6}
+              & Stokke BABYZEN YOYO & Cot, 0 mo  & 5 & 4 & 34.983 \\
+              &                     & Seat, 9 mo & 5 & 4 & 50.614 \\
+    \cline{2-6}
+              & Green Machine & Cot, 0 mo & 5 & 4 & 17.430 \\
+    \cline{2-6}
+              & Old Rusty & Seat, 9 mo & 5 & 4 & 31.100 \\
+    \cline{1-6}
+    Bicycles & Keiler tricycle & Melia, 3 mo & 5 & 2 & 52.248 \\
+
+             &               & Melia, 3 mo & 12 & 2 & 85.209 \\
+
+             &               & Melia, 3 mo & 20 & 2 & 123.592 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 0 mo & 5 & 2 & 112.755 \\
+
+             &               & Maxi-Cosi, 0 mo & 12 & 2 & 139.623 \\
+
+             &               & Maxi-Cosi, 0 mo & 20 & 2 & 115.345 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 3 mo & 5 & 2 & 151.469 \\
+
+             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160.000 \\
+
+             &               & Maxi-Cosi, 3 mo & 20 & 2 & 145.013 \\
+    \cline{2-6}
+             & Urban Arrow & Melia, 3 mo & 5 & 2 & 42.742 \\
+
+             &               & Melia, 3 mo & 12 & 2 & 42.688 \\
+
+             &               & Melia, 3 mo & 25 & 2 & 42.3917 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 0 mo & 5 & 1 & 50.433 \\
+
+             &               & Maxi-Cosi, 0 mo & 12 & 2 & 63.439 \\
+
+             &               & Maxi-Cosi, 0 mo & 25 & 2 & 130.491 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 3 mo & 5 & 2 & 156.429 \\
+
+             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160.000 \\
+
+             &               & Maxi-Cosi, 3 mo & 25 & 2 & 160.000 \\
     \bottomrule
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-compare-all.png}
-  \caption{Scatter plot of the vertical RMS acceleration of all trials broken
-  down by vehicle setup, trial duration, road surface, and plotted versus
-  speed.}
-  \label{fig:compare-all}
-\end{figure}
-
-\section{Conclusion}
+\subsection{Statistical Results}
+%
+Table~\ref{tab:stroller-ols} shows the results of the 11 DoF stroller model for
+the 104 trials (\(R^2=0.867,F=54.69\)). Both categorical variables have
+significant effects. The intercept gives the mean acceleration of the Green
+Machine stroller pushed over tarmac, which is not significant. All road surfaces
+cause significantly more acceleration than tarmac with cobblestones having the
+largest relative effect (3.0~\si{\mps\squared} larger), followed by sidewalk
+slabs (2.7~\si{\mps\squared} larger), sidewalk pavers (1.8~\si{\mps\squared}
+larger), and paver bricks (1.6~\si{\mps\squared} larger). The Bugaboo, Seat, 9
+mo and Maxi-Cosi, Seat, 9 mo are not significantly different than the Green
+Machine, Cot, 0 mo but the other strollers are. The Old Rusty, Seat, 9 mo and
+Bugaboo, Cot, 0 mo showed lower RMS acceleration than Green Machine, Cot, 0 mo
+by 0.8 and 0.5~\si{\mps\squared}, respectively. The remaining strollers have
+larger accelerations than the Green Machine, Cot, 0 Mo on tarmac: Maxi-Cosi,
+Cot, 0 mo (1.1~\si{\mps\squared}), Bugaboo, Cot, 0 mo (1.0~\si{\mps\squared}),
+YOYO, Seat, 9 mo (1.0~\si{\mps\squared}), and YOYO, Seat, 0 mo
+(0.6~\si{\mps\squared}).
+%
+\begin{table}
+  \centering
+  \caption{Ordinary Linear Regression Results for Stroller. Tarmac and Green Machine Cot month are the references for the categorical Road Surface and Vehicle Setup variables.}
+  \label{tab:stroller-ols}
+  \footnotesize
+\begin{tabular}{lcccccc}
+& \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$> |$t$|$} & \textbf{[0.025} & \textbf{0.975]}  \\
+\midrule
+\textbf{Intercept}                                                                                     &       0.2212  &        0.188     &     1.177  &         0.242        &       -0.152    &        0.595     \\
+Cobblestones                                     &       3.0117  &        0.163     &    18.473  &         0.000        &        2.688    &        3.336     \\
+Paver Bricks                                     &       1.6000  &        0.172     &     9.299  &         0.000        &        1.258    &        1.942     \\
+Sidewalk Pavers                                  &       1.7566  &        0.174     &    10.092  &         0.000        &        1.411    &        2.102     \\
+Sidewalk Slabs                                   &       2.7754  &        0.167     &    16.637  &         0.000        &        2.444    &        3.107     \\
+bugaboo, cot, 0 mo   &       0.9706  &        0.202     &     4.813  &         0.000        &        0.570    &        1.371     \\
+bugaboo, seat, 9 mo  &      -0.5065  &        0.199     &    -2.551  &         0.012        &       -0.901    &       -0.112     \\
+maxicosi, cot, 0 mo  &       1.0795  &        0.202     &     5.353  &         0.000        &        0.679    &        1.480     \\
+maxicosi, seat, 9 mo &       0.3012  &        0.209     &     1.441  &         0.153        &       -0.114    &        0.716     \\
+oldrusty, seat, 9 mo &      -0.7551  &        0.209     &    -3.605  &         0.001        &       -1.171    &       -0.339     \\
+yoyo, cot, 0 mo]     &       0.5766  &        0.209     &     2.753  &         0.007        &        0.161    &        0.993     \\
+yoyo, seat, 9 mo     &       0.9706  &        0.205     &     4.731  &         0.000        &        0.563    &        1.378     \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Table~\ref{tab:bicycle-ols} shows the results of the 8 DoF cargo bicycle model
+for the 50 trials (\(R^2=0.925,F=63.17\)). The vehicle setup categorical variable
+has significant effects, the road surface categorical variable alone does not,
+but the speed and interaction of speed with road surface do have significant
+effects. The intercept should theoretically be zero, because there is no
+vertical vibration when the speed is zero. The intercept is not significantly
+different than zero. Speed is not a significant predictor on tarmac, but the
+interaction variable shows that 0.8~\si{\mps\squared} is gained in
+acceleration for each 1~\si{\kph} increase on paver bricks. We see
+that only the Urban Arrow with the 3 mo infant in either seat has significant
+difference to the Keiler, Maxi-Cosi, 3 m, both showing reduction in relative acceleration.
+%
+\begin{table}
+  \centering
+  \caption{Ordinary Linear Regression Results for Cargo Bicycle. Tarmac and
+  Keiler Maxi-Cosi 3 mo are the references for the categorical Road Surface and
+  Vehicle Setup variables.}
+  \label{tab:bicycle-ols}
+  \footnotesize
+\begin{tabular}{lcccccc}
+& \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$> |$t$|$} & \textbf{[0.025} & \textbf{0.975]}  \\
+\midrule
+\textbf{Intercept}                                                                                          &       0.8067  &        0.643     &     1.255  &         0.216        &       -0.491    &        2.104     \\
+Paver Bricks                                          &       1.2956  &        0.889     &     1.457  &         0.153        &       -0.500    &        3.091     \\
+keiler, maxicosi, 0 mo     &       0.8664  &        0.415     &     2.085  &         0.043        &        0.027    &        1.705     \\
+keiler, melia, 3 mo        &      -0.5060  &        0.415     &    -1.219  &         0.230        &       -1.344    &        0.332     \\
+urbanarrow, maxicosi, 0 mo &      -0.0512  &        0.404     &    -0.127  &         0.900        &       -0.867    &        0.764     \\
+urbanarrow, maxicosi, 3 mo &      -0.8895  &        0.415     &    -2.141  &         0.038        &       -1.728    &       -0.051     \\
+urbanarrow, melia, 3 mo    &      -1.1357  &        0.403     &    -2.819  &         0.007        &       -1.949    &       -0.322     \\
+Mean Speed [m/s]                                                                              &       0.2034  &        0.116     &     1.747  &         0.088        &       -0.032    &        0.439     \\
+Mean Speed\(\times\)Road Surface                    &       0.7803  &        0.180     &     4.338  &         0.000        &        0.417    &        1.144     \\
+\bottomrule
+\end{tabular}
+  \end{table}
+
+\paragraph{Vehicle Comparisons}
+%
+Given that the vehicle setup is a significant effect, we can look at a posthoc
+analysis to compare vehicles on each road surface.
+Table~\ref{tab:sig-group-stroller}, derived from
+Figure~\ref{fig:tukey-stroller}, shows the groupings of non-significant
+comparisons. Old Rusty, Bugaboo with 9 month, and the Green Machine perform
+generally better (significantly) that the other vehicles. For cobblestones, this
+is true as well as: 1) the YOYO 9 month is the worse along with the heavier baby
+performing worst than the lighter baby in the YOYO, 2) the heavier baby sees
+less acceleration for the Bugaboo and Maxicosi. For paver bricks: 1) Old Rusty,
+Bugaboo 9 mo, and Green Machine are the best and 2) Stokke 9 mo sees more than
+the 0 mo. For sidewalk pavers, there is no significant difference among the
+strollers. For side walk slabs: 1) Old Rusty is the best and Bugaboo the second
+best, 2) the 0 month in the Bugaboo and Maxi-Cosi see more than the 9 month in
+the same vehicle, respectively, and 3) no difference in the YOYO when comparing
+baby ages. For tarmac: the Green Machine, Bugaboo 9 mo, and YOYO 9 mo are better
+than Maxi-cosi with either baby age and 2) the Green Machine is better than the
+Bugaboo 0 mo.
+%
+\begin{table}
+\centering
+\caption{Stroller Significance Ranking Groups (based on
+Figure~\ref{fig:tukey-stroller}). The numbers indicate the group where there is
+no significant difference with 1 being the best (lower acceleration) and 8 being
+the worst (higher acceleration).}
+\label{tab:sig-group-stroller}
+\begin{tabular}{lccccc}
+  \toprule
+  Vehicle Setup                 & Cobblestones & Paver Bricks & Sidewalk Pavers & Sidewalk Slabs & Tarmac \\
+  \midrule
+  yoyo, seat, 9 mo         & 8            & 6-8          & 1-8             & 5-6            & 1-6 \\
+  yoyo, cot, 0 mo          & 4-5          & 3-5          & 1-8             & 5-6            & 1-8 \\
+  oldrusty, seat, 9 mo     & 1-2          & 1-3          & 1-8             & 1              & 1-8 \\
+  maxicosi, seat, 9 mo     & 4-5          & 3-6          & 1-8             & 3-4            & 4-8 \\
+  maxicosi, seat, 0 mo     & 6-7          & 6-8          & 1-8             & 7-8            & 4-8 \\
+  greenmachine, cot, 0 mo  & 3            & 1-3          & 1-8             & 3-4            & 1-4 \\
+  bugaboo, seat, 9 mo      & 1-2          & 1-3          & 1-8             & 2              & 1-6 \\
+  bugaboo, cot, 0 mo       & 6-7          & 3-6          & 1-8             & 7-8            & 2-8 \\
+  \bottomrule
+\end{tabular}
+\end{table}
+
+When comparing the cargo bicycles, Table~\ref{tab:sig-group-bicycle}, most
+vehicle setups deliver similar acceleration to the seat pan when ridden over the
+same surface at the same target speed. For low speed on tarmac, the Urban Arrow
+with the Meila Baby Shell and a 3 month has significantly less acceleration than
+the Keiler with the Maxicosi anda 0 month baby. There is no significant
+difference in any vehicle setups at low speed on paver bricks. At higher speeds,
+the Urban Arrow and Kiler with the Meila seat and the 3 month is significantly
+better than the Keiler with the Maxicosi and the 0 month on paver bricks and on
+tarmac. It is important to point out that there is no significant difference
+when simply swapping the seat for the 3 month old.
+%
+\begin{table}
+\centering
+\caption{Cargo Bicycle Significance Ranking Groups (based on
+Figure~\ref{fig:tukey-bicycle}). The numbers indicate the group where there is
+no significant difference with 1 being the best (lower acceleration) and 6 being
+the worst (higher acceleration).}
+\label{tab:sig-group-bicycle}
+\begin{tabular}{lcccc}
+     \toprule
+                                & Paver Bricks & Tarmac    & Paver Bricks & Tarmac \\
+     Vehicle Setup              & Low Speed    & Low Speed & High Speed   & High Speed \\
+     \midrule
+     urbanarrow, melia, 3 mo    & 1-6 & 1-5 & 1-5 & 1-5\\
+     urbanarrow, maxicosi, 3 mo & 1-6 & 1-6 & 1-5 & 1-5\\
+     urbanarrow, maxicosi, 0 mo & 1-6 & 1-6 & 1-6 & 1-5\\
+     keiler, melia, 3 mo        & 1-6 & 1-6 & 1-5 & 1-5\\
+     keiler, maxicosi, 3 mo     & 1-6 & 1-6 & 1-6 & 1-6\\
+     keiler, maxicosi, 0 mo     & 1-6 & 2-6 & 3-6 & 4-6\\
+     \bottomrule
+\end{tabular}
+\end{table}
+
+\section{Discussion \& Conclusion}
 %
 We have presented a comprehensive set of acceleration measurements from
-experiments that simulate the vibrations experienced by babies in the 0-9 month
-age range during transportation via strollers and cargo bicycles. We compare the
-average magnitude of vertical acceleration at the seat pan across a variety of
-road surfaces and seats while moving at typical vehicle travel speeds. In this
-preliminary analysis, we report on the variation among the various independent
-variables, finding that average acceleration can be relatively large for some
-scenarios. We only report the characterization of the accelerations experienced
-by the baby and do not weigh in on whether these can cause discomfort or have
-negative health consequences. There is a large gap in the literature connecting
-acceleration magnitude to discomfort and/or health consequences.
-
-We show that average acceleration can range from
-\SIrange{0.5}{11.4}{\meter\per\second\squared} across all tested scenarios.
-Strollers experience \SIrange{0.5}{5.3}{\meter\per\second\squared} average
-acceleration for a mean walking speed of 5.2~\si{\kilo\meter\per\hour}. Cargo
-bicycles experience \SIrange{1.0}{11.4}{\meter\per\second\squared} over a speed
-range of \SIrange{12}{25}{\kilo\meter\per\hour}.
-
+experiments that simulate the vibrations experienced by dummy infants in the 0-9
+month mass range during transportation in both strollers and cargo bicycles. We
+compared the average magnitude of vertical and total acceleration at the seat
+pan across a variety of road surfaces and seats while moving at typical vehicle
+travel speeds. ISO weighted average acceleration can range from
+\SIrange{0.4}{10.7}{\mps\squared} across all tested scenarios. Strollers induced
+\SIrange{0.4}{5.0}{\mps\squared} average acceleration for a mean walking speed
+of 5.3~\si{\kph}. Cargo bicycles induced \SIrange{0.6}{10.7}{\mps\squared} over
+a speed range of \SIrange{12}{25}{\kph}. Our investigation compared different
+road surfaces, different stroller and cargo bicycle brands and types, and
+different speeds for cargo bicycles.
+
+\subsection{Surface \& Speed}
+%
 Travelling over a tarmac surface offers the least vibration to all vehicle types
 at any speed with a maximum average acceleration of
-2.7~\si{\meter\per\second\squared}. For strollers, travelling over surfaces
-rougher than tarmac at normal walking speed can cause from 1.6\(\times\) to
-6.6\(\times\) the accelerations experienced on tarmac with average accelerations
-reaching 5.3~\si{\meter\per\second\squared}. Cobblestones and the large gaps of
-the sidewalk slabs cause the largest magnitude vibrations to the baby in the
-strollers. For cargo bicycles, travelling over paver bricks at the same speeds
-can quadruple the magnitude of the average acceleration the baby experiences.
-Travelling at the maximum allowed speed of an electric cargo bike (25
-\si{\kilo\meter\per\hour}) over paver bricks causes the baby to experience
-average accelerations exceeding 8~\si{\meter\per\second\squared}. The effect of
-speed on vibration is higher for paver bricks than tarmac.
-
-The size of the baby (mass and shape) has no obvious effect on the average
-accelerations experienced at the seat pan body-seat interface. These vibrations
-are transmitted to the baby's body and the physical properties (mass, stiffness,
-damping) of the baby's body determine whether this excitation is amplified or
-not and to which body segment is more affected. Tests with more realistic
-dummies or real babies is necessary to know how the baby itself moves when
+1.2~\si{\meter\per\second\squared}. For strollers, travelling over surfaces
+rougher than tarmac at normal walking speed can cause on average 5\(\times\) the
+acceleration experienced on tarmac with average accelerations reaching
+5.0~\si{\meter\per\second\squared}. Cobblestones and the large gaps in the
+sidewalk slabs caused the largest magnitude of vibrations at the seat pan in the
+strollers. Cobblestones and sidewalk slabs approximately double the vibration
+amplitude relative to sidewalk paver and paver bricks, with them all being
+significant larger than tarmac vibrations.
+
+For cargo bicycles, travelling over paver bricks at the same speeds
+can quadruple the magnitude of the average acceleration the dummy experiences.
+Travelling at the maximum allowed speed of an electric cargo bike (25 \si{\kph})
+over paver bricks caused the dummy to experience average accelerations exceeding
+8~\si{\mps\squared}. The effect of speed on vibration is significant for paver
+bricks but not for tarmac. Cobblestones
+
+Whereas speed strongly affected the acceleration amplitude it does not strongly
+affect the peak frequency and the bandwidth below which 80\% of power is
+contained. This suggests that peak frequencies represent oscillations induced by
+the systems tested rather than dominant frequencies resulting from the road
+surface.
+
+\subsection{Baby Mass}
+%
+The size of the dummy (mass and build) had no obvious effect on the average
+acceleration at the seat pan body-seat interface. These vibrations
+are transmitted to an infant's body and the physical properties (mass, stiffness,
+damping) of the infant's body determine whether this excitation is amplified or
+not and which body segment is more affected. Tests with more realistic
+dummies or realinfants are necessary to investigate how the infant itself moves when
 excited by this level of vibration. This information is not readily available in
-the literature and may be hard to perform due to ethical limitations and absence
-of realistic dummies.
-
-When comparing stroller and cargo bicycle vehicle setups (vehicle, seat, baby
-age) among each other, the preliminary results show no obvious differences in
-the acceleration experienced by the baby other than the baby shell being better
-than a baby car seat for the 3 month old baby in the cargo bike at the maximum
-speeds. This may be attributed to the suspended mounting location of the baby
-seat in the cargo bay versus the baby shell being mounted to the existing bench
-in the cargo bay. Statistical analysis may reveal more nuance differences among
-the vehicle setups.
-
-We also investigated the dominant frequency and bandwidth of vibrations across
-the various scenarios. Vibrations at frequencies between
-\SIrange{4.9}{10.7}{\hertz} have the largest magnitude contribution to the
-vibrations but there is frequency content of magnitudes of interest in a
-bandwidth of up to 100~\si{\hertz}.
-
-We measured four other sensors on the vehicles, all with six accelerometer and
-gyroscope time histories, for a total of 30 time histories of possible interest.
-This paper provides a look into the experiments via three metrics: vertical RMS
-acceleration, peak frequency, and bandwidth of effectively one of the 30 time
-histories. There are a variety of other metrics that can provide insight, for
-example vibration dosage value and crest factor that characterize peak
-accelerations or ISO 2631-1 weighted linear and rotational accelerations that
-have more connection to experienced comfort. Future work will investigate these
-more closely as well as shock effects and apply standard statistical models to
-the data to make more definitive conclusions in the scenario comparisons.
+the literature and may be hard to acquire due to ethical limitations and the
+absence of validated infant dummies. The only effect that stood out for mass,
+was that the lighter dummy has less acceleration than the heavier dummy for the
+YOYO stroller.
+
+\subsection{Health}
+%
+The vibrations measured in the different scenarios showed that average
+acceleration can be relatively large when compared to the smoothest experience
+on tarmac. There is a large gap in the literature connecting acceleration
+magnitude to discomfort and/or health consequences, which is in particular
+absent for infants. The most used health and comfort assessment tool for whole body vibration is the ISO~2631-1 standard. When we investigated health risks using the standard we found that:
+%
+\begin{itemize}
+    \item only strollers pushed over tarmac at 5~\si{\kph} had
+    average acceleration below the ``health risk zone'' for 4~\si{\hour} daily
+    duration
+    \item strollers pushed over cobblestones and pavers can deliver
+    accelerations in the health risk zone with durations as short as
+    20~\si{\min}
+    \item cargo bicycles ridden at \SIrange{12}{25}{\kph} over tarmac
+    overwhelmingly delivered accelerations below the 1~\si{\hour} ``health risk
+    zone''
+    \item cargo bicycles ridden at \SIrange{12}{25}{\kph} over paver bricks
+    delivered accelerations well into the 10~\si{\min} ``health risk zone''
+\end{itemize}
+%
+We can conclude that strollers should be pushed slower than 5~\si{\kph} over
+non-tarmac road surfaces and for continuous durations less than 10~\si{\min}.
+Cargo bicycles carrying infants should slow down less than 12~\si{\min} over
+paver bricks and/or the duration should be kept under 10~\si{\min}. When riding
+a cargo bicycle over tarmac durations should be kept under 1~\si{\hour}.
+
+\subsection{Comfort}
+%
+When considering comfort, the ISO~2631-1 guidelines indicate that adults would
+report the vibrations experienced in strollers and bicycles as uncomfortable.
+For strollers, the vibrations over tarmac would be rated ``fairly
+uncomfortable'' and all other road surfaces would be ``very'' or ``extremely
+uncomfortable''. When riding a cargo bicycle over paver bricks, the vibrations
+would be rated as ``extremely uncomfortable'' and over tarmac spans ``fairly``
+to ``extremely''. The ISO comfort rating scale is derived from adult subjective
+ratings of vibrations felt when riding public transit for an unspecified
+duration, so this scale is unlikely appropriate to apply for our situation.
+Gao~\cite{gao2018} reports that cyclists do not rate vibrations as extremely
+uncomfortable on normal road surfaces, so that indicates some contradiction.
+
+\subsection{Vehicle \& Seat Design}
+%
+Different vehicle, seat, and baby mass combinations cause different average
+vertical acceleration at the seat pan. A striking discovery is that the two
+1970's strollers we tested were significantly better than many of the modern
+stroller setups on most road surfaces. The old strollers actually had more
+sophisticated suspension systems that utilized springs, straps, and mechanisms
+and they also had larger wheels. Road surfaces have gotten smoother over the
+last two centuries and stroller manufacturers may have reduced the efforts in
+suspension design as a side effect. The ``Old Rusty'' stroller was the only one
+that did not exceed the 1~\si{\hour} health risk line for all road surfaces.
+
+Both the Bugaboo and Maxi-Cosi stroller showed lower acceleration for the
+heavier baby, as expected, but the Stokke YOYO showed the opposite trend for
+cobblestones and paver bricks. This points to design choices that may cause
+resonance on certain surface profiles. The Bugaboo in the 9 mo seat
+configuration performed better than the other modern strollers for all
+non-tarmac road surfaces.
+
+Urban Arrow better than Keiler on tarmac but there is no difference on paver
+bricks. Additionally, there was no difference in the different seats for the 3
+month infant.
+
+\subsection{ISO Filters and Bandwidth}
+%
+Vibrations at frequencies between
+\SIrange{4.9}{10.7}{\hertz} showed to have the largest magnitude contribution to the
+vibrations, but there is a frequency content of magnitudes of interest in a
+bandwidth of up to 45~\si{\hertz}.
+
+We report root mean squared (RMS) accelerations up to 120 Hz as well as accelerations weighted according to the ISO norms for vibration (VDV).
+Our results show substantial differences between RMS and VDV highlighting the importance of reviewing their meaning.
+These differences emerge from the high bandwidth of the accelerations now measured, which greatly exceed the bandwidth of accelerations measured with adults seated in cars (see e.g Figure 2 in \cite{griffin2004experimental}).
+Adult experiments show that significant discomfort can be measured across all tested frequencies being 80 Hz \cite{morioka2010frequency} or even 315 Hz \cite{morioka2006magnitude} albeit with reduced sensitivity.
+The ISO frequency weightings are defined for adults in more or less erect postures with the head being unsupported, whereas we now studied dummies representing infants from 0 - 9 months lying with the head directly supported.
+The ISO weightings represent a reduced sensitivity above 8 Hz, which is associated by the vertical dynamics of erect seated subjects which filter out such high frequencies [add ref].
+However, adult experiments show higher discomfort for frequencies above 8 Hz when lying with head supported with 30-90 deg back inclination as compared to erect without head support.
+Higher frequencies have also been associated with effects on the central nervous system.
+For instance, experiments on rats showed brain injury visible in behaviour through functional impairment and in visual changes of brain structures in postmortem dissection after exposure to prolonged whole-body vibration at 30 Hz and 0.5 G \cite{Yan2015_cumulative_brain_injury/j.jstrokecerebrovasdis.2015.08.007}.
+In some conditions the RMS exceeds the ISO based VDV by a factor [add number], warranting further research on the effects of higher frequencies in particular for head supported conditions and for children.
+
+\subsection{Summary, Recommendations, and Future Work}
+%
+The results herein raise concerns about transporting infants in strollers and
+cargo bicycles. If the pusher or rider's behavior is not adjusted to avoid rough
+surfaces or to go very slow over them when the cargo is an infant, there are
+potential health risks if the large vibrations are experienced daily and
+repeatedly  for years. In most likelihood parents do adjust their travel
+behavior but maybe not enough or they are neglectful but this has yet to be
+studied. There is not direct evidence that connects whole body vibration as
+measured in this study to infant harm or negative health effects, so we can only
+extroplate from the limited guidelines on adults in occupational settings. But
+we did measure vibrations that would not be permitted for adults to maintain
+occuptaionl health and it is reasonble to beleive we should nto subject our
+infants to the same. It is well known that whole body vibration can be
+controlled with good suspension design. We see this in the drastic evolution of
+suspension in automobiles. We do not see this same kind of attention for
+suspsension in strollers, cargo bicycles, and baby seats for these vehicles.
+Increasing walking and cycling is well known to offer great societal and
+personal benefits over traveling with automoble, so it behoves us all to make
+transport for infants most optimal in these two transport modes. The following
+list provides recommendations for parents, researchers, and manufacturers based on the findings of this paper:
+%
+\begin{itemize}
+    \item Stroller, Cargo Bicycle, and Seat manufacturers must test for
+    vibration magnitude and frequency over all expected surface types to ensure
+    their designs dampened vibrations well for all scenarios.
+    \item Need to design better suspension systems, as vibrations can be
+    drastically reduced. Looking to past designs when road surfaces were not so
+    smooth is pertinent.
+    \item Parents should push or ride slowly over surfaces rougher than tarmac,
+    as bumpier surfaces can quickly multiply the experience acceleration.
+    \item Parents should limit the duration of transport over surfaces rougher
+    than tarmac periods that do not exceed 10 minutes with adequate
+    non-vibration breaks in between. When transporting over tarmac, durations should not exceed 4 hours.
+    \item E-cargo bicycles can easily reach the maximum speed of 25~\si{\kph}
+    and infants should be transported for long durations when riding over
+    non-tarmac surfaces at these speeds.
+    \item ISO 2631-1 is not adequate for accurately characterizing health and
+    comfort for infants or children or for short durations or non-erect seating.
+    Research is needed to develop a new standard for assessing whole body
+    vibration of infants and children.
+\end{itemize}
+
+We acquired data from four other sensors on the vehicles, all with three
+accelerometer and three gyroscope time histories, for a total of 30 time
+histories of possible interest. This paper provides a look into the experiments
+via three metrics: ISO weighted vertical RMS acceleration, peak frequency, and
+bandwidth of the seat pan sensor. The collected data can also be used to
+investigate transmissibility from sensor to sensor as well as rotational
+vibration effects. Investigating these further can give a more complete picture
+of the connections to health and comfort. This work also gives a benchmark that
+new designs can be tested against so show reduction in vibration.
 
@@
 
+\newpage
+\appendix
+
+% Ensure subsections retain "A.1", "A.2", etc.
+%\addcontentsline{toc}{section}{Appendix} % Optional: Add to TOC
+%\renewcommand{\thesection}{A}
+%\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
+
+\section{All Trial Metrics}
+%
+Table~\ref{tab:results} shows the mean over the scenario trials unweighted and
+ISO~2631-1 weighted seat pan vertical RMS acceleration, duration, peak
+frequency, bandwidth, and crest factor for all 52 combinations of vehicle setup,
+road surface, and target speed.
+% NOTE : This table is generated automatically from the Python scripts. I manually edit the header rows to fit on the page width. Save the edits between toprule and midrule!
+\bgroup
+\setlength\tabcolsep{0.8mm}  % reduces horiztonal padding between columns
+\begin{table}
+  \centering
+  \caption{Mean computed metrics for all 52 scenarios.}
+  \label{tab:results}
+  \footnotesize
+\begin{tabular}{lllcccccccc}
+\toprule
+& & & Target & Trial & RMS & Weighted & Peak & & & Crest \\
+& & Road & Speed & Count & Accel & RMS Accel & Frequency & Bandwidth & Duration  & Factor \\
+Vehicle & Seat, Baby & Surface & [km/h] & & [m/s/s] & [m/s/s] & [Hz] & [Hz] & [s]  & \\
+\midrule
+\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.4 & 4.3 & 6.5 & 14.3 & 20.4 & 6.2 \\
+\cline{3-11}
+ &  & Paver Bricks & 5 & 3 & 2.6 & 2.4 & 9.5 & 17.2 & 23.3 & 4.1 \\
+\cline{3-11}
+ &  & Sidewalk Pavers & 5 & 2 & 2.9 & 2.7 & 6.1 & 18.5 & 25.4 & 13.5 \\
+\cline{3-11}
+ &  & Sidewalk Slabs & 5 & 3 & 4.8 & 4.7 & 5.8 & 15.1 & 20.2 & 6.4 \\
+\cline{3-11}
+ &  & Tarmac & 5 & 2 & 0.7 & 0.6 & 10.1 & 18.5 & 23.1 & 3.3 \\
+\cline{2-11} \cline{3-11}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 4 & 2.5 & 2.3 & 6.6 & 20.7 & 22.5 & 4.7 \\
+\cline{3-11}
+ &  & Paver Bricks & 5 & 3 & 2.3 & 1.8 & 9.4 & 26.4 & 22.6 & 3.8 \\
+\cline{3-11}
+ &  & Sidewalk Pavers & 5 & 3 & 1.7 & 1.4 & 7.7 & 23.8 & 24.7 & 5.5 \\
+\cline{3-11}
+ &  & Sidewalk Slabs & 5 & 3 & 2.4 & 2.2 & 6.0 & 20.3 & 24.5 & 5.3 \\
+\cline{3-11}
+ &  & Tarmac & 5 & 2 & 0.6 & 0.4 & 8.4 & 29.3 & 34.6 & 6.5 \\
+\cline{1-11} \cline{2-11} \cline{3-11}
+\multirow[t]{5}{*}{greenmachine} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 3.2 & 2.9 & 4.1 & 17.3 & 23.7 & 5.3 \\
+\cline{3-11}
+ &  & Paver Bricks & 5 & 2 & 1.6 & 1.3 & 4.2 & 26.8 & 29.6 & 4.5 \\
+\cline{3-11}
+ &  & Sidewalk Pavers & 5 & 2 & 2.7 & 2.5 & 4.1 & 18.5 & 28.2 & 6.5 \\
+\cline{3-11}
+ &  & Sidewalk Slabs & 5 & 3 & 3.5 & 3.2 & 3.9 & 16.8 & 23.9 & 6.7 \\
+\cline{3-11}
+ &  & Tarmac & 5 & 2 & 0.5 & 0.4 & 4.2 & 33.4 & 22.1 & 4.1 \\
+\cline{1-11} \cline{2-11} \cline{3-11}
+\multirow[t]{12}{*}{keiler} & \multirow[t]{4}{*}{maxicosi, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 7.0 & 6.9 & 7.6 & 16.7 & 23.8 & 7.2 \\
+ &  &  & 20 & 1 & 12.6 & 10.7 & 6.8 & 26.9 & 34.0 & 9.9 \\
+\cline{3-11}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 1.8 & 1.8 & 8.1 & 13.3 & 24.6 & 8.3 \\
+ &  &  & 20 & 2 & 2.8 & 2.8 & 7.8 & 13.2 & 29.2 & 5.1 \\
+\cline{2-11} \cline{3-11}
+ & \multirow[t]{4}{*}{maxicosi, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 6.3 & 5.7 & 8.0 & 21.9 & 28.9 & 11.0 \\
+ &  &  & 20 & 2 & 9.8 & 7.8 & 7.2 & 30.7 & 21.4 & 14.4 \\
+\cline{3-11}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.5 & 1.5 & 7.6 & 12.8 & 27.8 & 8.1 \\
+ &  &  & 20 & 2 & 2.1 & 2.1 & 6.4 & 12.7 & 23.8 & 3.9 \\
+\cline{2-11} \cline{3-11}
+ & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 5.4 & 4.9 & 7.9 & 21.9 & 26.3 & 8.1 \\
+ &  &  & 20 & 2 & 9.5 & 6.7 & 6.8 & 34.8 & 23.0 & 10.2 \\
+\cline{3-11}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.2 & 1.2 & 7.8 & 14.2 & 25.4 & 8.2 \\
+ &  &  & 20 & 2 & 1.6 & 1.5 & 8.3 & 13.8 & 22.6 & 3.8 \\
+\cline{1-11} \cline{2-11} \cline{3-11}
+\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.6 & 4.4 & 8.1 & 18.3 & 20.7 & 4.9 \\
+\cline{3-11}
+ &  & Paver Bricks & 5 & 2 & 3.2 & 2.8 & 10.4 & 21.1 & 27.2 & 3.9 \\
+\cline{3-11}
+ &  & Sidewalk Pavers & 5 & 3 & 3.0 & 2.9 & 7.6 & 18.1 & 21.4 & 5.5 \\
+\cline{3-11}
+ &  & Sidewalk Slabs & 5 & 3 & 5.0 & 4.6 & 5.1 & 20.7 & 16.3 & 8.2 \\
+\cline{3-11}
+ &  & Tarmac & 5 & 2 & 0.9 & 0.8 & 9.6 & 24.4 & 34.3 & 8.0 \\
+\cline{2-11} \cline{3-11}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 4.1 & 3.7 & 8.0 & 20.3 & 25.9 & 5.8 \\
+\cline{3-11}
+ &  & Paver Bricks & 5 & 2 & 3.0 & 2.4 & 9.7 & 24.0 & 27.8 & 3.4 \\
+\cline{3-11}
+ &  & Sidewalk Pavers & 5 & 2 & 2.6 & 2.3 & 7.3 & 21.2 & 27.8 & 5.5 \\
+\cline{3-11}
+ &  & Sidewalk Slabs & 5 & 3 & 3.1 & 2.9 & 6.9 & 20.1 & 25.6 & 5.4 \\
+\cline{3-11}
+ &  & Tarmac & 5 & 2 & 1.0 & 0.7 & 10.2 & 30.0 & 36.1 & 5.8 \\
+\cline{1-11} \cline{2-11} \cline{3-11}
+\multirow[t]{5}{*}{oldrusty} & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 4.7 & 2.0 & 5.1 & 39.0 & 29.9 & 6.0 \\
+\cline{3-11}
+ &  & Paver Bricks & 5 & 3 & 3.4 & 1.2 & 5.2 & 44.2 & 21.9 & 6.1 \\
+\cline{3-11}
+ &  & Sidewalk Pavers & 5 & 2 & 3.3 & 1.4 & 5.4 & 40.1 & 27.3 & 9.7 \\
+\cline{3-11}
+ &  & Sidewalk Slabs & 5 & 3 & 3.2 & 1.6 & 5.3 & 39.0 & 23.8 & 11.6 \\
+\cline{3-11}
+ &  & Tarmac & 5 & 2 & 1.1 & 0.5 & 7.0 & 42.1 & 22.6 & 5.7 \\
+\cline{1-11} \cline{2-11} \cline{3-11}
+\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 3 & 6.5 & 5.7 & 7.6 & 21.4 & 20.8 & 9.6 \\
+ &  &  & 20 & 1 & 9.2 & 8.5 & 8.0 & 19.8 & 39.1 & 9.9 \\
+ &  &  & 25 & 1 & 11.6 & 8.2 & 6.9 & 38.0 & 38.3 & 13.7 \\
+\cline{3-11}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.3 & 1.2 & 9.3 & 18.5 & 29.0 & 8.3 \\
+ &  &  & 25 & 2 & 2.1 & 1.9 & 9.7 & 18.1 & 21.5 & 5.2 \\
+\cline{2-11} \cline{3-11}
+ & \multirow[t]{5}{*}{maxicosi, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 3.9 & 5.8 & 21.6 & 29.1 & 13.5 \\
+ &  &  & 20 & 1 & 10.8 & 7.4 & 5.0 & 32.4 & 32.1 & 14.7 \\
+ &  &  & 25 & 1 & 10.6 & 7.7 & 6.3 & 31.2 & 30.3 & 14.7 \\
+\cline{3-11}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.1 & 1.0 & 8.8 & 18.3 & 25.3 & 9.6 \\
+ &  &  & 25 & 2 & 1.6 & 1.5 & 9.5 & 18.3 & 21.6 & 4.9 \\
+\cline{2-11} \cline{3-11}
+ & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 4.1 & 7.5 & 18.9 & 24.1 & 8.3 \\
+ &  &  & 20 & 1 & 6.9 & 6.2 & 7.9 & 21.2 & 36.8 & 8.6 \\
+ &  &  & 25 & 1 & 7.6 & 6.8 & 9.2 & 21.1 & 31.7 & 7.2 \\
+\cline{3-11}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 0.9 & 0.9 & 9.4 & 16.7 & 20.4 & 9.3 \\
+ &  &  & 25 & 2 & 1.4 & 1.3 & 9.4 & 16.6 & 23.0 & 5.8 \\
+\cline{1-11} \cline{2-11} \cline{3-11}
+\multirow[t]{10}{*}{yoyo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 4.0 & 6.4 & 16.9 & 21.3 & 4.8 \\
+\cline{3-11}
+ &  & Paver Bricks & 5 & 2 & 3.0 & 2.1 & 9.4 & 41.7 & 29.5 & 4.1 \\
+\cline{3-11}
+ &  & Sidewalk Pavers & 5 & 3 & 2.8 & 2.6 & 6.7 & 18.8 & 22.2 & 5.5 \\
+\cline{3-11}
+ &  & Sidewalk Slabs & 5 & 2 & 4.0 & 3.8 & 5.2 & 19.6 & 25.7 & 6.4 \\
+\cline{3-11}
+ &  & Tarmac & 5 & 2 & 0.9 & 0.6 & 7.7 & 42.9 & 19.5 & 7.4 \\
+\cline{2-11} \cline{3-11}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 5.2 & 4.9 & 7.7 & 17.6 & 21.5 & 4.4 \\
+\cline{3-11}
+ &  & Paver Bricks & 5 & 3 & 3.6 & 3.0 & 10.4 & 25.0 & 22.5 & 3.8 \\
+\cline{3-11}
+ &  & Sidewalk Pavers & 5 & 2 & 3.1 & 2.7 & 8.3 & 23.4 & 28.5 & 9.9 \\
+\cline{3-11}
+ &  & Sidewalk Slabs & 5 & 3 & 4.0 & 3.7 & 5.3 & 19.0 & 23.3 & 6.2 \\
+\cline{3-11}
+ &  & Tarmac & 5 & 2 & 0.7 & 0.4 & 11.1 & 41.7 & 39.1 & 6.3 \\
+\cline{1-11} \cline{2-11} \cline{3-11}
+\bottomrule
+\end{tabular}
+\end{table}
+\egroup
+\section{Vehicle Statistical Comparisons}
+%
+\begin{figure}[!h]
+  \centering
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-stroller-Cobblestones.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-stroller-Paver Bricks.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-stroller-Sidewalk Pavers.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-stroller-Sidewalk Slabs.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-stroller-Tarmac.png}}
+  \caption{Tukey Comparison Plots for the Strollers}
+  \label{fig:tukey-stroller}
+\end{figure}
+%
+\begin{figure}[!h]
+  \centering
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-bicycle-Paver Bricks-Low.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-Low.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-bicycle-Paver Bricks-High.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=75mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-High.png}}
+  \caption{Tukey Comparison Plots for the Cargo Bicycles}
+  \label{fig:tukey-bicycle}
+\end{figure}
+
+\section{Experimental Equipment}
+\label{app:equipment}
+%
+In this section, we report the pictures of the strollers and bicycles used for
+the experiments. The reader can find the measurements, wheelbase, wheel
+diameter, sensor location and orientation for all the tested vehicles.
+
+\begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Joolz_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Joolz_front.PNG}}
+  \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
+  Maxicosi-Joolz baby pebble.}
+  \label{fig:tech_drawing_UA_Joolz}
+\end{figure}
+
+\begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_front.PNG}}
+  \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
+  Melia baby shell.}
+  \label{fig:tech_drawing_UA_Melia}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Joolz_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Joolz_front.PNG}}
+  \caption{IMU locations on the Keiler Tricycle, equipped with the
+  Maxicosi-Joolz baby pebble.}
+  \label{fig:tech_drawing_Trike_Joolz}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Melia_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Melia_front.PNG}}
+  \caption{IMU locations on the Keiler Tricycle, equipped with the
+  Melia baby shell.}
+  \label{fig:tech_drawing_Trike_Melia}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_front.PNG}}
+  \caption{IMU locations on the stroller Bugaboo Fox 5, configured for 0-months baby.}
+  \label{fig:tech_drawing_Bugaboo0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo9_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo9_front.PNG}}
+  \caption{IMU locations on the stroller Bugaboo Fox 5, configured for 9-months baby.}
+  \label{fig:tech_drawing_Bugaboo9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_Maxicosi0_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Maxicosi0_front.PNG}}
+  \caption{IMU locations on the stroller Maxi-cosi Street +, configured for 0-months baby.}
+  \label{fig:tech_drawing_Maxicosi0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_Maxicosi9_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Maxicosi9_front.PNG}}
+  \caption{IMU locations on the stroller Maxi-cosi Street +, configured for 9-months baby.}
+  \label{fig:tech_drawing_Maxicosi9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO0_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO0_front.PNG}}
+  \caption{IMU locations on the stroller Stokke YOYO, configured for 0-months baby.}
+  \label{fig:tech_drawing_YOYO0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO9_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO9_front.PNG}}
+  \caption{IMU locations on the stroller Stokke YOYO, configured for 9-months baby.}
+  \label{fig:tech_drawing_YOYO9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_GreenM0_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_GreenM0_front.PNG}}
+  \caption{IMU locations on the old stroller GreenMachine, configured for 0-months baby.}
+  \label{fig:tech_drawing_GreenM0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_OldR9_lat.PNG}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_OldR9_front.PNG}}
+  \caption{IMU locations on the old stroller OldRusty, configured for 9-months baby.}
+  \label{fig:tech_drawing_OldR9}
+\end{figure}
+
+\clearpage
+\newpage
+
+\subsection{Location and pictures of the experiment areas}
+
+\subsubsection{For Bicycles}
+
+\begin{itemize}
+    \item Tarmac
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Tarmac surface where we tested bicycles}{\includegraphics[width=70mm, angle=-90]{fig/Tarmac_bicycle.jpg}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Tarmac_bicycle_GPS.PNG}}
+  \caption{Details of the tarmac test area.}
+  \label{fig:tarmac_bicycle}
+\end{figure}
+
+The bicycle experiment on the tarmac was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands.
+
+    \item Paver bricks
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Paver bricks surface where we tested bicycles}{\includegraphics[width=70mm, angle=-90]{fig/Paver_bricks_bicycle.jpg}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Paver_bricks_bicycle_GPS.PNG}}
+  \caption{Details of the paver bricks test area.}
+  \label{fig:paver_bricks_bicycle}
+\end{figure}
+
+The bicycle experiment on the paver bricks was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands.
+
+\clearpage
+
+    \item Shock
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{We performed a shock test with bicycles riding over a 30x30 mm square section bar}{\includegraphics[width=70mm, angle=0]{fig/Shock_bicycle.PNG}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Tarmac_bicycle_GPS.PNG}}
+  \caption{Details of the shock test area.}
+  \label{fig:shock_bicycle}
+\end{figure}
+
+The bicycle shock experiment was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands (same location of the experiment on the tarmac).
+Details of the shock experiment: we rode over a squared section aluminium bar 30 x 30 mm.
+
+\end{itemize}
+
+\subsubsection{For Strollers}
+
+\begin{itemize}
+    \item Tarmac
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Tarmac surface where we tested strollers}{\includegraphics[width=70mm, angle=-90]{fig/Tarmac_stroller.jpg}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Tarmac_stroller_GPS.PNG}}
+  \caption{Details of the tarmac test area.}
+  \label{fig:tarmac_stroller}
+\end{figure}
+
+The bicycle experiment on the tarmac was conducted along Julianalaan Straat, 2628 BG Delft, The Netherlands.
+
+\clearpage
+
+    \item Cobblestone
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Cobblestone surface where we tested strollers}{\includegraphics[width=60mm, angle=0]{fig/Cobblestone_stroller.PNG}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Tarmac_stroller_GPS.PNG}}
+  \caption{Details of the cobblestone test area.}
+  \label{fig:cobblestone_area_stroller}
+\end{figure}
+
+The bicycle experiment on the cobblestone was conducted along Julianalaan Straat, 2628 BG Delft, The Netherlands.
+Details of cobblestone: rectangular shape, dimensions 180 x 125 mm (gap in between: 20±4 mm).
+
+    \item Sidewalk pavers
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Sidewalk pavers where we tested strollers}{\includegraphics[width=60mm, angle=0]{fig/Sidewalk_pavers_stroller.PNG}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Paver_bricks_stroller_GPS.PNG}}
+  \caption{Details of the sidewalk pavers test area.}
+  \label{fig:sidewalkpavers_area_stroller}
+\end{figure}
+
+The experiment was conducted along Prins Bernhardlaan, 2628 CN Delft, The Netherlands (same location as Paver bricks test).
+Details of sidewalk bricks: rectangular shape, dimensions 290 x 290 mm (gap in between: 12±2 mm).
+
+\clearpage
+
+    \item Sidewalk slabs
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Sidewalk slabs where we tested strollers}{\includegraphics[width=70mm, angle=-90]{fig/Sidewalk_slabs_stroller.jpg}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Sidewalk_slabs_stroller_GPS.PNG}}
+  \caption{Details of the sidewalk slab test area.}
+  \label{fig:sidewalkslabs_area_stroller}
+\end{figure}
+
+The experiment was conducted in front of TU Delft Aula Conference Centre (Building 20), Mekelweg 5, 2628 CC Delft, The Netherlands.
+Details of sidewalk slab: made of concrete, rectangular shape, dimensions 2000 x 990 mm (gap in between: 160±3 mm).
+
+    \item Paver bricks
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Paver bricks area where we tested strollers}{\includegraphics[width=50mm, angle=0]{fig/Paver_bricks_stroller.PNG}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Sidewalk_slabs_stroller_GPS.PNG}}
+  \caption{Details of the paver bricks test area.}
+  \label{fig:paverbrick_area_stroller}
+\end{figure}
+
+The experiment was conducted along Prins Bernhardlaan, 2628 CN Delft, The Netherlands (same location as Sidewalk bricks test).
+Details of paver brick: rectangular shape, dimensions 195 x 95 mm (gap in between: 7±2 mm).
+
+\clearpage
+
+    \item Shock
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Area where we tested strollers during the shock experiment.}{\includegraphics[width=60mm, angle=-90]{fig/Shock_stroller.jpg}}
+  \subcaptionbox{Satellite view from Google Maps, with the GPS coordinates}{\includegraphics[width=70mm]{fig/Shock_stroller_GPS.PNG}}
+  \caption{Details of the shock test area.}
+  \label{fig:shock_area_stroller}
+\end{figure}
+
+The experiment was conducted inside TU Delft Mechanical Engineering faculty (Building 34 - Ground floor, aisle in front of Gezelschap Leeghwater office), Mekelweg 2, 2628 CD Delft, The Netherlands
+Details of the shock experiment: we pushed the stroller over a squared section aluminium bar 30 x 30 mm.
+
+\end{itemize}
+
 \end{document}

### 2025-01-28 src/website.py
Added the Gao et. al 2018 cyclist vibration acceptance threshold.

@@ -35,6 +35,7 @@ COMFORT_BOUNDS = (
     (1.25, 2.5, 'very uncomfortable'),
     (2.0, 99.0, 'extremely uncomfortable'),
 )
+GAO_ACC_ACCEPTANCE = 2.54  # m/s/s
 
 sns.set_theme(style='whitegrid')
 
@@ -43,6 +44,10 @@ try:
         'git', 'rev-parse', 'HEAD']).decode('ascii').strip()
 except (FileNotFoundError, subprocess.CalledProcessError):
     githash = 'none found'
+
+#############################
+# Prepare Primary Data Frames
+#############################
 
 with open(os.path.join(PATH_TO_DATA_DIR, 'html-data.pkl'), 'rb') as f:
     html_data = pickle.load(f)
@@ -85,6 +90,10 @@ stats_df['Mean Speed [km/h]'] = stats_df['Mean Speed [m/s]']*3.6
 
 bicycle_df = stats_df[stats_df['Vehicle Type'] == 'bicycle']
 stroller_df = stats_df[stats_df['Vehicle Type'] == 'stroller']
+
+################
+# Data Summaries
+################
 
 print_header("Statistics Data Frame in Tidy Format")
 print("All columns:")
@@ -341,14 +350,23 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
     p.axes.axhline(low, color='tab:brown', alpha=0.6)
     p.axes.annotate('→ ' + note,
                     xy=(7.5, low),
-                    xytext=(9.6 - i*0.3, low + 0.02),
+                    xytext=(9.8 - i*0.3, low + 0.02),
                     color='tab:brown',
                     fontsize=8,
                     rotation=90,
                     arrowprops=dict(facecolor='tab:brown', width=2.0,
                                     headwidth=0.0, frac=0.0))
-p.axes.text(8.0, 3.5, 'ISO 2631-1 Adult\nPublic Transit Feelings',
+p.axes.text(8.2, 3.5, 'ISO 2631-1 Adult\nPublic Transit Rating',
             color='tab:brown')
+p.axes.axhline(GAO_ACC_ACCEPTANCE, color='red')
+p.axes.annotate('→ ' + "Cyclist's Acceptance\n    Threshold",
+                xy=(7.5, GAO_ACC_ACCEPTANCE),
+                xytext=(7.7, GAO_ACC_ACCEPTANCE + 0.02),
+                color='tab:red',
+                fontsize=8,
+                rotation=90,
[…]

### 2025-01-28 src/website.py
Changed acceptants to discomfort in legend.

@@ -359,7 +359,7 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
 p.axes.text(8.2, 3.5, 'ISO 2631-1 Adult\nPublic Transit Rating',
             color='tab:brown')
 p.axes.axhline(GAO_ACC_ACCEPTANCE, color='red')
-p.axes.annotate('→ ' + "Cyclist's Acceptance\n    Threshold",
+p.axes.annotate('→ ' + "Cyclists' Discomfort\n     Threshold",
                 xy=(7.5, GAO_ACC_ACCEPTANCE),
                 xytext=(7.7, GAO_ACC_ACCEPTANCE + 0.02),
                 color='tab:red',
@@ -406,7 +406,7 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
 p.axes.text(5.9, 5.8, 'ISO 2631-1 Adult\nPublic Transit Rating',
             color='tab:brown')
 p.axes.axhline(GAO_ACC_ACCEPTANCE, color='red')
-p.axes.annotate('→ ' + "Cyclist's Acceptance Threshold",
+p.axes.annotate('→ ' + "Cyclist's Discomfort Threshold",
                 xy=(5.25, GAO_ACC_ACCEPTANCE),
                 xytext=(5.5, GAO_ACC_ACCEPTANCE + 0.02),
                 color='tab:red',

### 2025-01-28 src/website.py
Changed Gao line to tab:red.

@@ -358,7 +358,7 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
                                     headwidth=0.0, frac=0.0))
 p.axes.text(8.2, 3.5, 'ISO 2631-1 Adult\nPublic Transit Rating',
             color='tab:brown')
-p.axes.axhline(GAO_ACC_ACCEPTANCE, color='red')
+p.axes.axhline(GAO_ACC_ACCEPTANCE, color='tab:red')
 p.axes.annotate('→ ' + "Cyclists' Discomfort\n     Threshold",
                 xy=(7.5, GAO_ACC_ACCEPTANCE),
                 xytext=(7.7, GAO_ACC_ACCEPTANCE + 0.02),
@@ -405,7 +405,7 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
                                     headwidth=0.0, frac=0.0))
 p.axes.text(5.9, 5.8, 'ISO 2631-1 Adult\nPublic Transit Rating',
             color='tab:brown')
-p.axes.axhline(GAO_ACC_ACCEPTANCE, color='red')
+p.axes.axhline(GAO_ACC_ACCEPTANCE, color='tab:red')
 p.axes.annotate('→ ' + "Cyclist's Discomfort Threshold",
                 xy=(5.25, GAO_ACC_ACCEPTANCE),
                 xytext=(5.5, GAO_ACC_ACCEPTANCE + 0.02),

### 2025-01-28 src/data.py
Simplified colors in the amplitude spectrum and made sure they work correctly for the various kwarg combinations.

@@ -206,13 +206,17 @@ class Trial():
             max_amp, peak_freq, thresh_freq = self.calc_spectrum_features(
                 sig_name, sample_rate, iso_weighted=iso_weighted,
                 smooth=smooth)
-            ax.axvline(peak_freq, color='C1', linewidth=3)
-            ax.axvline(thresh_freq, color='C2', linewidth=3)
+            if smooth:
+                color = 'black'
+            else:
+                color = 'C0'
+            ax.axvline(peak_freq, color=color, linestyle='--', linewidth=2)
+            ax.axvline(thresh_freq, color=color, linestyle='-.', linewidth=2)
             legend += ['Peak Frequency', '80% Bandwidth']
 
         # plot unweighted if smoothed
         if iso_weighted and smooth:
-            plot_kw = {'color': 'C3', 'linewidth': 3}
+            plot_kw = {'color': 'black', 'linewidth': 2}
             legend += ['Smoothed Raw FFT']
             freq, amp, _, _ = self.calculate_frequency_spectrum(
                 sig_name, sample_rate, cutoff=cutoff, iso_weighted=False,
@@ -224,11 +228,15 @@ class Trial():
             freq, amp, _, _ = self.calculate_frequency_spectrum(
                 sig_name, sample_rate, cutoff=cutoff,
                 iso_weighted=iso_weighted, smooth=smooth)
-            plot_kw = {'color': 'C0', 'linewidth': 3}
+            if iso_weighted:
+                color = 'C0'
+            else:
+                color = 'black'
+            plot_kw = {'color': color, 'linewidth': 2}
             legend += ['Smoothed ' +
                        ('ISO Weighted FFT' if iso_weighted else '')]
         else:
-            plot_kw = None
+            plot_kw = {'color': 'gray', 'alpha': 0.8}
 
         ax = plot_frequency_spectrum(freq, amp, ax=ax, plot_kw=plot_kw)
 

### 2025-01-28 src/data.py
Additional color fix for spectrum plots and added missing cutoff kwarg.

@@ -204,12 +204,12 @@ class Trial():
         # features are from fully processed, but plotted first
         if show_features:
             max_amp, peak_freq, thresh_freq = self.calc_spectrum_features(
-                sig_name, sample_rate, iso_weighted=iso_weighted,
-                smooth=smooth)
+                sig_name, sample_rate, cutoff=cutoff,
+                iso_weighted=iso_weighted, smooth=smooth)
             if smooth:
-                color = 'black'
-            else:
                 color = 'C0'
+            else:
+                color = 'black'
             ax.axvline(peak_freq, color=color, linestyle='--', linewidth=2)
             ax.axvline(thresh_freq, color=color, linestyle='-.', linewidth=2)
             legend += ['Peak Frequency', '80% Bandwidth']

### 2025-01-28 src/data.py
Change last threshold words to bandwidth.

@@ -188,7 +188,7 @@ class Trial():
         ax : Axis
             Matplotlib axis to plot on.
         show_features : boolean
-            If true, shows peak frequency and threshold frequency.
+            If true, shows peak frequency and bandwidth threshold frequency.
 
         """
 

### 2025-01-28 src/process.py

@@ -177,7 +177,7 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                             stats_data['Max Spectrum Amp [m/s/s]'].append(
                                 max_amp)
                             stats_data['Peak Frequency [Hz]'].append(peak_freq)
-                            stats_data['Threshold Frequency [Hz]'].append(
+                            stats_data['Bandwidth [Hz]'].append(
                                 thresh_freq)
                             stats_data['Baby Age [mo]'].append(
                                 s.meta_data['baby_age'])

### 2025-01-28 src/website.py

@@ -114,7 +114,7 @@ summary_df['ISO Weighted RMS Acceleration [m/s/s]'] = \
 summary_df['ISO Weighted Peak Frequency [Hz]'] = \
     stats_df.groupby(groups)['Peak Frequency [Hz]'].mean()
 summary_df['ISO Weighted Bandwidth (80%) [Hz]'] = \
-    stats_df.groupby(groups)['Threshold Frequency [Hz]'].mean()
+    stats_df.groupby(groups)['Bandwidth [Hz]'].mean()
 summary_df['Duration [s]'] = \
     stats_df.groupby(groups)['Duration [s]'].mean()
 summary_df['Crest Factor'] = stats_df.groupby(groups)['Crest Factor'].mean()
@@ -561,14 +561,14 @@ boxp_html.append(P.format(msg))
 p = sns.boxplot(
     data=stats_df,
     x="Target Speed [km/h]",
-    y="Threshold Frequency [Hz]",
+    y="Bandwidth [Hz]",
 )
 p.set_xticklabels([veh + ' @ ' + lab.get_text() for lab, veh in
                    zip(p.get_xticklabels(), ['Strollers', 'Bicycles',
                                              'Bicycles', 'Bicycles'])])
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH/2*MM2INCH))
 p.figure.set_layout_engine('constrained')
-fname = '{}-thresh-freq-dist.png'.format(SIGNAL)
+fname = '{}-bandwidth-dist.png'.format(SIGNAL)
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
 plt.clf()
 boxp_html.append(IMG.format('', fname) + '\n</br>')

### 2025-01-28 src/data.py
Half line width of raw fft.

@@ -198,6 +198,7 @@ class Trial():
             smooth=False)
         ax = plot_frequency_spectrum(freq, amp, ax=ax,
                                      plot_kw={'color': 'gray',
+                                              'linewidth': 0.5,
                                               'alpha': 0.8})
         legend = ['Raw FFT']
 

### 2025-01-28 src/website.py
Changed bandwidth figure to show at different speeds and surfaces.

@@ -562,12 +562,17 @@ p = sns.boxplot(
     data=stats_df,
     x="Target Speed [km/h]",
     y="Bandwidth [Hz]",
+    hue="Road Surface",
+    hue_order=sorted(stats_df["Road Surface"].unique()),
 )
 p.set_xticklabels([veh + ' @ ' + lab.get_text() for lab, veh in
                    zip(p.get_xticklabels(), ['Strollers', 'Bicycles',
                                              'Bicycles', 'Bicycles'])])
-p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH/2*MM2INCH))
+p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*2/3*MM2INCH))
 p.figure.set_layout_engine('constrained')
+p.axvline(0.5, color='gray')
+p.axvline(1.5, color='gray')
+p.axvline(2.5, color='gray')
 fname = '{}-bandwidth-dist.png'.format(SIGNAL)
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
 plt.clf()

### 2025-01-28 src/website.py
Switched to tab:grey and linestyles for comfort and health thresholds.

@@ -229,7 +229,7 @@ p = sns.scatterplot(
 # health risk lines for different durations
 for val, note in zip((10.0, 20.0, 60.0, 240.0),
                      ('10 min', '20 min', '1 hr', '4 hr')):
-    p.axes.axhline(eval_health(val)[1], color='grey')
+    p.axes.axhline(eval_health(val)[1], linestyle='--', color='tab:grey')
     p.axes.text(7.0, eval_health(val)[1] + 0.2, note,
                 bbox=dict(boxstyle='round,pad=0.1', color='white'))
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
@@ -257,8 +257,8 @@ p = sns.stripplot(
 # health risk lines for different durations Equation B.1
 for val, note in zip((10.0, 20.0, 60.0, 240.0),
                      ('10 min', '20 min', '1 hr', '4 hr')):
-    p.axes.axhline(eval_health(val)[1], color='grey')
-    p.axes.text(1.15, eval_health(val)[1] + 0.05, note)
+    p.axes.axhline(eval_health(val)[1], linestyle='--', color='tab:grey')
+    p.axes.text(1.18, eval_health(val)[1] + 0.05, note)
 p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
                    p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
@@ -288,7 +288,7 @@ p = sns.scatterplot(
 # health risk lines for different durations
 for val, note in zip((10.0, 20.0, 60.0, 240.0),
                      ('10 min', '20 min', '1 hr', '4 hr')):
-    p.axes.axhline(eval_health(val)[1], color='grey')
+    p.axes.axhline(eval_health(val)[1], linestyle='--', color='tab:grey')
     p.axes.text(1.1, eval_health(val)[1] + 0.15, note,
                 bbox=dict(boxstyle='round,pad=0.02', color='white'))
 p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
@@ -322,7 +322,7 @@ p = sns.scatterplot(
 )
 # comfort lines for different durations
 for low, high, note in COMFORT_BOUNDS:
-    p.axes.axhline(low, color='grey')
+    p.axes.axhline(low, linestyle='--', color='tab:grey')
     p.axes.text(7.0, low + 0.05, note, fontsize=8,
[…]

### 2025-01-29 src/process.py
Add time history and spectrum plots for the shock trials.

@@ -44,6 +44,7 @@ def process_sessions(start_num, end_num, signal, sample_rate):
         'aula': 'Sidewalk Slabs',
         'klinkers': 'Paver Bricks',
         'pave': 'Cobblestones',
+        'shock': 'Shock',
         'stoeptegels': 'Sidewalk Pavers',
         'tarmac': 'Tarmac',
     }
@@ -196,8 +197,11 @@ def process_sessions(start_num, end_num, signal, sample_rate):
 
                             fig, ax = plt.subplots(layout='constrained',
                                                    figsize=(8, 2))
-                            ax = trial.plot_signal(signal, show_rms=True,
-                                                   show_vdv=True, ax=ax)
+                            if mot_trial == 'shock':  # no RMS and VDV
+                                ax = trial.plot_signal(signal, ax=ax)
+                            else:
+                                ax = trial.plot_signal(signal, show_rms=True,
+                                                       show_vdv=True, ax=ax)
                             ax.figure.savefig(os.path.join(
                                 PATH_TO_TIME_HIST_DIR, file_name + '.png'))
                             plt.clf()

### 2025-01-29 src/website.py

@@ -59,6 +59,9 @@ stats_df = pd.DataFrame(stats_data)
 # drop duplicates.
 stats_df.drop_duplicates(inplace=True)
 
+# drop shock from overall analysis (for now)
+stats_df = stats_df[stats_df['Road Surface'] != 'Shock']
+
 stats_df['duration_weight'] = (stats_df['Duration [s]'] /
                                stats_df['Duration [s]'].max())
 

### 2025-01-29 src/html_templates.py
Reordered webpage sections.

@@ -11,11 +11,11 @@ INDEX = """\
 <html lang="en">
   <head>
     <meta charset="utf-8">
-    <title>Baby Vehicle Transport Vibration Results</title>
+    <title>Infant Vehicle Transport Vibration Results</title>
   </head>
   <body>
 
-  <h1>Baby Vehicle Transport Vibration Results</h1>
+  <h1>Infant Vehicle Transport Vibration Results</h1>
   <hr>
   <p>
     Last updated: {date}
@@ -26,17 +26,17 @@ INDEX = """\
     supporting paper is published.</strong>
   </p>
   <p>
-    This results page examines the signal: <strong>{signal}</strong>.
+    This page examines the signal: <strong>{signal}</strong>.
   </p>
 
   <h1>Table of Contents</h1>
   <ol>
-    <li><a href="#mean_table">Mean Table</a></li>
-    <li><a href="#statistics">Statistical Regression Results</a></li>
+    <li><a href="#mean_table">Scenario Mean Table</a></li>
     <li><a href="#boxp">Comparison Plots</a></li>
+    <li><a href="#iso">ISO 2631-1 Weights</a></li>
+    <li><a href="#statistics">Statistical Regression Results</a></li>
     <li><a href="#sess">Sessions Segmented into Trials</a></li>
     <li><a href="#trial_table">Table of All Trials</a></li>
-    <li><a href="#iso">ISO 2631-1 Weights</a></li>
     <li><a href="#trial">Seat Pan Vertical Acceleration Time Histories</a></li>
     <li><a href="#spec">Seat Pan Vertical Acceleration Spectrums</a></li>
     <li><a href="#srot">Sensor Rotation Checks</a></li>
@@ -46,12 +46,26 @@ INDEX = """\
   <h1 id="mean_table">Mean Over Scenarios for Signal: {signal}</h1>
   <hr>
   <p>
-    Mean values for each scenario: vehicle, seat, baby, road surface, and speed
-    combination.
+    Mean values for each scenario, i.e. combination of vehicle, seat, baby
+    mass, road surface, and speed.
   </p>
 {mean_table}
 
-  <h1 id="statistics">Regression Results</h1>
+  <h1 id="boxp">Comparison Plots of the Signal: {signal}</h1>
+  <hr>
+{boxp_html}
+
+  <h1 id="iso">ISO 2631-1 Weights</h1>
+  <hr>
+  <p>
[…]

### 2025-01-29 src/website.py
Use .loc.

@@ -60,7 +60,7 @@ stats_df = pd.DataFrame(stats_data)
 stats_df.drop_duplicates(inplace=True)
 
 # drop shock from overall analysis (for now)
-stats_df = stats_df[stats_df['Road Surface'] != 'Shock']
+stats_df = stats_df.loc[stats_df['Road Surface'] != 'Shock', :]
 
 stats_df['duration_weight'] = (stats_df['Duration [s]'] /
                                stats_df['Duration [s]'].max())

### 2025-01-29 src/html_templates.py
Html templ wording.

@@ -46,19 +46,23 @@ INDEX = """\
   <h1 id="mean_table">Mean Over Scenarios for Signal: {signal}</h1>
   <hr>
   <p>
-    Mean values for each scenario, i.e. combination of vehicle, seat, baby
-    mass, road surface, and speed.
+    Counts and mean values for each scenario, i.e. combination of vehicle,
+    seat, baby mass, road surface, and speed.
   </p>
 {mean_table}
 
   <h1 id="boxp">Comparison Plots of the Signal: {signal}</h1>
   <hr>
+  <p>
+    Descriptive statistical plots of the data.
+  </p>
 {boxp_html}
 
   <h1 id="iso">ISO 2631-1 Weights</h1>
   <hr>
   <p>
-    Plots of the filter weights versus frequency we apply to the data.
+    Plots of the ISO 2631-1 filter weights versus frequency we apply to the
+    data.
   </p>
   <img src='fig/iso-filter-weights-01.png'</img>
   <br>
@@ -97,12 +101,12 @@ INDEX = """\
   <h1 id="trial">{signal} Repetition Time Histories</h1>
   <hr>
   <p>
-    The time history of the signal of each repetition broken into trials
+    The time history of the signal of each trial broken into repetitions
     selected from each scenario.
   </p>
 {trial_html}
 
-  <h1 id="spec">{signal} ISO Weighted Frequency Spectrums</h1>
+  <h1 id="spec">{signal} Amplitude Spectra (with ISO 2631-1 weighting)</h1>
   <hr>
 {spec_html}
 

### 2025-01-29 src/data.py
Added the session printout to html page.

@@ -532,6 +532,9 @@ class Session():
 
         return desc
 
+    def _repr_html_(self):
+        return '<pre>' + self.__str__() + '</pre>'
+
     def load_data(self):
         """Loads the IMU CSV files for this session into ``imu_data_frames``
         and the trial bound data into ``bounds_data_frame``."""

### 2025-01-29 src/process.py

@@ -87,6 +87,11 @@ def process_sessions(start_num, end_num, signal, sample_rate):
             s.calculate_vector_magnitudes()
 
             print(s)  # print after full DataFrame is constructed
+            html_data['sess_html'].append(s._repr_html_())
+            html_data['spec_html'].append(s._repr_html_())
+            html_data['srot_html'].append(s._repr_html_())
+            html_data['trial_html'].append(s._repr_html_())
+            html_data['sync_html'].append(s._repr_html_())
 
             ax = s.plot_speed_with_trial_bounds()
             ses_img_fn = session_label + '.png'

### 2025-01-30 src/data.py
Function to calculate  max_peak
Added function to calculate  max_peak.

1st request to merge

@@ -299,6 +299,11 @@ class Trial():
                            self.imu_data[sig_name].mean())
         return np.sqrt(np.mean(mean_subtracted**2))
 
+    def calc_max_peak(self, sig_name):
+        """Returns the MAX value of the shock events."""
+        max_peak_sh = abs(self.imu_data[sig_name]).max()
+        return max_peak_sh
+
     @functools.cache
     def calc_crest_factor(self, sig_name, sample_rate, cutoff=None):
         """Returns the crest factor: ratio of maximum absolute value to the RMS

### 2025-01-30 src/process.py
Calculation of max_peak
Calculation of max_peak of events and store the value into stats_data

@@ -3,6 +3,7 @@ import argparse
 import gc
 import os
 import pickle
+import numpy as np
 
 import matplotlib.pyplot as plt
 import pandas as pd
@@ -47,6 +48,7 @@ def process_sessions(start_num, end_num, signal, sample_rate):
         'shock': 'Shock',
         'stoeptegels': 'Sidewalk Pavers',
         'tarmac': 'Tarmac',
+        'shock': 'Shock',
     }
 
     if end_num == 99:
@@ -113,8 +115,11 @@ def process_sessions(start_num, end_num, signal, sample_rate):
 
             for mot_trial in motion_trials.keys():
                 if mot_trial in s.trial_bounds:
-                    html_data['trial_html'].append(H3.format(mot_trial))
-                    html_data['spec_html'].append(H3.format(mot_trial))
+                    if mot_trial != 'shock':
+                        html_data['trial_html'].append(H3.format(mot_trial))
+                        html_data['spec_html'].append(H3.format(mot_trial))
+                    else:
+                        html_data['trial_html'].append(H3.format(mot_trial))
                     for trial_num in s.trial_bounds[mot_trial]:
                         print('Trial Surface and Number: ', mot_trial,
                               trial_num)
@@ -151,6 +156,7 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                             # TODO : RMS and VDV are calculated from
                             # oversampled data, should I change to calculate
                             # from the downsampled data?
+                            max_amp_shock = np.nan
                             rms = trial.calc_rms(signal)
                             vdv = trial.calc_vdv(signal)
                             # TODO : Move this to the input of process()
@@ -169,6 +175,7 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                                 trial.calc_spectrum_features(
                                     signal, sample_rate, cutoff=cutoff,
                                     smooth=True, iso_weighted=True)
+                            max_amp_shock = trial.calc_max_peak(signal)
 
                             stats_data[signal + '_rms'].append(rms)
                             stats_data[signal + '_rms_iso'].append(rms_iso)
@@ -185,6 +192,7 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                             stats_data['Peak Frequency [Hz]'].append(peak_freq)
                             stats_data['Bandwidth [Hz]'].append(
                                 thresh_freq)
+                            stats_data['Peak Value [m/s/s]'].append(max_amp_shock)                            
[…]

### 2025-01-30 src/html_templates.py
Update Table of contents and New shock figure
Added "Shock" to Table of contents and template for a New shock figure

@@ -39,6 +39,7 @@ INDEX = """\
     <li><a href="#trial_table">Table of All Trials</a></li>
     <li><a href="#trial">Seat Pan Vertical Acceleration Time Histories</a></li>
     <li><a href="#spec">Seat Pan Vertical Acceleration Spectrums</a></li>
+    <li><a href="#shock">Shock Test</a></li>
     <li><a href="#srot">Sensor Rotation Checks</a></li>
     <li><a href="#sync">Sensor Time Synchronization Checks</a></li>
   </ol>
@@ -109,6 +110,11 @@ INDEX = """\
   <h1 id="spec">{signal} Amplitude Spectra (with ISO 2631-1 weighting)</h1>
   <hr>
 {spec_html}
+
+  <h1 id="shock">Shock Test comparison across vehicles</h1>
+  <hr>
+{shock_html}
+
 
   <h1 id="srot">Sensor Rotation Check</h1>
   <hr>

### 2025-01-30 src/website.py
Updated figure shock test
Added whitegrid, "shock" --> "Shock", and "trike" --> "keiler"

@@ -816,13 +816,17 @@ shock_html = []
 shock_html.append(H2.format('Shock test Comparison'))
 msg = 'Compare accelerations across vehicles and speed.'
 shock_html.append(P.format(msg))
+sns.set_theme(style='whitegrid')
 p = sns.stripplot(
     data=shock_df,
     x="Vehicle",
     y="Peak Value [m/s/s]",
     hue='Mean Speed [m/s]',
 )
-p.set_ylabel(r'Vertical Acceleration shock test [m/s$^2$]')
+p.set_ylabel(r'Vertical Acceleration Shock test [m/s$^2$]')
+p.set_xticklabels(
+    [label.get_text().replace("trike", "keiler") for label in p.get_xticklabels()],
+    rotation=30)
 p.set_xticklabels(p.get_xticklabels(), rotation=30)
 fname = '{}-shock-test-compare.png'.format(SIGNAL)
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, 100*MM2INCH))

### 2025-01-31 src/html_templates.py
Final figure tweaks for the veiligheid report.

@@ -33,13 +33,13 @@ INDEX = """\
   <ol>
     <li><a href="#mean_table">Scenario Mean Table</a></li>
     <li><a href="#boxp">Comparison Plots</a></li>
+    <li><a href="#shock">Shock Test</a></li>
     <li><a href="#iso">ISO 2631-1 Weights</a></li>
     <li><a href="#statistics">Statistical Regression Results</a></li>
     <li><a href="#sess">Sessions Segmented into Trials</a></li>
     <li><a href="#trial_table">Table of All Trials</a></li>
     <li><a href="#trial">Seat Pan Vertical Acceleration Time Histories</a></li>
     <li><a href="#spec">Seat Pan Vertical Acceleration Spectrums</a></li>
-    <li><a href="#shock">Shock Test</a></li>
     <li><a href="#srot">Sensor Rotation Checks</a></li>
     <li><a href="#sync">Sensor Time Synchronization Checks</a></li>
   </ol>
@@ -58,6 +58,10 @@ INDEX = """\
     Descriptive statistical plots of the data.
   </p>
 {boxp_html}
+
+  <h1 id="shock">Shock Test Comparison Across Vehicles</h1>
+  <hr>
+{shock_html}
 
   <h1 id="iso">ISO 2631-1 Weights</h1>
   <hr>
@@ -110,11 +114,6 @@ INDEX = """\
   <h1 id="spec">{signal} Amplitude Spectra (with ISO 2631-1 weighting)</h1>
   <hr>
 {spec_html}
-
-  <h1 id="shock">Shock Test comparison across vehicles</h1>
-  <hr>
-{shock_html}
-
 
   <h1 id="srot">Sensor Rotation Check</h1>
   <hr>

### 2025-01-31 src/website.py

@@ -24,6 +24,7 @@ from run import SIGNAL
 SIGNAL_RMS = SIGNAL + '_rms'
 SIGNAL_RMS_ISO = SIGNAL + '_rms_iso'
 SIGNAL_RMS_MAG_ISO = SIGNAL.split('_')[0] + '_rms_mag_iso'
+SIGNAL_VDV = SIGNAL + '_vdv'
 KPH2MPS, MPS2KPH = 1.0/3.6, 3.6
 MM2INCH = 1.0/25.4
 MAXWIDTH = 160.0  # mm (max width suitable for an A4 with 25 mm margins)
@@ -101,9 +102,6 @@ stats_df = stats_df.loc[stats_df['Road Surface'] != 'Shock', :]
 bicycle_df = stats_df[stats_df['Vehicle Type'] == 'bicycle']
 stroller_df = stats_df[stats_df['Vehicle Type'] == 'stroller']
 
-
-
-
 ################
 # Data Summaries
 ################
@@ -112,9 +110,6 @@ print_header("Statistics Data Frame in Tidy Format")
 print("All columns:")
 pprint.pprint(stats_df.columns.to_list())
 print(stats_df)
-
-
-
 
 groups = ['Vehicle', 'Seat, Baby', 'Road Surface', 'Target Speed [km/h]']
 # weight means by duration
@@ -127,13 +122,15 @@ summary_df = stats_df.groupby(groups)[SIGNAL_RMS].agg(
 )
 summary_df['ISO Weighted RMS Acceleration [m/s/s]'] = \
     stats_df.groupby(groups)[SIGNAL_RMS_ISO].mean()
+summary_df['VDV Acceleration [m/s/s]'] = \
+    stats_df.groupby(groups)[SIGNAL_VDV].mean()
+summary_df['Crest Factor'] = stats_df.groupby(groups)['Crest Factor'].mean()
 summary_df['ISO Weighted Peak Frequency [Hz]'] = \
     stats_df.groupby(groups)['Peak Frequency [Hz]'].mean()
 summary_df['ISO Weighted Bandwidth (80%) [Hz]'] = \
     stats_df.groupby(groups)['Bandwidth [Hz]'].mean()
 summary_df['Duration [s]'] = \
     stats_df.groupby(groups)['Duration [s]'].mean()
-summary_df['Crest Factor'] = stats_df.groupby(groups)['Crest Factor'].mean()
 
 print_header("Means Per Scenario")
 print(summary_df)
[…]

### 2025-01-31 src/process.py
Make dpi 300 for all png figures.

@@ -80,7 +80,8 @@ def process_sessions(start_num, end_num, signal, sample_rate):
             s.rotate_imu_data(subtract_gravity=False)
             axes = s.plot_accelerometer_rotation()
             axes[0, 0].figure.savefig(os.path.join(PATH_TO_ACCROT_DIR,
-                                                   session_label + '.png'))
+                                                   session_label + '.png'),
+                                      dpi=300)
             plt.clf()
             html_data['srot_html'].append(
                 IMG.format('accrot', session_label + '.png'))
@@ -97,14 +98,16 @@ def process_sessions(start_num, end_num, signal, sample_rate):
 
             ax = s.plot_speed_with_trial_bounds()
             ses_img_fn = session_label + '.png'
-            ax.figure.savefig(os.path.join(PATH_TO_BOUNDS_DIR, ses_img_fn))
+            ax.figure.savefig(os.path.join(PATH_TO_BOUNDS_DIR, ses_img_fn),
+                              dpi=300)
             plt.clf()
             html_data['sess_html'].append(IMG.format('bounds', ses_img_fn))
 
             if 'synchro' in s.trial_bounds:
                 ax = s.plot_time_sync()
                 sync_img_fn = session_label + '.png'
-                ax.figure.savefig(os.path.join(PATH_TO_SYNC_DIR, sync_img_fn))
+                ax.figure.savefig(os.path.join(PATH_TO_SYNC_DIR, sync_img_fn),
+                                  dpi=300)
                 plt.clf()
                 html_data['sync_html'].append(IMG.format('sync', ses_img_fn))
             else:
@@ -192,7 +195,7 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                             stats_data['Peak Frequency [Hz]'].append(peak_freq)
                             stats_data['Bandwidth [Hz]'].append(
                                 thresh_freq)
-                            stats_data['Peak Value [m/s/s]'].append(max_amp_shock)                            
+                            stats_data['Peak Value [m/s/s]'].append(max_amp_shock)
                             stats_data['Baby Age [mo]'].append(
                                 s.meta_data['baby_age'])
                             stats_data['Baby Mass [kg]'].append(
@@ -216,7 +219,8 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                                 ax = trial.plot_signal(signal, show_rms=True,
                                                        show_vdv=True, ax=ax)
                             ax.figure.savefig(os.path.join(
-                                PATH_TO_TIME_HIST_DIR, file_name + '.png'))
[…]

### 2025-01-31 src/website.py

@@ -181,7 +181,7 @@ for surf in ('Tarmac', 'Paver Bricks'):
         ax.set_xlabel('RMS Acceleration [m/s$^2$]')
         fig.set_size_inches((MAXWIDTH*MM2INCH, 0.4*MAXWIDTH*MM2INCH))
         fname = 'tukey-{}-bicycle-{}-{}.png'.format(SIGNAL, surf, speed)
-        fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
+        fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
         plt.clf()
         bicycle_comp_tables.append((surf, speed, comp_tab,
                                     IMG.format('', fname) + '\n</br>'))
@@ -213,7 +213,7 @@ for surf in stroller_df['Road Surface'].unique():
     ax.set_xlabel('RMS Acceleration [m/s$^2$]')
     fig.set_size_inches((MAXWIDTH*MM2INCH, 0.4*MAXWIDTH*MM2INCH))
     fname = 'tukey-{}-stroller-{}.png'.format(SIGNAL, surf)
-    fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
+    fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
     plt.clf()
     stroller_comp_tables.append((surf, comp_tab,
                                  IMG.format('', fname) + '\n</br>'))
@@ -251,7 +251,7 @@ p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, 1.05*MAXWIDTH*MM2INCH))
 p.figure.set_layout_engine('constrained')
 fname = '{}-compare-all.png'.format(SIGNAL)
-p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname))
+p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
 plt.clf()
 boxp_html.append(IMG.format('', fname) + '\n</br>')
 
@@ -280,7 +280,7 @@ p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*MM2INCH))
[…]

### 2025-01-31 src/html_templates.py
900 px for iso images.

@@ -3,7 +3,7 @@ H2 = '<h2>{}</h2>'
 H3 = '<h3>{}</h3>'
 H4 = '<h4>{}</h4>'
 HR = '<hr>'
-IMG = '<img src="fig/{}/{}"></img>'
+IMG = '<img src="fig/{}/{}" width="900px" ></img>'
 P = '<p>{}</p>'
 
 INDEX = """\
@@ -69,9 +69,9 @@ INDEX = """\
     Plots of the ISO 2631-1 filter weights versus frequency we apply to the
     data.
   </p>
-  <img src='fig/iso-filter-weights-01.png'</img>
+  <img src='fig/iso-filter-weights-01.png' width="900px"></img>
   <br>
-  <img src='fig/iso-filter-weights-02.png'</img>
+  <img src='fig/iso-filter-weights-02.png' width="900px"></img>
 
   <h1 id="statistics">Statistical Regression Results</h1>
   <hr>

### 2025-01-31 src/website.py
Switch to target speed for shock and 90 wide for tukey.

@@ -179,7 +179,7 @@ for surf in ('Tarmac', 'Paver Bricks'):
         ax.set_title(f'Cargo Bicycle Tukey Comparison for\nSurface {surf} and '
                      f'Speed {speed}')
         ax.set_xlabel('RMS Acceleration [m/s$^2$]')
-        fig.set_size_inches((MAXWIDTH*MM2INCH, 0.4*MAXWIDTH*MM2INCH))
+        fig.set_size_inches((90*MM2INCH, 0.4*90*MM2INCH))
         fname = 'tukey-{}-bicycle-{}-{}.png'.format(SIGNAL, surf, speed)
         fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
         plt.clf()
@@ -807,9 +807,9 @@ complete_stats_df = complete_stats_df.reset_index(drop=True)
 # table you will have uncut values)
 shock_df['Peak Value [m/s/s]'] = shock_df['Peak Value [m/s/s]'].clip(upper=16*9.81)
 
-######################################
+#############################################
 # Figure: Shock test comparison -  All Trials
-######################################
+#############################################
 shock_html = []
 shock_html.append(H2.format('Shock test Comparison'))
 msg = 'Compare maximum acceleration across vehicles and speed.'
@@ -818,7 +818,7 @@ p = sns.stripplot(
     data=shock_df,
     x="Vehicle",
     y="Peak Value [m/s/s]",
-    hue='Mean Speed [m/s]',
+    hue='Target Speed [km/h]',
 )
 p.set_ylabel(r'Vertical Acceleration Shock test [m/s$^2$]')
 p.set_xticklabels(

### 2025-01-31 src/html_templates.py
Make comparison plots wide again.

@@ -22,8 +22,8 @@ INDEX = """\
     <br>
     Generated from Git hash: {githash}
     <br>
-    <strong>Warning: These results are preliminary, do not rely on them until a
-    supporting paper is published.</strong>
+    <strong style="color:red;">Warning: These results are preliminary, do not
+    rely on them until a supporting paper is published.</strong>
   </p>
   <p>
     This page examines the signal: <strong>{signal}</strong>.
@@ -59,8 +59,6 @@ INDEX = """\
   </p>
 {boxp_html}
 
-  <h1 id="shock">Shock Test Comparison Across Vehicles</h1>
-  <hr>
 {shock_html}
 
   <h1 id="iso">ISO 2631-1 Weights</h1>

### 2025-01-31 src/website.py

@@ -179,7 +179,8 @@ for surf in ('Tarmac', 'Paver Bricks'):
         ax.set_title(f'Cargo Bicycle Tukey Comparison for\nSurface {surf} and '
                      f'Speed {speed}')
         ax.set_xlabel('RMS Acceleration [m/s$^2$]')
-        fig.set_size_inches((90*MM2INCH, 0.4*90*MM2INCH))
+        # TODO : make these actual width in paper
+        fig.set_size_inches((MAXWIDTH*MM2INCH, 0.4*MAXWIDTH*MM2INCH))
         fname = 'tukey-{}-bicycle-{}-{}.png'.format(SIGNAL, surf, speed)
         fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
         plt.clf()
@@ -211,6 +212,7 @@ for surf in stroller_df['Road Surface'].unique():
     comp_tab.plot_simultaneous(ax=ax)
     ax.set_title(f'Stroller Tukey Comparison for Surface {surf}')
     ax.set_xlabel('RMS Acceleration [m/s$^2$]')
+    # TODO : make these actual width in paper
     fig.set_size_inches((MAXWIDTH*MM2INCH, 0.4*MAXWIDTH*MM2INCH))
     fname = 'tukey-{}-stroller-{}.png'.format(SIGNAL, surf)
     fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)

### 2025-01-31 main.tex
Updated the tex files to v3.

--- 2024-12-26 main.tex
@@
+% Style Guide
+% - use British English, exceptions: stroller vs buggy or pram, sidewalk vs pavement
+% - active voice is preferred over passive voice, minimize passive
+% - use past tense to describe what we did
+% - try to avoid subsub sections (keep to two layers)
+% - use siunitx for all units, surround with brackets [\si{\meter}], note the
+%   common definitions, e.g. \si{\kph}
+% - use tilde ~ to prevent line breaks in words that should stay together, e.g.
+%   something~\cite{} or ISO~2631-1
+% - only use "significant" when referring to statistical significance
+% - use "infant", not "baby"
+% - use "bicycle" instead of "bike"
+% - use "amplitude spectrum/spectra" for what we plot
+% - use "standard" not "norm"
+% - use the oxford comma
+% - TODO: acceleration vs accelerations ?
+% - Data breakdown terms are "Session", "Trial" (of specific "Scenario"),
+%   "Repetition"
+% -  Referencing: Figure~\ref{fig:name}, Equation~\ref{eq:name},
+%    Section~\ref{sec:name}, Appendix~\ref{app:name}, Table~\ref{tab:name}
+% - inline urls \href{https://www.e.com}{my hyperlink}
+% - do not use [h] for figures except in appendix, let latex place them where it
+%   wants
+% - figures should be 300 dpi and sized to the actual physical dimension in the
+%   paper
+% Other Notes
+% - be careful about editing autogenerated tables, they will be overwritten
+
 \documentclass[a4paper]{article}
@@
   urlcolor=blue,
+  citecolor=blue,
 }
 
+% NOTE : Use as \si{\kph} or \si{\mps}
+\def\kph{\kilo\meter\per\hour}
+\def\mps{\meter\per\second}
+
 \title{
-  DRAFT: v1 \\
-  Vibration Characterization of Babies\\
-  Transported in Strollers and Cargo Bicycles\\
+  Vibration Characterisation of Strollers and\\
+  Cargo Bicycles for Transporting Infants\\
+  \vspace{2mm}
+  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
   \vspace{2mm}
@@
 }
-\author{Gabriele Dell'Orto \and Brecht Daams \and Riender Happee \and Jason K. Moore}
+% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
+\author{
+Gabriele Dell'Orto \and
+Brecht Daams \and
+Riender Happee \and
+Georgios Papaioannou \and
+Arjo J. Loeve \and
+Jesper Meijerink \and
+Thomas Valk \and
+Jason K. Moore
+}
 
@@
 
+\color{red}
 \section*{\centering Notice}
 %
-\textbf{This is a draft report. The values and results must be considered
-preliminary and may change as the analysis is refined and rechecked.}
-
-\section*{\centering Acknowledgements}
-%
-Thomas Valk and Jesper Meijerink helped design and perform the experiments.
-Georgios Papaioannou and Arjo Loeve gave advice on the experimental design and
-analyses.
+This report or its findings may not be shared outside of VeiligheidNL and
+TU~Delft without further review of the methods and findings.
+We also need to carefully consider possible adverse effects of dissemination. In
+particular we need to consider:
+%
+\begin{itemize}
+  \item System manufacturers being negatively affected by publication.
+    Organisations like Consumentenbond typically give manufacturers access to
+    draft test results, and give an opportunity to react. We can do this as
+    well. We may now remove Brand and type information from this report. In a
+    later stage we may test multiple products and then publish a comparison.
+  \item Stimulating car use to transport infants and children. We don't want
+    newspaper/online headlines which are overly alarming, and later turn out to
+    be debatable.
+\end{itemize}
+\color{black}
+
+\begin{abstract}
+  Infants are transported in strollers and in baby seats mounted in cargo
+  bicycles. The infants experience whole-body vibration during the associated
+  walking and cycling trips, but there is little existing knowledge about
+  associated comfort and health effects. To improve this, we measure the seat
+  pan acceleration of five strollers and two styles of cargo bicycles with dummy
+  infants representing ages 0 to 9 months over six different road surfaces of
+  varying road roughness at typical travel speeds. The five strollers included
+  three modern systems and two vintage systems with some level of suspension.
+  One cargo bicycle had electric support enabling speeds up to 25~\si{\kph}. We
+  report average seat pan acceleration for 78 different scenarios and
+  investigate the effects of road surface, vehicle, seat type, and travel speed.
+  Using the whole-body vibration ISO standards, we show that rough road
+  surfaces, amplified by travel speed, may have health risks for travel
+  durations as low as \SIrange{10}{30}{\min}. Stroller designs from 50 years ago
+  significantly reduce vibrations, relative to most modern strollers we tested,
+  indicating the need for return of suspension elements. Cargo bicycles ridden
+  at the maximum electric bicycle speed over paver bricks can cause
+  accelerations that should likely be avoided except for only the shortest of
+  durations until more direct evidence of risks to infants is studied. Standards
+  are needed for infant transport testing and evaluation, designers need to
+  incorporate better suspension for infants, and research is needed to develop
+  clear and direct connections to health and comfort effects.
+\end{abstract}
+
+\newpage
+
+\tableofcontents
+
+\newpage
 
 \section{Introduction}
-%
-This paper reports on the vibration experienced by infants of different ages
-when transported in cargo bicycles and strollers. Vibration can be related to
-discomfort and might lead to negative health consequences. However, the topic is
-poorly addressed in scientific literature, and only a few studies focus on the
-effect of vibration on babies. To measure the actual vibration transmitted to
-the babies, we equipped three strollers and two cargo bicycles with inertial
-measurement units (IMU) and conducted several experiments across different road
-surfaces and travelling speeds, using dummies representing the size of 0, 3, and
-9 months old babies. We present analysis in the time and frequency domains,
-allowing us to compare vertical accelerations at the baby-seat interface, as
-recommended by ISO-2631-1. We investigate the influence of different variables
-on vibration, such as type of vehicle, baby seat, travelling speed, dummy size
-and mass, and road surfaces.
+%Paragraph to introduce baby transport
+When a baby is born, it is not able to walk. To move around or travel, it must
+be either carried by adults or transported in a suitable means of wheeled
+transport. Until about a century ago,  babies mainly stayed at home. This still
+is customary in some non-Western cultures. A century ago, perambulators were
+used to transport infants outdoors. However, mothers were advised that a playpen
+in the garden is healthier than the use of a perambulator, partly because the
+vibrations generated by a perambulator were deemed not comfortable and even
+harmful for the baby~\cite{behrend1931}, even though in those days perambulators
+had ample suspension. Since about 1970, cars became ubiquitous and the heavy and
+sizeable perambulators became strollers: lighter and smaller products to enable
+easy transportation in a car. Over the years, new means of transportation came
+into use for infants: cars with a child car seat, bicycles with a bicycle seat
+and cargo bicycles with either a car seat or a baby shell.
+
+%Paragraph to introduce baby vibration in transportation
+All means of transport cause vibration, which is transferred to the infant
+sitting or lying in it. Unlike the advice in the 1930s, vibration is seemingly
+not a subject of attention in the present design of these products. On the
+contrary, modern strollers do not have much suspension and cargo bicycles which
+generate more vibration are increasingly used for infants. Interestingly, in the
+literature we could find little about the maximal vibration load that babies and
+older children can receive during transport without discomfort or harm, and
+vibrations generated by infant transport are also only sparsely investigated.
+Therefore the effect of transport on infant comfort and health can not easily be
+assessed. To establish the amount of vibration that infants are subjected to in
+transportation products, we investigated the vibration that infants receive
+during transport in strollers and cargo bicycles.
+
+% Paragraph about motivation
+Cycling, one of the active transportation modes, is advantageous for
+health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\) emissions,
+congestion, and air pollution~\cite{Neves2019}. As a result, bicycles are
+increasingly used as a means to deliver goods to consumers, and also for daily
+commuting to work and personal matters (shopping, commuting with
+children/infants, and others). Among all journeys in the EU, 20-40\% are by
+bicycle or on foot, with bicycle trips most frequent in the Netherlands,
+Denmark, and Sweden and less frequent in Finland. Various countries and
+employers provide incentives to increase the use of bicycles. However, some
+challenges need to be overcome to secure the wide acceptance and use of active
+transportation modes. One of these challenges is the comfort levels experienced
+by riders and passengers (i.e., infants/children in cargo bicycles), which is a
+multifaceted aspect~\cite{ayachi2015identifying} and critical for the wide
+acceptance and use of bicycles as a daily means of transport. Meanwhile, this is
+a topic that is of great interest and requires attention when it comes to
+infants' transportation with strollers or bicycles.
+
+% Paragraph about comfort in bicycles
+The research on cyclist comfort is a natural starting point for investigations
+of similar road-induced vibrations for infants.
+Comfort on bicycles~\cite{too1990biomechanics} is mainly affected by physical
+comfort and the impact of environmental factors (weather, geometry of the route,
+and road roughness).  
+Physical comfort is related to mechanical (bicycle and component design),
+biomechanical (whole-body vibrations, human body dynamics, and kinematics) and
+physiological factors (individual characteristics, e.g. sex, body size, weight
+and others).
+While there is extensive literature exploring the impact of environmental
+factors (i.e., irregular road surface quality, weather conditions) on cyclists'
+comfort~\cite{Stinson2003,Hagemeister2003,ayachi2015identifying,Verhoeven2017,Teixeira2020},
+there is limited work on understanding the biomechanical and physiological
+factors of comfort while being carried by bicycle (infants/children in bicycle
+seats, on cargo bicycles, or in trailers). A particular concern is the transport
+of infants under one year, who cannot well express any experience of discomfort
+or pain.
+Similar concerns are raised when it comes to strollers, where infants are also
+exposed to vibrations induced by roads. 
+In this paper, we will explore biomechanical comfort by assessing the whole-body
+vibrations that could be experienced by transported infants both in cargo
+bicycles and strollers, and evaluating potential health risks and discomfort
+that might arise.
+
+% Paragraph about transmission of vibrations
+Biomechanical comfort is mostly related to the vibrations induced by road
+irregularities and transmitted via the vehicle to the human body and head while
+being driven~\cite{too1990biomechanics}. 
+According to the literature, road irregularities are a critical factor for the
+amplitude of the resulting vibrations experienced by the bicyclists and
+passengers, as the vibrations induced on the body and head are not efficiently
+isolated due to the lack of or inadequate suspension systems in most of the
+bicycle models~\cite{vasudevan2017comparison} or strollers.
+The bicycle or stroller design and its specific configuration can affect the
+sitting posture, and eventually the transmissibility of the
+vibrations~\cite{Brand2020,Verma2016}.
+The sitting posture can also vary in case of children/infants who may be
+transported sitting or lying down in a different posture and location than the
+cyclist (e.g. above a wheel when in a bicycle seat) and in/on a different `seat'
+(a car seat, bicycle seat, stroller seat, or cot). 
+These all influence the level of whole-body vibrations and the transmission of
+the vibrations from the seat to the body and head.
+Furthermore, the amplitude of the vibrations experienced by
+bicyclists/passengers/transported infants while biking or being transported in a
+stroller may increase because of increased travelling speed either due to
+running with a stroller or due to the increased power offered by electric
+bicycles (with and without trailers).
+For the latter, the average speed of electric bicycles and speed pedelecs is
+19\% higher (21.0~\si{\kph} and up to 63\% higher (28.1~\si{\kph}),
+respectively, than the average speed of conventional bicycling~\cite{SWOV2022}.
+The intensity of these vibrations could become even more critical with the
+change of load, which could be related with age and size of the infant/children
+transported. However, there is limited literature exploring the whole-body
+vibrations of infants and children being transported by bicycles with trailers,
+cargo bicycles, stroller seats and others
+~\cite{Ota2012,Ota2014,Kanya-Forstner2020, vanDriessche2018,
+Schwanitz2020,MalteChildComfort2022}.
+At the same time, the available literature is mostly focusing on comfort rather
+than health risks.
+
+% Paragraph about children in bicycles
+One of the research fields closely related to vibrations acting on infants
+during transportation is that of inflicted head injury by shaking trauma
+(IHI-ST). However, there is a lack of reliable, applicable, validated injury
+thresholds for assessing IHI-ST risks~\cite{hutchinson2024modeling}. Similarly,
+even if there are significant indications that the vibration amplitude affects
+comfort in bicycles or strollers, there are no standard assessment methods or
+guidelines available with regards to their design. ISO~2631~\cite{ISO2631}, the
+international standard for assessing whole-body vibrations, was derived using
+datasets on motion platforms, adults as human participants and sitting postures
+which are adopted in passenger vehicles rather than on bicycles.
+This inconsistency was captured by Gao~et~al.~\cite{Gao2018}, who derived
+different limits of comfort for adults riding on bicycles based on their
+subjective feedback, compared to the vibration limits suggested by
+ISO~2631-1.
+In addition, the exposure time to the vibrations is not considered as a factor
+of comfort by the ISO~2631-1, despite having a clear impact on health risks
+according to the European Directive (2002/44/EC, 2002)
+\cite{directive2002directive}.
+
+% Paragraph Potential effects of vibrations on adults
+Despite the lack of clarity with regards to comfort assessment or inflicted head
+injury by shaking trauma for children/infants on bicycles, there are clear
+indications in the literature that these should be explored and considered.
+About 36\% of males and 42\% of females in a total sample of 900 people had
+various complaints about comfort~\cite{groenendijk1992sitting}.
+Discomfort for both men and women occurred even during short bicycle trips
+(\SIrange{3}{10}{\kilo\meter}). However, results from research into comfort of
+adult cyclists can not be applied directly to infants or children sitting or
+lying in transportation systems.
+
+Schwanitz~et~al.~\cite{Schwanitz2020} assessed accelerations in a child bicycle
+trailer riding over smooth asphalt, gravel, and cobblestones using ISO~2631-1
+weighted RMS vertical accelerations.
+Anthropomorphic children shaped sandbag dummies (baby and toddler sizes) were
+used as lumped masses. According to the results, tyre pressure and the number of
+passengers had no significant effect on vibration magnitude, but road surface
+and travel speed did. 
+The baby sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
+the toddler sized dummy (10~\si{\kilo\gram}), while the measured values
+generally exceeded the ISO~2631-1 vibrational comfort of adults.
+Rothhämel~et~al.~\cite{MalteChildComfort2022} conducted measurements using a
+trailer seat and a tadpole configuration three-wheel cargo bicycle on smooth
+asphalt and cobblestones for speeds between \SIrange{10}{20}{\kph}. 
+After weighting the accelerations using ISO~2631-1 methods, they found a large
+increase of the vibration amplitude on cobblestones compared to asphalt on the
+same speed range. The child trailer exhibited larger weighted RMS accelerations
+than the cargo bicycle with the child seat between the front wheels. 
+Both the trailer and cargo bicycle child seats had generally larger magnitude
+vibrations than experienced in an automobile seat travelling at 30~\si{\kph} on
+a rough road \cite{gromadowski2013analysis}. Rothhämel and
+Liu~\cite{rothhamel2023comfort} conducted measurements with a
+6.5~\si{\kilo\gram} mass representing an infant with various tyre pressures. All
+their values fell into the ``extremely uncomfortable'' zone for the ISO~2631-1.
+
+In addition to the studies with dummies or lumped masses representing
+infants, Kanya-Forstner~\cite{Kanya-Forstner2020} measured acceleration in
+bicycle child trailers with human subjects aged 12 months to 6 years over
+asphalt and gravel terrain (averaged speed of 12~\si{\kph} over the
+20~\si{\minute} ride). 
+According to the health assessment using ISO~2631-1, the vibrations are similar
+to the ones experienced in car seats in vehicles and illustrated moderate or low
+health risk for a 2~\si{\hour} duration.
+On the other hand, if not corrected for duration, the values point to moderate
+and high risks. The terrain type had the greatest influence on vibration
+exposure levels followed by trailer type, while gel cushions as support did not
+significantly influence vibration measured at the seat/pan interface. Hence,
+there is a need to re-focus on the impact of vibrations on infants and
+children's health and comfort~\cite{rybarczyk2020physiological} to ensure the
+safe, comfortable and wide use of bicycles.
+
+% Don't edit, working to change the following paragraph
+In the context of infants transportation with stroller seats, Kok
+Siong~\cite{lim2018study} carried out an indoor and an outdoor experiment to
+capture the vibrations transmitted onto the seat and backrest of a baby
+stroller, using weights from \SIrange{4}{14.14}{\kilo\gram}, and  a child
+subject of 10.30~\si{\kilo\gram} as well as a dummy weighing
+10.30~\si{\kilo\gram}. 
+The comfort levels for the indoor testing were labelled as `Fairly
+uncomfortable' to `A little uncomfortable', but the outdoor testing resulted in
+`Extremely uncomfortable' and `Fairly uncomfortable' values. They used both a
+child and dummy for the experiments, identifying similar patterns. However, the
+results still consider ISO~2631-1 standard, which is designed for adults and
+specific postures. In a similar research, Sierzputowski~
+et~al.~\cite{sierzputowski2021pilot} investigated vibrations induced in a modern
+and
+an older stroller, when moving on different surfaces: asphalt road, concrete
+paving blocks, concrete plates, dirt road, lawn and damaged concrete. The
+obtained weighted RMS acceleration values based on ISO~2631-1 were several times
+in the range of the highest discomfort (>2~\si{\mps\squared}). 
+Another research which included also children as test subjects was conducted by
+Okajima~et~al.~\cite{okajima2020dynamic} measuring vibrations that seven
+children received, sitting upright in a stroller, when riding over a protrusion
+(13x60 mm) with either one wheel or two wheels. 
+The children were 3 to 6 years old, boys and girls, weighing
+\SIrange{15.94}{19.96}{\kilo\gram} and measuring
+\SIrange{98.0}{112.4}{\centi\meter} in length. 
+Based on the results, the infant’s head and chest exhibit strong vibrations at
+1~\si{\hertz} along all three axes (x,y and z), vibrate easily along the
+y-direction at 2~\si{\hertz}, and are less likely to vibrate at more than
+8~\si{\hertz}. 
+This result is critical as this range of frequencies is very common in bicycles
+and strollers. However, they did not assess the comfort and the health risk when
+the children were exposed to these vibrations. 
+Despite significant research on the effect of whole-body vibrations on
+children's comfort, there is limited research on infants.
+
+This paper reports on the vibration induced on infants of different ages when
+transported in strollers and cargo bicycles. 
+Vibration can be related to discomfort and might lead to negative health
+consequences. However, the topic is poorly addressed in scientific literature,
+and only a few studies focus on the effect of vibration on babies as reviewed
+above. 
+To measure the actual vibration transmitted to infants, we equipped five
+strollers and two cargo bicycles with inertial measurement units (IMU) and
+conducted 78 experiments on different road surfaces and travel speeds, using
+dummies representing the size and mass of 0, 3, and 9 months old infants.
+We present results in the time and frequency domains, which allows comparing
+vertical accelerations at the baby-seat interface, as recommended by ISO~2631-1
+standards for vibration discomfort.
+We investigated the influence of different variables on vibration, such as type
+of vehicle, baby seat, travelling speed, dummy size and mass, and road surfaces
+and provide recommendations to users, designers, and future researchers based on
+the findings.
 
@@
 %
-\subsection{Experimental Methodology}
-%
-In this section, we describe the measurement equipment used and the protocol
-followed during the experimental campaign.
-
-\subsubsection{Description of Test Equipment}
-%
-We conducted the experimental campaign using three different strollers, two
-cargo bicycles, and two baby seats, chosen for their popularity and/or
-distinctive features. The test involved three baby dummies representative of
-various ages (different sizes and masses).
-
-\paragraph{Strollers}
-%
+\subsection{Test Equipment}
+%
+Vibration measurements were conducted at approximate constant speed using five
+different strollers, two cargo bicycles, and two baby
+seats~\footnote{Appendix~\ref{app:equipment} provides figures and technical
+descriptions of all the strollers and cargo bicycles.}, chosen for their
+popularity and/or distinctive features:
+
 \begin{description}
-  \item[Maxi-Cosi Street Plus] Among the most popular brands, this stroller comes
-  with a cot configuration (0-3 months) and a baby seat option. It has large
-  wheels, with only a marginal suspension system.
+\item[Strollers] A selection of vintage and modern strollers for carrying
+infants. The modern strollers are configurable as cots for newborns and as seats
+for older infants.
+%
+\begin{description}
+  \item[Maxi-Cosi Street Plus] This stroller comes
+  with a cot configuration (0-3 months) and an infant seat option. It has large wheels, with only a marginal suspension system.
   (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
-  \item[Stokke BABYZEN YOYO 0+] It is the smallest foldable stroller on the
-  market, it has only a marginal suspension system and smaller wheels compared
-  to the other strollers on the market. It can be considered the ideal choice
-  for holidays, being one of the few buggies that can be taken as hand
-  luggage on the plane.
+  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the
+  market. It has only a marginal suspension system and smaller wheels compared to those of other strollers available on the market.
   (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
   rented for the experiment})
-  \item[Bugaboo Fox 5] It is featured by large wheels, and a suspension system
-  which makes it an all-terrain stroller (according to the manufacturer). It has
-  a large puncture-proof tyres and an air-permeable mattress.
+  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system
+  that makes it an all-terrain stroller according to the manufacturer. It has large puncture-proof tyres and an air-permeable mattress.
   (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
   website})
+  \item[Green Machine] An unknown brand vintage perambulator, dating
+  approximately from the 1970's that includes a leather strap suspended cot in a
+  metal frame. The wheels are relatively large in diameter compared to the
+  modern strollers.
+  \item[Old Rusty] An unknown brand vintage seat-style stroller from
+  approximately the 1970's that includes a metal spring suspension system and
+  wheels that are slightly larger than the modern strollers.
 \end{description}
-
-\paragraph{Cargo Bicycles}
+\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
+seats can be mounted.
 %
 \begin{description}
-  \item[Urban Arrow Bicycle] This is a popular electric cargo bicycle in The
-  Netherlands. This vehicle has two inline wheels which makes it roll into the
-  curve like a regular bicycle. It is featured by a long frame that can carry
-  loads usually placed in between the rider and the front wheel. It can fit
-  various accessories, including baby seats, rain covers, etc.
+  \item[Urban Arrow Bicycle] A popular electric cargo bicycle in The
+  Netherlands. This vehicle has two inline wheels which makes it roll into
+  curves like a regular bicycle. It is featured by a long frame that can carry
+  loads (e.g. a child in a car seat or baby shell) placed in between the rider
+  and the front wheel. 
   (\href{https://urbanarrow.com/}{Urban Arrow website})
-  \item[Keiler Tricycle] This is a tadpole (two wheels in the front, one in the
-  rear) cargo tricycle without electric assist. This vehicle will not roll in
+  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
+  rear) cargo tricycle  without electric assist. This vehicle will not roll into
   curves. However, differing road surface unevenness at the left and right front
-  wheel will induce lateral roll and lateral acceleration in infants. We
-  added masses in specific locations to simulate the presence of an electric
-  motor and battery package.
- (\href{https://kashop.nl/product/keiler-bakfiets/}{Product Webpage}) 
+  wheel will induce lateral roll and lateral acceleration in infants. We added
+  masses in specific locations to simulate the presence of an electric motor and
+  battery package. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
+  Webpage}) 
 \end{description}
-
-\paragraph{Baby Seats}
-
-These baby seats were mounted in the cargo bay of the two cargo bicycles.
+\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
+cargo bicycles.
 %
 \begin{description}
-  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] This seat can be adapted to
-    cargo bicycles with a proper fixing system (e.g. ``Urban Arrow Baby Car Seat
-    Adapter''). It comes with an integrated suspension system which is part of
-    the adapter.
-    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi Webpage})
-  \item[Melia Baby Shell]. The baby seat is meant for babies from 2 to 9 months,
-    specifically designed for cargo bikes.
-    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia Webpage})
+  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
+  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
+  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
+  adapter was used in both cargo bicycles.
+    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
+    Webpage})
+  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
+  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
+  cargo bicycles.
+    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
+    Webpage})
 \end{description}
-
-We conducted tests using three different dummies, of various sizes and masses
-according to the desired ages of 0, 3 and 9 months. We considered the use of
-``crash test dummies'' which are designed and commonly used to test
-child seats in cars in crash conditions. However, the nearest available body
-sizes for crash test dummies were a 6-weeks Q-dummy, a 6-months Crabi dummy, and a
-12-months Q-dummy. These 3 dummies are of a fundamentally different design,
-hampering comparison, and do not match the desired body size. Moreover, these
-child dummies have dynamic properties designed for crash conditions, and use
-scaling of adult biomechanical data, rather than child data.
-Testing with real children would be unethical for the most severe conditions
-tested, and would create challenges in terms of reproducibility.
-Hence we bought and adapted dummies available in a wide range of postures. We
-bought ``reborn'' dummies from a webshop specialising in dolls and dummies
-(\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). We filled the dummies
-with cat litter sand to reproduce the exact weight needed for testing. Cat
-litter sand indeed features smooth and round-shaped grains, which do not
-damage the dummies' material (fabric and plastic). The weight and body height of
-the dummies are average measures for children of exactly 0, 3 and 9 months old.
-We wanted to use the measurements from Steenbekkers \cite{Steenbekkers1993}. But
-the researchers provided the results only per three-month group, which did not fit our
-age categories. Therefore, we decided to use the growth charts to determine the average weight
-and body height at the right ages. Growth charts (`groeidiagrammen') are used by
-doctors to assess the growth of babies. The average weight at 0 months and the
-average body height at all three ages are derived from Dutch growth charts.
-Measurements of Dutch children are used because the Dutchies are the target group of
-VeiligheidNL. Dutch children are also the tallest in Europe. The average weight
-of 3 and 9 months children is derived from French growth charts. French children
-are the smallest in Europe. At 3 months, the weight difference is 4 ounces and
-at 9 months, it is 3 ounces compared to Dutch children.  
+\end{description}
+
+The tests involved three baby dummies with sizes and weights representative of
+newborns and 3 and 9 month old infants. Newborns (`0 months') are the youngest
+(smallest, lightest) children that are transported in strollers with a cot.
+Three month old infants are the youngest (smallest, lightest) children that are
+transported in cargo bicycles, fixated in a baby car seat or baby shell. Nine
+month old infants are the youngest (smallest, lightest) that can sit up straight
+by themselves and thus can be transported sitting up straight, in a stroller
+with a seat or on the bench of a cargo bicycle.
+
+We considered the use of ``crash test dummies'' (also known as anthropomorphic
+test devices or ATD's) which are designed and commonly used to test child seats
+in car crash tests. However, the nearest available body sizes for crash test
+dummies were a 6-weeks Q0-dummy, a 6-months Crabi dummy, and a 12-months Q-dummy
+(Humanetics, Farmington Hills, USA). These 3 dummies are of a fundamentally
+different design, hampering comparison, and did not match the desired body
+sizes. Moreover, these child dummies have dynamic properties designed for crash
+conditions, and they were designed based on scaling of adult biomechanical data
+rather than child data, so in that respect there is no benefit over other
+dummies.
+
+Testing with real infants would be unethical, and would create challenges in
+terms of reproducibility. Hence we bought and adapted ``reborn'' dummies
+available in a wide range of postures from a webshop specialising in dolls and
+dummies (\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). The dummies were
+filled with a mixture of cat litter sand and water to reproduce the exact
+weights needed for testing. Cat litter sand features smooth and round-shaped
+grains, which do not damage the dummies' materials (fabric and plastic). The
+weight and body height of the dummies were made to match the average measures
+for children of 0, 3 and 9 months old.
+
+We wanted to use the measurements from Steenbekkers~\cite{Steenbekkers1993}.
+However, this research provided the results only per three-month group, which
+did not fit our age categories. We decided to use the growth charts used by
+clinicians to assess infant growth to determine the average weight and body
+height at the right ages. The average weight at 0 months and the average body
+height at all three ages are derived from Dutch growth charts. We used
+measurements of Dutch children because they are the target group of the project
+funder, VeiligheidNL. Dutch children are also the tallest in Europe. We derived
+the average weight of 3 and 9 months old children from French growth charts.
+French children are the smallest in Europe. At 3 months, average Dutch children
+weigh 113 gram more than average French children and at 9 months, the difference
+is 85 gram. The following lists the dummies used:
 %
@@
   (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
+
   \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
@@
 
-To achieve a realistic mass distribution in the body of the dummies, it is
-important to fill each limb with the proper amount of sand. To do this, we
-simplified the geometry of each body segment according to defined basic
-geometric shapes: we assumed a sphere for the head, and cylinders for the torso,
-upper arms, upper legs and lower legs, according to what was stated in
-\cite{Snyder1977}. We also assumed an equal density of each limb, and we
-rescaled the measurements of the limb segments reported in \cite{Snyder1977} to
-match the dimensions of our dummies. In doing so, we were able to calculate the
-volume of each segment, thus the mass of each limb of the dummies (assuming a
-density of 1000~\si{\kg\per\cubic\meter}).
-
-\subsubsection{Description of Measurement Equipment}
-%
-Linear acceleration and angular velocity was measured using five IMUs.
-Specifically, we used a Consensys Shimmer3 IMU with a Consensys Base 6U.01 dock.
-The Shimmer units were updated to the firmware version LogAndStream v0.11.0, and
-managed via the software ConsensysBASIC v1.6.0-64bit on a Laptop Dell 7310, OS
-Microsoft Windows 10. We 3D printed supports for the sensors to ensure a firm
-clamp between the sensor and the bicycle/stroller tested (visible in
-Figure~\ref{fig:sensors_UA}). Each vehicle was equipped with five IMUs, as
-listed below. The pictures of sensors mounted on the cargo bicycle Urban Arrow
-are depicted in Figure~\ref{fig:sensors_UA}. The location and orientation of the
-sensors for Urban Arrow equipped with the Melia baby shell are reported in
-Figure~\ref{fig:tech_drawing_UA_Melia}, both for lateral and front view.
-Similarly, the Bugaboo configured to carry 0 months babies in the baby cot is
-shown in Figure~\ref{fig:tech_drawing_Bugaboo0}.
-%
-\begin{figure}
-  \centering
-  \subcaptionbox{IMU on the front fork}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/FW_UA.png}}
-  \subcaptionbox{IMU on the rear wheel hub}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/RW_UA.png}}
-  \subcaptionbox{IMU under the cargo bay}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/BT_UA.png}}
-  \subcaptionbox{IMUs on the baby seat surface}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/Maxicosi_sensors_UA.png}}
-  \caption{IMU locations on the Urban Arrow cargo bicycle. The white 3D printed
-  sensor supports are visible in (a) and (c).}
-  \label{fig:sensors_UA}
-\end{figure}
-%
-\begin{figure}
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA_Melia_lateral.PNG}}
-  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_UA_Melia_front.PNG}}
-  \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
-  Melia baby shell. Here you can see the locations from the front and the
-  lateral view. All the measurements are in \si{\mm}. You can also see the
-  sensors' orientation. The reference system from which we draw the measurements
-  is highlighted in red and placed on the rotational axis of the front wheel.}
-  \label{fig:tech_drawing_UA_Melia}
-\end{figure}
-%
-\begin{figure}
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_lateral.PNG}}
-  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_front.PNG}}
-  \caption{IMU locations on the Bugaboo Fox 5 stroller in the configuration for
-  the 0 month baby. Here you can see the location from the front and the lateral
-  view. All the measurements are in \si{\mm}. You can also see the sensors'
-  orientation. The reference system from which we draw the measurements is
-  highlighted in red, and placed on the rotational axis of the front wheel.}
-  \label{fig:tech_drawing_Bugaboo0}
-\end{figure}
+To achieve a realistic mass distribution in the body of the dummies, each limb
+was filled with a proper amount of wet sand (for the 0-month dummy, water was
+added to achieve the correct weight). To do this, we simplified the geometry of
+each body segment according to the defined basic geometric shapes: a sphere for
+the head, and cylinders for the torso, upper arms, upper legs and lower legs,
+according to what was stated in~\cite{Snyder1977}. We also assumed an equal
+density for each limb, and we rescaled the measurements of the limb segments
+reported in \cite{Snyder1977} to match the dimensions of our dummies. In doing
+so, we were able to calculate the volume of each segment, thus the mass of each
+limb of the dummies (assuming a density of 1000~\si{\kg\per\cubic\meter}).
+
+\subsection{Measurement Equipment}
+%
+Linear accelerations and angular velocities were measured tri-axially using
+Consensys Shimmer3 IMUs with a Consensys Base 6U.01 dock (Shimmen Sensing,
+Dublin, Ireland). The IMUs were updated to firmware version LogAndStream v0.11.0
+and managed via the software ConsensysBASIC v1.6.0-64bit on a Dell 7310 laptop
+with Microsoft Windows 10. We 3D printed supports (material: PLA) for the
+sensors to ensure a firm clamp between the sensor and the bicycle/stroller
+tested (Small white and orange boxes visible in Figure~\ref{fig:sensors_UA}).
+Each vehicle was equipped with five IMUs, as listed below. All the drawings
+showing the vehicles and the sensors' location are reported in
+Appendix~\ref{app:equipment}.
 %
 \begin{enumerate}
-  \item \textbf{Rear Wheel} The sensor was placed on the wheel hub (cargo
-  bicycles) or clamped to the wheel (strollers). The purpose of this sensor is
-  for a travel speed measurement. We can derive the travelling (longitudinal)
-  speed according to:
+  \item \textbf{Rear Wheel} This IMU was placed on the wheel hub (cargo
+  bicycles) or clamped to the wheel (strollers) for measuring the travel speed.
+  The travelling (longitudinal) speed was derived according to:
   %
   \begin{align}
-    v = \si{\omega} \cdot r
+    v = \omega \cdot r
     \label{eq:long-speed}
@@
   %
-  where \si{\omega} is the angular speed of the vehicle (from IMU gyroscope aligned with the wheel's axis) and $r$ is the radius of the wheel.
-  \item \textbf{Front Wheel} The sensor was mounted on the front wheel fork (the
-  caster wheel for the stroller). This is the measurement point closest to the
-  ground for a non-rotating sensor. The purpose of this sensor is to measure the
-  road roughness filtered out by the tyres.  
-  \item \textbf{Frame} As for the cargo bicycle, the third sensor was placed
-  below the frontal cargo bay, clamped to the frame. It can give us an
-  understanding of the damping characteristics of the bicycle frame, together
-  with an estimation of the effect of the suspension system. Regarding the
-  stroller, the sensor was placed under the baby seat.
-  \item \textbf{Seat Head} Sensor mounted into the baby seat, directly in
-  contact with the dummy's head. It measured the vibration transmitted to the
-  head contact point.
-  \item \textbf{Seat Buttock} This sensor was taped into the baby seat, at the
+  where \(\omega\) is the angular speed of the wheel (obtained from the IMU's
+  gyroscope aligned with the wheel's axis) and \(r\) is the radius of the wheel.
+  \item \textbf{Front Wheel} This IMU was mounted on the front wheel fork (the
+  caster wheel for the stroller). This was the non-rotating measurement point
+  closest to the ground. The purpose of this sensor was to measure the road
+  roughness filtered out only by the tyres.  
+  \item \textbf{Frame} On the cargo bicycle, an IMU was placed below the frontal
+  cargo bay and clamped to the frame. This was to provide an understanding of
+  the damping characteristics of the bicycle frame, together with an estimation
+  of the effect of the suspension system. On the stroller, the IMU was taped
+  under the baby seat.
+  \item \textbf{Seat Head} IMU taped into the baby seat (on the soft mattress),
+  directly in contact with the dummy's head. This IMU measured the vibration
+  transmitted to the head contact point.
+  \item \textbf{Seat Pan} This IMU was taped into the baby seat, at the
   interface between the dummy's buttock and the baby seat. It measured the
@@
 
-The IMU sensors for the seat head and seat buttock were placed at the surface at
-positions contacting the dummy. This matches the recommended practice in
-vibration testing norms such as ISO-2631-1. This generates acceleration data
-representative of the mechanical load transferred from the seat to the human
-body taking into account the compliance of the seat foams. We set the sampling
-frequency to 910.22~\si{\hertz} for all the sensors. The full-scale range was
-16~g for the accelerometer ("WR" or "wide range" configuration on Consensys
-Shimmer software), and 2000~\si{\degree\per\second} for the gyroscope. All the
-tests were recorded with two GoPro cameras Hero7: one directly mounted on the
-strollers/bicycles to record the relative motion dummy/seat, while the other one
-was held by an experimenter walking or riding alongside the vehicle to have a
-complete overview of the experiment.
-
-\subsubsection{Description of Experimental Protocol}
-%
-We conducted the experimental campaign in Delft, The Netherlands along public
-roads near the Delft University of Technology, Faculty of Mechanical
-Engineering.
-After mounting the sensors in the correct position and reaching the location
-of the experiment, we turned on the sensors to start the experimental session.
-Before each trial, we pushed the vehicle back and forth on level ground to mark
-the beginning of the trial for time synchronizing the sensors.
-For the cargo bicycle test, a single rider conducted the full experimental
-campaign to be consistent across different sessions (rider mass: 59~\si{\kg};
-rider height: 1.70~\si{\m}).
-We gathered data from multiple trials within the same session. The tests were
-conducted on six different surfaces for the strollers with the pusher manually
-keeping consistent walking speed of approximately 5~\si{\kilo\meter\per\hour}
-across different trials by observing a speedometer. We tested on three surface
-scenarios for the cargo bicycles (at different speeds). The test combinations
-are listed below.
+\begin{figure}
+  \centering
+  \subcaptionbox{IMU on the front fork}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/FW_UA.jpg}}
+  \subcaptionbox{IMU on the rear wheel hub}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/RW_UA.jpg}}
+  \subcaptionbox{IMU under the cargo bay}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/BT_UA.jpg}}
+  \subcaptionbox{IMUs on the baby seat surface}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/Maxicosi_sensors_UA.jpg}}
+  \caption{IMU locations on the Urban Arrow cargo bicycle. The white 3D printed
+  sensor supports are visible in (a) and (c). The last figure (d) shows how the
+  sensors were taped to the seat pan and backrest.}
+  \label{fig:sensors_UA}
+\end{figure}
+
+The IMUs for the seat head and seat buttock positions contacting the dummy were
+placed according to the recommended practice in vibration testing standard
+ISO-2631-1. This generates acceleration data representative of the mechanical
+load transferred from the seat to the human body taking into account the
+compliance of the seat foams and the inertia and compliance of the dummy.
+
+The target sampling frequency was 910.22~\si{\hertz} for all IMUs. The
+full-scale range was set to \(\pm\)16~g for the accelerometer (``WR: wide
+range'' configuration on Consensys Shimmer software), and
+\(\pm\)2000~\si{\degree\per\second} for the gyroscope. All tests were recorded
+with two GoPro Hero7 cameras: one directly mounted on the strollers/bicycles to
+record the dummy-seat relative motion, while the other was held by an
+experimenter walking or riding alongside the vehicle to have a complete overview
+of the experiment.
+
+\subsection{Experimental Protocol}
+%
+All tests were conducted in Delft, The Netherlands, on public roads near the
+Delft University of Technology, Faculty of Mechanical Engineering. Latitude and
+longitude of each location along with local photographs of each site are
+provided in Appendix~\ref{app:location}.
+After mounting the sensors and reaching the location of the experiment, we
+turned on the sensors to start the experimental session. Before each trial, we
+pushed the vehicle back and forth on level ground to mark the beginning of the
+trial as an extra time-synchronization measure.
+For the cargo bicycle test, a single rider conducted all trials to be consistent
+across different sessions (rider mass: 59~\si{\kg}; rider height:
+1.70~\si{\m}).
+We tested three types of road surfaces with the cargo bicycles and repeated
+those at different speeds.
+The stroller tests were conducted on six different surfaces with the pusher
+manually keeping a consistent walking speed of approximately
+5~\si{\kilo\meter\per\hour}.
+In all tests, speed was controlled by the pusher or cyclist using a speedometer
+mounted on the stroller handle bar or the steer of the cargo bicycle. We
+gathered data from multiple trials within the same session. The test
+combinations, ``scenarios'', are listed below.
 %
 \begin{itemize}
-  \item \textbf{Strollers} We tried to keep speed as constant and consistent as
-  possible among different trials and sessions. The experimental campaign was
-  conducted using dummies of 0 months and 9 months. Some of the test surfaces
-  are depicted in Figure~\ref{fig:surfaces_stroller} and all are listed below:
+  \item \textbf{Strollers}  The stroller tests were done with the dummies of 0
+  months and 9 months old. All the test surfaces listed below are shown in
+  Appendix~\ref{app:location}.
   \begin{itemize}
@@
       \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
-      \item Shock. A 30x30~\si{\mm} square section aluminium bar was taped on the ground (smooth surface)
+      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar was taped
+      to the ground (smooth surface)
   \end{itemize}
-  \item \textbf{Cargo bicycles} The experimental campaign was conducted using
-  dummies of 0 months and 3 months. Regarding the Keiler tricycle, the speed was
+  \item \textbf{Cargo bicycles} The cargo bicycle tests were conducted using the
+  dummies of 0 months and 3 months. With the Keiler tricycle, the speed was
   limited to 20~\si{\km\per\hour} for safety reasons (due to wobbling), and
-  difficulties to safely keep a constant speed over 22~\si{\km\per\hour}. The test surfaces are listed below:
+  difficulties to safely keep a constant speed over 22~\si{\km\per\hour}. The
+  test surfaces are listed below:
   \begin{itemize}
@@
       \item Paver bricks
-      \item Shock. As mentioned before, we conducted shock test riding over a
-      30x30~\si{\mm} square section aluminium bar, at three speeds: 
+      \item Shock bump: As mentioned before, we conducted shock test riding over
+      a 30x30~\si{\mm} square section aluminium bar, at three speeds: 
       \begin{itemize}
-          \item Low speed scenario: 5~\si{\km\per\hour}
-          \item Medium speed scenario: 12~\si{\km\per\hour}
-          \item High speed scenario: 20~\si{\km\per\hour} for the Keiler
-          tricycle, 25~\si{\km\per\hour} for the Urban Arrow cargo bicycle.
+          \item Low speed: 5~\si{\kph}
+          \item Medium speed: 12~\si{\kph}
+          \item High speed: 20~\si{\kph} for the Keiler tricycle,
+          25~\si{\kph} for the Urban Arrow cargo bicycle
       \end{itemize}
   \end{itemize}
-  \item \textbf{Baby seats} Both were tested on each cargo bicycle using the
-  same mounting systems.
-  \begin{itemize}
-      \item Maxi-Cosi X Joolz Pebble Pro i-Size car seat, it can be adapted to
-      cargo bicycles with a proper fixing system ("Urban Arrow Baby Car Seat
-      Adapter"). It comes with an integrated suspension system (part of the
-      adapter). 
-      \item Melia baby shell. The baby seat is meant for babies from 2 to 9
-      months, specifically designed for cargo bikes.
+  \item \textbf{Baby seats} Both the Maxi-Cosi X Joolz Pebble Pro i-Size and the
+  Melia baby shell were tested on each cargo bicycle using the same mounting
+  systems.
 \end{itemize}
-\end{itemize}
-
-\begin{figure}
-  \centering
-  \subcaptionbox{Paver bricks}{\includegraphics[width=0.45\textwidth]{fig/Klinkers.PNG}}
-  \subcaptionbox{Sidewalk slabs}{\includegraphics[width=0.45\textwidth]{fig/Aula_YOYO.PNG}}
-  \subcaptionbox{Sidewalk pavers}{\includegraphics[width=0.45\textwidth]{fig/Stoeptegels_YOYO.PNG}}
-  \subcaptionbox{Cobblestones}{\includegraphics[width=0.45\textwidth]{fig/Cobblestone_YOYO.PNG}}
-  \caption{Different road surfaces chosen for tests with strollers.}
-  \label{fig:surfaces_stroller}
-\end{figure}
-
-\subsubsection{Postures}
+
+\subsection{Postures}
+%
 All tested systems provided full support of back and head and allowed usage in
-lying or at least reclined postures. Nine months old babies would be able to
-sit erect but will often rest their heads or may even sleep. Although sitting
-upright is the best posture for children who can sit upright, a more recumbent
-posture was tested because this allowed measurement of vibration at the head
-(which is difficult with upright posture because the head does not always touch
-the back of the seat if in an upright position). We tested all systems with
+lying or at least reclined postures. Nine month old infants would be able to sit
+erect but will often rest their heads or be asleep. Although sitting upright is
+the best posture for children who can sit upright, a more reclined posture was
+tested because this allowed measurement of vibration at the head-seat interface
+while the head was always supported by the headrest. We tested all systems with
 horizontal or reclined postures. The inclination angle with respect to the
-ground is listed in Table~\ref{tab:baby-posture}, for each condition tested.
+ground is listed in Table~\ref{tab:baby-posture} for each condition tested.
 %
@@
   \centering
-  \caption{Inclination angles of the sensors ``Seat Head'' and ``Seat Buttock'',
-  per each tested configuration. We report the angles of the sensor at the
-  interface between the seat and the dummies' head and buttock, taken positive
-  counterclockwise. In this case, 0~\si{\degree} is defined by the ground plane.
-  In other words, 0~\si{\degree} means horizontal, -90~\si{\degree} means
-  vertical.}
+  \caption{Inclination angles of the IMUs ``Seat Head'' and ``Seat Pan'', per
+  each tested configuration. We report the angles defined by the axis of the
+  human body reference system (a reference system connected to the dummy, whose
+  z-axis is aligned with the body spine and x-axis points to the front of the
+  body) and the ground plane. An angle 90~\si{\degree} indicates supine posture,
+  -90~\si{\degree} indicates recumbent posture, and 0~\si{\degree} means erect
+  posture.}
 \begin{tabular}{lllrrr}
 \toprule
- &  &  & Count & \multicolumn{2}{c}{Inclination angle [deg]}  \\
-Vehicle Type & Model & Dummy & Baby seat & Seat Head & Seat Buttock\\
+ &  &  & & \multicolumn{2}{c}{Inclination angle [deg]}  \\
+Vehicle Type & Model & Dummy & Baby seat & Seat Head & Seat Pan\\
 \midrule
-\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 months & Maxi-Cosi X Joolz & -41 & -2 \\
- &  & 3 months & Maxi-Cosi X Joolz & -41 & -2 \\
- &  & 3 months & Melia & 64 & -2 \\
+\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Maxi-Cosi X Joolz & 49
+& -43 \\
+ &  & 3 mo & Maxi-Cosi X Joolz & 49 & -43 \\
+ &  & 3 mo & Melia & 26 & -28 \\
 \cline{2-6}
- & \multirow[t]{3}{*}{Tricycle} & 0 months & Maxi-Cosi X Joolz & -41 & -2 \\
- &  & 3 months & Maxi-Cosi X Joolz & -41 & -2 \\
- &  & 3 months & Melia & 64 & -2 \\
+ & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz & 49 & -43 \\
+ &  & 3 mo & Maxi-Cosi X Joolz & 49 & -43 \\
+ &  & 3 mo & Melia & 26 & -28 \\
 \cline{1-6} \cline{2-6}
-\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street+ & 0 months & Baby cot & 0 & 0\\
+\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street Plus & 0 mo & Baby cot & 90 & 90\\
 \cline{2-6}
- & Maxi-Cosi Street+ & 9 months & Baby seat & 40 & -10 \\
+ & Maxi-Cosi Street Plus & 9 mo & Baby seat & 50 & -40 \\
 \cline{2-6}
- & Babyzen Yoyo 0+ & 0 months & Baby cot & -12 & -12 \\
+ & Babyzen YOYO 0+ & 0 mo & Baby cot & 78 & 78 \\
 \cline{2-6}
- & Bugaboo Fox 5 & 0 months & Baby cot & 0 & 0 \\
+& Babyzen YOYO 0+ & 9 mo & Baby seat & 45 & -41 \\
 \cline{2-6}
- & Bugaboo Fox 5 & 9 months & Baby seat & 49 & -24\\
+& Bugaboo Fox 5 & 0 mo & Baby cot & 90 & 90 \\
+\cline{2-6}
+ & Bugaboo Fox 5 & 9 mo & Baby seat & 41 & -24\\
 \bottomrule
@@
 
-\subsection{Data Analysis Methodology}
-% 
-We analysed the raw data with a custom data processing pipeline hosted at
+\subsection{Data Processing}
+% 
+We analysed the raw data with a custom data processing pipeline. The pipeline's
+open source code (MIT license) is hosted at
 \href{https://github.com/mechmotum/baby-vibration}{github.com/mechmotum/baby-vibration}
@@
 generates a website at
-\href{https://mechmotum.github.io/baby-vibration}{mechmotum.github.io/baby-vibration}
-with an exhaustive collection of figures for examining the quality of the data
-and general results for all trials. Selected tables and figures from the website
-are presented and discussed in the results section of this paper.
-
-\subsubsection{Data Preparation}
-%
-The raw data consists of a single CSV file per session per IMU sensor along with
-meta-data for the sessions and vehicles. The CSV file contains the time series
-data from IMU: linear acceleration along and angular speed about each of the
-body-fixed orthogonal axes of the sensor alongside Epoch Unix timestamps. We
-segment the sessions into trials representing a motion state of the vehicle:
-either static level ground or being propelled over one of the surfaces of
-interest at a constant speed, as depicted in Figure~\ref{fig:session} as an
-example of the segmentation. We process the data per session as follows:
+\href{https://mechmotum.github.io/baby-vibration}{mechmotum.github.io/baby-vibration} with an exhaustive collection of figures for examining the
+quality of the data and general results for all trials including the selected
+tables and figures presented and discussed in the results section of this paper.
+
+We define a ``session'' as a continuous data collection period from a single
+vehicle. Each session is segmented into ``trials'' corresponding to a different
+road surface or activity and each trial is divided into subsequent, back-to-back
+``repetitions''.
+The raw data consists of a single comma-separated value (CSV) file per session
+per IMU along with metadata for the sessions and vehicles. The CSV file contains
+the time series data from each IMU: linear acceleration along and angular speed
+about each of the body-fixed orthogonal axes of the IMU alongside Epoch Unix
+timestamps. We segment the sessions into trials representing a motion state of
+the vehicle: either static on level ground or being propelled over one of the
+surfaces of interest at a constant speed. Figure~\ref{fig:session} gives an
+example of segmenting a session in different trials. The data were processed per
+session as follows:
 %
 \begin{enumerate}
+  \item Calculate the vehicle travel speed during the session from the angular
+    rate of the rear wheel and the vehicle's wheel radius.
   \item Extract segments representing a single trial from each session time
     history, based on the manually labelled segment ``start'' and ``end'' times.
+  \item Split the trials with durations longer than 40~\si{\second} into
+    repetitions of \SIrange{20}{39}{\second}.
   \item Rotate the accelerometer data for each sensor from body-fixed sensor
-    coordinates to body-fixed vehicle coordinates and remove the constant
+    coordinates to body-fixed vehicle coordinates and subtract the constant
     standard gravity component. This is achieved by rotating the coordinate axes
-    about the sensor's body-fixed axis which has was manually aligned with the
-    vehicle's pitch axis. We subtract the mean measured acceleration due to
+    about the sensor's body-fixed axis which was manually aligned with the
+    vehicle's pitch axis. We subtracted the mean measured acceleration due to
     gravity giving linear acceleration of each sensor projected into the
-    vehicle's SAE axes, named: longitudinal $x$, lateral $y$, and vertical $z$.
-  \item Extract each motion trial segment and select the vehicle vertical
-    component of the seat pan accelerometer.
-  \item Calculate the vehicle travel speed from the angular rate of the rear
-    wheel and the vehicle's wheel radius.
+    vehicle's SAE body-fixed axes~\cite{SocietyofAutomotiveEngineers2008},
+    named: longitudinal $x$, lateral $y$, and vertical $z$.
+  \item Extract each motion trial segment and select the vehicle body-fixed
+    longitudinal, lateral, and vertical component of the seat pan accelerometer.
 \end{enumerate}
 %
-This results in seat pan acceleration time histories of 78 trials of duration
-in the range of \SIrange{5}{80}{\second} (mean: 36~\si{\second}), see
-Table~\ref{tab:num-trials} for a breakdown of the trials.
+This resulted in acceleration-time recordings of 220 total repetitions. The
+non-shock repetitions have durations in the range of \SIrange{10}{40}{\second}
+(mean: 25~\si{\second}), see Table~\ref{tab:num-trials} for a breakdown of the
+non-shock repetitions.
 %
@@
 %
+% NOTE : This table is autogenerated from the data pipeline scripts and pasted in. I move the units to a second row manually for width conservation.
 \begin{table}
   \centering
-  \caption{Number of trials performed on each road surface and speed along with
-  the mean duration and its standard deviation.}
-\begin{tabular}{lllrrr}
+  \caption{Number of repetitions performed on each road surface, excluding
+  shock, and speed along with the mean duration in seconds and its standard
+  deviation.}
+\begin{tabular}{llcccc}
 \toprule
- &  &  & Count & \multicolumn{2}{c}{Duration [s]}  \\
-Vehicle Type & Road Surface & Target Speed [km/h] &  & Mean & STD  \\
+ &  &  & \multicolumn{2}{c}{Repetitions}\\
+ &  & Target Speed & Count & Mean Duration & STD Duration \\
+Vehicle Type & Road Surface & [\si{\kph}] & & [\si{\second}] & [\si{\second}] \\
 \midrule
-\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Tarmac} & 12 & 6 & 58.33 & 8.56 \\
- &  & 20 & 3 & 50.42 & 7.04 \\
- &  & 25 & 3 & 44.08 & 1.60 \\
+\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 13 & 25.1 & 7.0 \\
+ &  & 20 & 8 & 28.8 & 7.6 \\
+ &  & 25 & 3 & 33.4 & 4.3 \\
 \cline{2-6}
- & \multirow[t]{3}{*}{Paver Bricks} & 12 & 6 & 54.46 & 5.95 \\
- &  & 20 & 6 & 38.68 & 5.08 \\
- &  & 25 & 3 & 33.43 & 4.25 \\
+ & \multirow[t]{3}{*}{Tarmac} & 12 & 14 & 25.0 & 7.0 \\
+ &  & 20 & 6 & 25.2 & 7.2 \\
+ &  & 25 & 6 & 22.0 & 2.5 \\
 \cline{1-6} \cline{2-6}
-\multirow[t]{5}{*}{Stroller} & Tarmac & 5 & 10 & 27.87 & 10.07 \\
+\multirow[t]{5}{*}{Stroller} & Cobblestones & 5 & 26 & 22.8 & 5.6 \\
 \cline{2-6}
- & Cobblestones & 5 & 13 & 27.90 & 24.74 \\
+ & Paver Bricks & 5 & 20 & 25.0 & 7.6 \\
 \cline{2-6}
- & Paver Bricks & 5 & 6 & 51.47 & 21.62 \\
+ & Sidewalk Pavers & 5 & 19 & 25.2 & 8.2 \\
 \cline{2-6}
- & Sidewalk Slabs & 5 & 16 & 19.59 & 6.59 \\
+ & Sidewalk Slabs & 5 & 23 & 22.8 & 3.4 \\
 \cline{2-6}
- & Sidewalk Pavers & 5 & 6 & 48.94 & 19.71 \\
+ & Tarmac & 5 & 16 & 28.9 & 9.6 \\
 \cline{1-6} \cline{2-6}
- & & \textbf{Count Sum} & \textbf{78} & & \\
+ & & \textbf{Count Sum} & \textbf{154} & & \\
 \bottomrule
@@
 
-\subsubsection{Trial Analyses}
+\subsection{Trial Analyses}
 %
 Figure~\ref{fig:vert-acc-example} shows an example time history of the vertical
-acceleration of the seat pan during a single trial. We downsampled the time
-history from the set sampling frequency of 910.22~\si{\hertz} to \(N\) samples
-at a constant sample rate of 400~\si{\hertz} with linear interpolation.
+acceleration of the seat pan during a single repetition. To perform the
+ISO~2631-1 recommended health and comfort analysis, we first downsampled the
+time history from the hardware-set variable sampling frequency of approximately
+910.22~\si{\hertz} to a constant sample rate of 400~\si{\hertz} using linear
+interpolation, giving sufficient samples for the bandwidth of interest based on
+the Nyquist frequency. We set any acceleration values outside of the sensor
+manufacturer's reported operating range of \(\pm\)16~g to that maximum or
+minimum, respectively, given that values outside the range may be unreliable.
+Values that exceed the range are rare and only present in some of the cargo
+bicycle paver brick trials, but are common in the shock tests. Following the
+ISO~2631-1 recommendation, we low-pass filtered the signal at
+\(1.5\times80~\si{\hertz}=120~\si{\hertz}\) using a zero-lag
+2\textsuperscript{nd} order Butterworth filter, given that the standard only
+applies to frequencies up to 80~\si{\hertz}.
 %
@@
 
-We calculated the root mean square of the downsampled vertical component of
-acceleration at the seat pan for each trial using Equation~\ref{eq:rms-acc}.
-This quantity gives an indicator of the average vertical acceleration
-experienced at the baby's buttocks for the duration of the trial and can be seen
-in Figure~\ref{fig:vert-acc-example}. RMS acceleration is the primary metric
-recommended by ISO-2631-1 for evaluation of health and comfort in whole body
-vibration.
+ISO~2631-1 provides weighting filters that highlight those frequencies adults
+are most sensitive to. To apply them, we calculated the amplitude spectra of the
+acceleration time histories of each trial using the Fast Fourier Transform
+(FFT). Figure~\ref{fig:freq-spectrum} gives an example of a raw amplitude
+spectrum along with smoothened versions of the raw and ISO 2631-1 weighted
+signals. In almost all trials, there is a single dominant peak frequency in the
+ISO weighted and smoothed spectra. For the few trials that had two or more peaks
+at approximately the same amplitude, the second peak was sometimes selected.
+After ISO weighting, the area under the spectrum curve was calculated and the
+frequency below which 80\% of the amplitude content falls marked as an indicator
+of bandwidth.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/session004-t0-pave-stroller-maxicosi-cot-0-SeatBotacc_ver-rep0.png}
+  \caption{Seat pan vertical acceleration amplitude spectrum from session 004:
+  Maxi-Cosi Street Plus over cobblestones. The gray curve shows the result of
+  the FFT, the black line is a smoothed version of the FFT (zero-lag Butterworth
+  low pass), and the blue line is the smoothed ISO weighted FFT. The blue dashed
+  vertical line indicates the frequency at the maximum amplitude of the smoothed
+  curve. The blue dashed-dotted vertical line indicates the bandwidth threshold
+  for 80\% of the area under the blue curve.}
+  \label{fig:freq-spectrum}
+\end{figure}
+
+We calculated the root mean square (RMS) over \(N\) samples of the downsampled,
+low-pass filtered, and ISO 2631-1 weighted vertical component of acceleration
+\(a_{w,z}\) at the seat pan for each trial using Equation~\ref{eq:rms-acc} to
+use for the health assessment and the RMS of the magnitude of the acceleration
+vector at the seat pan using Equation~\ref{eq:rms-acc-mag} for the comfort
+assessment, as per ISO 2631-1 guidelines. We set the ISO~2631-1 adjustment
+factors \(k_x,k_y,k_z\) equal to 1 for all acceleration components. RMS gives an
+indication of the average vertical acceleration experienced at the infant's
+buttocks-seat interface for the duration of the trial and can be seen in
+Figure~\ref{fig:vert-acc-example}. It is the primary metric recommended by
+ISO-2631-1 for evaluation of health and comfort in adult whole-body vibration.
+We also calculated the vibration dose value (VDV) of the \(M\) raw data vertical
+acceleration \(a_{z}\) samples with Equation~\ref{eq:vdv-acc}, seen in
+Figure~\ref{fig:vert-acc-example}. Lastly, we compute the crest factor and
+absolute maximum of the downsampled and low pass filtered vertical
+acceleration\footnote{Some scenarios have crest factors larger than 9, but we
+do not report metrics other than RMS as ISO~2631-1 recommends for this study.}
+with Equations~\ref{eq:crest-factor} and \ref{eq:max-acc}, respectively. All of
+these per-repetition metrics are reported as mean values over the repetitions
+corresponding to a scenario in Table~\ref{tab:results} in
+Appendix~\ref{app:results}. Regarding the shock test, the analysis was conducted
+on unfiltered data (not downsampled). We selected the maximum (absolute) peak
+from the time history of the vertical acceleration of the seat pan starting from
+the events' time histories (Figure \ref{fig:shock_time-history}), limiting it to
+16~g when the peak exceeded that maximum. The following equations give the
+details of the metrics calculations:
 %
 \begin{align}
-  \textrm{RMS}_{a_z} = \sqrt{\frac{1}{N}\sum_{n=1}^{N} a_z^2(t_n)}
+  \textrm{RMS}_{a_{w,z}} = \sqrt{\frac{1}{N}\sum_{n=1}^{N} k_z^2 a_{w,z}^2(t_n)}
   \label{eq:rms-acc}
@@
 
-We also calculated the frequency spectrum of the vertical acceleration time
-history of each trial using the Fast Fourier Transform (FFT).
-Figure~\ref{fig:freq-spectrum} gives an example of a frequency spectrum. In this
-case, the primary peak frequency is identified to be 6.5~\si{\hertz} and the
-frequency content is mostly contained below about 80~\si{\hertz}.
-%
+\begin{align}
+  \textrm{RMS}_{a_{w,xyz}} = \sqrt{\frac{1}{N}\sum_{n=1}^{N} k_x^2 a_{w,x}^2(t_n) + k_y^2 a_{w,y}^2(t_n) + k_z^2 a_{w,z}^2(t_n)}
+  \label{eq:rms-acc-mag}
+\end{align}
+
+\begin{align}
+  \textrm{VDV}_{a_{z}} = \left(\frac{1}{M}\sum_{m=1}^{M} a_{z}^4(t_m)\right)^{1/4}
+  \label{eq:vdv-acc}
+\end{align}
+
+\begin{align}
+  \textrm{Crest Factor}_{a_{z}} =\frac{\max|a_{z}(t_m)|}{\sqrt{\frac{1}{M}\sum_{m=1}^{M} a_{z}^2(t_m)}}
+  \label{eq:crest-factor}
+\end{align}
+
+\begin{align}
+  \textrm{MAX}_{a_{z}} =\max|a_{z}(t_n)|
+  \label{eq:max-acc}
+\end{align}
+
 \begin{figure}
   \centering
-  \includegraphics[width=160mm]{fig/session004-t0-pave-stroller-maxicosi-cot-0-SeatBotacc_ver.png}
-  \caption{Seat pan vertical acceleration frequency spectrum from session 4:
-  Maxi-Cosi Stroller over cobblestones. The gray curve shows the result of the
-  FFT and the blue line is a smoothed version (Butterworth low pass
-  forward/reverse). The orange vertical line indicates the frequency at the
-  maximum amplitude of the smoothed curve. The green vertical line indicates the
-  bandwidth threshold for 80\% of the area under the filtered curve.}
-  \label{fig:freq-spectrum}
-\end{figure}
+  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-maxicosi-0-SeatBotacc_ver-rep0.png}
+  \caption{Raw seat pan vertical acceleration versus time from session 015:
+  Keiler tricycle during the shock test.}
+  \label{fig:shock_time-history}
+\end{figure}
+
+\subsection{Statistical Modelling}
+%
+To determine how road surface and stroller setup predict ISO~2631-1 weighted
+vertical RMS acceleration, we fit an ordinary linear least squares model to the
+data using:
+%
+\begin{align}
+  \textrm{RMS}_{a_{w,z}} = 
+  \beta_0 +
+  \beta_1 x_\textrm{Road Surface} +
+  \beta_2 x_\textrm{Stroller} +
+  \epsilon
+\end{align}
+%
+Both \(x_\textrm{Road Surface}\) and \(x_\textrm{Stroller}\) are categorical
+variables and we select tarmac and the Green Machine as the reference values
+when coding the categorical variables, respectively. We do not consider the
+interaction of road surface and stroller.
+
+To determine how speed, road surface, and cargo bicycle setup predict ISO~2631-1
+weighted vertical RMS acceleration, we fit an ordinary linear least squares
+model to the data using:
+%
+\begin{align}
+  \textrm{RMS}_{a_{w,z}} = 
+  \kappa_0 +
+  \kappa_1 x_\textrm{Road Surface} +
+  \kappa_2 x_\textrm{Cargo Bicycle} + 
+  \kappa_3 x_\textrm{Speed} +
+  \kappa_4 x_\textrm{Road Surface} \times x_\textrm{Speed} +
+  \epsilon
+\end{align}
+%
+Both \(x_\textrm{Road Surface}\) and \(x_\textrm{Cargo Bicycle}\) are
+categorical variables and \(x_\textrm{Speed}\) is a continuous variable. We
+select tarmac and the `Keiler, Maxi-Cosi seat, 0 mo' setup as the reference
+values when coding the categorical variables, respectively. We do not consider
+the interaction of road surface and cargo bicycle setup, but we do consider the
+interaction of speed with road surface. We use \(p<0.05\) to indicate
+significant differences for both models. Following fitting the two statistical
+models, we apply Tukey's Range Test to compare vehicle setups among each other
+for the different road surfaces and speed ranges with \(p=0.05\) for the
+adjusted limit for significance.
 
@@
 %
-\subsection{Effect of Speed}
-%
-We tested the two cargo bicycles at three different target speeds: 12, 20, and
-25~\si{\kilo\meter\per\hour}. Figure~\ref{fig:compare-bicycle-speed} shows the
-variation in vertical RMS acceleration across the tested speeds. Accelerations
-experienced when riding over the paver bricks are always larger than riding over
-tarmac at the same speed, with the paver bricks having about a 5\(\times\)
-increase in magnitude over tarmac. Over paver bricks, the RMS acceleration
-increases by 1.7\(\times\) when increasing the speed from
-\SIrange{12}{25}{\kilo\meter\per\hour}. The effect of speed while over tarmac is
-less drastic but also increases over the speed range.
+\subsection{Effect of Speed with Cargo Bicycles}
+%
+Figure~\ref{fig:compare-bicycle-speed} shows the variation in ISO~2631-1
+weighted vertical RMS acceleration across the tested speeds. Accelerations
+experienced when riding over the paver bricks were always larger than for tarmac
+at the same speed, with the paver bricks showing about a 4-5\(\times\) higher
+acceleration magnitude than tarmac. Over paver bricks, the RMS acceleration
+increased by about 1.6\(\times\) when increasing the speed from
+\SIrange{12}{25}{\kilo\meter\per\hour}. The effect of speed while cycling over
+tarmac was less drastic but also may show a slight increase of accelerations
+over the speed range.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-speed-compare.png}
-  \caption{Seat pan vertical acceleration RMS versus speed for all cargo bicycle
-  trials. Shaded regions represent the 95\% confidence intervals from a simple
-  linear regression.}
+  \caption{Seat pan ISO 2631-1 weighted vertical acceleration RMS versus speed
+  for all cargo bicycle repetitions. Shaded regions represent the 95\%
+  confidence intervals from a simple linear regression that ignores
+  \(x_\textrm{Cargo Bicycle}\).}
   \label{fig:compare-bicycle-speed}
@@
 
-\subsection{Effect of Baby Size}
-%
-We tested dummy babies representing ages 0~months (3.5~\si{\kilo\gram}),
-3~months (5.9~\si{\kilo\gram}), and 9~months (8.9~\si{\kilo\gram}).
-Figure~\ref{fig:compare-baby-mass} shows the vertical RMS acceleration for each
-trial for the strollers and the bicycles, comparing the baby size. There are
-larger accelerations experienced in the bicycle versus the stroller, mostly
-attributed to the different testing speeds. When comparing the vertical RMS
-acceleration values within each vehicle type there are no obvious differences
-due to baby size, i.e. each baby size experiences a similar range of
-acceleration magnitudes.
+\subsection{Effect of Dummy Size}
+%
+Figure~\ref{fig:compare-baby-mass} shows the ISO~2631-1 weighted vertical RMS
+acceleration for each repetition for all vehicles, comparing among dummy sizes.
+There were larger accelerations in the bicycle (high speeds) versus the stroller
+(low speeds), likely mostly attributed to the different testing speeds. When
+comparing the vertical RMS acceleration values between cargo bicycles and
+strollers there are no obvious differences due to baby size, i.e. each dummy
+size experienced a similar range of acceleration magnitudes when vehicle type
+and road surface are ignored. For the bicycles, the lightest dummy sometimes
+experienced higher acceleration than the heavier dummy, but high and low
+accelerations are seen across the speed range tested.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
-  \caption{Seat pan vertical RMS acceleration grouped by baby age (and thus size
-  \& mass) for all trials with colour indicating the mean speed of the
-  trial.}
+  \caption{Seat pan ISO~2631-1 weighted vertical RMS acceleration grouped by
+  baby age (and thus size \& mass) for all repetitions with colour indicating
+  the mean speed of the trial. The lightest colour dots are strollers and the
+  remaining are cargo bicycles.}
   \label{fig:compare-baby-mass}
@@
 %
-Figure~\ref{fig:compare-road-surface} shows vertical RMS acceleration from
-trials grouped into the various road surfaces we tested. All vehicles were
-tested on tarmac and paver bricks but only strollers were tested on cobblestones
-and sidewalks. It is notable that tarmac almost always has lower RMS
-acceleration regardless of speed and vehicle type. The sidewalk slabs can have
-slightly higher acceleration than cobblestones for the strollers. Paver bricks
-and sidewalk pavers have a similar range of RMS acceleration for the same
-5~\si{\kilo\meter\per\hour} walking speeds. Paver bricks cause relatively large
-accelerations at high travel speeds in the cargo bicycles.
+Figure~\ref{fig:compare-road-surface} shows ISO~2631-1 weighted vertical RMS
+acceleration from repetitions grouped into the various road surfaces tested. All
+vehicles were tested on paver bricks and tarmac but only strollers were tested
+on cobblestones and sidewalk pavers and sidewalk slabs, i.e. light colour dots
+(strollers are present in each column).
+It is notable that tarmac almost always induced lower RMS acceleration than
+other road types regardless of speed and vehicle type.
+The sidewalk slabs and cobblestones have very similar acceleration ranges for
+all strollers.
+Paver bricks and sidewalk pavers seem to have a similar range of RMS
+acceleration for the same 5~\si{\kilo\meter\per\hour} walking speeds.
+Paver bricks cause relatively large accelerations at high travel speeds in the
+cargo bicycles.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-road-surface-compare.png}
-  \caption{Seat pan vertical RMS acceleration grouped by road surface with
-  colour indicating the mean speed of the trial. The lightest colour dots are
-  strollers and the rest are cargo bicycles.}
+  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration grouped by
+  road surface with colour indicating the mean speed of the repetition. The
+  lightest colour dots are strollers and the rest are cargo bicycles.}
   \label{fig:compare-road-surface}
@@
 %
-We tested three models of strollers over five different road surfaces.
-Figure~\ref{fig:stroller-type-compare} compares the vertical RMS accelerations
-for each road surface for each of the three strollers. The Maxi-Cosi Street Plus
-and Stokke BABYZEN YOYO 0+ strollers have similar mean values across trials. The
-Bugaboo has a slightly lower mean, but much larger variation in the RMS values.
-There may be no significant difference in the acceleration experienced in each
-stroller model. All road surfaces compared to tarmac cause at least double the
-RMS acceleration.
+Figure~\ref{fig:stroller-type-compare} shows the vertical RMS accelerations for
+each road surface for each of the five strollers, lumping seat configurations
+and dummy sizes. The Maxi-Cosi Street Plus and Stokke BABYZEN YOYO 0+ strollers
+have similar mean values across repetitions. The Bugaboo Fox 5 has a slightly
+lower mean for cobblestones, paver bricks, and sidewalk pavers. The Green
+Machine performs better than the modern strollers on paver bricks, but similarly
+otherwise. The Old Rusty performs better than the modern strollers on all
+surfaces except tarmac. All strollers seem to experience the same acceleration
+on tarmac. There may be no significant difference in the acceleration
+experienced in each modern stroller model. All road surfaces compared to tarmac
+cause at least double the RMS acceleration.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-stroller-type-compare.png}
-  \caption{Mean seat pan vertical RMS acceleration per road surface for each
-  stroller. Vertical lines indicate the standard deviation for categories that
-  have more than one trial.} 
+  \caption{Mean seat pan ISO 2631-1 weighted vertical RMS acceleration per road
+  surface for each stroller. Vertical lines indicate the standard deviation for
+  categories that have more than one repetition.} 
   \label{fig:stroller-type-compare}
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-type-compare.png}
-  \caption{Seat pan vertical RMS acceleration versus speed grouped by road
-  surface and cargo bicycle model. Horizontal lines indicate a linear
-  regression, vertical lines are the standard deviation at those speeds, and
-  shaded regions show the 95\% confidence intervals for the regression.}
+  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration versus speed
+  grouped by road surface and cargo bicycle model. Slanted lines indicate a
+  linear regression, vertical lines are the standard deviation at those speeds,
+  and shaded regions show the 95\% confidence intervals for the regression.}
   \label{fig:bicycle-type-compare}
@@
 %
-Figure~\ref{fig:peak-freq-dist} shows the dominant frequency compared among road
-surface types for each of the target speeds. Peak frequencies range from
-\SIrange{5}{11}{\hertz} across all trials. For strollers
-(5~\si{\kilo\meter\per\hour}, the median frequency increases from sidewalk
-slabs, to cobblestones, to sidewalk pavers, to tarmac, to paver bricks. With the
-exception of paver bricks being larger than tarmac this increase corresponds to
-an increase in the size of the geometric surface features of the road.
+Figure~\ref{fig:peak-freq-dist} shows the distributions of dominant (peak)
+frequency compared among road surface types for each of the target speeds. Peak
+frequencies range from about \SIrange{4}{11}{\hertz} across all trials. For
+strollers (5~\si{\kilo\meter\per\hour}), the median frequency increases from
+sidewalk slabs to cobblestones and sidewalk pavers and then to tarmac and paver
+bricks. The peak frequency median does not correlate sequentially with the
+geometric width of the dimension of the road surface feature. For the cargo
+bicycles, difference in peak frequency between the two road surfaces is not so
+apparent or consistent.
 %
@@
   \caption{Peak frequency distributions comparisons among road surfaces for each
-  target speed group. The boxes bound the quartiles and indicate the median. The
-  whiskers indicate the 95th perentile and circles are any outliers.}
+  target speed group for non-shock repetitions. The boxes bound the quartiles
+  and indicate the median. The whiskers indicate the 95\textsuperscript{th}
+  percentile and circles are any outliers.}
   \label{fig:peak-freq-dist}
@@
 
-Figure~\ref{fig:thresh-freq-dist} gives a general indication of bandwidth
-distributions for each of the target speed groups. Most frequency content is
-below 100~\si{\hertz} for the all trials. The median threshold frequency across
-all trials is 70~\si{\hertz} which gives an idea of the bandwidth for the
-vibrations of interest.
+Figure~\ref{fig:bandwidth-dist} gives a general indication of bandwidth (80\% of
+the amplitude spectrum content) distributions for each of the target speed
+groups. Most frequency content is below 45~\si{\hertz} for all trials. The
+median bandwidth across all trials is 20~\si{\hertz}. For the cargo bicycles,
+the frequency content is spread wider for paver bricks than for tarmac, but for
+strollers there is likely no significant difference in these surfaces. For
+strollers, sidewalk pavers, sidewalk slabs, and cobblestones have similar
+bandwidths. However this is based on the ISO filtering which attenuated the
+higher frequencies. For the tested lying postures this weighting may have to be
+reconsidered, as will be addressed further in the discussion. 
 %
@@
   \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-thresh-freq-dist.png}
-  \caption{Threshold frequency  (based on 80\% of the area under the filtered
-  frequency spectrum) for each target speed group.}
-  \label{fig:thresh-freq-dist}
-\end{figure}
-
-\subsection{Overall Comparison}
-We tabulate the seat pan vertical RMS acceleration, trial duration, peak
-frequency, and threshold frequency for all 52 combinations of vehicle setup,
-road surface, and target speed in Table~\ref{tab:results}.
-Figure~\ref{fig:compare-all} shows the vertical RMS acceleration of all trials
-broken down by vehicle setup (vehicle, seat, baby age), road surface, trial
-duration, and travel speed. Some additional insights can be gathered from this
-figure, that are not seen in the prior figures.
-%
-\begin{itemize}
-    \item The baby in stroller travelling at 5~\si{\kilo\meter\per\hour} over
-    cobblestones and sidewalks slabs cracks can experience accelerations of
-    similar magnitude to a baby in a cargo bicycle travelling at
-    12~\si{\kilo\meter\per\hour} over paver bricks.
-    \item A 3 month old baby in a baby shell (Melia) travelling over brick
-    pavers at high speeds has lower RMS acceleration than the same baby in a car
-    seat (Maxi-Cosi Pebble Pro) in the Urban Arrow and it may also be true for
-    the Keiler tricycle. Switching to the baby shell in the Urban Arrow has a
-    similar effect to reducing speed by 10~\si{\kilo\meter\per\hour}.
-\end{itemize}
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bandwidth-dist.png}
+  \caption{Bandwidth (based on 80\% of the area under the ISO~2631-1 filtered
+  amplitude spectrum) for each target speed group for non-shock repetitions. The
+  boxes bound the quartiles and indicate the median. The whiskers indicate the
+  95\textsuperscript{th} percentile and circles are any outliers.}
+  \label{fig:bandwidth-dist}
+\end{figure}
+
+\subsection{Health Assessment}
+\label{sec:health-assesment}
+%
+Figures \ref{fig:health-stroller} and \ref{fig:health-bicycle} show the
+ISO~2631-1 weighted vertical acceleration at the seat pan for all repetitions of
+the stroller and cargo bicycles, respectively. The horizontal lines in the
+figure correspond to the boundary of the ``health caution'' and  ``health risk''
+zones in the standard, which has a dependence on exposure duration. If
+acceleration values are above the health caution zone, ISO~2631-1 states that
+``health risks are likely'' for adults in erect seating postures for a
+continuous daily dose. It must be emphasised that the ISO~2631-1 is based on
+adults and may not result in a representative risk for infants or older
+children.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-rms-stroller-compare-all.png}
+  \caption{ISO~2631-1 weighted seat pan vertical RMS acceleration of all
+  stroller repetitions with colour representing road surface. The horizontal
+  dashed grey lines with time duration indicators are the upper bound of the
+  ISO~2631-1 ``health caution zone'' at for adults seated erectly experiencing
+  vibrations for continuous duration in a daily dose.}
+  \label{fig:health-stroller}
+\end{figure}
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-rms-bicycle-compare-all.png}
+  \caption{ISO~2631-1 weighted seat pan vertical RMS acceleration of all cargo
+  bicycle trials with colour representing road surface and marker style
+  indicating the target speed. The horizontal dashed grey lines with time
+  duration indicators are the upper bound of the ISO~2631-1 ``health caution
+  zone'' for adults seated erectly experiencing vibrations for continuous
+  duration in a daily dose.}
+  \label{fig:health-bicycle}
+\end{figure}
+
+For the strollers, all vibration measurements were below the health caution zone
+boundary if the daily continuous exposure is less than 10~\si{\minute}.
+Additionally, all strollers pushed over tarmac were below the zone if the daily
+continuous exposure is less than 4~\si{\hour}. Pushing the Bugaboo Fox 5 and
+Maxi-Cosi Street Plus with a 0 month infant or the Stokke BABYZEN YOYO 0+ with a
+9 month infant over cobblestones and sidewalk slabs may have health risks if the
+duration exceeds 20~\si{\minute}. For almost all of the strollers pushing over
+any surface except tarmac exceeded the 1~\si{\hour} risk boundary. Notably the
+Bugaboo Fox 5 and Old Rusty with a 9 mo infant fell under the 1~\si{\hour}
+threshold for all surfaces. The 0 month dummy experienced worse accelerations
+than the 9 month dummy in the Bugaboo Fox 5 and Maxi-Cosi Street Plus, but that
+was opposite for the Stokke YOYO 0+. Old rusty showed the least overall
+acceleration magnitudes.
+
+For both cargo bicycles, the accelerations exceeded the 10~\si{\minute} health
+risk threshold when ridden above 20~\si{\kilo\meter\per\hour} on paver bricks
+and exceeded the 1~\si{\hour} health risk threshold when ridden more than
+1~\si{\hour} above 12~\si{\kilo\meter\per\hour} on paver bricks. All but the
+Keiler with the Maxi-Cosi seat and the 0 mo dummy were under the 1~\si{\hour}
+threshold for riding on tarmac at any target speed. Only the Urban Arrow with
+the 3 month dummy is (mostly) under the 4~\si{\hour} threshold when ridden at
+either speed over tarmac. The accelerations may be less when using the Meila
+Baby Shell seat versus the Maxi-Cosi car seat, this is statistically considered
+later in the results.
+
+\subsection{Comfort Assessment}
+%
+ISO~2631-1 recommends using the magnitude of the weighted seat pan acceleration
+vector for comfort assessment. Figures \ref{fig:comfort-stroller} and
+\ref{fig:comfort-bicycle} plot RMS of the acceleration magnitude along with the
+comfort indicators provided in the standard that are based on adults seated in
+public transit for an unspecified duration. It must be emphasised that the
+ISO~2631-1 comfort assessment is designed for adults and may not result in a
+representative comfort assessment for infants or older children. We also include
+a line representing cyclists' discomfort threshold reported by
+Gao~et.~al~\cite{Gao2018}. It is important to recognize that cyclists perched on
+a bicycle seat seem to tolerate more vibration discomfort than the public
+transit riders who were surveyed for the ISO ratings. This points to possible
+weakness in the ISO recommendations or to other factors affecting cycling
+discomfort (e.g. the ability to stand on the pedals to lower vibration to the
+body and the head).
+
+When following the threshold definitions from the ISO~2631-1 guidelines for the
+strollers, all are at least ``a little uncomfortable'' on all surfaces. All
+strollers are ``fairly uncomfortable'' on tarmac. All other road surfaces are at
+least ``very uncomfortable''. The `Bugaboo, seat, 9 mo' and `Green Machine, cot,
+0 mo' over paver bricks and `Old Rusty, seat, 9 mo' over paver bricks, sidewalk
+pavers, and sidewalk slabs are ``very uncomfortable'', but all other strollers
+and surfaces are ``extremely uncomfortable''. The Old Rusty is the only stroller
+that falls under the cyclist threshold discomfort line for all surfaces.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-rms-comfort-stroller-compare-all.png}
+  \caption{ISO~2631-1 weighted seat pan magnitude RMS acceleration of all
+  stroller repetitions with colour representing road surface. The horizontal
+  dashed lines are the lower bound of the ISO~2631-1 ``comfort zones'' for
+  adults seated erectly experiencing vibrations in public transit. The
+  horizontal dashed dotted line is the cyclists' vibration discomfort threshold
+  as reported by Gao et. al~\cite{Gao2018}.}
+  \label{fig:comfort-stroller}
+\end{figure}
+
+Both of the two cargo bicycles ridden at any tested speed over paver bricks, as
+well as the Keiler with the Maxi-Cosi seat ridden over tarmac at high speed fall
+into the category ``extremely uncomfortable''. Those are also above the the
+cyclist discomfort threshold. The other vehicle setups fall between ``fairly
+uncomfortable'' and ``very uncomfortable'' over tarmac for the range of speeds.
+The Urban Arrow with the Melia Baby Shell performs, on average, the best on
+paver bricks and tarmac at all speeds tested.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-rms-comfort-bicycle-compare-all.png}
+  \caption{ISO~2631-1 weighted seat pan magnitude RMS acceleration of all cargo
+  bicycle repetitions with colour representing road surface and marker style
+  representing target speed. The horizontal dashed lines with the upper bound of
+  the ISO~2631-1 ``comfort zones'' for adults seated erectly experiencing
+  vibrations in public transit. The horizontal dashed dotted line is the
+  cyclists' vibration discomfort threshold as reported by
+  Gao~et.~al~\cite{Gao2018}.}
+  \label{fig:comfort-bicycle}
+\end{figure}
+
+\subsection{Shock}
+%
+We identified the maximum peak acceleration values for each trial
+(Equation~\ref{eq:max-acc}), then averaged them across repetitions to obtain the
+results listed in Table~\ref{tab:shock} for different vehicles and
+configurations. There is a significant variation among tests, with the peaks for
+the bicycles sometimes reaching the accelerometer's full scale (\(\pm\)16~g).
+While the seat pan accelerations for the strollers are generally lower than
+those experienced with the bicycles, the configuration (0 or 9 months) may play
+a large role. Among bicycles, the use of Melia baby shell seems to transmit
+lower accelerations compared to Maxi-Cosi, 3 months, for both the Keiler
+tricycle and the Urban Arrow. Strollers with the baby seat configuration for 9
+months show much lower acceleration compared to the baby cot for 0 months
+(Bugaboo and Maxi-Cosi). Surprisingly, the oldest strollers (Old Rusty and Green
+Machine) performed very well during the shock test, resulting in the lowest seat
+pan acceleration among all the tested vehicles.
+Figure~\ref{fig:shock_vehicle_comparison} shows the peaks of the vertical
+acceleration recorded at the seat pan, grouped by different vehicles, for the
+shock test. As noted in Table~\ref{tab:shock}, the old strollers Old Rusty and
+Green Machine show lower acceleration values. We do not clearly distinguish any
+trend with speed for the bicycles (Keiler and Urban Arrow). During the tests
+involving Keiler tricycle and strollers, we cannot exclude that the front wheels
+(left and right) hit the bump at slightly different time instants.   
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-shock-test-compare.png}
+  \caption{Vertical acceleration recorded at the seat pan during the shock test
+  per each trial, grouped by vehicles. The colour indicates the mean speed of
+  the trial. The lighter the colour the lower the speed.}
+  \label{fig:shock_vehicle_comparison}
+\end{figure}
 
@@
   \centering
-  \caption{Computed metrics for all 52 scenarios measured.}
-  \label{tab:results}
+  \caption{Mean of the maximum seat pan acceleration across trials in
+  \si{\mps\squared} recorded for shock test, for different vehicles and baby
+  masses.}
+  \label{tab:shock}
   \footnotesize
-\begin{tabular}{lllcccccc}
+  \begin{tabular}{lllrrrr}
     \toprule
-        &            &              &        &       & Mean         &          & Mean      & Mean      \\
-Vehicle & Seat, Baby & Road Surface & Target & Trial & RMS          & Mean     & Peak      & Threshold \\
-        &            &              & Speed  & Count & Acceleration & Duration & Frequency & Frequency \\
-        &            &              & [km/h] &       &  [m/s\(^2\)]     & [s]      & [Hz]      & [Hz]      \\
+     & &  & Target Speed & Trial Count & Max Acceleration \\
+    Vehicle Type & Model & Seat, Baby & [km/h] & & [m/s²] \\
     \midrule
-\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 2 & 4.4 & 39.8 & 6.6 & 22.6 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 1 & 2.6 & 70.5 & 10.7 & 25.1 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 1 & 2.9 & 51.6 & 8.2 & 119.5 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 3 & 4.8 & 20.0 & 5.8 & 41.8 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 0.7 & 24.9 & 9.9 & 61.5 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 2.5 & 42.0 & 6.8 & 46.5 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 1 & 2.3 & 66.9 & 9.7 & 57.5 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 1 & 1.7 & 71.3 & 7.6 & 47.4 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 3 & 2.4 & 23.9 & 6.0 & 47.1 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 0.6 & 33.2 & 8.4 & 68.9 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
-\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 1 & 4.6 & 81.7 & 6.6 & 82.3 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 1 & 3.2 & 61.5 & 10.6 & 75.6 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 1 & 3.0 & 51.0 & 7.8 & 79.7 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 5 & 4.5 & 12.3 & 5.7 & 80.3 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 0.9 & 29.4 & 10.5 & 56.5 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 5 & 4.2 & 12.6 & 7.8 & 65.8 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 2 & 3.0 & 26.0 & 9.8 & 79.6 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 1 & 2.6 & 54.8 & 6.8 & 67.1 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 3 & 3.2 & 23.0 & 6.9 & 70.4 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 1.0 & 33.6 & 10.2 & 70.7 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
-\multirow[t]{12}{*}{trike} & \multirow[t]{4}{*}{maxicosi, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 7.2 & 47.6 & 8.0 & 44.9 \\
- &  &  & 20 & 1 & 11.1 & 35.3 & 6.4 & 101.6 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.9 & 73.7 & 8.1 & 23.8 \\
- &  &  & 20 & 1 & 2.7 & 58.4 & 6.5 & 18.8 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{4}{*}{maxicosi, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 6.8 & 57.8 & 7.9 & 72.3 \\
- &  &  & 20 & 1 & 9.8 & 42.8 & 7.1 & 87.2 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.5 & 55.6 & 7.6 & 31.7 \\
- &  &  & 20 & 1 & 2.1 & 47.6 & 6.2 & 19.2 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 1 & 5.8 & 52.6 & 8.9 & 100.5 \\
- &  &  & 20 & 1 & 10.2 & 46.0 & 6.9 & 120.9 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.2 & 50.8 & 7.9 & 91.1 \\
- &  &  & 20 & 1 & 1.6 & 45.2 & 8.1 & 72.8 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
-\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 6.6 & 62.3 & 7.6 & 110.4 \\
- &  &  & 20 & 1 & 9.2 & 39.1 & 8.0 & 71.6 \\
- &  &  & 25 & 1 & 11.4 & 38.3 & 7.1 & 117.5 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.4 & 58.1 & 8.7 & 28.9 \\
- &  &  & 25 & 1 & 2.1 & 43.1 & 10.0 & 28.5 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{5}{*}{maxicosi, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 5.2 & 58.2 & 7.9 & 85.7 \\
- &  &  & 20 & 1 & 10.6 & 32.1 & 4.9 & 102.8 \\
- &  &  & 25 & 1 & 10.5 & 30.3 & 6.2 & 99.3 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.1 & 50.7 & 8.8 & 37.8 \\
- &  &  & 25 & 1 & 1.6 & 43.2 & 9.6 & 31.8 \\
-\cline{2-9} \cline{3-9}
- & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 1 & 4.6 & 48.3 & 6.8 & 36.6 \\
- &  &  & 20 & 1 & 6.9 & 36.8 & 7.8 & 51.1 \\
- &  &  & 25 & 1 & 7.5 & 31.7 & 9.2 & 60.6 \\
-\cline{3-9}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 1 & 1.0 & 61.2 & 8.5 & 66.5 \\
- &  &  & 25 & 1 & 1.4 & 45.9 & 9.7 & 41.7 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
-\multirow[t]{5}{*}{yoyo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 18.1 & 6.6 & 91.1 \\
-\cline{3-9}
- &  & Paver Bricks & 5 & 1 & 2.8 & 57.8 & 9.7 & 123.9 \\
-\cline{3-9}
- &  & Sidewalk Pavers & 5 & 2 & 2.6 & 32.5 & 6.5 & 98.9 \\
-\cline{3-9}
- &  & Sidewalk Slabs & 5 & 2 & 4.0 & 25.7 & 5.1 & 103.8 \\
-\cline{3-9}
- &  & Tarmac & 5 & 2 & 0.8 & 18.1 & 7.4 & 156.6 \\
-\cline{1-9} \cline{2-9} \cline{3-9}
+    Strollers & Bugaboo & Cot, 0 mo  & 5 & 3 & 146 \\
+              &         & Seat, 9 mo & 5 & 4 & 49 \\
+    \cline{2-6}
+              & Maxi-Cosi & Cot, 0 mo  & 5 & 2 & 131 \\
+              &           & Seat, 9 mo & 5 & 4 & 35 \\
+    \cline{2-6}
+              & Stokke BABYZEN YOYO & Cot, 0 mo  & 5 & 4 & 35 \\
+              &                     & Seat, 9 mo & 5 & 4 & 51 \\
+    \cline{2-6}
+              & Green Machine & Cot, 0 mo & 5 & 4 & 17 \\
+    \cline{2-6}
+              & Old Rusty & Seat, 9 mo & 5 & 4 & 31 \\
+    \cline{1-6}
+    Bicycles & Keiler tricycle & Melia, 3 mo & 5 & 2 & 52 \\
+
+             &               & Melia, 3 mo & 12 & 2 & 85 \\
+
+             &               & Melia, 3 mo & 20 & 2 & 124 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 0 mo & 5 & 2 & 113 \\
+
+             &               & Maxi-Cosi, 0 mo & 12 & 2 & 140 \\
+
+             &               & Maxi-Cosi, 0 mo & 20 & 2 & 115 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 3 mo & 5 & 2 & 151 \\
+
+             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160 \\
+
+             &               & Maxi-Cosi, 3 mo & 20 & 2 & 145 \\
+    \cline{2-6}
+             & Urban Arrow & Melia, 3 mo & 5 & 2 & 43 \\
+
+             &               & Melia, 3 mo & 12 & 2 & 43 \\
+
+             &               & Melia, 3 mo & 25 & 2 & 42 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 0 mo & 5 & 1 & 50 \\
+
+             &               & Maxi-Cosi, 0 mo & 12 & 2 & 63 \\
+
+             &               & Maxi-Cosi, 0 mo & 25 & 2 & 130 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 3 mo & 5 & 2 & 156 \\
+
+             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160 \\
+
+             &               & Maxi-Cosi, 3 mo & 25 & 2 & 160 \\
     \bottomrule
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-compare-all.png}
-  \caption{Scatter plot of the vertical RMS acceleration of all trials broken
-  down by vehicle setup, trial duration, road surface, and plotted versus
-  speed.}
-  \label{fig:compare-all}
-\end{figure}
-
-\section{Conclusion}
+\subsection{Statistical Results}
+%
+Table~\ref{tab:stroller-ols} shows the results of the 11 degrees of freedom
+stroller model for the 104 repetitions~(\(R^2=0.867,F=54.69\)). Both categorical
+variables have significant effects. The intercept gives the mean acceleration of
+the Green Machine stroller pushed over tarmac, which is not significant. All
+road surfaces cause significantly more acceleration than tarmac with
+cobblestones having the largest relative effect (3.0~\si{\mps\squared} larger),
+followed by sidewalk slabs (2.7~\si{\mps\squared} larger), sidewalk pavers
+(1.8~\si{\mps\squared} larger), and paver bricks (1.6~\si{\mps\squared} larger).
+The `Bugaboo, Seat, 9 mo' and `Maxi-Cosi, Seat, 9 mo' are not significantly
+different than the `Green Machine, Cot, 0 mo' but the other strollers are. The
+`Old Rusty, Seat, 9 mo' and `Bugaboo, Cot, 0 mo' showed lower RMS acceleration
+than `Green Machine, Cot, 0 mo' by 0.8 and 0.5~\si{\mps\squared}, respectively.
+The remaining strollers have larger accelerations than the `Green Machine, Cot,
+0 Mo' on tarmac: `Maxi-Cosi, Cot, 0 mo' (1.1~\si{\mps\squared}), `Bugaboo, Cot,
+0 mo' (1.0~\si{\mps\squared}), `YOYO, Seat, 9 mo' (1.0~\si{\mps\squared}), and
+`YOYO, Seat, 0 mo' (0.6~\si{\mps\squared}).
+%
+\begin{table}
+  \centering
+  \caption{Ordinary Linear Regression Results for Stroller. Tarmac and Green
+  Machine Cot month are the references for the categorical Road Surface and
+  Stroller variables, respectively. The columns give the effect \(\beta\), standard
+  error, T-statistic, p-value, and the 95\% confidence interval lower and upper
+  bounds.}
+  \label{tab:stroller-ols}
+  \footnotesize
+\begin{tabular}{lcccccc}
+\toprule
+& \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$> |$t$|$} & \textbf{[0.025} & \textbf{0.975]}  \\
+\midrule
+\textbf{Intercept}                                                                                     &       0.2212  &        0.188     &     1.177  &         0.242        &       -0.152    &        0.595     \\
+Cobblestones                                     &       3.0117  &        0.163     &    18.473  &         0.000        &        2.688    &        3.336     \\
+Paver Bricks                                     &       1.6000  &        0.172     &     9.299  &         0.000        &        1.258    &        1.942     \\
+Sidewalk Pavers                                  &       1.7566  &        0.174     &    10.092  &         0.000        &        1.411    &        2.102     \\
+Sidewalk Slabs                                   &       2.7754  &        0.167     &    16.637  &         0.000        &        2.444    &        3.107     \\
+bugaboo, cot, 0 mo   &       0.9706  &        0.202     &     4.813  &         0.000        &        0.570    &        1.371     \\
+bugaboo, seat, 9 mo  &      -0.5065  &        0.199     &    -2.551  &         0.012        &       -0.901    &       -0.112     \\
+maxicosi, cot, 0 mo  &       1.0795  &        0.202     &     5.353  &         0.000        &        0.679    &        1.480     \\
+maxicosi, seat, 9 mo &       0.3012  &        0.209     &     1.441  &         0.153        &       -0.114    &        0.716     \\
+oldrusty, seat, 9 mo &      -0.7551  &        0.209     &    -3.605  &         0.001        &       -1.171    &       -0.339     \\
+yoyo, cot, 0 mo]     &       0.5766  &        0.209     &     2.753  &         0.007        &        0.161    &        0.993     \\
+yoyo, seat, 9 mo     &       0.9706  &        0.205     &     4.731  &         0.000        &        0.563    &        1.378     \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Table~\ref{tab:bicycle-ols} shows the results of the 8 degree of freedom cargo
+bicycle model for the 50 repetitions~(\(R^2=0.925,F=63.17\)). The vehicle setup
+categorical variable has significant effects, the road surface categorical
+variable alone does not, but the speed and interaction of speed with road
+surface do have significant effects. The intercept should theoretically be zero,
+because there is no vertical vibration when the speed is zero and the intercept
+is not significantly different than zero. Speed is not a significant predictor
+on tarmac, but the interaction variable shows that 0.8~\si{\mps\squared} is
+gained in acceleration for each 1~\si{\kph} increase on paver bricks. Only the
+Urban Arrow with the 3 mo infant in either seat has significant difference to
+the `Keiler, Maxi-Cosi, 3 mo', both showing reduction in relative acceleration.
+%
+\begin{table}
+  \centering
+  \caption{Ordinary Linear Regression Results for Cargo Bicycle. Tarmac and
+  `Keiler, Maxi-Cosi, 3 mo' are the references for the categorical Road Surface
+  and Cargo Bicycle variables, respectively. The columns give the effect
+  \(\kappa\), standard error, T-statistic, p-value, and the 95\% confidence
+  interval lower and upper bounds.}
+  \label{tab:bicycle-ols}
+  \footnotesize
+\begin{tabular}{lcccccc}
+\toprule
+& \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$> |$t$|$} & \textbf{[0.025} & \textbf{0.975]}  \\
+\midrule
+\textbf{Intercept}                                                                                          &       0.8067  &        0.643     &     1.255  &         0.216        &       -0.491    &        2.104     \\
+Paver Bricks                                          &       1.2956  &        0.889     &     1.457  &         0.153        &       -0.500    &        3.091     \\
+keiler, maxicosi, 0 mo     &       0.8664  &        0.415     &     2.085  &         0.043        &        0.027    &        1.705     \\
+keiler, melia, 3 mo        &      -0.5060  &        0.415     &    -1.219  &         0.230        &       -1.344    &        0.332     \\
+urbanarrow, maxicosi, 0 mo &      -0.0512  &        0.404     &    -0.127  &         0.900        &       -0.867    &        0.764     \\
+urbanarrow, maxicosi, 3 mo &      -0.8895  &        0.415     &    -2.141  &         0.038        &       -1.728    &       -0.051     \\
+urbanarrow, melia, 3 mo    &      -1.1357  &        0.403     &    -2.819  &         0.007        &       -1.949    &       -0.322     \\
+Mean Speed [m/s]                                                                              &       0.2034  &        0.116     &     1.747  &         0.088        &       -0.032    &        0.439     \\
+Mean Speed\(\times\)Road Surface                    &       0.7803  &        0.180     &     4.338  &         0.000        &        0.417    &        1.144     \\
+\bottomrule
+\end{tabular}
+  \end{table}
+
+\paragraph{Vehicle Comparisons}
+%
+Given that the vehicle setup (\(x_\textrm{Stroller}\) and \(x_\textrm{Cargo
+Bicycle}\)) is a significant effect, we perform a post-hoc analysis to compare
+vehicles on each road surface. Table~\ref{tab:sig-group-stroller}, derived from
+Figure~\ref{fig:tukey-stroller} in Appendix~\ref{app:compare}, shows the
+groupings of non-significant comparisons for a Tukey Range Test among the
+strollers.
+Old Rusty and `Bugaboo, Seat, 9 mo' and the Green Machine perform generally
+better (significantly) than the other vehicles, shown by the ``overall''
+ranking.
+For cobblestones, this is also true as well as: 1) the `YOYO, Seat, 9 mo' is the
+worst stroller tested and, interestingly, the the heavier dummy performs worse
+than the lighter dummy, 2) the 9 mo dummy experiences less acceleration in the
+Bugaboo and Maxi-Cosi.
+For paver bricks: 1) Old Rusty, `Bugaboo, Seat, 9 mo', and Green Machine are
+again the best and 2) `YOYO, Seat, 9 mo' sees more acceleration than the 0 mo
+configuration.
+For sidewalk pavers, there is no significant difference among the strollers.
+For side walk slabs: 1) Old Rusty is the best and Bugaboo the second best,
+2) the 0 month in the Bugaboo and Maxi-Cosi see more than the 9 month in the
+same vehicle, respectively, and 3) no difference in the YOYO when comparing
+dummy sizes.
+For tarmac: the Green Machine, `Bugaboo, Seat, 9 mo', and `YOYO, Seat, 9 mo' are
+better than Maxi-cosi with either dummy size and 2) the Green Machine is better
+than the `Bugaboo, Cot, 0 mo'.
+%
+\begin{table}
+\centering
+\caption{Stroller Significance Ranking Groups (based on
+Figure~\ref{fig:tukey-stroller}). The numbers indicate the group where there is
+no significant difference with 1 being the best (lower acceleration) and 8 being
+the worst (higher acceleration). The ``Overall'' column gives an overall ranking
+based on the mean ranking of the other columns.}
+\label{tab:sig-group-stroller}
+\begin{tabular}{lcccccc}
+  \toprule
+                          &         &              & Paver  & Sidewalk & Sidewalk & \\
+  Vehicle Setup           & Overall & Cobblestones & Bricks & Pavers   & Slabs    & Tarmac \\
+  \midrule
+  yoyo, seat, 9 mo        & 7 & 8   & 6-8 & 1-8 & 5-6 & 1-6 \\
+  yoyo, cot, 0 mo         & 4 & 4-5 & 3-5 & 1-8 & 5-6 & 1-8 \\
+  oldrusty, seat, 9 mo    & 1 & 1-2 & 1-3 & 1-8 & 1   & 1-8 \\
+  maxicosi, seat, 9 mo    & 4 & 4-5 & 3-6 & 1-8 & 3-4 & 4-8 \\
+  maxicosi, seat, 0 mo    & 8 & 6-7 & 6-8 & 1-8 & 7-8 & 4-8 \\
+  greenmachine, cot, 0 mo & 3 & 3   & 1-3 & 1-8 & 3-4 & 1-4 \\
+  bugaboo, seat, 9 mo     & 1 & 1-2 & 1-3 & 1-8 & 2   & 1-6 \\
+  bugaboo, cot, 0 mo      & 6 & 6-7 & 3-6 & 1-8 & 7-8 & 2-8 \\
+  \bottomrule
+\end{tabular}
+\end{table}
+
+When comparing the cargo bicycles, Table~\ref{tab:sig-group-bicycle}, most
+vehicle setups deliver similar acceleration to the seat pan when ridden over the
+same surface at the same target speed. For low speed on tarmac, the Urban Arrow
+with the Meila Baby Shell and a 3 mo dummy has significantly less acceleration
+than the Keiler with the Maxicosi and 0 mo dummy. There is no significant
+difference in any vehicle setups at low speed on paver bricks. At higher speeds,
+the Urban Arrow and Keiler with the Meila seat and the 3 mo dummy is
+significantly better than the Keiler with the Maxicosi and the 0 mo on paver
+bricks and on tarmac. It is important to point out that there is no significant
+difference when simply swapping the seat for the 3 mo dummy, which does not
+support the hypothesis in Section~\ref{sec:health-assesment}.
+%
+\begin{table}
+\centering
+\caption{Cargo Bicycle Significance Ranking Groups (based on
+Figure~\ref{fig:tukey-bicycle}). The numbers indicate the group where there is
+no significant difference with 1 being the best (lower acceleration) and 6 being
+the worst (higher acceleration). The ``Overall'' column gives an overall ranking
+based on the mean ranking of the other columns. Note that the mean ranking is
+very close for all cargo bicycles.}
+\label{tab:sig-group-bicycle}
+\begin{tabular}{lccccc}
+     \toprule
+                                &         & Paver Bricks & Tarmac    & Paver Bricks & Tarmac \\
+     Vehicle Setup              & Overall & Low Speed    & Low Speed & High Speed   & High Speed \\
+     \midrule
+     urbanarrow, melia, 3 mo    & 1 & 1-6 & 1-5 & 1-5 & 1-5\\
+     urbanarrow, maxicosi, 3 mo & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
+     urbanarrow, maxicosi, 0 mo & 4 & 1-6 & 1-6 & 1-6 & 1-5\\
+     keiler, melia, 3 mo        & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
+     keiler, maxicosi, 3 mo     & 5 & 1-6 & 1-6 & 1-6 & 1-6\\
+     keiler, maxicosi, 0 mo     & 6 & 1-6 & 2-6 & 3-6 & 4-6\\
+     \bottomrule
+\end{tabular}
+\end{table}
+
+\section{Discussion}
 %
 We have presented a comprehensive set of acceleration measurements from
-experiments that simulate the vibrations experienced by babies in the 0-9 month
-age range during transportation via strollers and cargo bicycles. We compare the
-average magnitude of vertical acceleration at the seat pan across a variety of
-road surfaces and seats while moving at typical vehicle travel speeds. In this
-preliminary analysis, we report on the variation among the various independent
-variables, finding that average acceleration can be relatively large for some
-scenarios. We only report the characterization of the accelerations experienced
-by the baby and do not weigh in on whether these can cause discomfort or have
-negative health consequences. There is a large gap in the literature connecting
-acceleration magnitude to discomfort and/or health consequences.
-
-We show that average acceleration can range from
-\SIrange{0.5}{11.4}{\meter\per\second\squared} across all tested scenarios.
-Strollers experience \SIrange{0.5}{5.3}{\meter\per\second\squared} average
-acceleration for a mean walking speed of 5.2~\si{\kilo\meter\per\hour}. Cargo
-bicycles experience \SIrange{1.0}{11.4}{\meter\per\second\squared} over a speed
-range of \SIrange{12}{25}{\kilo\meter\per\hour}.
-
+experiments that simulate the vibrations experienced by dummy infants in the 0-9
+month mass range during transportation in both strollers and cargo bicycles. We
+compared the average magnitude of vertical and total acceleration at the seat
+pan across a variety of road surfaces and seats while moving at typical vehicle
+travel speeds. Excluding the shock tests, ISO~2631-1 weighted average
+acceleration can range from \SIrange{0.4}{10.7}{\mps\squared} across all tested
+scenarios. Strollers induced \SIrange{0.4}{5.0}{\mps\squared} average
+acceleration for a mean walking speed of 5.3~\si{\kph}. Cargo bicycles induced
+\SIrange{0.6}{10.7}{\mps\squared} over a speed range of \SIrange{12}{25}{\kph}.
+
+\subsection{Surface and Speed}
+%
 Travelling over a tarmac surface offers the least vibration to all vehicle types
 at any speed with a maximum average acceleration of
-2.7~\si{\meter\per\second\squared}. For strollers, travelling over surfaces
-rougher than tarmac at normal walking speed can cause from 1.6\(\times\) to
-6.6\(\times\) the accelerations experienced on tarmac with average accelerations
-reaching 5.3~\si{\meter\per\second\squared}. Cobblestones and the large gaps of
-the sidewalk slabs cause the largest magnitude vibrations to the baby in the
-strollers. For cargo bicycles, travelling over paver bricks at the same speeds
-can quadruple the magnitude of the average acceleration the baby experiences.
-Travelling at the maximum allowed speed of an electric cargo bike (25
-\si{\kilo\meter\per\hour}) over paver bricks causes the baby to experience
-average accelerations exceeding 8~\si{\meter\per\second\squared}. The effect of
-speed on vibration is higher for paver bricks than tarmac.
-
-The size of the baby (mass and shape) has no obvious effect on the average
-accelerations experienced at the seat pan body-seat interface. These vibrations
-are transmitted to the baby's body and the physical properties (mass, stiffness,
-damping) of the baby's body determine whether this excitation is amplified or
-not and to which body segment is more affected. Tests with more realistic
-dummies or real babies is necessary to know how the baby itself moves when
-excited by this level of vibration. This information is not readily available in
-the literature and may be hard to perform due to ethical limitations and absence
-of realistic dummies.
-
-When comparing stroller and cargo bicycle vehicle setups (vehicle, seat, baby
-age) among each other, the preliminary results show no obvious differences in
-the acceleration experienced by the baby other than the baby shell being better
-than a baby car seat for the 3 month old baby in the cargo bike at the maximum
-speeds. This may be attributed to the suspended mounting location of the baby
-seat in the cargo bay versus the baby shell being mounted to the existing bench
-in the cargo bay. Statistical analysis may reveal more nuance differences among
-the vehicle setups.
-
-We also investigated the dominant frequency and bandwidth of vibrations across
-the various scenarios. Vibrations at frequencies between
-\SIrange{4.9}{10.7}{\hertz} have the largest magnitude contribution to the
-vibrations but there is frequency content of magnitudes of interest in a
-bandwidth of up to 100~\si{\hertz}.
-
-We measured four other sensors on the vehicles, all with six accelerometer and
-gyroscope time histories, for a total of 30 time histories of possible interest.
-This paper provides a look into the experiments via three metrics: vertical RMS
-acceleration, peak frequency, and bandwidth of effectively one of the 30 time
-histories. There are a variety of other metrics that can provide insight, for
-example vibration dosage value and crest factor that characterize peak
-accelerations or ISO 2631-1 weighted linear and rotational accelerations that
-have more connection to experienced comfort. Future work will investigate these
-more closely as well as shock effects and apply standard statistical models to
-the data to make more definitive conclusions in the scenario comparisons.
+1.2~\si{\meter\per\second\squared}. For strollers, travelling over surfaces
+rougher than tarmac at normal walking speed can cause, on average, 5\(\times\)
+the acceleration experienced on tarmac with average accelerations reaching
+5.0~\si{\meter\per\second\squared}. Cobblestones and the large gaps in the
+sidewalk slabs caused the largest magnitude of vibrations at the seat pan in the
+strollers. Cobblestones and sidewalk slabs approximately double the vibration
+amplitude relative to sidewalk paver and paver bricks, with them all being
+significant larger than tarmac vibrations.
+
+For cargo bicycles, travelling over paver bricks at the same speeds can
+quadruple the magnitude of the average acceleration the dummy experiences.
+Travelling at the maximum allowed speed of an electric cargo bicycle (25
+\si{\kph}) over paver bricks caused the dummy to experience average
+accelerations exceeding 8~\si{\mps\squared}. The effect of speed on vibration is
+significant for paver bricks but not for tarmac.
+
+Whereas speed strongly affected the acceleration amplitude it does not strongly
+affect the peak frequency and the bandwidth below which 80\% of power is
+contained. This suggests that peak frequencies represent oscillations induced by
+the systems tested rather than dominant frequencies resulting from the road
+surface.
+
+\subsection{Baby Mass}
+%
+The size of the dummy (mass and build) had no obvious and systematic effect on
+the average acceleration at the seat pan body-seat interface. These vibrations
+are transmitted to an infant's body and the physical properties (mass,
+stiffness, damping) of the infant's body determine whether this excitation is
+amplified or not and which body segment is more affected. Tests with more
+realistic dummies or real infants are necessary to investigate how the infant
+itself moves when excited by this level of vibration. This information is not
+readily available in the literature and may be hard to acquire due to ethical
+limitations and the absence of validated infant dummies. The only effect that
+stood out for mass was that, counter-intuitively, the lighter dummy has less
+acceleration than the heavier dummy for the Stokke BABYZEN YOYO 0+ stroller.
+
+\subsection{Health}
+%
+The vibrations measured in the different scenarios showed that RMS acceleration
+can be relatively large when compared to the smoothest experience on tarmac.
+There is a large gap in the literature connecting acceleration magnitude to
+discomfort and/or health consequences, which is particularly absent for infants.
+The most used health and comfort assessment tool for whole-body vibration is the
+ISO~2631-1 standard. When we investigated health risks using the standard we
+found that:
+%
+\begin{itemize}
+    \item only strollers pushed over tarmac at 5~\si{\kph} had average
+    acceleration below the ``health risk zone" for 4~\si{\hour} daily duration,
+    \item strollers pushed over cobblestones and sidewalk slabs can deliver
+    accelerations in the ``health risk zone'' with durations less than
+    20~\si{\min},
+    \item cargo bicycles ridden at \SIrange{12}{25}{\kph} over tarmac
+    overwhelmingly delivered accelerations below the 1~\si{\hour} ``health risk
+    zone'', and
+    \item cargo bicycles ridden at \SIrange{12}{25}{\kph} over paver bricks
+    delivered accelerations well into the 10~\si{\min} ``health risk zone''.
+\end{itemize}
+%
+When we compare the vibration we measured for infants in strollers and cargo
+bicycles with the vibration ``health risk zone'' as defined for adults in the
+ISO~2631-1 standard, we see that:
+%
+\begin{itemize}
+    \item cycling with an infant in a cargo bicycle on paver bricks with
+    20~\si{\kph} for 10~\si{\min} gives the infant a vibration load that equals
+    or exceeds the ``health risk zone'' for adults seated erectly experiencing
+    vibrations,
+    \item cycling with an infant in a cargo bicycle on tarmac at 12~\si{\kph} can
+    be maintained for approximately two hours before exceeding the ``health risk
+    zone'' for adults seated erectly experiencing vibrations,
+    \item walking with an infant in a stroller on cobblestones can exceed the
+    ``health risk zone'' for adults seated erectly experiencing vibrations
+    within 15~\si{\min} to 1~\si{\hour}, depending on the stroller model and the
+    age of the child, and
+    \item walking with an infant in a stroller on tarmac can be continued for
+    four hours without exceeding the ``health risk zone'' for adults seated
+    erectly experiencing vibrations.
+\end{itemize}
+
+We can conclude that strollers can be pushed over paver bricks and sidewalk
+pavers continuously for maximal about half an hour. On extreme surfaces like
+cobblestones and sidewalk slabs, strollers should be pushed slower than
+5~\si{\kph} with a duration of maximal 10~\si{\min}. Only on tarmac a stroller
+can be walked continuously for four hours (but only if the infant is in the cot,
+for if it is sitting it needs appropriate breaks to enable movement). Cargo
+bicycles carrying infants over paver bricks should slow down to 12~\si{\kph} or
+preferably less and the duration should be kept under 10~\si{\min}. When riding
+a cargo bicycle over tarmac at 20\si{\kph}, the duration should be kept under
+1~\si{\hour}. At 12~\si{\kph} cargo bicycles can ride over tarmac for maximal
+2~\si{\hour}.
+
+\subsection{Comfort}
+%
+When considering comfort, the ISO~2631-1 guidelines indicate that adults would
+report the vibrations experienced in strollers and bicycles as uncomfortable.
+For strollers, the vibrations over tarmac would be rated ``fairly
+uncomfortable'' and all other road surfaces would be ``very'' or ``extremely
+uncomfortable''. When riding a cargo bicycle over paver bricks, the vibrations
+would be rated as ``extremely uncomfortable'' and over tarmac spans ``fairly``
+to ``extremely''. The ISO~2631-1 comfort rating scale is derived from adult
+subjective ratings of vibrations felt when riding public transit for an
+unspecified duration, so this scale is unlikely appropriate to apply for our
+situation. Gao~et~al.~\cite{Gao2018} reports that cyclists do not rate
+vibrations as extremely uncomfortable on normal road surfaces, indicating some
+contradiction.
+
+\subsection{Vehicle and Seat Design}
+%
+Different vehicle, seat, and baby mass combinations cause different average
+vertical accelerations at the seat pan. We are only able to compare vehicle
+setup to vehicle setup, other than comparing the same two different baby seats
+in both cargo bikes. A striking discovery is that the two 1970's strollers we
+tested were significantly better than many of the modern stroller setups on most
+road surfaces. The vintage strollers actually had more sophisticated suspension
+systems that used springs, straps, and mechanisms, and they also had larger
+wheels. Stroller manufacturers may have reduced suspension as a side effect to
+decreasing the size and weight of strollers and introducing swivelling front
+wheels (which makes steering lighter but can technically not be combined with
+the design of old suspension types). As an example, the ``Old Rusty'' stroller
+was the only one that did not exceed the 1~\si{\hour} health risk line for all
+road surfaces.
+
+Both the Bugaboo Fox 5 and Maxi-Cosi Street Plus stroller showed lower
+acceleration for the heavier baby, as expected, but the Stokke BABYZEN YOYO 0+
+showed the opposite trend for cobblestones and paver bricks. This points to
+design choices that may cause resonance on certain surface profiles. The
+`Bugaboo, Seat, 9 mo' configuration performed better than the other modern
+strollers for all non-tarmac road surfaces. Urban Arrow performed better than
+Keiler on tarmac but there is no difference on paver bricks. Additionally, there
+was no difference in the different seats for the 3 month infant. Performance of
+a vehicle setup is not necessarily constant with respect to cot or seat
+configuration, contrarily, performance is often significantly different when
+converting for different baby ages. This points towards designs that are only
+optimized for one configuration.
+
+\subsection{ISO Filters and Bandwidth}
+%
+We report RMS accelerations up to 120~\si{\hertz} Hz as well as accelerations
+weighted according to the ISO standards for vibration (VDV). Vibrations at
+frequencies between \SIrange{4.9}{10.7}{\hertz} showed to have the largest
+magnitude contribution to the vibrations, but there is a frequency content of
+magnitudes of interest in a bandwidth of up to 45~\si{\hertz}. Our results show
+substantial differences between RMS and VDV highlighting the importance of
+reviewing their meaning. These differences emerge from the high bandwidth of the
+accelerations now measured, which greatly exceed the bandwidth of accelerations
+measured with adults seated in cars (see e.g Figure 2 in
+\cite{griffin2004experimental}). Adult experiments show that significant
+discomfort can be measured across all tested frequencies being 80 Hz
+\cite{morioka2010frequency} or even 315~\si{\hertz}~\cite{morioka2006magnitude}
+albeit with reduced sensitivity.
+
+The ISO frequency weightings are defined for adults in more or less erect
+postures with the head being unsupported, whereas we now studied dummies
+representing infants from 0-9 months lying with the head directly supported. The
+ISO~2631-1 weightings represent a reduced sensitivity above 8~\si{\hertz}, which
+is associated with the vertical dynamics of erect seated subjects which filter
+out such high frequencies \cite{toward2011transmission,mirakhorlo2022effects}.
+However, adult experiments show higher discomfort for frequencies above
+8~\si{\hertz} when lying with head supported with \SIrange{30}{90}{\degree} back
+inclination as compared to erect without head support. Higher frequencies have
+also been associated with effects on the central nervous system. For instance,
+experiments on rats showed brain injury visible in behaviour through functional
+impairment and in visual changes of brain structures in postmortem dissection
+after exposure to prolonged whole-body vibration at 30~\si{\hertz} and
+5~\si{\mps\squared}~\cite{Yan2015_cumulative_brain_injury/j.jstrokecerebrovasdis.2015.08.007}.
+In some conditions, the RMS exceeds the ISO Weighted RMS substantially,
+warranting further research on the effects of higher frequencies in particular
+for head supported conditions and for children. The VDV showed even higher
+values warranting further research on the relevance of peaks and transients.
+
+\section{Conclusion}
+%
+\subsection{Summary}
+%
+The results herein raise concerns about transporting infants in strollers and
+cargo bicycles. If the user's behaviour is not adjusted to avoid rough surfaces
+or to go very slow over them when the cargo is an infant, there are potential
+health risks if the large vibrations are experienced daily and repeatedly over a
+longer time. In most likelihood, users do adjust their travel behaviour, but
+maybe not enough or possibly they are neglectful, but this has yet to be
+studied. There is no direct evidence that connects whole-body vibration as
+measured in this study to infant harm or negative health effects, so we can only
+extrapolate from the limited guidelines on adults in occupational settings. But
+we did measure vibrations that would not be permitted for adults to maintain
+long term occupational health and it is reasonable to believe we should not
+subject our infants to the same.
+
+It is well known that whole-body vibration can be controlled with good
+suspension design. We see this in the drastic historical evolution of suspension
+in automobiles. We do not see this same kind of attention to suspension in
+strollers, cargo bicycles, and baby seats for these vehicles. Walking and
+cycling is well known to offer great societal and personal benefits over
+travelling by car, so it behoves us all to make transport for infants most
+optimal in these two transport modes.
+
+\subsection{Recommendations}
+%
+Our conclusions result primarily from the recommended application of ISO~2631-1.
+It is of utmost importance to recognize that this standard cautions extending
+the use of the standard to situations of which its supporting data was not
+derived. The standard is based primarily on pre-1997 studies of adult whole-body
+vibration in occupational durations (\SIrange{4}{8}{\hour} daily dose) or during
+public transportation.
+%
+\begin{quote}
+  \textbf{The recommendations in standard ISO~2631-1 have not been based on or validated for: 1)
+  short durations that dominate stroller and cargo bicycle travel, 2) infants,
+  children, or young adults, 3) nor to recumbent or reclined seating postures with the head supported.
+  So our recommendations must be taken with utmost caution, at least until more
+  research is done to improve the standard guidance.}
+\end{quote}
+%
+Nevertheless, the following list provides recommendations for users,
+researchers, designers, and manufacturers based on the findings of this paper
+that we believe stand in spite of the standard's limitations:
+%
+\begin{enumerate}
+    \item Stroller, cargo bicycle, and seat manufacturers should test for
+    vibration for all expected surface types and ranges of relevant body sizes
+    and posture to ensure their designs isolate vibrations well for all use
+    conditions. Testing across relevant body sizes is especially important for
+    strollers, due to the high mass of the infant relative to the stroller mass.
+    \item Manufacturers should collaborate in testing and report their results
+    publicly, similar to the automobile industry safety ratings. For the
+    combined use of cargo bicycles and baby seats, manufacturers should
+    collaborate in this effort.
+    \item Manufacturers and scientists should collaborate to develop metrics and
+    testing procedures for the long-term goal of a new standard.
+    \item Designers should ensure that adequate vibration isolation occurs for
+    vehicles that have multiple configurations (e.g. recumbent vs. erect
+    seating).
+    \item Designers and manufacturers should incorporate better suspension
+    systems, as currently occurring vibrations can be drastically reduced.
+    Useful information may be derived from past designs with better suspension.
+    \item Cycling roads should have a tarmac-like smoothness. Cobblestones
+    should be avoided.
+    \item Sidewalks should have a tarmac-like smoothness. Cobblestones should be
+    avoided for strollers.
+    \item Users should limit their speed when walking with strollers or riding
+    over surfaces rougher than tarmac, as bumpier surfaces can quickly multiply
+    the experienced accelerations.
+    \item Users are suggested to limit the duration of transport over surfaces
+    rougher than tarmac to periods that do not exceed 10-30 continuous minutes
+    depending on the system (existence of suspension, larger tyres or wheels)
+    and other countermeasures like adequate non-vibration breaks in between.
+    When transporting over tarmac, continuous durations should not exceed
+    4~hours and need to include regular breaks, if only to give the infant
+    opportunity to move.
+    \item Preferably ride any cargo bicycle at a speed of maximal 12~\si{\kph}
+    over surfaces rougher than tarmac. E-cargo bicycles can easily reach the
+    maximum speed of 25~\si{\kph}. Infants should only be transported for short
+    durations when riding over non-tarmac surfaces at these speeds.
+    \item Standard ISO~2631-1 is not based on or validated to characterize
+    health and comfort effects of vibration for infants or children or for short
+    durations or non-erect seating. However, this is the only available standard
+    in the literature assessing health and comfort levels on vibrations, and
+    could be used as benchmark.
+\end{enumerate}
+
+\subsection{Future Work}
+% 
+There are four possible directions for future work: more in-depth analysis of
+the present measurements, more research on vibrations generated by infant
+transport systems, more research on the effects of vibration on infants, and
+development of a benchmark.
+
+\paragraph{Concerning further analysis of the present measurements:}
+%
+We acquired data from four other sensors on the vehicles, each with three
+accelerometer and three gyroscope time histories, for a total of 30 time
+histories of possible interest. This paper provides a look into the experiments
+via four metrics: ISO weighted vertical RMS acceleration, maximum acceleration,
+peak frequency, and bandwidth of the seat pan sensor. The collected data can
+also be used to investigate the transmissibility from sensor to sensor, as well
+as rotational vibration effects. Investigating these further can give a more
+complete picture of the connections to health and comfort. This work also gives
+a benchmark against which new designs can be tested to show reduction in
+vibration.
+
+\paragraph{Concerning more research on vibrations generated by infant transport
+systems:}
+%
+There are products and variables that have not yet been investigated for their
+effect on vibration. For example, running with an infant in a sports stroller is
+not tested. Investigating this is important because we expect that vibrations
+when running may quickly exceed health limits. In addition, recumbent posture in
+sports strollers is estimated to increase the vibration load on the head of the
+infant. It is important to establish the actual vibration load on the head in
+practice.
+
+\paragraph{Concerning more research on the effects of vibration on infants:}
+%
+The frequency weighting of the ISO~2631-1 standard is not designed or validated
+to characterise health and comfort for infants or children, for short durations,
+and for non-erect seating. Research is urgently needed to develop a new standard
+with a more appropriate frequency weighting to improve assessment of the comfort
+and health effects of whole-body vibration of infants and children, also for
+short durations and for non-erect seating. Furthermore, tests with more
+realistic dummies and/or real infants are necessary to investigate how the
+infant itself moves when excited by various vibrations in different postures.
+The results will contribute to the assessment of the transmissibility of
+vibration in children, which is needed to deduce the vibrations transmitted to
+the head.
+
+\paragraph{Concerning the development of a benchmark:}
+%
+At this moment, no requirements are made for the vibrational properties of child
+transport systems in the standards for strollers, cargo bicycles, bicycle seats,
+and car seats. Due to the magnitude of vibrations that can occur during child
+transport, it is imperative to include a requirement to the vibrational
+properties in the standards for these products. At this moment, no new
+requirements can be defined because there is not enough information. With the
+information resulting from more research on infant vibration, a benchmark for
+the vibration properties of infant transportation products needs to be
+developed. This will enable the inclusion of minimal requirements for vibration
+properties in the standards, which would greatly increase the health and comfort
+of the infants who must use these products.
+
+\subsection{Acknowledgement}
+%
+We acknowledge the advice and financial support of VeiligheidNL.
 
@@
 
+\newpage
+\appendix
+
+% Ensure subsections retain "A.1", "A.2", etc.
+%\addcontentsline{toc}{section}{Appendix} % Optional: Add to TOC
+%\renewcommand{\thesection}{A}
+%\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
+
+\section{Experimental Equipment}
+\label{app:equipment}
+%
+In this section, we report the pictures of the strollers and bicycles used for
+the experiments. The reader can find the measurements, wheelbase, wheel
+diameter, sensor location and orientation for all the tested vehicles.
+
+\begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Joolz_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_UA-Joolz_front.pdf}}
+  \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
+  Maxicosi-Joolz baby Pebble.}
+  \label{fig:tech_drawing_UA_Joolz}
+\end{figure}
+
+\begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_UA-Melia_front.pdf}}
+  \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
+  Melia baby shell.}
+  \label{fig:tech_drawing_UA_Melia}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Joolz_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_Trike-Joolz_front.pdf}}
+  \caption{IMU locations on the Keiler Tricycle, equipped with the
+  Maxicosi-Joolz baby pebble.}
+  \label{fig:tech_drawing_Trike_Joolz}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Melia_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Melia_front.pdf}}
+  \caption{IMU locations on the Keiler Tricycle, equipped with the
+  Melia baby shell.}
+  \label{fig:tech_drawing_Trike_Melia}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_front.pdf}}
+  \caption{IMU locations on the stroller Bugaboo Fox 5, configured for 0-months baby.}
+  \label{fig:tech_drawing_Bugaboo0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Bugaboo9_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo9_front.pdf}}
+  \caption{IMU locations on the stroller Bugaboo Fox 5, configured for 9-months baby.}
+  \label{fig:tech_drawing_Bugaboo9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Maxicosi0_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Maxicosi0_front.pdf}}
+  \caption{IMU locations on the stroller Maxi-Cosi Street Plus, configured for 0-months baby.}
+  \label{fig:tech_drawing_Maxicosi0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Maxicosi9_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm,angle=-90]{fig/TechDraw_Maxicosi9_front.pdf}}
+  \caption{IMU locations on the stroller Maxi-Cosi Street Plus, configured for 9-months baby.}
+  \label{fig:tech_drawing_Maxicosi9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_YOYO0_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO0_front.pdf}}
+  \caption{IMU locations on the stroller Stokke BABYZEN YOYO 0+, configured for 0-months baby.}
+  \label{fig:tech_drawing_YOYO0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_YOYO9_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO9_front.pdf}}
+  \caption{IMU locations on the stroller Stokke BABYZEN YOYO 0+, configured for 9-months baby.}
+  \label{fig:tech_drawing_YOYO9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_GreenM0_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_GreenM0_front.pdf}}
+  \caption{IMU locations on the old stroller Green Machine, configured for 0-months baby.}
+  \label{fig:tech_drawing_GreenM0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_OldR9_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_OldR9_front.pdf}}
+  \caption{IMU locations on the old stroller Old Rusty, configured for 9-months baby.}
+  \label{fig:tech_drawing_OldR9}
+\end{figure}
+
+\clearpage
+\newpage
+
+\subsection{Location and pictures of the experiment areas}
+\label{app:location}
+
+\subsubsection{For Bicycles}
+
+\begin{itemize}
+    \item Tarmac
+\begin{figure}[htbp]
+  \centering
+  {\includegraphics[width=70mm, angle=-90]{fig/Tarmac_bicycle.pdf}}
+  \caption{Tarmac surface where we tested bicycles.}
+  \label{fig:tarmac_bicycle}
+\end{figure}
+
+The bicycle experiment on the tarmac was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands (GPS coordinates: 52.001053, 4.369071).
+
+    \item Paver bricks
+\begin{figure}[htbp]
+  \centering
+ {\includegraphics[width=70mm, angle=-90]{fig/Paver_bricks_bicycle.pdf}}
+  \caption{Paver bricks surface where we tested bicycles.}
+  \label{fig:paver_bricks_bicycle}
+\end{figure}
+
+The bicycle experiment on the paver bricks was conducted along Kanaalweg, 2611 DD Delft, The Netherlands (GPS coordinates: 52.006264, 4.363013).\\
+Details of paver brick: rectangular shape, dimensions 195 x 95 mm (gap in between: 7±2 mm).
+
+\clearpage
+
+    \item Shock
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=70mm, angle=0]{fig/Shock_bicycle.pdf}
+  \caption{We performed a shock test with bicycles riding over a 30x30 mm square section bar.}
+  \label{fig:shock_bicycle}
+\end{figure}
+
+The bicycle shock experiment was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands (same location of the experiment on the tarmac, GPS coordinates: 52.001053, 4.369071).\\
+Details of the shock experiment: we rode over a squared section aluminium bar 30 x 30 mm.
+
+\end{itemize}
+
+\subsubsection{For Strollers}
+
+\begin{itemize}
+    \item Tarmac
+
+\begin{figure}[htbp]
+  \centering
+    \includegraphics[width=70mm, angle=-90]{fig/Tarmac_stroller.pdf}
+  \caption{Tarmac test area.}
+  \label{fig:tarmac_stroller}
+\end{figure}
+
+The bicycle experiment on the tarmac was conducted along Julianalaan Straat, 2628 BG Delft, The Netherlands (GPS coordinates: 52.002727, 4.366845).
+
+\clearpage
+
+    \item Cobblestone
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=60mm, angle=-90]{fig/Cobblestone_stroller.pdf}
+  \caption{Cobblestone surface where we tested strollers.}
+  \label{fig:cobblestone_area_stroller}
+\end{figure}
+
+The bicycle experiment on the cobblestone was conducted along Julianalaan Straat, 2628 BG Delft, The Netherlands (GPS coordinates: 52.002727, 4.366845).
+Details of cobblestone: rectangular shape, dimensions 180 x 125 mm (gap in between: 20±4 mm).
+
+    \item Sidewalk pavers
+
+\begin{figure}[htbp]
+  \centering
+    \includegraphics[width=60mm, angle=-90]{fig/Sidewalk_pavers_stroller.pdf}
+  \caption{Sidewalk pavers test area for strollers.}
+  \label{fig:sidewalkpavers_area_stroller}
+\end{figure}
+
+The experiment was conducted along Prins Bernhardlaan, 2628 CN Delft, The Netherlands (same location as Paver bricks test, GPS coordinates: 52.003147, 4.369530).\\
+Details of sidewalk bricks: rectangular shape, dimensions 290 x 290 mm (gap in between: 12±2 mm).
+
+\clearpage
+
+    \item Sidewalk slabs
+
+\begin{figure}[htbp]
+  \centering
+    \includegraphics[width=70mm, angle=-90]{fig/Sidewalk_slabs_stroller.pdf}
+  \caption{Sidewalk slab test area where we conducted test with strollers.}
+  \label{fig:sidewalkslabs_area_stroller}
+\end{figure}
+
+The experiment was conducted in front of TU Delft Aula Conference Centre (Building 20), Mekelweg 5, 2628 CC Delft, The Netherlands (GPS coordinates: 52.002250, 4.372665).\\
+Details of sidewalk slab: made of concrete, rectangular shape, dimensions 2000 x 990 mm (gap in between: 160±3 mm).
+
+    \item Paver bricks
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=50mm, angle=-90]{fig/Paver_bricks_stroller.pdf}
+  \caption{Details of the paver bricks test area.}
+  \label{fig:paverbrick_area_stroller}
+\end{figure}
+
+The experiment was conducted along Prins Bernhardlaan, 2628 CN Delft, The Netherlands (same location as Sidewalk paver test, GPS coordinates: 52.003147, 4.369530).\\
+Details of paver brick: rectangular shape, dimensions 195 x 95 mm (gap in between: 7±2 mm).
+
+\clearpage
+
+    \item Shock
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=60mm, angle=-90]{fig/Shock_stroller.pdf}
+  \caption{Area where we tested strollers during the shock experiment.}
+  \label{fig:shock_area_stroller}
+\end{figure}
+
+The experiment was conducted inside TU Delft Mechanical Engineering faculty (Building 34 - Ground floor, aisle in front of Gezelschap Leeghwater office), Mekelweg 2, 2628 CD Delft, The Netherlands (GPS coordinates: 52.000587, 4.372224).\\
+Details of the shock experiment: we pushed the stroller over a squared section aluminium bar 30 x 30 mm.
+
+\end{itemize}
+
+\newpage
+\section{Table of Repetition Metrics}
+\label{app:results}
+%
+Table~\ref{tab:results} shows the mean over the scenario repetitions unweighted
+and ISO~2631-1 weighted seat pan vertical RMS acceleration, unweighted seat pan
+vertical VDV, crest factor, peak frequency, bandwidth, and duration for all 52
+combinations of vehicle setup, road surface, and target speed.
+% NOTE : This table is generated automatically from the Python scripts. I manually edit the header rows to fit on the page width. Save the edits between toprule and midrule!
+\bgroup
+\setlength\tabcolsep{0.4mm}  % reduces horiztonal padding between columns
+\begin{table}[!h]
+  \centering
+  \caption{Mean computed metrics for all 52 non-shock scenarios, using seat pan
+  vertical accelerations.}
+  \label{tab:results}
+  \scriptsize
+\begin{tabular}{lllccccccccc}
+\toprule
+        &            &         & Target & Trial     & RMS     & ISO Weighted & VDV      & Crest  & Peak      & \\
+        &            & Road    & Speed  & Count     & Accel   & RMS Accel    & Accel    & Factor & Freq. & Bandwidth  & Duration \\
+Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\
+\midrule
+\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.4 & 4.3 & 6.6 & 6.2 & 6.5 & 14.3 & 20.4 \\
+\cline{3-12}
+ &  & Paver Bricks & 5 & 3 & 2.6 & 2.4 & 3.4 & 4.1 & 9.5 & 17.2 & 23.3 \\
+\cline{3-12}
+ &  & Sidewalk Pavers & 5 & 2 & 2.9 & 2.7 & 7.5 & 13.5 & 6.1 & 18.5 & 25.4 \\
+\cline{3-12}
+ &  & Sidewalk Slabs & 5 & 3 & 4.8 & 4.7 & 7.9 & 6.4 & 5.8 & 15.1 & 20.2 \\
+\cline{3-12}
+ &  & Tarmac & 5 & 2 & 0.7 & 0.6 & 0.9 & 3.3 & 10.1 & 18.5 & 23.1 \\
+\cline{2-12} \cline{3-12}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 4 & 2.5 & 2.3 & 3.4 & 4.7 & 6.6 & 20.7 & 22.5 \\
+\cline{3-12}
+ &  & Paver Bricks & 5 & 3 & 2.3 & 1.8 & 3.0 & 3.8 & 9.4 & 26.4 & 22.6 \\
+\cline{3-12}
+ &  & Sidewalk Pavers & 5 & 3 & 1.7 & 1.4 & 2.5 & 5.5 & 7.7 & 23.8 & 24.7 \\
+\cline{3-12}
+ &  & Sidewalk Slabs & 5 & 3 & 2.4 & 2.2 & 3.6 & 5.3 & 6.0 & 20.3 & 24.5 \\
+\cline{3-12}
+ &  & Tarmac & 5 & 2 & 0.6 & 0.4 & 0.8 & 6.5 & 8.4 & 29.3 & 34.6 \\
+\cline{1-12} \cline{2-12} \cline{3-12}
+\multirow[t]{5}{*}{greenmachine} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 3.2 & 2.9 & 4.6 & 5.3 & 4.1 & 17.3 & 23.7 \\
+\cline{3-12}
+ &  & Paver Bricks & 5 & 2 & 1.6 & 1.3 & 2.1 & 4.5 & 4.2 & 26.8 & 29.6 \\
+\cline{3-12}
+ &  & Sidewalk Pavers & 5 & 2 & 2.7 & 2.5 & 4.2 & 6.5 & 4.1 & 18.5 & 28.2 \\
+\cline{3-12}
+ &  & Sidewalk Slabs & 5 & 3 & 3.5 & 3.2 & 5.5 & 6.7 & 3.9 & 16.8 & 23.9 \\
+\cline{3-12}
+ &  & Tarmac & 5 & 2 & 0.5 & 0.4 & 0.6 & 4.1 & 4.2 & 33.4 & 22.1 \\
+\cline{1-12} \cline{2-12} \cline{3-12}
+\multirow[t]{12}{*}{keiler} & \multirow[t]{4}{*}{maxicosi, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 7.0 & 6.9 & 11.2 & 7.2 & 7.6 & 16.7 & 23.8 \\
+ &  &  & 20 & 1 & 12.6 & 10.7 & 27.1 & 9.9 & 6.8 & 26.9 & 34.0 \\
+\cline{3-12}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 1.8 & 1.8 & 3.3 & 8.3 & 8.1 & 13.3 & 24.6 \\
+ &  &  & 20 & 2 & 2.8 & 2.8 & 3.9 & 5.1 & 7.8 & 13.2 & 29.2 \\
+\cline{2-12} \cline{3-12}
+ & \multirow[t]{4}{*}{maxicosi, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 6.3 & 5.7 & 12.3 & 11.0 & 8.0 & 21.9 & 28.9 \\
+ &  &  & 20 & 2 & 9.8 & 7.8 & 23.5 & 14.4 & 7.2 & 30.7 & 21.4 \\
+\cline{3-12}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.5 & 1.5 & 2.6 & 8.1 & 7.6 & 12.8 & 27.8 \\
+ &  &  & 20 & 2 & 2.1 & 2.1 & 2.8 & 3.9 & 6.4 & 12.7 & 23.8 \\
+\cline{2-12} \cline{3-12}
+ & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 5.4 & 4.9 & 8.9 & 8.1 & 7.9 & 21.9 & 26.3 \\
+ &  &  & 20 & 2 & 9.5 & 6.7 & 19.7 & 10.2 & 6.8 & 34.8 & 23.0 \\
+\cline{3-12}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.2 & 1.2 & 2.1 & 8.2 & 7.8 & 14.2 & 25.4 \\
+ &  &  & 20 & 2 & 1.6 & 1.5 & 2.1 & 3.8 & 8.3 & 13.8 & 22.6 \\
+\cline{1-12} \cline{2-12} \cline{3-12}
+\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.6 & 4.4 & 6.4 & 4.9 & 8.1 & 18.3 & 20.7 \\
+\cline{3-12}
+ &  & Paver Bricks & 5 & 2 & 3.2 & 2.8 & 4.2 & 3.9 & 10.4 & 21.1 & 27.2 \\
+\cline{3-12}
+ &  & Sidewalk Pavers & 5 & 3 & 3.0 & 2.9 & 4.5 & 5.5 & 7.6 & 18.1 & 21.4 \\
+\cline{3-12}
+ &  & Sidewalk Slabs & 5 & 3 & 5.0 & 4.6 & 8.4 & 8.2 & 5.1 & 20.7 & 16.3 \\
+\cline{3-12}
+ &  & Tarmac & 5 & 2 & 0.9 & 0.8 & 1.4 & 8.0 & 9.6 & 24.4 & 34.3 \\
+\cline{2-12} \cline{3-12}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 4.1 & 3.7 & 5.8 & 5.8 & 8.0 & 20.3 & 25.9 \\
+\cline{3-12}
+ &  & Paver Bricks & 5 & 2 & 3.0 & 2.4 & 3.9 & 3.4 & 9.7 & 24.0 & 27.8 \\
+\cline{3-12}
+ &  & Sidewalk Pavers & 5 & 2 & 2.6 & 2.3 & 4.1 & 5.5 & 7.3 & 21.2 & 27.8 \\
+\cline{3-12}
+ &  & Sidewalk Slabs & 5 & 3 & 3.1 & 2.9 & 4.7 & 5.4 & 6.9 & 20.1 & 25.6 \\
+\cline{3-12}
+ &  & Tarmac & 5 & 2 & 1.0 & 0.7 & 1.4 & 5.8 & 10.2 & 30.0 & 36.1 \\
+\cline{1-12} \cline{2-12} \cline{3-12}
+\multirow[t]{5}{*}{oldrusty} & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 4.7 & 2.0 & 7.5 & 6.0 & 5.1 & 39.0 & 29.9 \\
+\cline{3-12}
+ &  & Paver Bricks & 5 & 3 & 3.4 & 1.2 & 4.9 & 6.1 & 5.2 & 44.2 & 21.9 \\
+\cline{3-12}
+ &  & Sidewalk Pavers & 5 & 2 & 3.3 & 1.4 & 5.5 & 9.7 & 5.4 & 40.1 & 27.3 \\
+\cline{3-12}
+ &  & Sidewalk Slabs & 5 & 3 & 3.2 & 1.6 & 6.1 & 11.6 & 5.3 & 39.0 & 23.8 \\
+\cline{3-12}
+ &  & Tarmac & 5 & 2 & 1.1 & 0.5 & 1.6 & 5.7 & 7.0 & 42.1 & 22.6 \\
+\cline{1-12} \cline{2-12} \cline{3-12}
+\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 3 & 6.5 & 5.7 & 14.5 & 9.6 & 7.6 & 21.4 & 20.8 \\
+ &  &  & 20 & 1 & 9.2 & 8.5 & 15.9 & 9.9 & 8.0 & 19.8 & 39.1 \\
+ &  &  & 25 & 1 & 11.6 & 8.2 & 30.4 & 13.7 & 6.9 & 38.0 & 38.3 \\
+\cline{3-12}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.3 & 1.2 & 2.4 & 8.3 & 9.3 & 18.5 & 29.0 \\
+ &  &  & 25 & 2 & 2.1 & 1.9 & 2.9 & 5.2 & 9.7 & 18.1 & 21.5 \\
+\cline{2-12} \cline{3-12}
+ & \multirow[t]{5}{*}{maxicosi, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 3.9 & 11.0 & 13.5 & 5.8 & 21.6 & 29.1 \\
+ &  &  & 20 & 1 & 10.8 & 7.4 & 30.2 & 14.7 & 5.0 & 32.4 & 32.1 \\
+ &  &  & 25 & 1 & 10.6 & 7.7 & 29.4 & 14.7 & 6.3 & 31.2 & 30.3 \\
+\cline{3-12}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.1 & 1.0 & 2.0 & 9.6 & 8.8 & 18.3 & 25.3 \\
+ &  &  & 25 & 2 & 1.6 & 1.5 & 2.3 & 4.9 & 9.5 & 18.3 & 21.6 \\
+\cline{2-12} \cline{3-12}
+ & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 4.1 & 7.3 & 8.3 & 7.5 & 18.9 & 24.1 \\
+ &  &  & 20 & 1 & 6.9 & 6.2 & 11.5 & 8.6 & 7.9 & 21.2 & 36.8 \\
+ &  &  & 25 & 1 & 7.6 & 6.8 & 11.9 & 7.2 & 9.2 & 21.1 & 31.7 \\
+\cline{3-12}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 0.9 & 0.9 & 2.0 & 9.3 & 9.4 & 16.7 & 20.4 \\
+ &  &  & 25 & 2 & 1.4 & 1.3 & 2.0 & 5.8 & 9.4 & 16.6 & 23.0 \\
+\cline{1-12} \cline{2-12} \cline{3-12}
+\multirow[t]{10}{*}{yoyo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 4.0 & 5.7 & 4.8 & 6.4 & 16.9 & 21.3 \\
+\cline{3-12}
+ &  & Paver Bricks & 5 & 2 & 3.0 & 2.1 & 4.0 & 4.1 & 9.4 & 41.7 & 29.5 \\
+\cline{3-12}
+ &  & Sidewalk Pavers & 5 & 3 & 2.8 & 2.6 & 4.2 & 5.5 & 6.7 & 18.8 & 22.2 \\
+\cline{3-12}
+ &  & Sidewalk Slabs & 5 & 2 & 4.0 & 3.8 & 6.7 & 6.4 & 5.2 & 19.6 & 25.7 \\
+\cline{3-12}
+ &  & Tarmac & 5 & 2 & 0.9 & 0.6 & 1.4 & 7.4 & 7.7 & 42.9 & 19.5 \\
+\cline{2-12} \cline{3-12}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 5.2 & 4.9 & 7.1 & 4.4 & 7.7 & 17.6 & 21.5 \\
+\cline{3-12}
+ &  & Paver Bricks & 5 & 3 & 3.6 & 3.0 & 4.7 & 3.8 & 10.4 & 25.0 & 22.5 \\
+\cline{3-12}
+ &  & Sidewalk Pavers & 5 & 2 & 3.1 & 2.7 & 5.8 & 9.9 & 8.3 & 23.4 & 28.5 \\
+\cline{3-12}
+ &  & Sidewalk Slabs & 5 & 3 & 4.0 & 3.7 & 6.0 & 6.2 & 5.3 & 19.0 & 23.3 \\
+\cline{3-12}
+ &  & Tarmac & 5 & 2 & 0.7 & 0.4 & 1.0 & 6.3 & 11.1 & 41.7 & 39.1 \\
+\cline{1-12} \cline{2-12} \cline{3-12}
+\bottomrule
+\end{tabular}
+\end{table}
+\egroup
+
+\newpage
+\section{Vehicle Statistical Comparisons}
+\label{app:compare}
+%
+Tukey Range Test multiple comparison plots. Horizontal lines indicate 95\%
+confidence intervals. Non-overlapping confidence intervals indicate a
+significant difference.
+%
+\begin{figure}[!h]
+  \centering
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Cobblestones.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Paver Bricks.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Sidewalk Pavers.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Sidewalk Slabs.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Tarmac.png}}
+  \caption{Tukey Comparison Plots for the Strollers}
+  \label{fig:tukey-stroller}
+\end{figure}
+%
+\begin{figure}[!h]
+  \centering
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Paver Bricks-Low.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-Low.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Paver Bricks-High.png}}
+  \subcaptionbox{}{
+  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-High.png}}
+  \caption{Tukey Comparison Plots for the Cargo Bicycles}
+  \label{fig:tukey-bicycle}
+\end{figure}
+
 \end{document}

### 2025-02-01 src/html_templates.py
Apply basic bootstrap formatting to the website.

@@ -3,7 +3,7 @@ H2 = '<h2>{}</h2>'
 H3 = '<h3>{}</h3>'
 H4 = '<h4>{}</h4>'
 HR = '<hr>'
-IMG = '<img src="fig/{}/{}" width="900px" ></img>'
+IMG = '<img src="fig/{}/{}" class="img-fluid"></img>'
 P = '<p>{}</p>'
 
 INDEX = """\
@@ -11,19 +11,23 @@ INDEX = """\
 <html lang="en">
   <head>
     <meta charset="utf-8">
+    <meta name="viewport" content="width=device-width, initial-scale=1">
     <title>Infant Vehicle Transport Vibration Results</title>
+    <link href="https://cdn.jsdelivr.net/npm/bootstrap@5.3.3/dist/css/bootstrap.min.css" rel="stylesheet" integrity="sha384-QWTKZyjpPEjISv5WaRU9OFeRpok6YctnYmDr5pNlyT2bRjXh0JMhjY6hW+ALEwIH" crossorigin="anonymous">
   </head>
   <body>
 
+  <div class="container">
   <h1>Infant Vehicle Transport Vibration Results</h1>
   <hr>
+  <div class="alert alert-danger" role="alert">
+    <p>Warning: These results are preliminary, do not rely on them until a
+    supporting paper is published.</p>
+  </div>
   <p>
     Last updated: {date}
     <br>
     Generated from Git hash: {githash}
-    <br>
-    <strong style="color:red;">Warning: These results are preliminary, do not
-    rely on them until a supporting paper is published.</strong>
   </p>
   <p>
     This page examines the signal: <strong>{signal}</strong>.
@@ -67,9 +71,9 @@ INDEX = """\
     Plots of the ISO 2631-1 filter weights versus frequency we apply to the
     data.
   </p>
-  <img src='fig/iso-filter-weights-01.png' width="900px"></img>
+  <img src='fig/iso-filter-weights-01.png' class="img-fluid"></img>
   <br>
-  <img src='fig/iso-filter-weights-02.png' width="900px"></img>
+  <img src='fig/iso-filter-weights-02.png' class="img-fluid"></img>
 
   <h1 id="statistics">Statistical Regression Results</h1>
   <hr>
@@ -136,5 +140,7 @@ INDEX = """\
   <hr>
 {sync_html}
 
+  </div>  <!--container-->
[…]

### 2025-02-01 src/website.py

@@ -849,14 +849,23 @@ html_source = INDEX.format(
     bicycle_comp='\n'.join([H4.format(surf + ' ' + speed) + '\n' +
                             tab.summary().as_html() + img
                             for surf, speed, tab, img in bicycle_comp_tables]),
-    mean_table=summary_df.to_html(float_format="%0.2f"),
+    mean_table=summary_df.to_html(float_format="%0.2f",
+                                  sparsify=False,
+                                  justify='center',
+                                  show_dimensions=True,
+                                  classes=['table', 'table-hover',
+                                           'table-sm']),
     sess_html='\n  '.join(html_data['sess_html']),
     spec_html='\n  '.join(html_data['spec_html']),
     trial_html='\n  '.join(html_data['trial_html']),
     shock_html=shock_html,
     srot_html='\n  '.join(html_data['srot_html']),
     sync_html='\n  '.join(html_data['sync_html']),
-    trial_table=complete_stats_df.to_html(),
+    trial_table=complete_stats_df.to_html(
+        float_format="%0.3f",
+        justify='center',
+        show_dimensions=True,
+        classes=['table', 'table-hover', 'table-sm']),
 )
 with open(os.path.join(PATH_TO_REPO, 'index.html'), 'w') as f:
     f.write(html_source)

### 2025-02-07 main.tex
Updated paper to version 4.

@@
 \usepackage{booktabs}  % nice tables
+\usepackage{draftwatermark}  % use [nostamp] to disable
+\usepackage{fancyhdr}
 \usepackage[margin=25mm]{geometry}
@@
 \usepackage{subcaption}  % for subfigures
+
+% fancyhdr settings
+\pagestyle{fancy}
+\fancyhead[L]{Dell'Orto et. al, Vibration Characterisation of Strollers and Cargo Bicycles for Transporting Infants}
+\fancyhead[R]{\thepage}
+
+% watermark settings
+\SetWatermarkColor[gray]{0.92}
+\SetWatermarkText{Non-disclosure}
+\SetWatermarkScale{5}
 
@@
 \title{
+  DRAFT: v4 \\
   Vibration Characterisation of Strollers and\\
@@
 Thomas Valk \and
-Jason K. Moore
+Jason K. Moore~\footnote{corresponding author: j.k.moore@tudelft.nl, +31 (0)15 278 3556}
 }
@@
 %
-This report or its findings may not be shared outside of VeiligheidNL and
-TU~Delft without further review of the methods and findings.
-We also need to carefully consider possible adverse effects of dissemination. In
-particular we need to consider:
-%
-\begin{itemize}
-  \item System manufacturers being negatively affected by publication.
-    Organisations like Consumentenbond typically give manufacturers access to
-    draft test results, and give an opportunity to react. We can do this as
-    well. We may now remove Brand and type information from this report. In a
-    later stage we may test multiple products and then publish a comparison.
-  \item Stimulating car use to transport infants and children. We don't want
-    newspaper/online headlines which are overly alarming, and later turn out to
-    be debatable.
-\end{itemize}
+This draft report is shared by TU Delft and VeiligheidNL with a number of
+societal, industrial and, scientific parties. We aim to submit this to a journal
+at the end of February 2025. Your feedback will be appreciated.
+\\ \\
+This report is shared under NON-DISCLOSURE. If you receive this report you may
+share and discuss it with colleagues but do not distribute it further without
+our permission. Do not place this document anywhere on internet and do not cite
+this version.
+
 \color{black}
-
 \begin{abstract}
@@
 obtained weighted RMS acceleration values based on ISO~2631-1 were several times
-in the range of the highest discomfort (>2~\si{\mps\squared}). 
+in the range of the highest discomfort ($>$2~\si{\mps\squared}). 
 Another research which included also children as test subjects was conducted by
@@
 \begin{description}
-  \item[Maxi-Cosi Street Plus] This stroller comes
-  with a cot configuration (0-3 months) and an infant seat option. It has large wheels, with only a marginal suspension system.
+  \item[Maxi-Cosi Street Plus] This stroller comes with a cot configuration (0-3
+  months) and an infant seat option. It has large wheels, with only a marginal
+  suspension system.
   (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
-  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the
-  market. It has only a marginal suspension system and smaller wheels compared to those of other strollers available on the market.
+  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the market. It
+  has only a marginal suspension system and smaller wheels compared to those of
+  other strollers available on the market.
   (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
   rented for the experiment})
-  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system
-  that makes it an all-terrain stroller according to the manufacturer. It has large puncture-proof tyres and an air-permeable mattress.
+  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system that makes
+  it an all-terrain stroller according to the manufacturer. It has large
+  puncture-proof tyres and an air-permeable mattress.
   (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
@@
   z-axis is aligned with the body spine and x-axis points to the front of the
-  body) and the ground plane. An angle 90~\si{\degree} indicates supine posture,
+  body) and the ground plane. An angle 90~\si{\degree} indicates supine posture (lying horizontally),
   -90~\si{\degree} indicates recumbent posture, and 0~\si{\degree} means erect
@@
 \begin{quote}
-  \textbf{The recommendations in standard ISO~2631-1 have not been based on or validated for: 1)
-  short durations that dominate stroller and cargo bicycle travel, 2) infants,
-  children, or young adults, 3) nor to recumbent or reclined seating postures with the head supported.
-  So our recommendations must be taken with utmost caution, at least until more
-  research is done to improve the standard guidance.}
+  \textbf{The recommendations in standard ISO~2631-1 have not been based on or
+  validated for infants, children, or young adults nor for recumbent or reclined
+  seating postures with the head supported. Additionally, the admissible
+  durations for health are not validated for daily short durations or shorter
+  lifetime accumulation that dominate stroller and cargo bicycle travel with
+  infants. So our recommendations must be taken with caution, at least until
+  more research is done to improve the standard guidance.}
 \end{quote}
@@
     durations when riding over non-tarmac surfaces at these speeds.
-    \item Standard ISO~2631-1 is not based on or validated to characterize
-    health and comfort effects of vibration for infants or children or for short
-    durations or non-erect seating. However, this is the only available standard
-    in the literature assessing health and comfort levels on vibrations, and
-    could be used as benchmark.
+    \item Standard ISO~2631-1 is not validated to characterize health and
+    comfort effects of vibration for infants or children, for short travel
+    durations, for vibration accumulation over only a small number of years, or
+    for non-erect seating. However, this is the only available standard in the
+    literature assessing health and comfort levels on vibrations, and should be
+    used as benchmark.
 \end{enumerate}

### 2025-03-03 main.tex
Version 5.

@@
 \usepackage{booktabs}  % nice tables
-\usepackage{draftwatermark}  % use [nostamp] to disable
+%\usepackage{draftwatermark}  % use [nostamp] to disable
 \usepackage{fancyhdr}
@@
 % watermark settings
-\SetWatermarkColor[gray]{0.92}
-\SetWatermarkText{Non-disclosure}
-\SetWatermarkScale{5}
+%\SetWatermarkColor[gray]{0.92}
+%\SetWatermarkText{Non-disclosure}
+%\SetWatermarkScale{5}
 
@@
 \title{
-  DRAFT: v4 \\
+  DRAFT: v5 \\
   Vibration Characterisation of Strollers and\\
@@
   \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
-  \vspace{2mm}
-  \large{Prepared for VeiligheidNL}
 }
@@
 Thomas Valk \and
-Jason K. Moore~\footnote{corresponding author: j.k.moore@tudelft.nl, +31 (0)15 278 3556}
+Jason K. Moore\footnote{corresponding author: j.k.moore@tudelft.nl, +31 (0)15 278 3556}
 }
@@
 %
-This draft report is shared by TU Delft and VeiligheidNL with a number of
-societal, industrial and, scientific parties. We aim to submit this to a journal
-at the end of February 2025. Your feedback will be appreciated.
-\\ \\
-This report is shared under NON-DISCLOSURE. If you receive this report you may
-share and discuss it with colleagues but do not distribute it further without
-our permission. Do not place this document anywhere on internet and do not cite
-this version.
+This draft report is not yet peer reviewed and is subject to change with
+revisions. These results are preliminary, so we do not recommend relying on them
+until a supporting peer reviewed paper is published.
 
@@
   \caption{Inclination angles of the IMUs ``Seat Head'' and ``Seat Pan'', per
-  each tested configuration. We report the angles defined by the axis of the
-  human body reference system (a reference system connected to the dummy, whose
-  z-axis is aligned with the body spine and x-axis points to the front of the
-  body) and the ground plane. An angle 90~\si{\degree} indicates supine posture (lying horizontally),
-  -90~\si{\degree} indicates recumbent posture, and 0~\si{\degree} means erect
-  posture.}
+  each tested configuration.
+%We report the angles defined by the axis of the human body reference system (a reference system connected to the dummy, whose z-axis is aligned with the body spine and x-axis points to the front of the body) and the ground plane.
+  For the head 0~\si{\degree} means erect posture, and positive angles represent rearward head rotation with 90~\si{\degree} indicating a fully  supine posture (lying horizontally).
+For the seat pan I STILL DONT UNDERSTAND especially the -28 for Melia.}
 \begin{tabular}{lllrrr}
@@
  &  &  & & \multicolumn{2}{c}{Inclination angle [deg]}  \\
-Vehicle Type & Model & Dummy & Baby seat & Seat Head & Seat Pan\\
+Vehicle Type & Model & Dummy & Baby seat (facing direction)& Seat Head & Seat Pan\\
 \midrule
-\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Maxi-Cosi X Joolz & 49
-& -43 \\
- &  & 3 mo & Maxi-Cosi X Joolz & 49 & -43 \\
- &  & 3 mo & Melia & 26 & -28 \\
+\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Maxi-Cosi X Joolz (RF)& 41
+& 2 \\
+ &  & 3 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
+ &  & 3 mo & Melia (FF)& 64 & 2 \\
 \cline{2-6}
- & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz & 49 & -43 \\
- &  & 3 mo & Maxi-Cosi X Joolz & 49 & -43 \\
- &  & 3 mo & Melia & 26 & -28 \\
+ & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
+ &  & 3 mo & Maxi-Cosi X Joolz (RF)& 49 & -43 \\
+ &  & 3 mo & Melia (FF)& 64 & 2 \\
 \cline{1-6} \cline{2-6}
-\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street Plus & 0 mo & Baby cot & 90 & 90\\
+\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street Plus & 0 mo & Baby cot (RF)& 0 & 0\\
 \cline{2-6}
- & Maxi-Cosi Street Plus & 9 mo & Baby seat & 50 & -40 \\
+ & Maxi-Cosi Street Plus & 9 mo & Baby seat (FF)& 40 & 10 \\
 \cline{2-6}
- & Babyzen YOYO 0+ & 0 mo & Baby cot & 78 & 78 \\
+ & Babyzen YOYO 0+ & 0 mo & Baby cot (RF)& 12 & 12 \\
 \cline{2-6}
-& Babyzen YOYO 0+ & 9 mo & Baby seat & 45 & -41 \\
+& Babyzen YOYO 6+ & 9 mo & Baby seat (FF)& 45 & 4 \\
 \cline{2-6}
-& Bugaboo Fox 5 & 0 mo & Baby cot & 90 & 90 \\
+& Bugaboo Fox 5 & 0 mo & Baby cot (RF)& 0 & 0 \\
 \cline{2-6}
- & Bugaboo Fox 5 & 9 mo & Baby seat & 41 & -24\\
+ & Bugaboo Fox 5 & 9 mo & Baby seat (FF) & 49 & 24\\
 \bottomrule
@@
     literature assessing health and comfort levels on vibrations, and should be
-    used as benchmark.
+    used as a benchmark.
 \end{enumerate}
@@
 \setlength\tabcolsep{0.4mm}  % reduces horiztonal padding between columns
-\begin{table}[!h]
+\begin{table}[!ht]
   \centering
@@
 %
-\begin{figure}[!h]
+\begin{figure}[!ht]
   \centering

### 2025-04-01 src/data.py
Store the amplitude vs frequency arrays for each repitition and make a plot comparing vehicles.

@@ -436,6 +436,7 @@ class Trial():
         ==========
         sig_name : string
         duration : float, optional
+            Duration in seconds to integrate over.
 
         Returns
         =======

### 2025-04-01 src/process.py

@@ -183,6 +183,15 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                                     signal, sample_rate, cutoff=cutoff,
                                     smooth=True, iso_weighted=True)
                             max_amp_shock = trial.calc_max_peak(signal)
+                            freq, amp, _, _ = trial.calculate_frequency_spectrum(
+                                signal, sample_rate, cutoff=cutoff,
+                                smooth=True)
+                            # NOTE : The frequency spectrum can be different
+                            # lengths depending on the length of the signal. It
+                            # seems len() = 2047, 4095, 8191 are common. So
+                            # interpolate to make a common length.
+                            freq_new = np.linspace(0.0, 120.0, num=2001)
+                            amp_new = np.interp(freq_new, freq, amp)
 
                             stats_data[signal + '_rms'].append(rms)
                             stats_data[signal + '_rms_iso'].append(rms_iso)
@@ -199,7 +208,8 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                             stats_data['Peak Frequency [Hz]'].append(peak_freq)
                             stats_data['Bandwidth [Hz]'].append(
                                 thresh_freq)
-                            stats_data['Peak Value [m/s/s]'].append(max_amp_shock)
+                            stats_data['Peak Value [m/s/s]'].append(
+                                max_amp_shock)
                             stats_data['Baby Age [mo]'].append(
                                 s.meta_data['baby_age'])
                             stats_data['Baby Mass [kg]'].append(
@@ -214,6 +224,8 @@ def process_sessions(start_num, end_num, signal, sample_rate):
                             stats_data['Vehicle Type'].append(
                                 s.meta_data['vehicle_type'])
                             stats_data['repetition_number'].append(rep_num)
+                            stats_data['Frequency Array'].append(freq_new)
+                            stats_data['Amplitude Array'].append(amp_new)
 
                             fig, ax = plt.subplots(layout='constrained',
                                                    figsize=(8, 2))

### 2025-04-01 src/website.py

@@ -8,6 +8,7 @@ import subprocess
 # external dependencies
 from statsmodels.stats.multicomp import pairwise_tukeyhsd
 import matplotlib.pyplot as plt
+import matplotlib.ticker as ticker
 import numpy as np
 import pandas as pd
 import seaborn as sns
@@ -56,10 +57,6 @@ with open(os.path.join(PATH_TO_DATA_DIR, 'stats-data.pkl'), 'rb') as f:
     stats_data = pickle.load(f)
 
 stats_df = pd.DataFrame(stats_data)
-# NOTE : It may be possible to add duplicate rows when running process.py, so
-# drop duplicates.
-stats_df.drop_duplicates(inplace=True)
-
 
 stats_df['Duration Weight'] = (stats_df['Duration [s]'] /
                                stats_df['Duration [s]'].max())
@@ -244,6 +241,65 @@ for surf in stroller_df['Road Surface'].unique():
     print(comp_tab)
 
 boxp_html = []
+
+
+##################################################
+# Figure: Stroller and Bicycle Spectrum Comparison
+##################################################
+fig, axes = plt.subplots(ncols=2, nrows=2, layout='constrained',
+                         figsize=(MAXWIDTH*MM2INCH, 0.6*MAXWIDTH*MM2INCH))
+tick_spacing = 20
+
+gs = axes[0, 0].get_gridspec()
+# remove axes on left column
+axes[0, 0].remove()
+axes[1, 0].remove()
+# add axis that spans whole left column
+strol_ax = fig.add_subplot(gs[:, 0])
+surf_select = stroller_df['Road Surface'] == 'Sidewalk Pavers'
+freq = stroller_df.loc[50, 'Frequency Array']
+for vehicle in ['bugaboo', 'greenmachine', 'maxicosi', 'oldrusty', 'yoyo']:
+    vehi_select = stroller_df['Vehicle'] == vehicle
+    mean_amp = stroller_df.loc[surf_select & vehi_select,
+                               'Amplitude Array'].mean()
+    strol_ax.plot(freq, mean_amp, label=vehicle)
+strol_ax.xaxis.set_major_locator(ticker.MultipleLocator(tick_spacing))
+strol_ax.set_ylabel('Amplitude [m/s$^2$]')
+strol_ax.set_xlabel('Frequency [Hz]')
+strol_ax.grid(visible=True)
+strol_ax.legend()
[…]

### 2025-04-01 main.tex
Paper updates from overleaf.

@@
 \title{
-  DRAFT: v5 \\
+  DRAFT: v6.dev \\
   Vibration Characterisation of Strollers and\\
@@
 %
-This draft report is not yet peer reviewed and is subject to change with
+This draft report is not yet peer-reviewed and is subject to change with
 revisions. These results are preliminary, so we do not recommend relying on them
-until a supporting peer reviewed paper is published.
+until a supporting peer-reviewed paper is published.
 
@@
 \begin{abstract}
-  Infants are transported in strollers and in baby seats mounted in cargo
+  Infants are transported in strollers and in baby seats mounted on cargo
   bicycles. The infants experience whole-body vibration during the associated
@@
   significantly reduce vibrations, relative to most modern strollers we tested,
-  indicating the need for return of suspension elements. Cargo bicycles ridden
+  indicating the need for a return of suspension elements. Cargo bicycles ridden
   at the maximum electric bicycle speed over paver bricks can cause
@@
 Cycling, one of the active transportation modes, is advantageous for
-health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\) emissions,
-congestion, and air pollution~\cite{Neves2019}. As a result, bicycles are
+health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\) emissions, congestion, and air pollution~\cite{Neves2019}. As a result, bicycles are
 increasingly used as a means to deliver goods to consumers, and also for daily
@@
 Anthropomorphic children shaped sandbag dummies (baby and toddler sizes) were
-used as lumped masses. According to the results, tyre pressure and the number of
+used as lumped masses to represent the child body. According to the results, tyre pressure and the number of
 passengers had no significant effect on vibration magnitude, but road surface
@@
 in the range of the highest discomfort ($>$2~\si{\mps\squared}). 
-Another research which included also children as test subjects was conducted by
+Another research which also included children as test subjects was conducted by
 Okajima~et~al.~\cite{okajima2020dynamic} measuring vibrations that seven
@@
 %We report the angles defined by the axis of the human body reference system (a reference system connected to the dummy, whose z-axis is aligned with the body spine and x-axis points to the front of the body) and the ground plane.
-  For the head 0~\si{\degree} means erect posture, and positive angles represent rearward head rotation with 90~\si{\degree} indicating a fully  supine posture (lying horizontally).
-For the seat pan I STILL DONT UNDERSTAND especially the -28 for Melia.}
+  For the head positive angles represent forward head rotation with 0~\si{\degree} indicating a fully  supine posture (lying horizontally) and 90~\si{\degree} fully erect.
+For the seat pan  0~\si{\degree} is horizontal and positive angles indicate elevated legs, see Figures in Appendix \ref{app:equipment}.
+I STILL DONT UNDERSTAND -43.
+RF is rearward facing and FF is forward facing.}
 \begin{tabular}{lllrrr}
@@
  &  &  & & \multicolumn{2}{c}{Inclination angle [deg]}  \\
-Vehicle Type & Model & Dummy & Baby seat (facing direction)& Seat Head & Seat Pan\\
+Vehicle Type & Model & Dummy & Baby seat (facing direction)& Head & Seat Pan\\
 \midrule
@@
   Maxi-Cosi Street Plus Stroller over the Sidewalk Slabs. Black horizontal lines
-  indicate the \(\pm\)root mean square (RMS) about the mean and grey horizontal
-  lines indicate the \(\pm\)vibration dose value (VDV) about the mean.}
+  indicate the \(\pm\)root mean square (RMS) about the mean. The vibration dose
+  value (VDV) for the printed duration is shown in the bottom left.}
   \label{fig:vert-acc-example}
@@
   vertical line indicates the frequency at the maximum amplitude of the smoothed
-  curve. The blue dashed-dotted vertical line indicates the bandwidth threshold
-  for 80\% of the area under the blue curve.}
+  curve. The black dashed-dotted vertical line indicates the bandwidth threshold
+  for 80\% of the area under the black curve.}
   \label{fig:freq-spectrum}
@@
 \begin{align}
-  \textrm{VDV}_{a_{z}} = \left(\frac{1}{M}\sum_{m=1}^{M} a_{z}^4(t_m)\right)^{1/4}
+  \textrm{VDV}_{a_{z}} = \left[\sum_{m=2}^{M} \frac{1}{2} (a_{z,m}^4 - a_{z,m-1}^4) (t_m -t_{m-1})\right]^{1/4}
   \label{eq:vdv-acc}
@@
   \label{fig:compare-bicycle-speed}
-\end{figure}
-
-\subsection{Effect of Dummy Size}
-%
-Figure~\ref{fig:compare-baby-mass} shows the ISO~2631-1 weighted vertical RMS
-acceleration for each repetition for all vehicles, comparing among dummy sizes.
-There were larger accelerations in the bicycle (high speeds) versus the stroller
-(low speeds), likely mostly attributed to the different testing speeds. When
-comparing the vertical RMS acceleration values between cargo bicycles and
-strollers there are no obvious differences due to baby size, i.e. each dummy
-size experienced a similar range of acceleration magnitudes when vehicle type
-and road surface are ignored. For the bicycles, the lightest dummy sometimes
-experienced higher acceleration than the heavier dummy, but high and low
-accelerations are seen across the speed range tested.
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
-  \caption{Seat pan ISO~2631-1 weighted vertical RMS acceleration grouped by
-  baby age (and thus size \& mass) for all repetitions with colour indicating
-  the mean speed of the trial. The lightest colour dots are strollers and the
-  remaining are cargo bicycles.}
-  \label{fig:compare-baby-mass}
-\end{figure}
-
-\subsection{Effect of Road Surface}
-%
-Figure~\ref{fig:compare-road-surface} shows ISO~2631-1 weighted vertical RMS
-acceleration from repetitions grouped into the various road surfaces tested. All
-vehicles were tested on paver bricks and tarmac but only strollers were tested
-on cobblestones and sidewalk pavers and sidewalk slabs, i.e. light colour dots
-(strollers are present in each column).
-It is notable that tarmac almost always induced lower RMS acceleration than
-other road types regardless of speed and vehicle type.
-The sidewalk slabs and cobblestones have very similar acceleration ranges for
-all strollers.
-Paver bricks and sidewalk pavers seem to have a similar range of RMS
-acceleration for the same 5~\si{\kilo\meter\per\hour} walking speeds.
-Paver bricks cause relatively large accelerations at high travel speeds in the
-cargo bicycles.
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-road-surface-compare.png}
-  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration grouped by
-  road surface with colour indicating the mean speed of the repetition. The
-  lightest colour dots are strollers and the rest are cargo bicycles.}
-  \label{fig:compare-road-surface}
 \end{figure}
@@
   \label{fig:bicycle-type-compare}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-spectra-compare.png}
+  \caption{Mean amplitude spectra of each vehicle.} 
+  \label{fig:spectra-compare}
 \end{figure}
@@
 \end{figure}
-
-\subsection{Shock}
-%
-We identified the maximum peak acceleration values for each trial
-(Equation~\ref{eq:max-acc}), then averaged them across repetitions to obtain the
-results listed in Table~\ref{tab:shock} for different vehicles and
-configurations. There is a significant variation among tests, with the peaks for
-the bicycles sometimes reaching the accelerometer's full scale (\(\pm\)16~g).
-While the seat pan accelerations for the strollers are generally lower than
-those experienced with the bicycles, the configuration (0 or 9 months) may play
-a large role. Among bicycles, the use of Melia baby shell seems to transmit
-lower accelerations compared to Maxi-Cosi, 3 months, for both the Keiler
-tricycle and the Urban Arrow. Strollers with the baby seat configuration for 9
-months show much lower acceleration compared to the baby cot for 0 months
-(Bugaboo and Maxi-Cosi). Surprisingly, the oldest strollers (Old Rusty and Green
-Machine) performed very well during the shock test, resulting in the lowest seat
-pan acceleration among all the tested vehicles.
-Figure~\ref{fig:shock_vehicle_comparison} shows the peaks of the vertical
-acceleration recorded at the seat pan, grouped by different vehicles, for the
-shock test. As noted in Table~\ref{tab:shock}, the old strollers Old Rusty and
-Green Machine show lower acceleration values. We do not clearly distinguish any
-trend with speed for the bicycles (Keiler and Urban Arrow). During the tests
-involving Keiler tricycle and strollers, we cannot exclude that the front wheels
-(left and right) hit the bump at slightly different time instants.   
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-shock-test-compare.png}
-  \caption{Vertical acceleration recorded at the seat pan during the shock test
-  per each trial, grouped by vehicles. The colour indicates the mean speed of
-  the trial. The lighter the colour the lower the speed.}
-  \label{fig:shock_vehicle_comparison}
-\end{figure}
-
-\begin{table}
-  \centering
-  \caption{Mean of the maximum seat pan acceleration across trials in
-  \si{\mps\squared} recorded for shock test, for different vehicles and baby
-  masses.}
-  \label{tab:shock}
-  \footnotesize
-  \begin{tabular}{lllrrrr}
-    \toprule
-     & &  & Target Speed & Trial Count & Max Acceleration \\
-    Vehicle Type & Model & Seat, Baby & [km/h] & & [m/s²] \\
-    \midrule
-    Strollers & Bugaboo & Cot, 0 mo  & 5 & 3 & 146 \\
-              &         & Seat, 9 mo & 5 & 4 & 49 \\
-    \cline{2-6}
-              & Maxi-Cosi & Cot, 0 mo  & 5 & 2 & 131 \\
-              &           & Seat, 9 mo & 5 & 4 & 35 \\
-    \cline{2-6}
-              & Stokke BABYZEN YOYO & Cot, 0 mo  & 5 & 4 & 35 \\
-              &                     & Seat, 9 mo & 5 & 4 & 51 \\
-    \cline{2-6}
-              & Green Machine & Cot, 0 mo & 5 & 4 & 17 \\
-    \cline{2-6}
-              & Old Rusty & Seat, 9 mo & 5 & 4 & 31 \\
-    \cline{1-6}
-    Bicycles & Keiler tricycle & Melia, 3 mo & 5 & 2 & 52 \\
-
-             &               & Melia, 3 mo & 12 & 2 & 85 \\
-
-             &               & Melia, 3 mo & 20 & 2 & 124 \\
-    \cline{2-6}
-             &               & Maxi-Cosi, 0 mo & 5 & 2 & 113 \\
-
-             &               & Maxi-Cosi, 0 mo & 12 & 2 & 140 \\
-
-             &               & Maxi-Cosi, 0 mo & 20 & 2 & 115 \\
-    \cline{2-6}
-             &               & Maxi-Cosi, 3 mo & 5 & 2 & 151 \\
-
-             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160 \\
-
-             &               & Maxi-Cosi, 3 mo & 20 & 2 & 145 \\
-    \cline{2-6}
-             & Urban Arrow & Melia, 3 mo & 5 & 2 & 43 \\
-
-             &               & Melia, 3 mo & 12 & 2 & 43 \\
-
-             &               & Melia, 3 mo & 25 & 2 & 42 \\
-    \cline{2-6}
-             &               & Maxi-Cosi, 0 mo & 5 & 1 & 50 \\
-
-             &               & Maxi-Cosi, 0 mo & 12 & 2 & 63 \\
-
-             &               & Maxi-Cosi, 0 mo & 25 & 2 & 130 \\
-    \cline{2-6}
-             &               & Maxi-Cosi, 3 mo & 5 & 2 & 156 \\
-
-             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160 \\
-
-             &               & Maxi-Cosi, 3 mo & 25 & 2 & 160 \\
-    \bottomrule
-  \end{tabular}
-\end{table}
 
@@
 
-\subsection{Future Work}
-% 
-There are four possible directions for future work: more in-depth analysis of
-the present measurements, more research on vibrations generated by infant
-transport systems, more research on the effects of vibration on infants, and
-development of a benchmark.
-
-\paragraph{Concerning further analysis of the present measurements:}
-%
-We acquired data from four other sensors on the vehicles, each with three
-accelerometer and three gyroscope time histories, for a total of 30 time
-histories of possible interest. This paper provides a look into the experiments
-via four metrics: ISO weighted vertical RMS acceleration, maximum acceleration,
-peak frequency, and bandwidth of the seat pan sensor. The collected data can
-also be used to investigate the transmissibility from sensor to sensor, as well
-as rotational vibration effects. Investigating these further can give a more
-complete picture of the connections to health and comfort. This work also gives
-a benchmark against which new designs can be tested to show reduction in
-vibration.
-
-\paragraph{Concerning more research on vibrations generated by infant transport
-systems:}
-%
-There are products and variables that have not yet been investigated for their
-effect on vibration. For example, running with an infant in a sports stroller is
-not tested. Investigating this is important because we expect that vibrations
-when running may quickly exceed health limits. In addition, recumbent posture in
-sports strollers is estimated to increase the vibration load on the head of the
-infant. It is important to establish the actual vibration load on the head in
-practice.
-
-\paragraph{Concerning more research on the effects of vibration on infants:}
-%
-The frequency weighting of the ISO~2631-1 standard is not designed or validated
-to characterise health and comfort for infants or children, for short durations,
-and for non-erect seating. Research is urgently needed to develop a new standard
-with a more appropriate frequency weighting to improve assessment of the comfort
-and health effects of whole-body vibration of infants and children, also for
-short durations and for non-erect seating. Furthermore, tests with more
-realistic dummies and/or real infants are necessary to investigate how the
-infant itself moves when excited by various vibrations in different postures.
-The results will contribute to the assessment of the transmissibility of
-vibration in children, which is needed to deduce the vibrations transmitted to
-the head.
-
-\paragraph{Concerning the development of a benchmark:}
-%
-At this moment, no requirements are made for the vibrational properties of child
-transport systems in the standards for strollers, cargo bicycles, bicycle seats,
-and car seats. Due to the magnitude of vibrations that can occur during child
-transport, it is imperative to include a requirement to the vibrational
-properties in the standards for these products. At this moment, no new
-requirements can be defined because there is not enough information. With the
-information resulting from more research on infant vibration, a benchmark for
-the vibration properties of infant transportation products needs to be
-developed. This will enable the inclusion of minimal requirements for vibration
-properties in the standards, which would greatly increase the health and comfort
-of the infants who must use these products.
-
 \subsection{Acknowledgement}
@@
 %\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
+
+\section{Exploratory Statistics}
+%
+\subsection{Effect of Dummy Size}
+%
+Figure~\ref{fig:compare-baby-mass} shows the ISO~2631-1 weighted vertical RMS
+acceleration for each repetition for all vehicles, comparing among dummy sizes.
+There were larger accelerations in the bicycle (high speeds) versus the stroller
+(low speeds), likely mostly attributed to the different testing speeds. When
+comparing the vertical RMS acceleration values between cargo bicycles and
+strollers there are no obvious differences due to baby size, i.e. each dummy
+size experienced a similar range of acceleration magnitudes when vehicle type
+and road surface are ignored. For the bicycles, the lightest dummy sometimes
+experienced higher acceleration than the heavier dummy, but high and low
+accelerations are seen across the speed range tested.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-baby-mass-compare.png}
+  \caption{Seat pan ISO~2631-1 weighted vertical RMS acceleration grouped by
+  baby age (and thus size \& mass) for all repetitions with colour indicating
+  the mean speed of the trial. The lightest colour dots are strollers and the
+  remaining are cargo bicycles.}
+  \label{fig:compare-baby-mass}
+\end{figure}
+
+\subsection{Effect of Road Surface}
+%
+Figure~\ref{fig:compare-road-surface} shows ISO~2631-1 weighted vertical RMS
+acceleration from repetitions grouped into the various road surfaces tested. All
+vehicles were tested on paver bricks and tarmac but only strollers were tested
+on cobblestones and sidewalk pavers and sidewalk slabs, i.e. light colour dots
+(strollers are present in each column).
+It is notable that tarmac almost always induced lower RMS acceleration than
+other road types regardless of speed and vehicle type.
+The sidewalk slabs and cobblestones have very similar acceleration ranges for
+all strollers.
+Paver bricks and sidewalk pavers seem to have a similar range of RMS
+acceleration for the same 5~\si{\kilo\meter\per\hour} walking speeds.
+Paver bricks cause relatively large accelerations at high travel speeds in the
+cargo bicycles.
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-road-surface-compare.png}
+  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration grouped by
+  road surface with colour indicating the mean speed of the repetition. The
+  lightest colour dots are strollers and the rest are cargo bicycles.}
+  \label{fig:compare-road-surface}
+\end{figure}
 
@@
 %
-Table~\ref{tab:results} shows the mean over the scenario repetitions unweighted
-and ISO~2631-1 weighted seat pan vertical RMS acceleration, unweighted seat pan
-vertical VDV, crest factor, peak frequency, bandwidth, and duration for all 52
+Table~\ref{tab:summary-stroller} and Table~\ref{tab:summary-bicycle} show mean
+values over the scenario repetitions. They report the unweighted and ISO~2631-1
+weighted seat pan vertical RMS acceleration, weighted seat pan magnitude RMS
+acceleration, unweighted seat pan vertical VDV for the first 10 seconds of the
+reptition, crest factor, peak frequency, bandwidth, and duration for all 67
 combinations of vehicle setup, road surface, and target speed.
-% NOTE : This table is generated automatically from the Python scripts. I manually edit the header rows to fit on the page width. Save the edits between toprule and midrule!
+% NOTE : These tables are generated automatically from the Python scripts. I manually edit the header rows to fit on the page width. Save the edits between toprule and midrule!
 \bgroup
@@
   \centering
-  \caption{Mean computed metrics for all 52 non-shock scenarios, using seat pan
-  vertical accelerations.}
-  \label{tab:results}
+  \caption{Mean computed metrics of the strollers for all 40 non-shock
+  scenarios, using seat pan acceleration.}
+  \label{tab:summary-stroller}
   \scriptsize
-\begin{tabular}{lllccccccccc}
+\begin{tabular}{lllcccccccccc}
 \toprule
-        &            &         & Target & Trial     & RMS     & ISO Weighted & VDV      & Crest  & Peak      & \\
-        &            & Road    & Speed  & Count     & Accel   & RMS Accel    & Accel    & Factor & Freq. & Bandwidth  & Duration \\
-Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\
+        &            &         &        & .     &     & ISO      & ISO      &     &        &      &       &       \\
+        &            &         & Target & Rep.  & RMS & Weighted & Weighted & VDV & Crest  & Peak & Band- & Dur-  \\
+        &            & Road    & Speed  & Count & Acc & RMS Acc  & RMS Mag  & Acc & Factor & Freq & width & ation \\
+Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\meter\second}\(^{-1.75}\)] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\
 \midrule
-\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.4 & 4.3 & 6.6 & 6.2 & 6.5 & 14.3 & 20.4 \\
-\cline{3-12}
- &  & Paver Bricks & 5 & 3 & 2.6 & 2.4 & 3.4 & 4.1 & 9.5 & 17.2 & 23.3 \\
-\cline{3-12}
- &  & Sidewalk Pavers & 5 & 2 & 2.9 & 2.7 & 7.5 & 13.5 & 6.1 & 18.5 & 25.4 \\
-\cline{3-12}
- &  & Sidewalk Slabs & 5 & 3 & 4.8 & 4.7 & 7.9 & 6.4 & 5.8 & 15.1 & 20.2 \\
-\cline{3-12}
- &  & Tarmac & 5 & 2 & 0.7 & 0.6 & 0.9 & 3.3 & 10.1 & 18.5 & 23.1 \\
-\cline{2-12} \cline{3-12}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 4 & 2.5 & 2.3 & 3.4 & 4.7 & 6.6 & 20.7 & 22.5 \\
-\cline{3-12}
- &  & Paver Bricks & 5 & 3 & 2.3 & 1.8 & 3.0 & 3.8 & 9.4 & 26.4 & 22.6 \\
-\cline{3-12}
- &  & Sidewalk Pavers & 5 & 3 & 1.7 & 1.4 & 2.5 & 5.5 & 7.7 & 23.8 & 24.7 \\
-\cline{3-12}
- &  & Sidewalk Slabs & 5 & 3 & 2.4 & 2.2 & 3.6 & 5.3 & 6.0 & 20.3 & 24.5 \\
-\cline{3-12}
- &  & Tarmac & 5 & 2 & 0.6 & 0.4 & 0.8 & 6.5 & 8.4 & 29.3 & 34.6 \\
-\cline{1-12} \cline{2-12} \cline{3-12}
-\multirow[t]{5}{*}{greenmachine} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 3.2 & 2.9 & 4.6 & 5.3 & 4.1 & 17.3 & 23.7 \\
-\cline{3-12}
- &  & Paver Bricks & 5 & 2 & 1.6 & 1.3 & 2.1 & 4.5 & 4.2 & 26.8 & 29.6 \\
-\cline{3-12}
- &  & Sidewalk Pavers & 5 & 2 & 2.7 & 2.5 & 4.2 & 6.5 & 4.1 & 18.5 & 28.2 \\
-\cline{3-12}
- &  & Sidewalk Slabs & 5 & 3 & 3.5 & 3.2 & 5.5 & 6.7 & 3.9 & 16.8 & 23.9 \\
-\cline{3-12}
- &  & Tarmac & 5 & 2 & 0.5 & 0.4 & 0.6 & 4.1 & 4.2 & 33.4 & 22.1 \\
-\cline{1-12} \cline{2-12} \cline{3-12}
-\multirow[t]{12}{*}{keiler} & \multirow[t]{4}{*}{maxicosi, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 7.0 & 6.9 & 11.2 & 7.2 & 7.6 & 16.7 & 23.8 \\
- &  &  & 20 & 1 & 12.6 & 10.7 & 27.1 & 9.9 & 6.8 & 26.9 & 34.0 \\
-\cline{3-12}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 1.8 & 1.8 & 3.3 & 8.3 & 8.1 & 13.3 & 24.6 \\
- &  &  & 20 & 2 & 2.8 & 2.8 & 3.9 & 5.1 & 7.8 & 13.2 & 29.2 \\
-\cline{2-12} \cline{3-12}
- & \multirow[t]{4}{*}{maxicosi, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 6.3 & 5.7 & 12.3 & 11.0 & 8.0 & 21.9 & 28.9 \\
- &  &  & 20 & 2 & 9.8 & 7.8 & 23.5 & 14.4 & 7.2 & 30.7 & 21.4 \\
-\cline{3-12}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.5 & 1.5 & 2.6 & 8.1 & 7.6 & 12.8 & 27.8 \\
- &  &  & 20 & 2 & 2.1 & 2.1 & 2.8 & 3.9 & 6.4 & 12.7 & 23.8 \\
-\cline{2-12} \cline{3-12}
- & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 5.4 & 4.9 & 8.9 & 8.1 & 7.9 & 21.9 & 26.3 \\
- &  &  & 20 & 2 & 9.5 & 6.7 & 19.7 & 10.2 & 6.8 & 34.8 & 23.0 \\
-\cline{3-12}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.2 & 1.2 & 2.1 & 8.2 & 7.8 & 14.2 & 25.4 \\
- &  &  & 20 & 2 & 1.6 & 1.5 & 2.1 & 3.8 & 8.3 & 13.8 & 22.6 \\
-\cline{1-12} \cline{2-12} \cline{3-12}
-\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.6 & 4.4 & 6.4 & 4.9 & 8.1 & 18.3 & 20.7 \\
-\cline{3-12}
- &  & Paver Bricks & 5 & 2 & 3.2 & 2.8 & 4.2 & 3.9 & 10.4 & 21.1 & 27.2 \\
-\cline{3-12}
- &  & Sidewalk Pavers & 5 & 3 & 3.0 & 2.9 & 4.5 & 5.5 & 7.6 & 18.1 & 21.4 \\
-\cline{3-12}
- &  & Sidewalk Slabs & 5 & 3 & 5.0 & 4.6 & 8.4 & 8.2 & 5.1 & 20.7 & 16.3 \\
-\cline{3-12}
- &  & Tarmac & 5 & 2 & 0.9 & 0.8 & 1.4 & 8.0 & 9.6 & 24.4 & 34.3 \\
-\cline{2-12} \cline{3-12}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 4.1 & 3.7 & 5.8 & 5.8 & 8.0 & 20.3 & 25.9 \\
-\cline{3-12}
- &  & Paver Bricks & 5 & 2 & 3.0 & 2.4 & 3.9 & 3.4 & 9.7 & 24.0 & 27.8 \\
-\cline{3-12}
- &  & Sidewalk Pavers & 5 & 2 & 2.6 & 2.3 & 4.1 & 5.5 & 7.3 & 21.2 & 27.8 \\
-\cline{3-12}
- &  & Sidewalk Slabs & 5 & 3 & 3.1 & 2.9 & 4.7 & 5.4 & 6.9 & 20.1 & 25.6 \\
-\cline{3-12}
- &  & Tarmac & 5 & 2 & 1.0 & 0.7 & 1.4 & 5.8 & 10.2 & 30.0 & 36.1 \\
-\cline{1-12} \cline{2-12} \cline{3-12}
-\multirow[t]{5}{*}{oldrusty} & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 4.7 & 2.0 & 7.5 & 6.0 & 5.1 & 39.0 & 29.9 \\
-\cline{3-12}
- &  & Paver Bricks & 5 & 3 & 3.4 & 1.2 & 4.9 & 6.1 & 5.2 & 44.2 & 21.9 \\
-\cline{3-12}
- &  & Sidewalk Pavers & 5 & 2 & 3.3 & 1.4 & 5.5 & 9.7 & 5.4 & 40.1 & 27.3 \\
-\cline{3-12}
- &  & Sidewalk Slabs & 5 & 3 & 3.2 & 1.6 & 6.1 & 11.6 & 5.3 & 39.0 & 23.8 \\
-\cline{3-12}
- &  & Tarmac & 5 & 2 & 1.1 & 0.5 & 1.6 & 5.7 & 7.0 & 42.1 & 22.6 \\
-\cline{1-12} \cline{2-12} \cline{3-12}
-\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 3 & 6.5 & 5.7 & 14.5 & 9.6 & 7.6 & 21.4 & 20.8 \\
- &  &  & 20 & 1 & 9.2 & 8.5 & 15.9 & 9.9 & 8.0 & 19.8 & 39.1 \\
- &  &  & 25 & 1 & 11.6 & 8.2 & 30.4 & 13.7 & 6.9 & 38.0 & 38.3 \\
-\cline{3-12}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.3 & 1.2 & 2.4 & 8.3 & 9.3 & 18.5 & 29.0 \\
- &  &  & 25 & 2 & 2.1 & 1.9 & 2.9 & 5.2 & 9.7 & 18.1 & 21.5 \\
-\cline{2-12} \cline{3-12}
- & \multirow[t]{5}{*}{maxicosi, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 3.9 & 11.0 & 13.5 & 5.8 & 21.6 & 29.1 \\
- &  &  & 20 & 1 & 10.8 & 7.4 & 30.2 & 14.7 & 5.0 & 32.4 & 32.1 \\
- &  &  & 25 & 1 & 10.6 & 7.7 & 29.4 & 14.7 & 6.3 & 31.2 & 30.3 \\
-\cline{3-12}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.1 & 1.0 & 2.0 & 9.6 & 8.8 & 18.3 & 25.3 \\
- &  &  & 25 & 2 & 1.6 & 1.5 & 2.3 & 4.9 & 9.5 & 18.3 & 21.6 \\
-\cline{2-12} \cline{3-12}
- & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 4.1 & 7.3 & 8.3 & 7.5 & 18.9 & 24.1 \\
- &  &  & 20 & 1 & 6.9 & 6.2 & 11.5 & 8.6 & 7.9 & 21.2 & 36.8 \\
- &  &  & 25 & 1 & 7.6 & 6.8 & 11.9 & 7.2 & 9.2 & 21.1 & 31.7 \\
-\cline{3-12}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 0.9 & 0.9 & 2.0 & 9.3 & 9.4 & 16.7 & 20.4 \\
- &  &  & 25 & 2 & 1.4 & 1.3 & 2.0 & 5.8 & 9.4 & 16.6 & 23.0 \\
-\cline{1-12} \cline{2-12} \cline{3-12}
-\multirow[t]{10}{*}{yoyo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 4.0 & 5.7 & 4.8 & 6.4 & 16.9 & 21.3 \\
-\cline{3-12}
- &  & Paver Bricks & 5 & 2 & 3.0 & 2.1 & 4.0 & 4.1 & 9.4 & 41.7 & 29.5 \\
-\cline{3-12}
- &  & Sidewalk Pavers & 5 & 3 & 2.8 & 2.6 & 4.2 & 5.5 & 6.7 & 18.8 & 22.2 \\
-\cline{3-12}
- &  & Sidewalk Slabs & 5 & 2 & 4.0 & 3.8 & 6.7 & 6.4 & 5.2 & 19.6 & 25.7 \\
-\cline{3-12}
- &  & Tarmac & 5 & 2 & 0.9 & 0.6 & 1.4 & 7.4 & 7.7 & 42.9 & 19.5 \\
-\cline{2-12} \cline{3-12}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 5.2 & 4.9 & 7.1 & 4.4 & 7.7 & 17.6 & 21.5 \\
-\cline{3-12}
- &  & Paver Bricks & 5 & 3 & 3.6 & 3.0 & 4.7 & 3.8 & 10.4 & 25.0 & 22.5 \\
-\cline{3-12}
- &  & Sidewalk Pavers & 5 & 2 & 3.1 & 2.7 & 5.8 & 9.9 & 8.3 & 23.4 & 28.5 \\
-\cline{3-12}
- &  & Sidewalk Slabs & 5 & 3 & 4.0 & 3.7 & 6.0 & 6.2 & 5.3 & 19.0 & 23.3 \\
-\cline{3-12}
- &  & Tarmac & 5 & 2 & 0.7 & 0.4 & 1.0 & 6.3 & 11.1 & 41.7 & 39.1 \\
-\cline{1-12} \cline{2-12} \cline{3-12}
+\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.4 & 4.3 & 4.5 & 11.5 & 6.2 & 6.5 & 20.5 & 20.4 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 3 & 2.6 & 2.4 & 2.5 & 6.1 & 4.1 & 9.5 & 23.4 & 23.3 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 2.9 & 2.7 & 2.9 & 15.6 & 13.5 & 6.1 & 49.8 & 25.4 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 4.8 & 4.7 & 4.8 & 12.5 & 6.4 & 5.8 & 30.6 & 20.2 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.7 & 0.6 & 0.7 & 1.7 & 3.3 & 10.1 & 33.3 & 23.1 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 4 & 2.5 & 2.3 & 2.5 & 6.2 & 4.7 & 6.6 & 37.9 & 22.5 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 3 & 2.3 & 1.8 & 1.8 & 5.2 & 3.8 & 9.4 & 43.2 & 22.6 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 3 & 1.7 & 1.4 & 1.6 & 4.5 & 5.5 & 7.7 & 39.5 & 24.7 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 2.4 & 2.2 & 2.3 & 5.9 & 5.3 & 6.0 & 36.6 & 24.5 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.6 & 0.4 & 0.5 & 1.6 & 6.5 & 8.4 & 51.2 & 34.6 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{5}{*}{greenmachine} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 3.2 & 2.9 & 3.4 & 7.2 & 5.3 & 4.1 & 38.1 & 23.7 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 2 & 1.6 & 1.3 & 1.6 & 3.2 & 4.5 & 4.2 & 47.4 & 29.6 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 2.7 & 2.5 & 2.9 & 7.4 & 6.5 & 4.1 & 41.3 & 28.2 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 3.5 & 3.2 & 3.4 & 7.6 & 6.7 & 3.9 & 36.0 & 23.9 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.5 & 0.4 & 0.7 & 1.1 & 4.1 & 4.2 & 52.5 & 22.1 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.6 & 4.4 & 4.5 & 11.3 & 4.9 & 8.1 & 51.2 & 20.7 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 2 & 3.2 & 2.8 & 2.9 & 7.5 & 3.9 & 10.4 & 53.6 & 27.2 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 3 & 3.0 & 2.9 & 3.0 & 8.3 & 5.5 & 7.6 & 40.1 & 21.4 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 5.0 & 4.6 & 4.7 & 13.8 & 8.2 & 5.1 & 70.3 & 16.3 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.9 & 0.8 & 0.8 & 2.1 & 8.0 & 9.6 & 43.4 & 34.3 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 4.1 & 3.7 & 3.8 & 10.4 & 5.8 & 8.0 & 46.9 & 25.9 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 2 & 3.0 & 2.4 & 2.4 & 6.9 & 3.4 & 9.7 & 57.4 & 27.8 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 2.6 & 2.3 & 2.5 & 7.2 & 5.5 & 7.3 & 47.2 & 27.8 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 3.1 & 2.9 & 3.0 & 7.8 & 5.4 & 6.9 & 51.4 & 25.6 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 1.0 & 0.7 & 0.8 & 2.6 & 5.8 & 10.2 & 55.5 & 36.1 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{5}{*}{oldrusty} & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 4.7 & 2.0 & 2.3 & 13.0 & 6.0 & 5.1 & 105.1 & 29.9 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 3 & 3.4 & 1.2 & 1.4 & 8.7 & 6.1 & 5.2 & 106.1 & 21.9 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 3.3 & 1.4 & 1.7 & 9.7 & 9.7 & 5.4 & 104.2 & 27.3 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 3.2 & 1.6 & 1.7 & 10.5 & 11.6 & 5.3 & 103.9 & 23.8 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 1.1 & 0.5 & 0.6 & 2.7 & 5.7 & 7.0 & 105.5 & 22.6 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{10}{*}{yoyo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 4.0 & 4.1 & 10.5 & 4.8 & 6.4 & 66.3 & 21.3 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 2 & 3.0 & 2.1 & 2.2 & 6.9 & 4.1 & 9.4 & 97.7 & 29.5 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 3 & 2.8 & 2.6 & 2.7 & 7.0 & 5.5 & 6.7 & 69.9 & 22.2 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 2 & 4.0 & 3.8 & 3.9 & 11.6 & 6.4 & 5.2 & 79.1 & 25.7 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.9 & 0.6 & 0.6 & 2.8 & 7.4 & 7.7 & 89.3 & 19.5 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 5.2 & 4.9 & 5.0 & 12.4 & 4.4 & 7.7 & 69.1 & 21.5 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 3 & 3.6 & 3.0 & 3.0 & 8.2 & 3.8 & 10.4 & 93.4 & 22.5 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 3.1 & 2.7 & 2.8 & 11.9 & 9.9 & 8.3 & 78.3 & 28.5 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 4.0 & 3.7 & 3.8 & 9.7 & 6.2 & 5.3 & 69.7 & 23.3 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.7 & 0.4 & 0.5 & 1.9 & 6.3 & 11.1 & 95.6 & 39.1 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\bottomrule
+\end{tabular}
+\end{table}
+\egroup
+
+\bgroup
+\setlength\tabcolsep{0.4mm}  % reduces horiztonal padding between columns
+\begin{table}[!ht]
+  \centering
+  \caption{Mean computed metrics of the cargo bicycles for all 27 non-shock scenarios, using seat pan
+  acceleration.}
+  \label{tab:summary-bicycle}
+  \scriptsize
+\begin{tabular}{lllcccccccccc}
+\toprule
+        &            &         &        & .     &     & ISO      & ISO      &     &        &      &       &       \\
+        &            &         & Target & Rep.  & RMS & Weighted & Weighted & VDV & Crest  & Peak & Band- & Dur-  \\
+        &            & Road    & Speed  & Count & Acc & RMS Acc  & RMS Mag  & Acc & Factor & Freq & width & ation \\
+Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\meter\second}\(^{-1.75}\)] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\
+\midrule
+\multirow[t]{12}{*}{keiler} & \multirow[t]{4}{*}{maxicosi, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 7.0 & 6.9 & 7.1 & 15.7 & 7.2 & 7.6 & 36.6 & 23.8 \\
+ &  &  & 20 & 1 & 12.6 & 10.7 & 10.9 & 26.6 & 9.9 & 6.8 & 74.8 & 34.0 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 1.8 & 1.8 & 1.9 & 6.4 & 8.3 & 8.1 & 18.7 & 24.6 \\
+ &  &  & 20 & 2 & 2.8 & 2.8 & 2.8 & 6.7 & 5.1 & 7.8 & 16.7 & 29.2 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{4}{*}{maxicosi, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 6.3 & 5.7 & 5.9 & 14.7 & 11.0 & 8.0 & 47.5 & 28.9 \\
+ &  &  & 20 & 2 & 9.8 & 7.8 & 8.0 & 28.7 & 14.4 & 7.2 & 68.3 & 21.4 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.5 & 1.5 & 1.6 & 4.9 & 8.1 & 7.6 & 18.5 & 27.8 \\
+ &  &  & 20 & 2 & 2.1 & 2.1 & 2.2 & 5.1 & 3.9 & 6.4 & 16.0 & 23.8 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 5.4 & 4.9 & 5.0 & 12.9 & 8.1 & 7.9 & 62.5 & 26.3 \\
+ &  &  & 20 & 2 & 9.5 & 6.7 & 6.9 & 31.9 & 10.2 & 6.8 & 82.6 & 23.0 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.2 & 1.2 & 1.3 & 2.7 & 8.2 & 7.8 & 41.6 & 25.4 \\
+ &  &  & 20 & 2 & 1.6 & 1.5 & 1.6 & 3.6 & 3.8 & 8.3 & 28.9 & 22.6 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 3 & 6.5 & 5.7 & 5.7 & 26.1 & 9.6 & 7.6 & 58.5 & 20.8 \\
+ &  &  & 20 & 1 & 9.2 & 8.5 & 8.6 & 15.5 & 9.9 & 8.0 & 53.1 & 39.1 \\
+ &  &  & 25 & 1 & 11.6 & 8.2 & 8.3 & 31.8 & 13.7 & 6.9 & 85.0 & 38.3 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.3 & 1.2 & 1.2 & 4.8 & 8.3 & 9.3 & 24.8 & 29.0 \\
+ &  &  & 25 & 2 & 2.1 & 1.9 & 1.9 & 4.7 & 5.2 & 9.7 & 24.6 & 21.5 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{maxicosi, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 3.9 & 3.9 & 11.5 & 13.5 & 5.8 & 46.0 & 29.1 \\
+ &  &  & 20 & 1 & 10.8 & 7.4 & 7.5 & 15.2 & 14.7 & 5.0 & 71.9 & 32.1 \\
+ &  &  & 25 & 1 & 10.6 & 7.7 & 7.8 & 36.3 & 14.7 & 6.3 & 71.0 & 30.3 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.1 & 1.0 & 1.0 & 3.8 & 9.6 & 8.8 & 28.3 & 25.3 \\
+ &  &  & 25 & 2 & 1.6 & 1.5 & 1.5 & 3.8 & 4.9 & 9.5 & 25.4 & 21.6 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 4.1 & 4.1 & 12.0 & 8.3 & 7.5 & 31.9 & 24.1 \\
+ &  &  & 20 & 1 & 6.9 & 6.2 & 6.3 & 15.2 & 8.6 & 7.9 & 40.1 & 36.8 \\
+ &  &  & 25 & 1 & 7.6 & 6.8 & 6.8 & 15.1 & 7.2 & 9.2 & 47.7 & 31.7 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 0.9 & 0.9 & 0.9 & 3.6 & 9.3 & 9.4 & 33.2 & 20.4 \\
+ &  &  & 25 & 2 & 1.4 & 1.3 & 1.3 & 3.4 & 5.8 & 9.4 & 27.8 & 23.0 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
 \bottomrule
@@
 
+\newpage
+\section{Shock tests}
+\label{app:shock}
+
+We identified the maximum peak acceleration values for each trial
+(Equation~\ref{eq:max-acc}), then averaged them across repetitions to obtain the
+results listed in Table~\ref{tab:shock} for different vehicles and
+configurations. There is a significant variation among tests, with the peaks for
+the bicycles sometimes reaching the accelerometer's full scale (\(\pm\)16~g).
+While the seat pan accelerations for the strollers are generally lower than
+those experienced with the bicycles, the configuration (0 or 9 months) may play
+a large role. Among bicycles, the use of Melia baby shell seems to transmit
+lower accelerations compared to Maxi-Cosi, 3 months, for both the Keiler
+tricycle and the Urban Arrow. Strollers with the baby seat configuration for 9
+months show much lower acceleration compared to the baby cot for 0 months
+(Bugaboo and Maxi-Cosi). Surprisingly, the oldest strollers (Old Rusty and Green
+Machine) performed very well during the shock test, resulting in the lowest seat
+pan acceleration among all the tested vehicles.
+Figure~\ref{fig:shock_vehicle_comparison} shows the peaks of the vertical
+acceleration recorded at the seat pan, grouped by different vehicles, for the
+shock test. As noted in Table~\ref{tab:shock}, the old strollers Old Rusty and
+Green Machine show lower acceleration values. We do not clearly distinguish any
+trend with speed for the bicycles (Keiler and Urban Arrow). During the tests
+involving Keiler tricycle and strollers, we cannot exclude that the front wheels
+(left and right) hit the bump at slightly different time instants.   
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-shock-test-compare.png}
+  \caption{Vertical acceleration recorded at the seat pan during the shock test
+  per each trial, grouped by vehicles. The colour indicates the mean speed of
+  the trial. The lighter the colour the lower the speed.}
+  \label{fig:shock_vehicle_comparison}
+\end{figure}
+
+\begin{table}
+  \centering
+  \caption{Mean of the maximum seat pan acceleration across trials in
+  \si{\mps\squared} recorded for shock test, for different vehicles and baby
+  masses.}
+  \label{tab:shock}
+  \footnotesize
+  \begin{tabular}{lllrrrr}
+    \toprule
+     & &  & Target Speed & Trial Count & Max Acceleration \\
+    Vehicle Type & Model & Seat, Baby & [km/h] & & [m/s²] \\
+    \midrule
+    Strollers & Bugaboo & Cot, 0 mo  & 5 & 3 & 146 \\
+              &         & Seat, 9 mo & 5 & 4 & 49 \\
+    \cline{2-6}
+              & Maxi-Cosi & Cot, 0 mo  & 5 & 2 & 131 \\
+              &           & Seat, 9 mo & 5 & 4 & 35 \\
+    \cline{2-6}
+              & Stokke BABYZEN YOYO & Cot, 0 mo  & 5 & 4 & 35 \\
+              &                     & Seat, 9 mo & 5 & 4 & 51 \\
+    \cline{2-6}
+              & Green Machine & Cot, 0 mo & 5 & 4 & 17 \\
+    \cline{2-6}
+              & Old Rusty & Seat, 9 mo & 5 & 4 & 31 \\
+    \cline{1-6}
+    Bicycles & Keiler tricycle & Melia, 3 mo & 5 & 2 & 52 \\
+
+             &               & Melia, 3 mo & 12 & 2 & 85 \\
+
+             &               & Melia, 3 mo & 20 & 2 & 124 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 0 mo & 5 & 2 & 113 \\
+
+             &               & Maxi-Cosi, 0 mo & 12 & 2 & 140 \\
+
+             &               & Maxi-Cosi, 0 mo & 20 & 2 & 115 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 3 mo & 5 & 2 & 151 \\
+
+             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160 \\
+
+             &               & Maxi-Cosi, 3 mo & 20 & 2 & 145 \\
+    \cline{2-6}
+             & Urban Arrow & Melia, 3 mo & 5 & 2 & 43 \\
+
+             &               & Melia, 3 mo & 12 & 2 & 43 \\
+
+             &               & Melia, 3 mo & 25 & 2 & 42 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 0 mo & 5 & 1 & 50 \\
+
+             &               & Maxi-Cosi, 0 mo & 12 & 2 & 63 \\
+
+             &               & Maxi-Cosi, 0 mo & 25 & 2 & 130 \\
+    \cline{2-6}
+             &               & Maxi-Cosi, 3 mo & 5 & 2 & 156 \\
+
+             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160 \\
+
+             &               & Maxi-Cosi, 3 mo & 25 & 2 & 160 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\subsection{Future Work}
+% 
+There are four possible directions for future work: more in-depth analysis of
+the present measurements, more research on vibrations generated by infant
+transport systems, more research on the effects of vibration on infants, and
+development of a benchmark.
+
+\paragraph{Concerning further analysis of the present measurements:}
+%
+We acquired data from four other sensors on the vehicles, each with three
+accelerometer and three gyroscope time histories, for a total of 30 time
+histories of possible interest. This paper provides a look into the experiments
+via four metrics: ISO weighted vertical RMS acceleration, maximum acceleration,
+peak frequency, and bandwidth of the seat pan sensor. The collected data can
+also be used to investigate the transmissibility from sensor to sensor, as well
+as rotational vibration effects. Investigating these further can give a more
+complete picture of the connections to health and comfort. This work also gives
+a benchmark against which new designs can be tested to show reduction in
+vibration.
+
+\paragraph{Concerning more research on vibrations generated by infant transport
+systems:}
+%
+There are products and variables that have not yet been investigated for their
+effect on vibration. For example, running with an infant in a sports stroller is
+not tested. Investigating this is important because we expect that vibrations
+when running may quickly exceed health limits. In addition, recumbent posture in
+sports strollers is estimated to increase the vibration load on the head of the
+infant. It is important to establish the actual vibration load on the head in
+practice.
+
+\paragraph{Concerning more research on the effects of vibration on infants:}
+%
+The frequency weighting of the ISO~2631-1 standard is not designed or validated
+to characterise health and comfort for infants or children, for short durations,
+and for non-erect seating. Research is urgently needed to develop a new standard
+with a more appropriate frequency weighting to improve assessment of the comfort
+and health effects of whole-body vibration of infants and children, also for
+short durations and for non-erect seating. Furthermore, tests with more
+realistic dummies and/or real infants are necessary to investigate how the
+infant itself moves when excited by various vibrations in different postures.
+The results will contribute to the assessment of the transmissibility of
+vibration in children, which is needed to deduce the vibrations transmitted to
+the head.
+
+\paragraph{Concerning the development of a benchmark:}
+%
+At this moment, no requirements are made for the vibrational properties of child
+transport systems in the standards for strollers, cargo bicycles, bicycle seats,
+and car seats. Due to the magnitude of vibrations that can occur during child
+transport, it is imperative to include a requirement to the vibrational
+properties in the standards for these products. At this moment, no new
+requirements can be defined because there is not enough information. With the
+information resulting from more research on infant vibration, a benchmark for
+the vibration properties of infant transportation products needs to be
+developed. This will enable the inclusion of minimal requirements for vibration
+properties in the standards, which would greatly increase the health and comfort
+of the infants who must use these products.
+
 \end{document}

### 2025-04-03 src/website.py
Clean up the code Gabriele added to deal with the shock data frame.

@@ -89,15 +89,16 @@ stats_df['Seat, Baby'] = (
 
 stats_df['Mean Speed [km/h]'] = stats_df['Mean Speed [m/s]']*3.6
 
-# store the original order of stats_df before removing shock
-stats_df['original_order'] = np.arange(len(stats_df))
-
-# drop shock from overall analysis (for now)
+# separate in to vibration and shock sets and vibration into bicycle and
+# stroller sets
+vibr_df = stats_df[stats_df['Road Surface'] != 'Shock']
 shock_df = stats_df[stats_df['Road Surface'] == 'Shock']
-stats_df = stats_df.loc[stats_df['Road Surface'] != 'Shock', :]
+bicycle_df = vibr_df[vibr_df['Vehicle Type'] == 'bicycle']
+stroller_df = vibr_df[vibr_df['Vehicle Type'] == 'stroller']
 
-bicycle_df = stats_df[stats_df['Vehicle Type'] == 'bicycle']
-stroller_df = stats_df[stats_df['Vehicle Type'] == 'stroller']
+# these aren't needed in this data frame and just cause printing issues
+del stats_df['Frequency Array']
+del stats_df['Amplitude Array']
 
 ################
 # Data Summaries
@@ -111,8 +112,8 @@ print(stats_df)
 
 groups = ['Vehicle', 'Seat, Baby', 'Road Surface', 'Target Speed [km/h]']
 # weight means by duration
-weighted_mean_df = stats_df.groupby(groups)[SIGNAL_RMS].agg(
-    lambda x: np.average(x, weights=stats_df.loc[x.index, "Duration Weight"]))
+weighted_mean_df = vibr_df.groupby(groups)[SIGNAL_RMS].agg(
+    lambda x: np.average(x, weights=vibr_df.loc[x.index, "Duration Weight"]))
 
 
 def create_summary_data_frame(df):
@@ -136,7 +137,7 @@ def create_summary_data_frame(df):
     return summary_df
 
 
-summary_df = create_summary_data_frame(stats_df)
+summary_df = create_summary_data_frame(vibr_df)
 print_header("Means Per Scenario")
 print(summary_df)
 with open(os.path.join(PATH_TO_TABLE_DIR, 'summary-data-frame.tex'), 'w') as f:
@@ -158,7 +159,7 @@ with open(os.path.join(PATH_TO_TABLE_DIR,
 
 # Table that shows how many trials and the mean duration
[…]

### 2025-04-03 src/website.py
Fix the matplotlib userwarnings about xticks and frac.

@@ -91,10 +91,10 @@ stats_df['Mean Speed [km/h]'] = stats_df['Mean Speed [m/s]']*3.6
 
 # separate in to vibration and shock sets and vibration into bicycle and
 # stroller sets
-vibr_df = stats_df[stats_df['Road Surface'] != 'Shock']
-shock_df = stats_df[stats_df['Road Surface'] == 'Shock']
-bicycle_df = vibr_df[vibr_df['Vehicle Type'] == 'bicycle']
-stroller_df = vibr_df[vibr_df['Vehicle Type'] == 'stroller']
+vibr_df = stats_df[stats_df['Road Surface'] != 'Shock'].copy()
+shock_df = stats_df[stats_df['Road Surface'] == 'Shock'].copy()
+bicycle_df = vibr_df[vibr_df['Vehicle Type'] == 'bicycle'].copy()
+stroller_df = vibr_df[vibr_df['Vehicle Type'] == 'stroller'].copy()
 
 # these aren't needed in this data frame and just cause printing issues
 del stats_df['Frequency Array']
@@ -354,8 +354,13 @@ for val, note in zip((10.0, 20.0, 60.0, 240.0),
                      ('10 min', '20 min', '1 hr', '4 hr')):
     p.axes.axhline(eval_health(val)[1], linestyle='--', color='tab:grey')
     p.axes.text(1.18, eval_health(val)[1] + 0.05, note)
+# NOTE : calling set_xticks before set_xticklabels gets rid of the userwarning,
+# see:
+# https://stackoverflow.com/questions/63723514/userwarning-fixedformatter-should-only-be-used-together-with-fixedlocator
+p.set_xticks(p.get_xticks())
+xlabs = p.get_xticklabels()
 p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
-                   p.get_xticklabels()], rotation=90)
+                   xlabs], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
 p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*MM2INCH))
@@ -386,6 +391,7 @@ for val, note in zip((10.0, 20.0, 60.0, 240.0),
     p.axes.axhline(eval_health(val)[1], linestyle='--', color='tab:grey')
     p.axes.text(1.1, eval_health(val)[1] + 0.15, note,
[…]

### 2025-04-03 src/website.py
Fixed more warnings and added spectra plot to website.

@@ -243,10 +243,12 @@ for surf in stroller_df['Road Surface'].unique():
 
 boxp_html = []
 
-
 ##################################################
 # Figure: Stroller and Bicycle Spectrum Comparison
 ##################################################
+boxp_html.append(H2.format("""Mean spectra of each vehicle at each speed."""))
+msg = """TODO"""
+boxp_html.append(P.format(msg))
 fig, axes = plt.subplots(ncols=2, nrows=2, layout='constrained',
                          figsize=(MAXWIDTH*MM2INCH, 0.6*MAXWIDTH*MM2INCH))
 tick_spacing = 20
@@ -267,6 +269,7 @@ for vehicle in ['bugaboo', 'greenmachine', 'maxicosi', 'oldrusty', 'yoyo']:
 strol_ax.xaxis.set_major_locator(ticker.MultipleLocator(tick_spacing))
 strol_ax.set_ylabel('Amplitude [m/s$^2$]')
 strol_ax.set_xlabel('Frequency [Hz]')
+strol_ax.set_title('Target Speed: 5 km/h')
 strol_ax.grid(visible=True)
 strol_ax.legend()
 
@@ -301,6 +304,7 @@ axes[0, 1].legend()
 fname = '{}-spectra-compare.png'.format(SIGNAL)
 fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
 plt.clf()
+boxp_html.append(IMG.format('', fname) + '\n</br>')
 
 #########################################################
 # Figure: Health ISO Weighted RMS All Trials Scatter Plot
@@ -382,7 +386,7 @@ p = sns.scatterplot(
     y=SIGNAL_RMS_ISO,
     x="Vehicle, Seat, Baby Age",
     hue='Road Surface',
-    palette=['C1', 'C4', 'C0', 'C2', 'C3', 'C5'],
+    palette=['C1', 'C4'],
     style="Target Speed [km/h]",
 )
 # health risk lines for different durations
@@ -620,7 +624,7 @@ p = sns.scatterplot(
     y=SIGNAL + "_vdv",
     x="Vehicle, Seat, Baby Age",
     hue='Road Surface',
-    palette=['C1', 'C4', 'C0', 'C2', 'C3', 'C5'],
+    palette=['C1', 'C4'],
     style="Target Speed [km/h]",
 )
 p.set_xticks(p.get_xticks())

### 2025-04-03 src/html_templates.py
Export an excel file and make downloadable from website.

@@ -111,7 +111,8 @@ INDEX = """\
   <h1 id="trial_table">Repetitions</h1>
   <hr>
   <p>
-    This lists all of the repetitions in long form (tidy data).
+  This lists all of the repetitions in long form (tidy data). Download as an
+  excel spreadsheet: <a href='all-reps.xlxs'>all-reps.xlxs</a>.
   </p>
 {trial_table}
 

### 2025-04-03 src/website.py

@@ -100,6 +100,8 @@ stroller_df = vibr_df[vibr_df['Vehicle Type'] == 'stroller'].copy()
 del stats_df['Frequency Array']
 del stats_df['Amplitude Array']
 
+stats_df.to_excel(os.path.join(PATH_TO_DATA_DIR, 'all-reps.xlsx'))
+
 ################
 # Data Summaries
 ################

### 2025-04-03 src/html_templates.py
Fix file extension in html.

@@ -112,7 +112,7 @@ INDEX = """\
   <hr>
   <p>
   This lists all of the repetitions in long form (tidy data). Download as an
-  excel spreadsheet: <a href='all-reps.xlxs'>all-reps.xlxs</a>.
+  excel spreadsheet: <a href='all-reps.xlsx'>all-reps.xlsx</a>.
   </p>
 {trial_table}
 

### 2025-04-03 src/html_templates.py
Added excel downloads of the bicycle and stroller summaries.

@@ -22,9 +22,10 @@ INDEX = """\
   <hr>
   <div class="alert alert-danger" role="alert">
     <p>
-      Warning: These results are preliminary, do not rely on them until a
-      supporting paper is published. See the latest preprint for more context:
-      <a href="https://doi.org/10.31224/4415">doi.org/10.31224/4415</a>.
+      Warning: These results are a work-in-progress, we caution reliance on
+      them until a supporting paper is published. See the latest preprint for
+      more context: <a
+      href="https://doi.org/10.31224/4415">doi.org/10.31224/4415</a>.
     </p>
   </div>
   <p>
@@ -58,6 +59,9 @@ INDEX = """\
   <p>
     Counts and mean values for each scenario, i.e. combination of vehicle,
     seat, baby mass, road surface, and speed.
+    Download summary tables for the strollers and bicycles in excel format: <a
+    href='stroller-summary.xlsx'>stroller-summary.xlsx</a> and <a
+    href='bicycle-summary.xlsx'>bicycle-summary.xlsx</a>.
   </p>
 {mean_table}
 

### 2025-04-03 src/website.py

@@ -146,6 +146,8 @@ with open(os.path.join(PATH_TO_TABLE_DIR, 'summary-data-frame.tex'), 'w') as f:
     f.write(summary_df.to_latex(float_format="%0.1f"))
 
 stroller_summary_df = create_summary_data_frame(stroller_df)
+stroller_summary_df.to_excel(os.path.join(PATH_TO_DATA_DIR,
+                                          'stroller-summary.xlsx'))
 print_header("Means Per Scenario: Stroller")
 print(stroller_summary_df)
 with open(os.path.join(PATH_TO_TABLE_DIR,
@@ -153,6 +155,8 @@ with open(os.path.join(PATH_TO_TABLE_DIR,
     f.write(stroller_summary_df.to_latex(float_format="%0.1f"))
 
 bicycle_summary_df = create_summary_data_frame(bicycle_df)
+bicycle_summary_df.to_excel(os.path.join(PATH_TO_DATA_DIR,
+                                         'bicycle-summary.xlsx'))
 print_header("Means Per Scenario: Bicycle")
 print(bicycle_summary_df)
 with open(os.path.join(PATH_TO_TABLE_DIR,

### 2025-08-28 main.tex
Update tex file from overleaf.

@@
 \begin{abstract}
-  Infants are transported in strollers and in baby seats mounted on cargo
-  bicycles. The infants experience whole-body vibration during the associated
-  walking and cycling trips, but there is little existing knowledge about
-  associated comfort and health effects. To improve this, we measure the seat
-  pan acceleration of five strollers and two styles of cargo bicycles with dummy
-  infants representing ages 0 to 9 months over six different road surfaces of
-  varying road roughness at typical travel speeds. The five strollers included
-  three modern systems and two vintage systems with some level of suspension.
-  One cargo bicycle had electric support enabling speeds up to 25~\si{\kph}. We
-  report average seat pan acceleration for 78 different scenarios and
-  investigate the effects of road surface, vehicle, seat type, and travel speed.
-  Using the whole-body vibration ISO standards, we show that rough road
-  surfaces, amplified by travel speed, may have health risks for travel
-  durations as low as \SIrange{10}{30}{\min}. Stroller designs from 50 years ago
-  significantly reduce vibrations, relative to most modern strollers we tested,
-  indicating the need for a return of suspension elements. Cargo bicycles ridden
-  at the maximum electric bicycle speed over paver bricks can cause
-  accelerations that should likely be avoided except for only the shortest of
-  durations until more direct evidence of risks to infants is studied. Standards
-  are needed for infant transport testing and evaluation, designers need to
-  incorporate better suspension for infants, and research is needed to develop
-  clear and direct connections to health and comfort effects.
+  Infants transported in strollers and cargo bicycles experience whole-body vibrations.
+Only little information was found on  these vibrations and the associated comfort and health effects on infants.
+To improve this, we measure the acceleration of  the seat pan of five strollers and two styles of cargo bicycles with dummy infants representing ages 0 to 9 months over six different road surfaces of varying road roughness, at typical travel speeds.
+The five strollers included three modern systems and two vintage systems, all with some level of suspension.
+One cargo bicycle had electric support that enabled speeds up to 25~\si{\kph}.
+We report average seat pan acceleration for 78 different scenarios and investigate the effects of road surface, vehicle, seat type, and travel speed.
+Using the ISO standard for whole-body vibration, we show that rough road surfaces, amplified by travel speed, may have health risks for travel durations as low as \SIrange{10}{30}{\min}.
+Vintage stroller designs from 50 years ago significantly reduce vibrations compared to  modern strollers tested, indicating the need to return to better suspensions.
+Cargo bicycles ridden over paver bricks at the maximum speed of an electric bicycle can cause accelerations that should likely be avoided, except for the shortest of durations, until more direct evidence of risks to infants is studied.
+Vibration standards are needed for infant transport testing and evaluation, designers need to incorporate better suspension for infants, and research is needed to develop clear and direct connections to health and comfort effects.
 \end{abstract}
@@
 %Paragraph to introduce baby transport
-When a baby is born, it is not able to walk. To move around or travel, it must
-be either carried by adults or transported in a suitable means of wheeled
-transport. Until about a century ago,  babies mainly stayed at home. This still
-is customary in some non-Western cultures. A century ago, perambulators were
+When a baby is born, it is not able to walk and must
+be either carried by adults or transported in suitable wheeled
+transport. Until about a century ago,  babies mainly stayed at home, which is still customary in some non-Western cultures. A century ago, perambulators were
 used to transport infants outdoors. However, mothers were advised that a playpen
-in the garden is healthier than the use of a perambulator, partly because the
-vibrations generated by a perambulator were deemed not comfortable and even
-harmful for the baby~\cite{behrend1931}, even though in those days perambulators
-had ample suspension. Since about 1970, cars became ubiquitous and the heavy and
-sizeable perambulators became strollers: lighter and smaller products to enable
-easy transportation in a car. Over the years, new means of transportation came
-into use for infants: cars with a child car seat, bicycles with a bicycle seat
-and cargo bicycles with either a car seat or a baby shell.
+in the garden is healthier than the use of perambulators, partly because vibrations generated by a perambulator were deemed not comfortable and even
+harmful for babies~\cite{behrend1931}, even though in those days perambulators had ample suspension. Since about 1970, cars became ubiquitous, and the heavy and
+sizeable perambulators became strollers: lighter and smaller products foldable for
+easy transportation in cars. Over the years, new means of transportation came
+into use for infants: child safety seats to use in cars, bicycles with child seats
+and cargo bicycles with child seats or baby shells.
 
 %Paragraph to introduce baby vibration in transportation
-All means of transport cause vibration, which is transferred to the infant
-sitting or lying in it. Unlike the advice in the 1930s, vibration is seemingly
-not a subject of attention in the present design of these products. On the
-contrary, modern strollers do not have much suspension and cargo bicycles which
-generate more vibration are increasingly used for infants. Interestingly, in the
-literature we could find little about the maximal vibration load that babies and
-older children can receive during transport without discomfort or harm, and
-vibrations generated by infant transport are also only sparsely investigated.
-Therefore the effect of transport on infant comfort and health can not easily be
-assessed. To establish the amount of vibration that infants are subjected to in
+All means of transport cause vibration, which is transferred to the sitting or lying infant. Unlike the advice in the 1930s, vibration is seemingly
+not a subject of attention in the present design of these products.
+On the contrary, modern strollers do not have much suspension, and (electric) cargo bicycles are increasingly used for infants with seats that offer marginal suspension or padding.
+We thoroughly reviewed the literature, but found very little about the maximal vibration load that babies and older children can receive during transport without discomfort or harm, and vibrations generated by infant transport are only sparsely investigated.
+%Therefore the effect of transport on infant comfort and health can not easily be assessed. 
+To establish the amount of vibration to which infants are subjected in
 transportation products, we investigated the vibration that infants receive
@@
 % Paragraph about motivation
-Cycling, one of the active transportation modes, is advantageous for
+Research on vibration comfort during cycling is a logical starting point for investigating similar road-induced vibrations for infants. Cycling is beneficial for
 health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\) emissions, congestion, and air pollution~\cite{Neves2019}. As a result, bicycles are
-increasingly used as a means to deliver goods to consumers, and also for daily
-commuting to work and personal matters (shopping, commuting with
-children/infants, and others). Among all journeys in the EU, 20-40\% are by
+increasingly being used to deliver goods, for daily
+commuting and leisure. Among all journeys in the EU, 20-40\% are by
 bicycle or on foot, with bicycle trips most frequent in the Netherlands,
-Denmark, and Sweden and less frequent in Finland. Various countries and
-employers provide incentives to increase the use of bicycles. However, some
-challenges need to be overcome to secure the wide acceptance and use of active
-transportation modes. One of these challenges is the comfort levels experienced
-by riders and passengers (i.e., infants/children in cargo bicycles), which is a
-multifaceted aspect~\cite{ayachi2015identifying} and critical for the wide
-acceptance and use of bicycles as a daily means of transport. Meanwhile, this is
-a topic that is of great interest and requires attention when it comes to
-infants' transportation with strollers or bicycles.
-
+Denmark, and Sweden and less frequent in Finland. Various countries and employers provide incentives to increase the use of bicycles. However, the comfort experienced
+by riders and passengers (i.e., infants/children in cargo bicycles), is 
+a multifaceted ~\cite{ayachi2015identifying} challenge in their wide
+acceptance. %Meanwhile, this is a topic that is of great interest and requires attention when it comes to infants' transportation with strollers or bicycles.
 % Paragraph about comfort in bicycles
-The research on cyclist comfort is a natural starting point for investigations
-of similar road-induced vibrations for infants.
-Comfort on bicycles~\cite{too1990biomechanics} is mainly affected by physical
-comfort and the impact of environmental factors (weather, geometry of the route,
+The comfort of bicycles~\cite{too1990biomechanics} is mainly affected by physical
+comfort and the impact of environmental factors (weather, route geometry,
 and road roughness).  
 Physical comfort is related to mechanical (bicycle and component design),
-biomechanical (whole-body vibrations, human body dynamics, and kinematics) and
-physiological factors (individual characteristics, e.g. sex, body size, weight
-and others).
-While there is extensive literature exploring the impact of environmental
-factors (i.e., irregular road surface quality, weather conditions) on cyclists'
+biomechanical (whole-body vibrations, human body dynamics, and kinematics), and
+physiological factors (individual characteristics, e.g. sex, body size, weight, etc.).
+Although there is relevant literature exploring the impact of environmental
+factors (i.e., irregular road surface quality, weather conditions) on cyclist
 comfort~\cite{Stinson2003,Hagemeister2003,ayachi2015identifying,Verhoeven2017,Teixeira2020},
 there is limited work on understanding the biomechanical and physiological
-factors of comfort while being carried by bicycle (infants/children in bicycle
-seats, on cargo bicycles, or in trailers). A particular concern is the transport
-of infants under one year, who cannot well express any experience of discomfort
+factors of comfort of bicycle passengers (infants/children in bicycle
+seats, cargo bicycles, or trailers). A particular concern is the transport
+of infants under one year of age, who cannot well express any experience of discomfort
 or pain.
-Similar concerns are raised when it comes to strollers, where infants are also
-exposed to vibrations induced by roads. 
-In this paper, we will explore biomechanical comfort by assessing the whole-body
-vibrations that could be experienced by transported infants both in cargo
-bicycles and strollers, and evaluating potential health risks and discomfort
-that might arise.
+Similar concerns are raised about strollers, where infants are also
+exposed to road-induced vibrations. 
+In this paper, we will explore biomechanical comfort by assessing whole-body
+vibrations experienced by infants transported in cargo
+bicycles and strollers, and by evaluating potential health risks and discomfort.
 
 % Paragraph about transmission of vibrations
-Biomechanical comfort is mostly related to the vibrations induced by road
-irregularities and transmitted via the vehicle to the human body and head while
-being driven~\cite{too1990biomechanics}. 
-According to the literature, road irregularities are a critical factor for the
-amplitude of the resulting vibrations experienced by the bicyclists and
-passengers, as the vibrations induced on the body and head are not efficiently
-isolated due to the lack of or inadequate suspension systems in most of the
-bicycle models~\cite{vasudevan2017comparison} or strollers.
-The bicycle or stroller design and its specific configuration can affect the
-sitting posture, and eventually the transmissibility of the
-vibrations~\cite{Brand2020,Verma2016}.
-The sitting posture can also vary in case of children/infants who may be
-transported sitting or lying down in a different posture and location than the
-cyclist (e.g. above a wheel when in a bicycle seat) and in/on a different `seat'
+Biomechanical comfort is mainly related to vibrations induced by road
+irregularities and transmitted through the vehicle to the human body ~\cite{too1990biomechanics}. 
+Road irregularities are a driving factor, as vibrations induced in children are not efficiently
+isolated due to the lack of adequate suspension systems in most bicycle models~\cite{vasudevan2017comparison} and strollers.
+The bicycle or stroller design and the seating configuration affect posture and vibration transmission~\cite{Brand2020,Verma2016}.
+Children/infants can be
+transported sitting or lying in a different location than the cyclist (e.g. above a wheel when in a bicycle seat) and in/on a different `seat'
 (a car seat, bicycle seat, stroller seat, or cot). 
-These all influence the level of whole-body vibrations and the transmission of
-the vibrations from the seat to the body and head.
-Furthermore, the amplitude of the vibrations experienced by
-bicyclists/passengers/transported infants while biking or being transported in a
-stroller may increase because of increased travelling speed either due to
+%These all influence the transmission of vibrations from the seat to the body and head.
+Vibrations increase with travel speed, for example, when
 running with a stroller or due to the increased power offered by electric
 bicycles (with and without trailers).
-For the latter, the average speed of electric bicycles and speed pedelecs is
+For the latter, the average speed using electric bicycles and speed pedelecs is
 19\% higher (21.0~\si{\kph} and up to 63\% higher (28.1~\si{\kph}),
-respectively, than the average speed of conventional bicycling~\cite{SWOV2022}.
-The intensity of these vibrations could become even more critical with the
-change of load, which could be related with age and size of the infant/children
-transported. However, there is limited literature exploring the whole-body
-vibrations of infants and children being transported by bicycles with trailers,
-cargo bicycles, stroller seats and others
+respectively, than conventional bicycling~\cite{SWOV2022}.
+%The intensity of these vibrations could become even more critical with the change of load, which could be related with age and size of the infant/children transported. 
+However, there is limited literature exploring whole-body
+vibrations of infants and children transported by bicycle trailers,
+cargo bicycles, and strollers 
 ~\cite{Ota2012,Ota2014,Kanya-Forstner2020, vanDriessche2018,
-Schwanitz2020,MalteChildComfort2022}.
-At the same time, the available literature is mostly focusing on comfort rather
+Schwanitz2020,MalteChildComfort2022}, and literature focusses on comfort rather
 than health risks.
@@
 % Paragraph about children in bicycles
-One of the research fields closely related to vibrations acting on infants
+One of the research fields closely related to the vibrations that act on infants
 during transportation is that of inflicted head injury by shaking trauma
-(IHI-ST). However, there is a lack of reliable, applicable, validated injury
-thresholds for assessing IHI-ST risks~\cite{hutchinson2024modeling}. Similarly,
-even if there are significant indications that the vibration amplitude affects
-comfort in bicycles or strollers, there are no standard assessment methods or
-guidelines available with regards to their design. ISO~2631~\cite{ISO2631}, the
+(IHI-ST). However, there is a lack of reliable, applicable, and validated injury
+thresholds to assess IHI-ST risks~\cite{hutchinson2024modeling}. Similarly,
+even if there are indications that vibration affects
+comfort in bicycles or strollers, there are no standard vibration assessment methods or
+guidelines available with respect to their design. ISO~2631~\cite{ISO2631}, the
 international standard for assessing whole-body vibrations, was derived using
-datasets on motion platforms, adults as human participants and sitting postures
-which are adopted in passenger vehicles rather than on bicycles.
-This inconsistency was captured by Gao~et~al.~\cite{Gao2018}, who derived
-different limits of comfort for adults riding on bicycles based on their
-subjective feedback, compared to the vibration limits suggested by
-ISO~2631-1.
-In addition, the exposure time to the vibrations is not considered as a factor
-of comfort by the ISO~2631-1, despite having a clear impact on health risks
+data sets on motion platforms, with adults as participants and sitting postures
+as adopted in passenger vehicles rather than on bicycles.
+Gao~et~al.~\cite{Gao2018} therefore derived vibration
+comfort limits for adults riding bicycles, based on their
+subjective feedback.
+Furthermore, in ISO~2631-1 the exposure time to vibrations is not considered a factor
+in the determination of comfort, despite having a clear impact on health risks
 according to the European Directive (2002/44/EC, 2002)
@@
 % Paragraph Potential effects of vibrations on adults
-Despite the lack of clarity with regards to comfort assessment or inflicted head
+Despite the lack of knowledge and test methods with regard to comfort or inflicted head
 injury by shaking trauma for children/infants on bicycles, there are clear
-indications in the literature that these should be explored and considered.
-About 36\% of males and 42\% of females in a total sample of 900 people had
-various complaints about comfort~\cite{groenendijk1992sitting}.
-Discomfort for both men and women occurred even during short bicycle trips
-(\SIrange{3}{10}{\kilo\meter}). However, results from research into comfort of
-adult cyclists can not be applied directly to infants or children sitting or
+indications in the literature that these should be considered.
+About 36\% of males and 42\% of females in a total sample of 900 cyclists had
+various discomfort complaints~\cite{groenendijk1992sitting}.
+Discomfort of both men and women occurred even during short bicycle trips
+(\SIrange{3}{10}{\kilo\meter}). However, results from research into comfort of active
+adult cyclists cannot be applied directly to infants or children sitting or
 lying in transportation systems.
 
-Schwanitz~et~al.~\cite{Schwanitz2020} assessed accelerations in a child bicycle
-trailer riding over smooth asphalt, gravel, and cobblestones using ISO~2631-1
-weighted RMS vertical accelerations.
-Anthropomorphic children shaped sandbag dummies (baby and toddler sizes) were
-used as lumped masses to represent the child body. According to the results, tyre pressure and the number of
+Schwanitz~et~al.~\cite{Schwanitz2020} tested a child bicycle
+trailer on smooth asphalt, gravel, and cobblestones using child shaped sandbag dummies (baby and toddler sizes) using ISO~2631-1
+weightings. Tyre pressure and number of
 passengers had no significant effect on vibration magnitude, but road surface
 and travel speed did. 
-The baby sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
-the toddler sized dummy (10~\si{\kilo\gram}), while the measured values
-generally exceeded the ISO~2631-1 vibrational comfort of adults.
-Rothhämel~et~al.~\cite{MalteChildComfort2022} conducted measurements using a
+The baby-sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
+the toddler-sized dummy (10~\si{\kilo\gram}), while the measured values
+generally exceeded the ISO~2631-1 limit for vibrational comfort of adults.
+Rothhämel~et~al.~\cite{MalteChildComfort2022} tested a
 trailer seat and a tadpole configuration three-wheel cargo bicycle on smooth
-asphalt and cobblestones for speeds between \SIrange{10}{20}{\kph}. 
-After weighting the accelerations using ISO~2631-1 methods, they found a large
-increase of the vibration amplitude on cobblestones compared to asphalt on the
-same speed range. The child trailer exhibited larger weighted RMS accelerations
+asphalt and cobblestones for speeds from \SIrange{10}{20}{\kph} using ISO~2631-1 weightings. They found a large
+increase in vibration amplitude on cobblestones compared to asphalt in the
+same speed range. The child trailer exhibited larger accelerations
 than the cargo bicycle with the child seat between the front wheels. 
-Both the trailer and cargo bicycle child seats had generally larger magnitude
-vibrations than experienced in an automobile seat travelling at 30~\si{\kph} on
-a rough road \cite{gromadowski2013analysis}. Rothhämel and
+Child seats in trailers and cargo bicycles generally had
+vibrations of higher magnitude than those experienced in a car seat travelling at 30~\si{\kph} on a rough road \cite{gromadowski2013analysis}. Rothhämel and
 Liu~\cite{rothhamel2023comfort} conducted measurements with a
 6.5~\si{\kilo\gram} mass representing an infant with various tyre pressures. All
-their values fell into the ``extremely uncomfortable'' zone for the ISO~2631-1.
-
-In addition to the studies with dummies or lumped masses representing
+their values fell into the ``extremely uncomfortable'' zone for ISO~2631-1.
+
+In addition to studies with dummies or lumped masses representing
 infants, Kanya-Forstner~\cite{Kanya-Forstner2020} measured acceleration in
 bicycle child trailers with human subjects aged 12 months to 6 years over
-asphalt and gravel terrain (averaged speed of 12~\si{\kph} over the
+asphalt and gravel terrain (average speed of 12~\si{\kph} over a
 20~\si{\minute} ride). 
 According to the health assessment using ISO~2631-1, the vibrations are similar
-to the ones experienced in car seats in vehicles and illustrated moderate or low
+to those experienced in child seats in cars and illustrate moderate or low
 health risk for a 2~\si{\hour} duration.
 On the other hand, if not corrected for duration, the values point to moderate
-and high risks. The terrain type had the greatest influence on vibration
-exposure levels followed by trailer type, while gel cushions as support did not
-significantly influence vibration measured at the seat/pan interface. Hence,
-there is a need to re-focus on the impact of vibrations on infants and
-children's health and comfort~\cite{rybarczyk2020physiological} to ensure the
+and high risks. The type of road surface had the greatest influence on the levels of vibration
+exposure, followed by type of trailer, while gel cushions as support did not
+significantly influence the vibration measured at the seat/pan interface. Hence,
+there is a need to refocus on the impact of vibrations on infants and
+children's health and comfort~\cite{rybarczyk2020physiological} to ensure 
 safe, comfortable and wide use of bicycles.
@@
 Siong~\cite{lim2018study} carried out an indoor and an outdoor experiment to
-capture the vibrations transmitted onto the seat and backrest of a baby
+capture the vibrations at the seat and backrest of a baby
 stroller, using weights from \SIrange{4}{14.14}{\kilo\gram}, and  a child
@@
 10.30~\si{\kilo\gram}. 
-The comfort levels for the indoor testing were labelled as `Fairly
-uncomfortable' to `A little uncomfortable', but the outdoor testing resulted in
-`Extremely uncomfortable' and `Fairly uncomfortable' values. They used both a
-child and dummy for the experiments, identifying similar patterns. However, the
-results still consider ISO~2631-1 standard, which is designed for adults and
-specific postures. In a similar research, Sierzputowski~
-et~al.~\cite{sierzputowski2021pilot} investigated vibrations induced in a modern
+Comfort levels (ISO~2631-1) for indoor testing were  `Fairly
+uncomfortable' to `A little uncomfortable', where outdoor testing resulted in
+`Extremely uncomfortable' and `Fairly uncomfortable' values.
+The child and dummy provided similar results.
+%However, the results still consider ISO~2631-1 standard, which is designed for adults and specific postures.
+Sierzputowski~
+et~al.~\cite{sierzputowski2021pilot} tested a modern
 and
-an older stroller, when moving on different surfaces: asphalt road, concrete
-paving blocks, concrete plates, dirt road, lawn and damaged concrete. The
-obtained weighted RMS acceleration values based on ISO~2631-1 were several times
-in the range of the highest discomfort ($>$2~\si{\mps\squared}). 
-Another research which also included children as test subjects was conducted by
-Okajima~et~al.~\cite{okajima2020dynamic} measuring vibrations that seven
-children received, sitting upright in a stroller, when riding over a protrusion
+an older stroller on asphalt road, concrete
+paving blocks, concrete plates, dirt road, lawn and damaged concrete. Several conditions resulted in the highest discomfort levels ($>$2~\si{\mps\squared} according to ISO~2631-1). 
+Okajima~et~al.~\cite{okajima2020dynamic} tested seven
+children, sitting upright in a stroller, riding over a protrusion
 (13x60 mm) with either one wheel or two wheels. 
 The children were 3 to 6 years old, boys and girls, weighing
-\SIrange{15.94}{19.96}{\kilo\gram} and measuring
-\SIrange{98.0}{112.4}{\centi\meter} in length. 
-Based on the results, the infant’s head and chest exhibit strong vibrations at
-1~\si{\hertz} along all three axes (x,y and z), vibrate easily along the
-y-direction at 2~\si{\hertz}, and are less likely to vibrate at more than
+\SIrange{15.94}{19.96}{\kilo\gram} with a length of
+\SIrange{98.0}{112.4}{\centi\meter}. 
+The infant’s head and chest exhibited strong vibrations at
+1~\si{\hertz} along all three axes (x, y and z), vibration along the
+y-direction at 2~\si{\hertz}, with limited vibration above
 8~\si{\hertz}. 
-This result is critical as this range of frequencies is very common in bicycles
-and strollers. However, they did not assess the comfort and the health risk when
-the children were exposed to these vibrations. 
-Despite significant research on the effect of whole-body vibrations on
-children's comfort, there is limited research on infants.
-
-This paper reports on the vibration induced on infants of different ages when
-transported in strollers and cargo bicycles. 
-Vibration can be related to discomfort and might lead to negative health
-consequences. However, the topic is poorly addressed in scientific literature,
-and only a few studies focus on the effect of vibration on babies as reviewed
-above. 
-To measure the actual vibration transmitted to infants, we equipped five
+%This result is critical as this range of frequencies is very common in bicycles and strollers. 
+However, they did not assess comfort and health risk.
+
+The above studies provide experimental evidence of strong vibrations in real children, dummies, or simple masses transported in cargo bicycles, bike trailers, and strollers.
+Most studies use ISO~2631-1 frequency weighting and report very or extremely uncomfortable conditions with higher speeds and rough surfaces, while only one study evaluated health effects.
+Only a few studies focus on the effect of vibration on babies and infants under 12 months of age.
+
+This paper addresses both comfort and potential health effects for babies and infants.
+We equipped five
 strollers and two cargo bicycles with inertial measurement units (IMU) and
-conducted 78 experiments on different road surfaces and travel speeds, using
-dummies representing the size and mass of 0, 3, and 9 months old infants.
-We present results in the time and frequency domains, which allows comparing
-vertical accelerations at the baby-seat interface, as recommended by ISO~2631-1
-standards for vibration discomfort.
-We investigated the influence of different variables on vibration, such as type
-of vehicle, baby seat, travelling speed, dummy size and mass, and road surfaces
-and provide recommendations to users, designers, and future researchers based on
-the findings.
+carried out 78 experiments on different road surfaces and with different travel speeds, using
+dummies representing 0, 3, and 9 month-old infants.
+We present results using ISO~2631-1
+frequency weightings. 
+Given that ISO-2631-1 is neither validated for children nor for lying postures, we also report unweighted results to assess power spectrum and bandwidth.
+We investigated the influence of vehicle, seat, body size, speed, and road surface
+and provide recommendations to users, designers, and future researchers.
 
@@
 %
-Vibration measurements were conducted at approximate constant speed using five
-different strollers, two cargo bicycles, and two baby
-seats~\footnote{Appendix~\ref{app:equipment} provides figures and technical
-descriptions of all the strollers and cargo bicycles.}, chosen for their
-popularity and/or distinctive features:
-
-\begin{description}
-\item[Strollers] A selection of vintage and modern strollers for carrying
-infants. The modern strollers are configurable as cots for newborns and as seats
-for older infants.
-%
-\begin{description}
-  \item[Maxi-Cosi Street Plus] This stroller comes with a cot configuration (0-3
-  months) and an infant seat option. It has large wheels, with only a marginal
-  suspension system.
-  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
-  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the market. It
-  has only a marginal suspension system and smaller wheels compared to those of
-  other strollers available on the market.
-  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
-  rented for the experiment})
-  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system that makes
-  it an all-terrain stroller according to the manufacturer. It has large
-  puncture-proof tyres and an air-permeable mattress.
-  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
-  website})
-  \item[Green Machine] An unknown brand vintage perambulator, dating
-  approximately from the 1970's that includes a leather strap suspended cot in a
-  metal frame. The wheels are relatively large in diameter compared to the
-  modern strollers.
-  \item[Old Rusty] An unknown brand vintage seat-style stroller from
-  approximately the 1970's that includes a metal spring suspension system and
-  wheels that are slightly larger than the modern strollers.
-\end{description}
-\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
-seats can be mounted.
-%
-\begin{description}
-  \item[Urban Arrow Bicycle] A popular electric cargo bicycle in The
-  Netherlands. This vehicle has two inline wheels which makes it roll into
-  curves like a regular bicycle. It is featured by a long frame that can carry
-  loads (e.g. a child in a car seat or baby shell) placed in between the rider
-  and the front wheel. 
-  (\href{https://urbanarrow.com/}{Urban Arrow website})
-  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
-  rear) cargo tricycle  without electric assist. This vehicle will not roll into
-  curves. However, differing road surface unevenness at the left and right front
-  wheel will induce lateral roll and lateral acceleration in infants. We added
-  masses in specific locations to simulate the presence of an electric motor and
-  battery package. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
-  Webpage}) 
-\end{description}
-\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
-cargo bicycles.
-%
-\begin{description}
-  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
-  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
-  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
-  adapter was used in both cargo bicycles.
-    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
-    Webpage})
-  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
-  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
-  cargo bicycles.
-    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
-    Webpage})
-\end{description}
-\end{description}
+Vibration measurements were conducted at approximately constant speed using five
+different strollers and two cargo bicycles with two baby seats, chosen for their
+popularity and/or distinctive features. The strollers consisted of three modern
+strollers: Maxi-Cosi Street Plus (Dorel Juvenile, Foxborough, USA), BABYZEN YOYO
+0+ (Stokke, Ålesund, Norway), Fox 5 (Bugaboo, Amsterdam, The Netherlands) and
+two vintage strollers from unknown manufacturers ``Green Machine'' cot-style and
+``Old Rusty'' seat-style. The cargo bicycles were a two-wheel UrbanArrow (Pon,
+Amsterdam, The Netherlands) and a delta configuration tricycle (Keiler Bakfiets, The Netherlands) which were each fitted with the two seats: Joolz Pebble Pro (Dorel Juvenile, Foxborough, USA), Melia Baby Shell (Melia, Rotterdam, The Netherlands).
+~\footnote{Appendix~\ref{app:equipment} provides.
+figures and technical descriptions of all strollers and cargo bicycles.}
 
 The tests involved three baby dummies with sizes and weights representative of
-newborns and 3 and 9 month old infants. Newborns (`0 months') are the youngest
-(smallest, lightest) children that are transported in strollers with a cot.
-Three month old infants are the youngest (smallest, lightest) children that are
-transported in cargo bicycles, fixated in a baby car seat or baby shell. Nine
-month old infants are the youngest (smallest, lightest) that can sit up straight
-by themselves and thus can be transported sitting up straight, in a stroller
-with a seat or on the bench of a cargo bicycle.
+newborns and infants 3 and 9 months of age. Newborns (`0 months') are the
+youngest (smallest, lightest) children that are transported in strollers with a
+cot. Three-month-old infants are the youngest (smallest, lightest) children that
+are transported in cargo bicycles, fixed in a baby car seat or baby shell.
+Nine month old infants are the youngest (smallest, lightest) that can sit up
+straight by themselves and thus can be transported sitting up straight, in a
+stroller with a seat or on the bench of a cargo bicycle.
 
 We considered the use of ``crash test dummies'' (also known as anthropomorphic
-test devices or ATD's) which are designed and commonly used to test child seats
-in car crash tests. However, the nearest available body sizes for crash test
-dummies were a 6-weeks Q0-dummy, a 6-months Crabi dummy, and a 12-months Q-dummy
-(Humanetics, Farmington Hills, USA). These 3 dummies are of a fundamentally
-different design, hampering comparison, and did not match the desired body
-sizes. Moreover, these child dummies have dynamic properties designed for crash
-conditions, and they were designed based on scaling of adult biomechanical data
-rather than child data, so in that respect there is no benefit over other
-dummies.
-
-Testing with real infants would be unethical, and would create challenges in
+test devices or ATDs), which are designed and commonly used to test child seats
+in car crash tests. However, the closest available body sizes for crash test
+dummies do not meet the body sizes desired for this investigation. Furthermore, crash test dummies are of a fundamentally
+different design, based on scaling of adult biomechanical data
+rather than child data and with dynamic properties designed for crash
+conditions, not for vibration testing. Therefore crash test dummies were not considered a good option to use for the envisaged vibration testing.
+
+Testing with real infants would be unethical for the most severe conditions and create challenges in
 terms of reproducibility. Hence we bought and adapted ``reborn'' dummies
@@
 dummies (\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). The dummies were
-filled with a mixture of cat litter sand and water to reproduce the exact
-weights needed for testing. Cat litter sand features smooth and round-shaped
+filled with a mixture of cat litter, sand, and water to reproduce the exact
+weights needed. Cat litter sand features smooth and round shapes
 grains, which do not damage the dummies' materials (fabric and plastic). The
 weight and body height of the dummies were made to match the average measures
-for children of 0, 3 and 9 months old.
-
-We wanted to use the measurements from Steenbekkers~\cite{Steenbekkers1993}.
-However, this research provided the results only per three-month group, which
-did not fit our age categories. We decided to use the growth charts used by
-clinicians to assess infant growth to determine the average weight and body
-height at the right ages. The average weight at 0 months and the average body
-height at all three ages are derived from Dutch growth charts. We used
-measurements of Dutch children because they are the target group of the project
-funder, VeiligheidNL. Dutch children are also the tallest in Europe. We derived
-the average weight of 3 and 9 months old children from French growth charts.
-French children are the smallest in Europe. At 3 months, average Dutch children
-weigh 113 gram more than average French children and at 9 months, the difference
-is 85 gram. The following lists the dummies used:
-%
-\begin{description}
-  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
-  ``Andi Asleep'' (product code AW380008).
-  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
-
-  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
-  ``Asia - Limited Edition'' (product code 300287).
-  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
-  \item[Dummy 9 months] weight 8.90~\si{\kg}. Size 70~\si{\cm}. Dollkit 28'',
-  ``Hailey'' (product code 304137).
-  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
-\end{description}
-
-To achieve a realistic mass distribution in the body of the dummies, each limb
+for children of 0, 3 and 9 months old: 3.48~\si{\kg}|50~\si{\cm}
+5.90~\si{\kg}|62.5~\si{\cm}, and 8.90~\si{\kg}|70~\si{\cm}, respectively.
+
+%We wanted to use the measurements from Steenbekkers~\cite{Steenbekkers1993}. However, this research provided the results only per three-month group, which did not fit our age categories. 
+We used Dutch infant growth charts to determine the average weight and body
+height at age 0 months [reference needed!] and French growth charts for 3 and 9
+months. French children are the smallest in Europe, and Dutch children are the
+tallest. At 3 months, average Dutch children weigh 113 grams more than average
+French children and at 9 months, the difference is 85 grams.
+
+To achieve a realistic mass distribution, each limb
 was filled with a proper amount of wet sand (for the 0-month dummy, water was
@@
 the head, and cylinders for the torso, upper arms, upper legs and lower legs,
-according to what was stated in~\cite{Snyder1977}. We also assumed an equal
-density for each limb, and we rescaled the measurements of the limb segments
-reported in \cite{Snyder1977} to match the dimensions of our dummies. In doing
-so, we were able to calculate the volume of each segment, thus the mass of each
-limb of the dummies (assuming a density of 1000~\si{\kg\per\cubic\meter}).
+according to~\cite{Snyder1977}. We assumed equal
+density for each limb (1000~\si{\kg\per\cubic\meter}), and rescaled the limb segments
+in \cite{Snyder1977} to match the dimensions of our dummies. %In doing so, we were able to calculate the volume of each segment, thus the mass of each limb of the dummies.
 
@@
 Linear accelerations and angular velocities were measured tri-axially using
-Consensys Shimmer3 IMUs with a Consensys Base 6U.01 dock (Shimmen Sensing,
+Consensys Shimmer3 IMUs with a Consensys Base 6U.01 dock (Shimmer Sensing,
 Dublin, Ireland). The IMUs were updated to firmware version LogAndStream v0.11.0
@@
 tested (Small white and orange boxes visible in Figure~\ref{fig:sensors_UA}).
-Each vehicle was equipped with five IMUs, as listed below. All the drawings
-showing the vehicles and the sensors' location are reported in
+Each vehicle was equipped with five IMUs, as listed below. Drawings
+showing the vehicles and the sensors' location are in
 Appendix~\ref{app:equipment}.
@@
   \item \textbf{Rear Wheel} This IMU was placed on the wheel hub (cargo
-  bicycles) or clamped to the wheel (strollers) for measuring the travel speed.
-  The travelling (longitudinal) speed was derived according to:
-  %
-  \begin{align}
-    v = \omega \cdot r
-    \label{eq:long-speed}
-  \end{align}
-  %
-  where \(\omega\) is the angular speed of the wheel (obtained from the IMU's
-  gyroscope aligned with the wheel's axis) and \(r\) is the radius of the wheel.
+  bicycles) or clamped to the wheel (strollers) for measuring travel speed. The
+  travelling (longitudinal) speed was derived according to the wheel radius and
+  the IMU angular speed.
   \item \textbf{Front Wheel} This IMU was mounted on the front wheel fork (the
@@
   \subcaptionbox{IMU under the cargo bay}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/BT_UA.jpg}}
-  \subcaptionbox{IMUs on the baby seat surface}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/Maxicosi_sensors_UA.jpg}}
+  \subcaptionbox{two IMUs on the baby seat surface}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/Maxicosi_sensors_UA.jpg}}
   \caption{IMU locations on the Urban Arrow cargo bicycle. The white 3D printed
@@
 All tests were conducted in Delft, The Netherlands, on public roads near the
-Delft University of Technology, Faculty of Mechanical Engineering. Latitude and
-longitude of each location along with local photographs of each site are
-provided in Appendix~\ref{app:location}.
+Delft University of Technology.
 After mounting the sensors and reaching the location of the experiment, we
@@
 trial as an extra time-synchronization measure.
-For the cargo bicycle test, a single rider conducted all trials to be consistent
+For the cargo bicycle, a single rider conducted all trials to be consistent
 across different sessions (rider mass: 59~\si{\kg}; rider height:
@@
 mounted on the stroller handle bar or the steer of the cargo bicycle. We
-gathered data from multiple trials within the same session. The test
-combinations, ``scenarios'', are listed below.
+gathered data from multiple trials within the same session.
+The test ``scenarios'' combining vehicle type, body size, speed and test surfaces are listed below.
+All test locations and surfaces are shown in
+  Appendix~\ref{app:location}.
 %
 \begin{itemize}
-  \item \textbf{Strollers}  The stroller tests were done with the dummies of 0
-  months and 9 months old. All the test surfaces listed below are shown in
-  Appendix~\ref{app:location}.
+  \item \textbf{Strollers} were tested with dummies of 0 months and 9 months at
+  5~\si{\kph} at:
   \begin{itemize}
@@
       \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
-      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar was taped
-      to the ground (smooth surface)
+      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar 
   \end{itemize}
-  \item \textbf{Cargo bicycles} The cargo bicycle tests were conducted using the
-  dummies of 0 months and 3 months. With the Keiler tricycle, the speed was
-  limited to 20~\si{\km\per\hour} for safety reasons (due to wobbling), and
-  difficulties to safely keep a constant speed over 22~\si{\km\per\hour}. The
-  test surfaces are listed below:
+  \item \textbf{Cargo bicycles} were tested with dummies of 0 months and 3
+  months. Test were performed at 12~\si{\kph} for both vehicles. The Urban Arrow
+  was also tested at 25~\si{\kph} whereas the Keiler was tested at
+  20~\si{\km\per\hour} for safety reasons (due to wobbling). The test surfaces
+  are:
   \begin{itemize}
@@
       \item Paver bricks
-      \item Shock bump: As mentioned before, we conducted shock test riding over
-      a 30x30~\si{\mm} square section aluminium bar, at three speeds: 
-      \begin{itemize}
-          \item Low speed: 5~\si{\kph}
-          \item Medium speed: 12~\si{\kph}
-          \item High speed: 20~\si{\kph} for the Keiler tricycle,
-          25~\si{\kph} for the Urban Arrow cargo bicycle
-      \end{itemize}
+      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar (also tested at 5~\si{\kph})
       \end{itemize}
@@
 %
-All tested systems provided full support of back and head and allowed usage in
+All tested systems provided full support for back and head and allowed usage in
 lying or at least reclined postures. Nine month old infants would be able to sit
-erect but will often rest their heads or be asleep. Although sitting upright is
+erect, but will often rest their heads or be asleep. Although sitting upright is
 the best posture for children who can sit upright, a more reclined posture was
@@
 For the seat pan  0~\si{\degree} is horizontal and positive angles indicate elevated legs, see Figures in Appendix \ref{app:equipment}.
-I STILL DONT UNDERSTAND -43.
-RF is rearward facing and FF is forward facing.}
+RF is rearward facing, and FF is forward facing.}
 \begin{tabular}{lllrrr}
@@
  & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
- &  & 3 mo & Maxi-Cosi X Joolz (RF)& 49 & -43 \\
+ &  & 3 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
  &  & 3 mo & Melia (FF)& 64 & 2 \\
@@
  & Bugaboo Fox 5 & 9 mo & Baby seat (FF) & 49 & 24\\
+ & Green Machine & 0 mo & Baby cot (RF) & 0 & 0\\
+ & Old Rusty & 9 mo & Baby seat (FF) & 47.8 & 5\\
 \bottomrule
@@
 % 
-We analysed the raw data with a custom data processing pipeline. The pipeline's
-open source code (MIT license) is hosted at
+We analysed the raw data with a custom data processing pipeline. The open source code (MIT license) is hosted at
 \href{https://github.com/mechmotum/baby-vibration}{github.com/mechmotum/baby-vibration}
-implemented in Python 3.13.1 using the following software packages:
+implemented in Python 3.13.1 using the following software:
 DynamicistToolKit 0.6.1, Matplotlib 3.9.3, NumPy 2.2.0, Pandas 2.2.3, pyyaml
@@
 quality of the data and general results for all trials including the selected
-tables and figures presented and discussed in the results section of this paper.
+tables and figures in this paper.
 
@@
 The raw data consists of a single comma-separated value (CSV) file per session
-per IMU along with metadata for the sessions and vehicles. The CSV file contains
+per IMU, along with metadata for the sessions and vehicles. The CSV file contains
 the time series data from each IMU: linear acceleration along and angular speed
@@
   \item Extract segments representing a single trial from each session time
-    history, based on the manually labelled segment ``start'' and ``end'' times.
+    history, based on the manually labelled segment ``start'', and ``end'' times.
   \item Split the trials with durations longer than 40~\si{\second} into
@@
     standard gravity component. This is achieved by rotating the coordinate axes
-    about the sensor's body-fixed axis which was manually aligned with the
+    about the sensor's body-fixed axis, which was manually aligned with the
     vehicle's pitch axis. We subtracted the mean measured acceleration due to
@@
 non-shock repetitions have durations in the range of \SIrange{10}{40}{\second}
-(mean: 25~\si{\second}), see Table~\ref{tab:num-trials} for a breakdown of the
-non-shock repetitions.
+(mean: 25~\si{\second}), see Table~\ref{tab:num-trials}.
 %
@@
   trials in the shaded grey areas. Gold horizontal lines depict the mean speed
-  during the trial bounded by the standard deviation of the speed.}
+  during trials bounded by its standard deviation.}
   \label{fig:session}
@@
   \caption{Number of repetitions performed on each road surface, excluding
-  shock, and speed along with the mean duration in seconds and its standard
+  shock, and speed along with the mean duration and its standard
   deviation.}
@@
 
-\subsection{Trial Analyses}
+\subsection{Analysis}
 %
@@
 Values that exceed the range are rare and only present in some of the cargo
-bicycle paver brick trials, but are common in the shock tests. Following the
+bicycle paver brick trials, but more common in the shock tests. Following the
 ISO~2631-1 recommendation, we low-pass filtered the signal at
@@
 spectrum along with smoothened versions of the raw and ISO 2631-1 weighted
-signals. In almost all trials, there is a single dominant peak frequency in the
+signals.
+
+In almost all trials, there is a single dominant peak frequency in the
 ISO weighted and smoothed spectra. For the few trials that had two or more peaks
 at approximately the same amplitude, the second peak was sometimes selected.
-After ISO weighting, the area under the spectrum curve was calculated and the
+After ISO weighting, the area under the spectrum curve was calculated, and the
 frequency below which 80\% of the amplitude content falls marked as an indicator
 of bandwidth.
-%
+
 \begin{figure}
@@
 \(a_{w,z}\) at the seat pan for each trial using Equation~\ref{eq:rms-acc} to
-use for the health assessment and the RMS of the magnitude of the acceleration
+use for the health assessment and the RMS of the magnitude of the 3D acceleration
 vector at the seat pan using Equation~\ref{eq:rms-acc-mag} for the comfort
@@
 these per-repetition metrics are reported as mean values over the repetitions
-corresponding to a scenario in Table~\ref{tab:results} in
-Appendix~\ref{app:results}. Regarding the shock test, the analysis was conducted
+corresponding to a scenario in Table~\ref{tab:summary-stroller} and Table~\ref{tab:summary-bicycle} in
+Appendix~\ref{app:results}. Regarding the shock test, the analysis presented in Appendix~\ref{app:shock} was conducted
 on unfiltered data (not downsampled). We selected the maximum (absolute) peak
@@
 \end{align}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-maxicosi-0-SeatBotacc_ver-rep0.png}
-  \caption{Raw seat pan vertical acceleration versus time from session 015:
-  Keiler tricycle during the shock test.}
-  \label{fig:shock_time-history}
-\end{figure}
 
@@
 Both \(x_\textrm{Road Surface}\) and \(x_\textrm{Stroller}\) are categorical
-variables and we select tarmac and the Green Machine as the reference values
+variables, and we select tarmac and the Green Machine as the reference values
 when coding the categorical variables, respectively. We do not consider the
@@
 the interaction of road surface and cargo bicycle setup, but we do consider the
-interaction of speed with road surface. We use \(p<0.05\) to indicate
+interaction of speed with road surface. 
+Both for strollers and cargo bicycles each tested combination of vehicle, seat and body size is considered as a different vehicle type.
+We use \(p<0.05\) to indicate
 significant differences for both models. Following fitting the two statistical
@@
 %
-\subsection{Effect of Speed with Cargo Bicycles}
-%
-Figure~\ref{fig:compare-bicycle-speed} shows the variation in ISO~2631-1
-weighted vertical RMS acceleration across the tested speeds. Accelerations
-experienced when riding over the paver bricks were always larger than for tarmac
-at the same speed, with the paver bricks showing about a 4-5\(\times\) higher
-acceleration magnitude than tarmac. Over paver bricks, the RMS acceleration
-increased by about 1.6\(\times\) when increasing the speed from
-\SIrange{12}{25}{\kilo\meter\per\hour}. The effect of speed while cycling over
-tarmac was less drastic but also may show a slight increase of accelerations
-over the speed range.
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-speed-compare.png}
-  \caption{Seat pan ISO 2631-1 weighted vertical acceleration RMS versus speed
-  for all cargo bicycle repetitions. Shaded regions represent the 95\%
-  confidence intervals from a simple linear regression that ignores
-  \(x_\textrm{Cargo Bicycle}\).}
-  \label{fig:compare-bicycle-speed}
-\end{figure}
-
-\subsection{Effect of Vehicle Model}
-%
-Figure~\ref{fig:stroller-type-compare} shows the vertical RMS accelerations for
-each road surface for each of the five strollers, lumping seat configurations
-and dummy sizes. The Maxi-Cosi Street Plus and Stokke BABYZEN YOYO 0+ strollers
-have similar mean values across repetitions. The Bugaboo Fox 5 has a slightly
-lower mean for cobblestones, paver bricks, and sidewalk pavers. The Green
-Machine performs better than the modern strollers on paver bricks, but similarly
-otherwise. The Old Rusty performs better than the modern strollers on all
-surfaces except tarmac. All strollers seem to experience the same acceleration
-on tarmac. There may be no significant difference in the acceleration
-experienced in each modern stroller model. All road surfaces compared to tarmac
-cause at least double the RMS acceleration.
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/SeatBotacc_ver-stroller-type-compare.png}
-  \caption{Mean seat pan ISO 2631-1 weighted vertical RMS acceleration per road
-  surface for each stroller. Vertical lines indicate the standard deviation for
-  categories that have more than one repetition.} 
-  \label{fig:stroller-type-compare}
-\end{figure}
-
-Figure~\ref{fig:bicycle-type-compare} compares the two cargo bicycle models we
-tested. Each cargo bicycle was fitted with the same set of two baby seats (Melia
-baby shell and Maxi-Cosi Pebble Pro baby seat). On tarmac the two-wheel cargo
-bicycle delivers lower accelerations to the seat pan, but on paver bricks the
-two vehicles show little difference in RMS accelerations. Both vehicles show
-increasing vertical RMS acceleration with speed.
+Results for all 67 combinations of vehicle setup, road surface, and target speed are shown in
+Table~\ref{tab:summary-stroller} for strollers and Table~\ref{tab:summary-bicycle} for cargo bicycles.
+The magnitude (combining x,y,z) ISO weighted RMS is only a bit higher ($<$4\% in  modern strollers and cargo bicycles) than the vertical (z) ISO weighted RMS, indicating that vertical vibration is dominant.
+This holds also for the three-wheeled Keiler which will roll due to differing road unevenness at left and right wheels, resulting in lateral seat motion, but this seems hardly relevant in the current data.
+An exception is the vintage green machine stroller where the magnitude is up to 24\% higher indicating relevant contributions of horizontal seat pan motion. 
+As expected, in all cases the vertical ISO weighted RMS acceleration is below the vertical unweighted RMS, and this reduction is on average 10\% for modern strollers, 13\% for the vintage green machine, and even 56\% for the vintage old rusty which sees the highest bandwidth (105 Hz).
+For cargo bicycles the ISO weighting leads to an average reduction of 16\%. 
+The Keiler cargo tricycle with Melia seat on paver bricks at 20 km/h sees a 29\% reduction with a bandwidth of 83 Hz. 
+These strong effects of ISO frequency weighting in some vehicle and speed combinations are addressed further in the discussion.
+Below we present ISO weighted results for which guidelines have been published using magnitude for discomfort and vertical for health.
+
+\subsection{Effect of Speed and model with Cargo Bicycles}
+%
+Figure~\ref{fig:bicycle-type-compare} compares the two cargo bicycle models which were both  fitted with the same set of two baby seats (Melia baby shell and Maxi-Cosi Pebble Pro baby seat).
+The three-wheeled Keiler sees higher accelerations compared to the two-wheeled Urban Arrow, with a pronounced increase on asphalt and a modest increase on paver bricks.
+%Both vehicles show increasing accelerations with speed.%
+
 %
@@
 
+\subsection{Effect of Stroller Model}
+%
+Figure~\ref{fig:stroller-type-compare} shows the vertical RMS accelerations for
+each road surface for each of the five strollers, lumping seat configurations
+and dummy sizes. The Maxi-Cosi Street Plus and Stokke BABYZEN YOYO 0+ strollers
+have similar mean values. The Bugaboo Fox 5 has a slightly
+lower mean for cobblestones, paver bricks, and sidewalk pavers. The Green
+Machine performs better than the modern strollers on paver bricks, but similarly
+otherwise. The Old Rusty performs better than the modern strollers on all
+surfaces except tarmac. All strollers seem to experience the same acceleration
+on tarmac. %There may be no significant difference in the acceleration experienced in each modern stroller model. 
+All road surfaces compared to tarmac
+at least double the RMS acceleration.
+%
 \begin{figure}
   \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-stroller-type-compare.png}
+  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration per road
+  surface for each stroller. Vertical lines indicate the standard deviation for
+  categories that have more than one repetition.} 
+  \label{fig:stroller-type-compare}
+\end{figure}
+
+\begin{figure}
+  \centering
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-spectra-compare.png}
-  \caption{Mean amplitude spectra of each vehicle.} 
+  \caption{Mean amplitude spectra of each vehicle for strollers on sidewalk pavers (left) and cargo bicycles on paver bricks (right).} 
   \label{fig:spectra-compare}
@@
 %
+Figure~\ref{fig:spectra-compare} shows frequency spectra averaged over body size and posture for all strollers on sidewalk pavers (left) and cargo bicycles on paver bricks.
+These surfaces are highly relevant as they are common in the Netherlands.
+Apparently, the two vintage strollers show a lower peak frequency, which is 4.1 Hz for green machine and 5.6 Hz for old rusty whereas modern systems peak around 7-9 Hz.
+This can be explained by the more compliant suspension of the vintage strollers.
+The old rusty shows the lowest acceleration peak, and the lowest RMS weighted acceleration, but above 30 Hz it shows the highest power of all strollers.
+The Keiler tricycle sees much higher peak values as compared to the Urban Arrow bicycle. In both cargo bicycles peak frequencies range from 6-10 Hz and hardly depend on vehicle and speed.
 Figure~\ref{fig:peak-freq-dist} shows the distributions of dominant (peak)
-frequency compared among road surface types for each of the target speeds. Peak
+frequency across road surface types for each of the target speeds. Peak
 frequencies range from about \SIrange{4}{11}{\hertz} across all trials. For
@@
 sidewalk slabs to cobblestones and sidewalk pavers and then to tarmac and paver
-bricks. The peak frequency median does not correlate sequentially with the
-geometric width of the dimension of the road surface feature. For the cargo
-bicycles, difference in peak frequency between the two road surfaces is not so
-apparent or consistent.
+bricks.
+%The peak frequency median does not correlate sequentially with the geometric width of the dimension of the road surface feature.
+For the cargo bicycles, the difference in peak frequency between the two road surfaces is not so apparent or consistent.
 %
@@
 Figure~\ref{fig:bandwidth-dist} gives a general indication of bandwidth (80\% of
-the amplitude spectrum content) distributions for each of the target speed
-groups. Most frequency content is below 45~\si{\hertz} for all trials. The
-median bandwidth across all trials is 20~\si{\hertz}. For the cargo bicycles,
-the frequency content is spread wider for paver bricks than for tarmac, but for
-strollers there is likely no significant difference in these surfaces. For
-strollers, sidewalk pavers, sidewalk slabs, and cobblestones have similar
-bandwidths. However this is based on the ISO filtering which attenuated the
-higher frequencies. For the tested lying postures this weighting may have to be
-reconsidered, as will be addressed further in the discussion. 
+the amplitude spectrum content) for each of the target speed
+groups.
+On average the bandwidth is 56 Hz for modern strollers, 46 Hz for Green Machine, 105 Hz for Old Rusty, and 44 Hz for cargo bicycles.%Most frequency content is below 45~\si{\hertz} for all trials.
+%The median bandwidth across all trials is 20~\si{\hertz}.
+For the cargo bicycles, the frequency content is spread wider for paver bricks than for tarmac, but for strollers there is likely no significant difference in these surfaces.
+For strollers, sidewalk pavers, sidewalk slabs, and cobblestones have similar bandwidths.
+%However this is based on the ISO filtering which attenuated the higher frequencies.
+For the tested lying postures this weighting may have to be reconsidered, as will be addressed further in the discussion.
 %
@@
 weakness in the ISO recommendations or to other factors affecting cycling
-discomfort (e.g. the ability to stand on the pedals to lower vibration to the
+discomfort (e.g., the ability to stand on the pedals to lower vibration to the
 body and the head).
@@
   bicycle repetitions with colour representing road surface and marker style
-  representing target speed. The horizontal dashed lines with the upper bound of
+  representing the target speed. The horizontal dashed lines with the upper bound of
   the ISO~2631-1 ``comfort zones'' for adults seated erectly experiencing
-  vibrations in public transit. The horizontal dashed dotted line is the
+  vibrations in public transit. The horizontal dashed-dotted line is the
   cyclists' vibration discomfort threshold as reported by
@@
 %
-Table~\ref{tab:stroller-ols} shows the results of the 11 degrees of freedom
-stroller model for the 104 repetitions~(\(R^2=0.867,F=54.69\)). Both categorical
+For strollers, Table~\ref{tab:stroller-ols} shows the results of the 11 degrees of freedom
+statistical model for the 104 repetitions~(\(R^2=0.867,F=54.69\)). Both categorical
 variables have significant effects. The intercept gives the mean acceleration of
@@
   \centering
-  \caption{Ordinary Linear Regression Results for Stroller. Tarmac and Green
-  Machine Cot month are the references for the categorical Road Surface and
+  \caption{Ordinary Linear Regression Results for Strollers. Tarmac and Green
+  Machine (with Cot 0 month) are the references for the categorical Road Surface and
   Stroller variables, respectively. The columns give the effect \(\beta\), standard
-  error, T-statistic, p-value, and the 95\% confidence interval lower and upper
-  bounds.}
+  error, T-statistic, p-value, and the 95\% confidence interval.}
   \label{tab:stroller-ols}
@@
 oldrusty, seat, 9 mo &      -0.7551  &        0.209     &    -3.605  &         0.001        &       -1.171    &       -0.339     \\
-yoyo, cot, 0 mo]     &       0.5766  &        0.209     &     2.753  &         0.007        &        0.161    &        0.993     \\
+yoyo, cot, 0 mo     &       0.5766  &        0.209     &     2.753  &         0.007        &        0.161    &        0.993     \\
 yoyo, seat, 9 mo     &       0.9706  &        0.205     &     4.731  &         0.000        &        0.563    &        1.378     \\
@@
 
-Table~\ref{tab:bicycle-ols} shows the results of the 8 degree of freedom cargo
-bicycle model for the 50 repetitions~(\(R^2=0.925,F=63.17\)). The vehicle setup
+For cargo bicycles, Table~\ref{tab:bicycle-ols} shows the results of the 8 degree of freedom statistical model for the 50 repetitions~(\(R^2=0.925,F=63.17\)). The vehicle setup
 categorical variable has significant effects, the road surface categorical
@@
   \centering
-  \caption{Ordinary Linear Regression Results for Cargo Bicycle. Tarmac and
+  \caption{Ordinary Linear Regression Results for Cargo Bicycles. Tarmac and
   `Keiler, Maxi-Cosi, 3 mo' are the references for the categorical Road Surface
@@
   \(\kappa\), standard error, T-statistic, p-value, and the 95\% confidence
-  interval lower and upper bounds.}
+  interval.}
   \label{tab:bicycle-ols}
@@
 keiler, melia, 3 mo        &      -0.5060  &        0.415     &    -1.219  &         0.230        &       -1.344    &        0.332     \\
-urbanarrow, maxicosi, 0 mo &      -0.0512  &        0.404     &    -0.127  &         0.900        &       -0.867    &        0.764     \\
-urbanarrow, maxicosi, 3 mo &      -0.8895  &        0.415     &    -2.141  &         0.038        &       -1.728    &       -0.051     \\
-urbanarrow, melia, 3 mo    &      -1.1357  &        0.403     &    -2.819  &         0.007        &       -1.949    &       -0.322     \\
+urban arrow, maxicosi, 0 mo &      -0.0512  &        0.404     &    -0.127  &         0.900        &       -0.867    &        0.764     \\
+urban arrow, maxicosi, 3 mo &      -0.8895  &        0.415     &    -2.141  &         0.038        &       -1.728    &       -0.051     \\
+urban arrow, melia, 3 mo    &      -1.1357  &        0.403     &    -2.819  &         0.007        &       -1.949    &       -0.322     \\
 Mean Speed [m/s]                                                                              &       0.2034  &        0.116     &     1.747  &         0.088        &       -0.032    &        0.439     \\
@@
 Given that the vehicle setup (\(x_\textrm{Stroller}\) and \(x_\textrm{Cargo
-Bicycle}\)) is a significant effect, we perform a post-hoc analysis to compare
+Bicycle}\)) has a significant effect, we perform a post-hoc analysis to compare
 vehicles on each road surface. Table~\ref{tab:sig-group-stroller}, derived from
@@
 For cobblestones, this is also true as well as: 1) the `YOYO, Seat, 9 mo' is the
-worst stroller tested and, interestingly, the the heavier dummy performs worse
-than the lighter dummy, 2) the 9 mo dummy experiences less acceleration in the
+worst stroller tested and, interestingly, the heavier dummy performs worse
+than the lighter one, 2) the 9 mo dummy experiences less acceleration in the
 Bugaboo and Maxi-Cosi.
@@
 difference in any vehicle setups at low speed on paver bricks. At higher speeds,
-the Urban Arrow and Keiler with the Meila seat and the 3 mo dummy is
+the Urban Arrow and Keiler with the Meila seat and the 3 mo dummy are
 significantly better than the Keiler with the Maxicosi and the 0 mo on paver
@@
      \midrule
-     urbanarrow, melia, 3 mo    & 1 & 1-6 & 1-5 & 1-5 & 1-5\\
-     urbanarrow, maxicosi, 3 mo & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
-     urbanarrow, maxicosi, 0 mo & 4 & 1-6 & 1-6 & 1-6 & 1-5\\
+     urban arrow, melia, 3 mo    & 1 & 1-6 & 1-5 & 1-5 & 1-5\\
+     urban arrow, maxicosi, 3 mo & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
+     urban arrow, maxicosi, 0 mo & 4 & 1-6 & 1-6 & 1-6 & 1-5\\
      keiler, melia, 3 mo        & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
@@
 We have presented a comprehensive set of acceleration measurements from
-experiments that simulate the vibrations experienced by dummy infants in the 0-9
-month mass range during transportation in both strollers and cargo bicycles. We
+experiments that simulate vibrations experienced by infants in the 0-9
+month mass range during transportation in strollers and cargo bicycles. We
 compared the average magnitude of vertical and total acceleration at the seat
-pan across a variety of road surfaces and seats while moving at typical vehicle
-travel speeds. Excluding the shock tests, ISO~2631-1 weighted average
+pan across a variety of road surfaces and seats at typical 
+travel speeds. ISO~2631-1 weighted average
 acceleration can range from \SIrange{0.4}{10.7}{\mps\squared} across all tested
-scenarios. Strollers induced \SIrange{0.4}{5.0}{\mps\squared} average
-acceleration for a mean walking speed of 5.3~\si{\kph}. Cargo bicycles induced
+scenarios. Strollers induced \SIrange{0.4}{5.0}{\mps\squared}  for a mean walking speed of 5.3~\si{\kph}. Cargo bicycles induced
 \SIrange{0.6}{10.7}{\mps\squared} over a speed range of \SIrange{12}{25}{\kph}.
@@
 %
-Travelling over a tarmac surface offers the least vibration to all vehicle types
+Travelling over a tarmac surface offers the least vibration in all vehicle types
 at any speed with a maximum average acceleration of
-1.2~\si{\meter\per\second\squared}. For strollers, travelling over surfaces
-rougher than tarmac at normal walking speed can cause, on average, 5\(\times\)
-the acceleration experienced on tarmac with average accelerations reaching
-5.0~\si{\meter\per\second\squared}. Cobblestones and the large gaps in the
-sidewalk slabs caused the largest magnitude of vibrations at the seat pan in the
-strollers. Cobblestones and sidewalk slabs approximately double the vibration
-amplitude relative to sidewalk paver and paver bricks, with them all being
-significant larger than tarmac vibrations.
+1.2~\si{\meter\per\second\squared}. For strollers, the roughest surfaces being cobblestones and the sidewalk slabs with large gaps cause 5\(\times\) the acceleration experienced on tarmac reaching
+5.0~\si{\meter\per\second\squared}. More common surfaces being sidewalk pavers and paver bricks, reach values up 3~\si{\meter\per\second\squared}.
 
 For cargo bicycles, travelling over paver bricks at the same speeds can
-quadruple the magnitude of the average acceleration the dummy experiences.
+quadruple accelerations relative to asphalt.
 Travelling at the maximum allowed speed of an electric cargo bicycle (25
-\si{\kph}) over paver bricks caused the dummy to experience average
-accelerations exceeding 8~\si{\mps\squared}. The effect of speed on vibration is
-significant for paver bricks but not for tarmac.
+\si{\kph}) over paver bricks caused average
+accelerations exceeding 8~\si{\mps\squared}. %The effect of speed on vibration is significant for paver bricks but not for tarmac.
 
@@
 The size of the dummy (mass and build) had no obvious and systematic effect on
-the average acceleration at the seat pan body-seat interface. These vibrations
-are transmitted to an infant's body and the physical properties (mass,
-stiffness, damping) of the infant's body determine whether this excitation is
+the average acceleration at the seat pan to body interface. These vibrations
+are transmitted to an infant's body, and the physical properties (mass,
+stiffness, and damping) of the infant's body determine whether this excitation is
 amplified or not and which body segment is more affected. Tests with more
@@
 The most used health and comfort assessment tool for whole-body vibration is the
-ISO~2631-1 standard. When we investigated health risks using the standard we
+ISO~2631-1 standard. When we investigated health risks using the standard, we
 found that:
@@
 %
-When we compare the vibration we measured for infants in strollers and cargo
+When we compare the vibration measured for infants in strollers and cargo
 bicycles with the vibration ``health risk zone'' as defined for adults in the
@@
 We can conclude that strollers can be pushed over paver bricks and sidewalk
-pavers continuously for maximal about half an hour. On extreme surfaces like
+pavers continuously for no more than half an hour. On extreme surfaces like
 cobblestones and sidewalk slabs, strollers should be pushed slower than
-5~\si{\kph} with a duration of maximal 10~\si{\min}. Only on tarmac a stroller
-can be walked continuously for four hours (but only if the infant is in the cot,
-for if it is sitting it needs appropriate breaks to enable movement). Cargo
+5~\si{\kph} with a duration of maximal 10~\si{\min}. A stroller
+can be walked continuously for four hours only on tarmac, and only if the infant is lying in the cot.
+If the infant is sitting, the parent/caregiver would need to consider appropriate breaks to allow the infant to move. Cargo
 bicycles carrying infants over paver bricks should slow down to 12~\si{\kph} or
-preferably less and the duration should be kept under 10~\si{\min}. When riding
+preferably less, and the duration should be kept under 10~\si{\min}. When riding
 a cargo bicycle over tarmac at 20\si{\kph}, the duration should be kept under
-1~\si{\hour}. At 12~\si{\kph} cargo bicycles can ride over tarmac for maximal
+1~\si{\hour}. At 12~\si{\kph}, cargo bicycles can ride over tarmac for maximal
 2~\si{\hour}.
@@
 subjective ratings of vibrations felt when riding public transit for an
-unspecified duration, so this scale is unlikely appropriate to apply for our
-situation. Gao~et~al.~\cite{Gao2018} reports that cyclists do not rate
+unspecified duration, so this scale is unlikely to be appropriate to apply to our
+situation. Gao~et~al.~\cite{Gao2018} report that cyclists do not rate
 vibrations as extremely uncomfortable on normal road surfaces, indicating some
@@
 vertical accelerations at the seat pan. We are only able to compare vehicle
-setup to vehicle setup, other than comparing the same two different baby seats
-in both cargo bikes. A striking discovery is that the two 1970's strollers we
+setups, other than comparing the same two different baby seats
+in both cargo bicycles. A striking discovery is that the two 1970s strollers we
 tested were significantly better than many of the modern stroller setups on most
@@
 wheels (which makes steering lighter but can technically not be combined with
-the design of old suspension types). As an example, the ``Old Rusty'' stroller
+the design of vintage suspension types). As an example, the ``Old Rusty'' stroller
 was the only one that did not exceed the 1~\si{\hour} health risk line for all
@@
 a vehicle setup is not necessarily constant with respect to cot or seat
-configuration, contrarily, performance is often significantly different when
+configuration; contrarily, performance is often significantly different when
 converting for different baby ages. This points towards designs that are only
@@
 
-\subsection{ISO Filters and Bandwidth}
-%
-We report RMS accelerations up to 120~\si{\hertz} Hz as well as accelerations
+\subsection{ISO Frequency Weighting and Bandwidth}
+%
+We report RMS accelerations as well as accelerations
 weighted according to the ISO standards for vibration (VDV). Vibrations at
 frequencies between \SIrange{4.9}{10.7}{\hertz} showed to have the largest
-magnitude contribution to the vibrations, but there is a frequency content of
-magnitudes of interest in a bandwidth of up to 45~\si{\hertz}. Our results show
-substantial differences between RMS and VDV highlighting the importance of
+magnitude, but there are substantial accelerations at higher frequencies. Our results show
+substantial differences between RMS and VDV, highlighting the importance of
 reviewing their meaning. These differences emerge from the high bandwidth of the
@@
 ISO~2631-1 weightings represent a reduced sensitivity above 8~\si{\hertz}, which
-is associated with the vertical dynamics of erect seated subjects which filter
+is associated with the vertical dynamics of erect seated subjects, and filter
 out such high frequencies \cite{toward2011transmission,mirakhorlo2022effects}.
@@
 8~\si{\hertz} when lying with head supported with \SIrange{30}{90}{\degree} back
-inclination as compared to erect without head support. Higher frequencies have
+inclination as compared to erect without head support \cite{BASRI2013inclined}. Higher frequencies have
 also been associated with effects on the central nervous system. For instance,
@@
 In some conditions, the RMS exceeds the ISO Weighted RMS substantially,
-warranting further research on the effects of higher frequencies in particular
-for head supported conditions and for children. The VDV showed even higher
-values warranting further research on the relevance of peaks and transients.
+warranting further research on the effects of higher frequencies, in particular
+for head supported conditions, and for children.
+Meanwhile, a conservative approach is to (also) consider the unweighted RMS in the design and evaluation of transport means for very young children.
+%The VDV showed even higher values warranting further research on the relevance of peaks and transients.
 
@@
 cargo bicycles. If the user's behaviour is not adjusted to avoid rough surfaces
-or to go very slow over them when the cargo is an infant, there are potential
-health risks if the large vibrations are experienced daily and repeatedly over a
-longer time. In most likelihood, users do adjust their travel behaviour, but
-maybe not enough or possibly they are neglectful, but this has yet to be
-studied. There is no direct evidence that connects whole-body vibration as
-measured in this study to infant harm or negative health effects, so we can only
-extrapolate from the limited guidelines on adults in occupational settings. But
-we did measure vibrations that would not be permitted for adults to maintain
-long term occupational health and it is reasonable to believe we should not
+or to travel very slowly over them when transporting an infant, there are potential
+health risks from daily and repeated exposure to large vibrations over a
+longer time. However, this has yet to be studied. There is no direct evidence that connects whole-body vibration as
+measured in this study to infant harm or negative health effects, thus we can only
+extrapolate from the limited guidelines on adults in occupational settings. We did measure vibrations that would not be permitted for adults to maintain
+long-term occupational health, and it is reasonable to believe we should not
 subject our infants to the same.
@@
 in automobiles. We do not see this same kind of attention to suspension in
-strollers, cargo bicycles, and baby seats for these vehicles. Walking and
-cycling is well known to offer great societal and personal benefits over
-travelling by car, so it behoves us all to make transport for infants most
-optimal in these two transport modes.
+strollers, cargo bicycles, and baby seats for these vehicles. Both walking and
+cycling are well known to offer great societal and personal benefits over
+travelling by car, so it behoves us all to make transport for infants
+optimal in these two modes of transportation.
 
@@
 Our conclusions result primarily from the recommended application of ISO~2631-1.
-It is of utmost importance to recognize that this standard cautions extending
-the use of the standard to situations of which its supporting data was not
+It is of utmost importance to recognize that this standard cautions against extending
+the use of the standard to situations for which its supporting data was not
 derived. The standard is based primarily on pre-1997 studies of adult whole-body
@@
   \textbf{The recommendations in standard ISO~2631-1 have not been based on or
-  validated for infants, children, or young adults nor for recumbent or reclined
+  validated for infants, children, or young adults, nor for recumbent or reclined
   seating postures with the head supported. Additionally, the admissible
@@
     When transporting over tarmac, continuous durations should not exceed
-    4~hours and need to include regular breaks, if only to give the infant
-    opportunity to move.
+    4 hours, and need to include regular breaks, if only to give the infant
+    an opportunity to move.
     \item Preferably ride any cargo bicycle at a speed of maximal 12~\si{\kph}
@@
 
-\section{Exploratory Statistics}
+\section{Additional Exploratory Statistics}
+\subsection{Effect of Speed}
+%
+Figure~\ref{fig:compare-bicycle-speed} shows the variation in ISO~2631-1 weighted vertical RMS acceleration across the tested speeds. Paver bricks result in about  4-5\(\times\) higher
+accelerations compared to tarmac. On paver bricks, the RMS acceleration
+increased by about 1.6\(\times\) when increasing the speed from
+\SIrange{12}{25}{\kilo\meter\per\hour}. The effect of speed while cycling over
+tarmac was less drastic, but also shows a slight increase.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-speed-compare.png}
+  \caption{Seat pan ISO 2631-1 weighted vertical acceleration RMS versus speed
+  for all cargo bicycle repetitions. Shaded regions represent the 95\%
+  confidence intervals from a simple linear regression that ignores
+  \(x_\textrm{Cargo Bicycle}\).}
+  \label{fig:compare-bicycle-speed}
+\end{figure}
 %
@@
 acceleration for each repetition for all vehicles, comparing among dummy sizes.
-There were larger accelerations in the bicycle (high speeds) versus the stroller
-(low speeds), likely mostly attributed to the different testing speeds. When
-comparing the vertical RMS acceleration values between cargo bicycles and
+The substantial variation has been shown to relate significantly to surface and within cargo bicycles also to speed (see tables \ref{tab:sig-group-stroller},\ref{tab:sig-group-bicycle}).
+%There were larger accelerations in the bicycle (high speeds) versus the stroller (low speeds), likely mostly attributed to the different testing speeds. 
+When comparing the vertical RMS acceleration values between cargo bicycles and
 strollers there are no obvious differences due to baby size, i.e. each dummy
@@
   baby age (and thus size \& mass) for all repetitions with colour indicating
-  the mean speed of the trial. The lightest colour dots are strollers and the
-  remaining are cargo bicycles.}
+  the mean speed of the trial. The lightest colour dots are strollers (4 km/h) and the
+  remaining are cargo bicycles (8-24 km/h).}
   \label{fig:compare-baby-mass}
@@
   road surface with colour indicating the mean speed of the repetition. The
-  lightest colour dots are strollers and the rest are cargo bicycles.}
+  lightest colour dots are strollers (4 km/h), and the rest are cargo bicycles (8-24 km/h).}
   \label{fig:compare-road-surface}
@@
 \label{app:equipment}
+ The following lists the dummies used:
+%
+\begin{description}
+  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
+  ``Andi Asleep'' (product code AW380008).
+  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
+
+  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
+  ``Asia - Limited Edition'' (product code 300287).
+  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
+  \item[Dummy 9 months] weight 8.90~\si{\kg}, size 70~\si{\cm}. Dollkit 28'',
+  ``Hailey'' (product code 304137).
+  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
+\end{description}
 %
@@
 
+\begin{description}
+\item[Strollers] A selection of vintage and modern strollers for carrying
+infants. The modern strollers are configurable as cots for newborns and as seats
+for older infants.
+%
+\begin{description}
+  \item[Maxi-Cosi Street Plus] This stroller comes with a cot configuration (0-6
+  months) and an infant seat option. It has large wheels with only a marginal suspension system.
+  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
+  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the market. It has only a marginal suspension system and smaller wheels compared to other strollers available on the market.
+  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
+  rented for the experiment})
+  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system that makes
+  it an all-terrain stroller according to the manufacturer. It has large
+  puncture-resistant tyres and an air-permeable mattress.
+  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
+  website})
+  \item[Green Machine] An unknown brand vintage perambulator with a cot, dating
+  approximately from the 1970s that includes a leather strap suspended cot in a
+  metal frame. The wheels are relatively large compared to modern strollers.
+  \item[Old Rusty] An unknown brand vintage seat-style stroller dating approximately from the 1970s that includes a metal spring suspension system and wheels that are slightly larger than those on modern strollers.
+\end{description}
+\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
+seats can be mounted.
+%
+\begin{description}
+  \item[Urban Arrow Cargo Bicycle] An electric cargo bicycle that is popular in The Netherlands.
+This vehicle has two inline wheels, which makes it roll into curves like a regular bicycle.
+It is featured by a long frame that can carry loads (e.g., a child in a car seat or a baby shell) placed in between the rider and the front wheel.
+  (\href{https://urban arrow.com/}{Urban Arrow website})
+  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
+  rear) cargo tricycle without electric assist. This vehicle will not roll into
+  curves. However, differing road surface unevenness at the left and right front
+  wheels will induce lateral roll and lateral acceleration in infants. We added
+  masses in specific locations to simulate the presence of an electric motor and
+  battery package, in order to compare the results with those of the Urban Arrow cargo bike. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
+  Webpage}) 
+\end{description}
+\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
+cargo bicycles.
+%
+\begin{description}
+  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
+  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
+  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
+  adapter was used in both cargo bicycles.
+    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
+    Webpage})
+  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
+  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
+  cargo bicycles.
+    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
+    Webpage})
+\end{description}
+\end{description}
 \begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_GreenM0_front.pdf}}
-  \caption{IMU locations on the old stroller Green Machine, configured for 0-months baby.}
+  \caption{IMU locations on the vintage stroller Green Machine, configured for 0-months baby.}
   \label{fig:tech_drawing_GreenM0}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_OldR9_front.pdf}}
-  \caption{IMU locations on the old stroller Old Rusty, configured for 9-months baby.}
+  \caption{IMU locations on the vintage stroller Old Rusty, configured for 9-months baby.}
   \label{fig:tech_drawing_OldR9}
@@
 
-\subsection{Location and pictures of the experiment areas}
+\section{Location and pictures of the experiment areas}
 \label{app:location}
 
-\subsubsection{For Bicycles}
+\subsection{For Bicycles}
 
@@
 
-\subsubsection{For Strollers}
+\subsection{For Strollers}
 
@@
 \newpage
-\section{Table of Repetition Metrics}
+\section{Table of Metrics - move to main text?}
 \label{app:results}
@@
 acceleration, unweighted seat pan vertical VDV for the first 10 seconds of the
-reptition, crest factor, peak frequency, bandwidth, and duration for all 67
+repetition, crest factor, peak frequency, bandwidth, and duration for all 67
 combinations of vehicle setup, road surface, and target speed.
@@
 \cline{1-13} \cline{2-13} \cline{3-13}
-\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 3 & 6.5 & 5.7 & 5.7 & 26.1 & 9.6 & 7.6 & 58.5 & 20.8 \\
+\multirow[t]{15}{*}{urban arrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 3 & 6.5 & 5.7 & 5.7 & 26.1 & 9.6 & 7.6 & 58.5 & 20.8 \\
  &  &  & 20 & 1 & 9.2 & 8.5 & 8.6 & 15.5 & 9.9 & 8.0 & 53.1 & 39.1 \\
@@
 those experienced with the bicycles, the configuration (0 or 9 months) may play
-a large role. Among bicycles, the use of Melia baby shell seems to transmit
+a large role. Among bicycles, the Melia baby shell seems to transmit
 lower accelerations compared to Maxi-Cosi, 3 months, for both the Keiler
@@
 months show much lower acceleration compared to the baby cot for 0 months
-(Bugaboo and Maxi-Cosi). Surprisingly, the oldest strollers (Old Rusty and Green
+(Bugaboo and Maxi-Cosi). Surprisingly, the vintage strollers (Old Rusty and Green
 Machine) performed very well during the shock test, resulting in the lowest seat
@@
 acceleration recorded at the seat pan, grouped by different vehicles, for the
-shock test. As noted in Table~\ref{tab:shock}, the old strollers Old Rusty and
+shock test. As noted in Table~\ref{tab:shock}, the vintage strollers Old Rusty and
 Green Machine show lower acceleration values. We do not clearly distinguish any
@@
   \label{fig:shock_vehicle_comparison}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-maxicosi-0-SeatBotacc_ver-rep0.png}
+  \caption{Raw seat pan vertical acceleration versus time from session 015:
+  Keiler tricycle during the shock test.}
+  \label{fig:shock_time-history}
 \end{figure}
@@
 
-\subsection{Future Work}
+\section{Future Work - can be one of the first appendices}
 % 
@@
 not tested. Investigating this is important because we expect that vibrations
-when running may quickly exceed health limits. In addition, recumbent posture in
-sports strollers is estimated to increase the vibration load on the head of the
+when running may quickly exceed health limits. In addition, recumbent postures in
+sports strollers are estimated to increase the vibration load on the head of the
 infant. It is important to establish the actual vibration load on the head in
@@
 %
-At this moment, no requirements are made for the vibrational properties of child
+At this moment, no requirements exist for the vibrational properties of child
 transport systems in the standards for strollers, cargo bicycles, bicycle seats,
@@
 transport, it is imperative to include a requirement to the vibrational
-properties in the standards for these products. At this moment, no new
-requirements can be defined because there is not enough information. With the
-information resulting from more research on infant vibration, a benchmark for
-the vibration properties of infant transportation products needs to be
-developed. This will enable the inclusion of minimal requirements for vibration
+properties in the standards for these products.
+%At this moment, no new requirements can be defined because there is not enough information.
+With the information resulting from more research on infant vibration, a benchmark for the vibration properties of infant transportation products needs to be developed.
+Tests as performed in this study, could serve as a first basis.
+Road surfaces, speeds, dummies, posture and metrics could be standardized.
+Over the years these could be refined building upon scientific research.
+Acceptance thresholds could be set to accept well performing current products.
+This will enable the inclusion of (minimal) requirements for vibration
 properties in the standards, which would greatly increase the health and comfort

### 2025-09-18 src/website.py
Change comfort plots y axis label to state magnitude RMS.

@@ -484,7 +484,7 @@ p.set_xticks(p.get_xticks())
 p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
                    p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
-p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
+p.set_ylabel(r'Acceleration Magnitude RMS [m/s$^2$]')
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, 1.1*MAXWIDTH*MM2INCH))
 p.figure.set_layout_engine('constrained')
 fname = '{}-rms-comfort-stroller-compare-all.png'.format(SIGNAL)
@@ -492,9 +492,9 @@ p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
 plt.clf()
 boxp_html.append(IMG.format('', fname) + '\n</br>')
 
-###################################################################
-# Figure: Health ISO Weighted RMS Cargo Bicycle Trials Scatter Plot
-###################################################################
+####################################################################
+# Figure: Comfort ISO Weighted RMS Cargo Bicycle Trials Scatter Plot
+####################################################################
 boxp_html.append(
     H2.format(f'Cargo Bicycle ISO Weighted RMS {SIGNAL} Comparison'))
 msg = """"""
@@ -533,7 +533,7 @@ p.set_xticks(p.get_xticks())
 p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
                    p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
-p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
+p.set_ylabel(r'Acceleration Magnitude RMS [m/s$^2$]')
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*MM2INCH))
 p.figure.set_layout_engine('constrained')
 fname = '{}-rms-comfort-bicycle-compare-all.png'.format(SIGNAL)

### 2025-09-18 src/website.py
Adjsuted custom legend placement.

@@ -468,7 +468,7 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
                     rotation=90,
                     arrowprops=dict(facecolor='tab:grey', width=2.0,
                                     headwidth=0.0))
-p.axes.text(8.3, 3.5, 'ISO 2631-1 Adult\nPublic Transit Rating',
+p.axes.text(8.3, 3.6, 'ISO 2631-1 Adult\nPublic Transit Rating',
             color='tab:grey')
 p.axes.axhline(GAO_ACC_ACCEPTANCE, linestyle='-.', color='tab:grey')
 p.axes.annotate('→ ' + "Cyclists' Discomfort\n     Threshold (Gao 2018)",
@@ -485,7 +485,7 @@ p.set_xticklabels([lab.get_text().replace(', ', ',\n', count=1) for lab in
                    p.get_xticklabels()], rotation=90)
 sns.move_legend(p, "upper left", bbox_to_anchor=(1, 1))
 p.set_ylabel(r'Acceleration Magnitude RMS [m/s$^2$]')
-p.figure.set_size_inches((MAXWIDTH*MM2INCH, 1.1*MAXWIDTH*MM2INCH))
+p.figure.set_size_inches((MAXWIDTH*MM2INCH, 1.2*MAXWIDTH*MM2INCH))
 p.figure.set_layout_engine('constrained')
 fname = '{}-rms-comfort-stroller-compare-all.png'.format(SIGNAL)
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
@@ -517,7 +517,7 @@ for i, (low, high, note) in enumerate(COMFORT_BOUNDS):
                     rotation=90,
                     arrowprops=dict(facecolor='tab:grey', width=2.0,
                                     headwidth=0.0))
-p.axes.text(6.0, 5.8, 'ISO 2631-1 Adult\nPublic Transit Rating',
+p.axes.text(6.0, 6.0, 'ISO 2631-1 Adult\nPublic Transit Rating',
             color='tab:grey')
 p.axes.axhline(GAO_ACC_ACCEPTANCE, linestyle='-.', color='tab:grey')
 p.axes.annotate('→ ' + "Cyclists' Discomfort\n     Threshold (Gao 2018)",

### 2025-09-18 src/website.py
Rename the maxicosi seat to pebble.

@@ -181,7 +181,7 @@ with open(os.path.join(PATH_TO_TABLE_DIR,
 f = (f"{SIGNAL_RMS_ISO} ~ "
      "Q('Mean Speed [m/s]') * "
      "C(Q('Road Surface'), Treatment('Tarmac')) + "
-     "C(Q('Vehicle, Seat, Baby Age'), Treatment('keiler, maxicosi, 3 mo'))")
+     "C(Q('Vehicle, Seat, Baby Age'), Treatment('keiler, pebble, 3 mo'))")
 mod = smf.ols(formula=f, data=bicycle_df)
 bicycle_res = mod.fit()
 print_header("Bicycle OLS Results (Vertical ISO Weigthed RMS)")

### 2025-09-18 src/website.py
Changed vehicle name from yoyo to stokke.

@@ -267,7 +267,7 @@ axes[1, 0].remove()
 strol_ax = fig.add_subplot(gs[:, 0])
 surf_select = stroller_df['Road Surface'] == 'Sidewalk Pavers'
 freq = stroller_df.loc[50, 'Frequency Array']
-for vehicle in ['bugaboo', 'greenmachine', 'maxicosi', 'oldrusty', 'yoyo']:
+for vehicle in ['bugaboo', 'greenmachine', 'maxicosi', 'oldrusty', 'stokke']:
     vehi_select = stroller_df['Vehicle'] == vehicle
     mean_amp = stroller_df.loc[surf_select & vehi_select,
                                'Amplitude Array'].mean()

### 2025-09-19 src/website.py
Remove lines in the stroller comparison plot.

@@ -862,12 +862,14 @@ p = sns.pointplot(
     y=SIGNAL_RMS_ISO,
     hue='Vehicle',
     dodge=True,
+    linestyle="none",
     order=sorted(stroller_df['Road Surface'].unique()),
     hue_order=sorted(stroller_df['Vehicle'].unique()),
 )
 p.set_ylabel(r'Vertical Acceleration RMS [m/s$^2$]')
 p.set_xticks(p.get_xticks())
 p.set_xticklabels(p.get_xticklabels(), rotation=30)
+plt.setp(p.get_legend().get_texts(), fontsize='9')
 fname = '{}-stroller-type-compare.png'.format(SIGNAL)
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, 100*MM2INCH))
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)

### 2025-09-19 src/website.py
Decrease legend font size in spectra metric summary figures.

@@ -667,6 +667,7 @@ p.figure.set_layout_engine('constrained')
 p.axvline(0.5, color='gray')
 p.axvline(1.5, color='gray')
 p.axvline(2.5, color='gray')
+plt.setp(p.get_legend().get_texts(), fontsize='9')
 fname = '{}-peak-freq-dist.png'.format(SIGNAL)
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
 plt.clf()
@@ -695,6 +696,7 @@ p.figure.set_layout_engine('constrained')
 p.axvline(0.5, color='gray')
 p.axvline(1.5, color='gray')
 p.axvline(2.5, color='gray')
+plt.setp(p.get_legend().get_texts(), fontsize='9')
 fname = '{}-bandwidth-dist.png'.format(SIGNAL)
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
 plt.clf()

### 2025-09-20 src/website.py
Change to the seaborn colorblind palette.

@@ -40,6 +40,7 @@ COMFORT_BOUNDS = (
 GAO_ACC_ACCEPTANCE = 2.54  # m/s/s
 
 sns.set_theme(style='whitegrid')
+sns.set_palette('colorblind')
 
 try:
     githash = subprocess.check_output([
@@ -664,9 +665,9 @@ p.set_xticklabels([veh + ' @ ' + lab.get_text() for lab, veh in
                                              'Bicycles', 'Bicycles'])])
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*2/3*MM2INCH))
 p.figure.set_layout_engine('constrained')
-p.axvline(0.5, color='gray')
-p.axvline(1.5, color='gray')
-p.axvline(2.5, color='gray')
+p.axvline(0.5, color='tab:grey')
+p.axvline(1.5, color='tab:grey')
+p.axvline(2.5, color='tab:grey')
 plt.setp(p.get_legend().get_texts(), fontsize='9')
 fname = '{}-peak-freq-dist.png'.format(SIGNAL)
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
@@ -693,9 +694,9 @@ p.set_xticklabels([veh + ' @ ' + lab.get_text() for lab, veh in
                                              'Bicycles', 'Bicycles'])])
 p.figure.set_size_inches((MAXWIDTH*MM2INCH, MAXWIDTH*2/3*MM2INCH))
 p.figure.set_layout_engine('constrained')
-p.axvline(0.5, color='gray')
-p.axvline(1.5, color='gray')
-p.axvline(2.5, color='gray')
+p.axvline(0.5, color='tab:grey')
+p.axvline(1.5, color='tab:grey')
+p.axvline(2.5, color='tab:grey')
 plt.setp(p.get_legend().get_texts(), fontsize='9')
 fname = '{}-bandwidth-dist.png'.format(SIGNAL)
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
@@ -706,8 +707,8 @@ boxp_html.append(IMG.format('', fname) + '\n</br>')
 # Figure: Cargo Bicycles vs Speed
 #################################
 boxp_html.append(H2.format('Cargo Bicycle Speed Comparison'))
-msg = f"""How does vibration vary across speed for the cargo bicycles? This plot
-shows a linear regression of ISO weighted {SIGNAL} versus speed for both
[…]

### 2025-09-20 src/website.py
Use default palette for all plots.

@@ -772,7 +772,6 @@ p = sns.catplot(
     col='Road Surface',
     col_wrap=2,
     kind='strip',
-    palette='deep',
     sharex=False,
     sharey=False,
     size=10,
@@ -798,7 +797,6 @@ p = sns.catplot(
     hue="Seat, Baby",
     col='Road Surface',
     kind='strip',
-    palette='deep',
     sharex=False,
     sharey=False,
     size=10,

### 2025-09-20 main.tex
Version of paper text just after Jason reviewed entirety after last comments from co-authors before journal submission.

@@
 % - use the oxford comma
-% - TODO: acceleration vs accelerations ?
+% - TODO: acceleration vs accelerations?
 % - Data breakdown terms are "Session", "Trial" (of specific "Scenario"),
@@
 }
-% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
+
 \author{
@@
 %
-This draft report is not yet peer-reviewed and is subject to change with
-revisions. These results are preliminary, so we do not recommend relying on them
-until a supporting peer-reviewed paper is published.
+\begin{center}
+  This paper has been submitted for peer review and is subject to change with
+  revisions.
+\end{center}
 
@@
 \begin{abstract}
-  Infants transported in strollers and cargo bicycles experience whole-body vibrations.
-Only little information was found on  these vibrations and the associated comfort and health effects on infants.
-To improve this, we measure the acceleration of  the seat pan of five strollers and two styles of cargo bicycles with dummy infants representing ages 0 to 9 months over six different road surfaces of varying road roughness, at typical travel speeds.
-The five strollers included three modern systems and two vintage systems, all with some level of suspension.
-One cargo bicycle had electric support that enabled speeds up to 25~\si{\kph}.
-We report average seat pan acceleration for 78 different scenarios and investigate the effects of road surface, vehicle, seat type, and travel speed.
-Using the ISO standard for whole-body vibration, we show that rough road surfaces, amplified by travel speed, may have health risks for travel durations as low as \SIrange{10}{30}{\min}.
-Vintage stroller designs from 50 years ago significantly reduce vibrations compared to  modern strollers tested, indicating the need to return to better suspensions.
-Cargo bicycles ridden over paver bricks at the maximum speed of an electric bicycle can cause accelerations that should likely be avoided, except for the shortest of durations, until more direct evidence of risks to infants is studied.
-Vibration standards are needed for infant transport testing and evaluation, designers need to incorporate better suspension for infants, and research is needed to develop clear and direct connections to health and comfort effects.
+  % NOTE: keep to 150 words max
+  We evaluated road-induced vibrations with dummies representing infants aged 0,
+  3, and 9 months with five strollers and two cargo bicycles on six common road
+  surfaces using the ISO standard for whole-body vibration. Strollers induced on
+  average 0.4~\si{\mps\squared} on tarmac and up to 5.0~\si{\mps\squared} on
+  cobblestones at a mean walking speed of 5.3~\si{\kph}. Cargo bicycles induced
+  induced as low as 0.6~\si{\mps\squared} on tarmac and up to
+  10.7~\si{\mps\squared} at 25~\si{\kph} on paver bricks. The standard suggests
+  that the highest accelerations for the strollers and cargo bicycles should be
+  limited to continuous duration less than 10~\si{\minute}. Effects of body size
+  and posture were minor. Two vintage stroller designs significantly reduced
+  vibrations compared to three modern strollers, indicating the benefits of
+  compliant suspensions. 
 \end{abstract}
 
+\section*{Keywords}
+%
+whole-body vibration, infant, bicycle, stroller, ISO
+
 \newpage
@@
 \section{Introduction}
-%Paragraph to introduce baby transport
-When a baby is born, it is not able to walk and must
-be either carried by adults or transported in suitable wheeled
-transport. Until about a century ago,  babies mainly stayed at home, which is still customary in some non-Western cultures. A century ago, perambulators were
-used to transport infants outdoors. However, mothers were advised that a playpen
-in the garden is healthier than the use of perambulators, partly because vibrations generated by a perambulator were deemed not comfortable and even
-harmful for babies~\cite{behrend1931}, even though in those days perambulators had ample suspension. Since about 1970, cars became ubiquitous, and the heavy and
-sizeable perambulators became strollers: lighter and smaller products foldable for
-easy transportation in cars. Over the years, new means of transportation came
-into use for infants: child safety seats to use in cars, bicycles with child seats
+% Paragraph to introduce baby transport
+When a baby is born, it is not able to walk and must be carried by others or
+transported in a suitable wheeled transport. Until about a century ago, babies
+were mainly kept at home, which is still customary in some non-western cultures.
+More than a century ago, perambulators were introduced to transport infants
+outdoors. However, mothers were advised that a playpen in the garden is
+healthier than the use of perambulators, in part because vibrations generated by
+a perambulator were deemed not comfortable and even harmful to
+babies~\cite{behrend1931}, even though in those days perambulators had ample
+suspension. Since about 1970, cars became ubiquitous and the heavy and sizeable
+perambulators became strollers: lighter and smaller products foldable for easy
+transportation in cars. Over the years, new means of transportation came into
+use for infants: child safety seats to use in cars, bicycles with child seats,
 and cargo bicycles with child seats or baby shells.
@@
 %Paragraph to introduce baby vibration in transportation
-All means of transport cause vibration, which is transferred to the sitting or lying infant. Unlike the advice in the 1930s, vibration is seemingly
-not a subject of attention in the present design of these products.
-On the contrary, modern strollers do not have much suspension, and (electric) cargo bicycles are increasingly used for infants with seats that offer marginal suspension or padding.
-We thoroughly reviewed the literature, but found very little about the maximal vibration load that babies and older children can receive during transport without discomfort or harm, and vibrations generated by infant transport are only sparsely investigated.
-%Therefore the effect of transport on infant comfort and health can not easily be assessed. 
-To establish the amount of vibration to which infants are subjected in
-transportation products, we investigated the vibration that infants receive
-during transport in strollers and cargo bicycles.
+All means of transport cause vibration, which is transferred to the sitting or
+lying infant. Unlike the advice in the 1930's, vibration is seemingly not a
+subject of attention in the present design of these products. On the contrary;
+modern strollers do not have much suspension, and (electric) cargo bicycles are
+increasingly used for infants with seats that offer marginal suspension or
+padding. We thoroughly reviewed the literature, but found very little about the
+maximal vibration load that babies and older children can receive during
+transport without discomfort or harm, and vibrations generated by infant
+transport are only sparsely investigated. To establish the amount of vibration
+to which infants are subjected in transportation products, we measured seat pan
+vibrations while transporting infant dummies in strollers and cargo bicycles
+with a focus on potential health risks and discomfort.
 
 % Paragraph about motivation
-Research on vibration comfort during cycling is a logical starting point for investigating similar road-induced vibrations for infants. Cycling is beneficial for
-health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\) emissions, congestion, and air pollution~\cite{Neves2019}. As a result, bicycles are
-increasingly being used to deliver goods, for daily
-commuting and leisure. Among all journeys in the EU, 20-40\% are by
-bicycle or on foot, with bicycle trips most frequent in the Netherlands,
-Denmark, and Sweden and less frequent in Finland. Various countries and employers provide incentives to increase the use of bicycles. However, the comfort experienced
-by riders and passengers (i.e., infants/children in cargo bicycles), is 
-a multifaceted ~\cite{ayachi2015identifying} challenge in their wide
-acceptance. %Meanwhile, this is a topic that is of great interest and requires attention when it comes to infants' transportation with strollers or bicycles.
+Research on vibration comfort during cycling is a logical starting point for
+investigating similar road-induced vibrations for infants. Cycling is beneficial
+for health~\cite{Oja1998} and greatly contributes to reducing CO\(_2\)
+emissions, congestion, and air pollution~\cite{Neves2019}. As a result, bicycles
+are increasingly being used to deliver goods, for daily commuting and for
+leisure. Among all journeys in the EU, 20-40\% are by bicycle or on foot, with
+bicycle trips most frequent in the Netherlands, Denmark, and Sweden and least
+frequent in, for example, Finland. Various countries and employers offer
+incentives to increase bicycle use. However, the comfort experienced by riders
+and passengers (e.g. infants/children in cargo bicycles), is a
+multifaceted~\cite{ayachi2015identifying} challenge to wide acceptance of
+bicycling.
+
 % Paragraph about comfort in bicycles
-The comfort of bicycles~\cite{too1990biomechanics} is mainly affected by physical
-comfort and the impact of environmental factors (weather, route geometry,
-and road roughness).  
-Physical comfort is related to mechanical (bicycle and component design),
-biomechanical (whole-body vibrations, human body dynamics, and kinematics), and
-physiological factors (individual characteristics, e.g. sex, body size, weight, etc.).
-Although there is relevant literature exploring the impact of environmental
-factors (i.e., irregular road surface quality, weather conditions) on cyclist
+The comfort of bicycles~\cite{too1990biomechanics} is mainly affected by
+physical comfort and the impact of environmental factors (weather, route
+geometry, and road roughness). Physical comfort is related to mechanical
+(bicycle and component design), biomechanical (whole-body vibrations, human body
+dynamics, and kinematics), and physiological factors (individual
+characteristics, e.g. sex, body size, weight). Although there is relevant
+literature exploring the impact of environmental factors (i.e., irregular road
+surface quality, weather conditions) on cyclist
 comfort~\cite{Stinson2003,Hagemeister2003,ayachi2015identifying,Verhoeven2017,Teixeira2020},
-there is limited work on understanding the biomechanical and physiological
-factors of comfort of bicycle passengers (infants/children in bicycle
-seats, cargo bicycles, or trailers). A particular concern is the transport
-of infants under one year of age, who cannot well express any experience of discomfort
-or pain.
-Similar concerns are raised about strollers, where infants are also
+there is only limited work on understanding the biomechanical and physiological
+factors of comfort of bicycle passengers (infants/children in bicycle seats,
+cargo bicycles, or trailers). A particular concern is the transport of infants
+under one year of age, who cannot well express any experience of discomfort or
+pain. Similar concerns are raised about strollers, where infants are also
 exposed to road-induced vibrations.
-In this paper, we will explore biomechanical comfort by assessing whole-body
-vibrations experienced by infants transported in cargo
-bicycles and strollers, and by evaluating potential health risks and discomfort.
 
@@
 Biomechanical comfort is mainly related to vibrations induced by road
-irregularities and transmitted through the vehicle to the human body ~\cite{too1990biomechanics}. 
-Road irregularities are a driving factor, as vibrations induced in children are not efficiently
-isolated due to the lack of adequate suspension systems in most bicycle models~\cite{vasudevan2017comparison} and strollers.
-The bicycle or stroller design and the seating configuration affect posture and vibration transmission~\cite{Brand2020,Verma2016}.
-Children/infants can be
-transported sitting or lying in a different location than the cyclist (e.g. above a wheel when in a bicycle seat) and in/on a different `seat'
-(a car seat, bicycle seat, stroller seat, or cot). 
-%These all influence the transmission of vibrations from the seat to the body and head.
-Vibrations increase with travel speed, for example, when
-running with a stroller or due to the increased power offered by electric
-bicycles (with and without trailers).
-For the latter, the average speed using electric bicycles and speed pedelecs is
-19\% higher (21.0~\si{\kph} and up to 63\% higher (28.1~\si{\kph}),
-respectively, than conventional bicycling~\cite{SWOV2022}.
-%The intensity of these vibrations could become even more critical with the change of load, which could be related with age and size of the infant/children transported. 
-However, there is limited literature exploring whole-body
-vibrations of infants and children transported by bicycle trailers,
-cargo bicycles, and strollers 
-~\cite{Ota2012,Ota2014,Kanya-Forstner2020, vanDriessche2018,
-Schwanitz2020,MalteChildComfort2022}, and literature focusses on comfort rather
-than health risks.
+irregularities and transmitted through the vehicle to the human
+body~\cite{too1990biomechanics}. Road irregularities are a driving factor, as
+vibrations induced in children are not efficiently isolated due to the lack of
+adequate suspension systems in most bicycle
+models~\cite{vasudevan2017comparison} and strollers. The bicycle or stroller
+design and the seating configuration affect posture and vibration
+transmission~\cite{Brand2020,Verma2016}. Children/infants can be transported
+sitting or lying in a different location than the cyclist (e.g. above a wheel
+when in a bicycle seat) and in/on a different `seat' (a car seat, bicycle seat,
+stroller seat, or cot). Vibrations generally increase with travel speed, for
+example, when running with a stroller or due to the increased power offered by
+electric bicycles (with and without trailers). For the latter, the average speed
+using electric bicycles and speed pedelecs is 19\% higher (21.0~\si{\kph} and up
+to 63\% higher (28.1~\si{\kph}), respectively, than conventional
+bicycling~\cite{SWOV2022}. The intensity of these vibrations could become even
+more critical with the change of load, which is related with age and size of the
+infant/children transported. However, there is limited literature exploring
+whole-body vibrations of infants and children transported by bicycle trailers,
+cargo bicycles, and strollers~\cite{Ota2012,Ota2014,Kanya-Forstner2020,
+vanDriessche2018, Schwanitz2020,MalteChildComfort2022}. Most literature focusses
+on comfort rather than health risks.
 
@@
 (IHI-ST). However, there is a lack of reliable, applicable, and validated injury
-thresholds to assess IHI-ST risks~\cite{hutchinson2024modeling}. Similarly,
-even if there are indications that vibration affects
-comfort in bicycles or strollers, there are no standard vibration assessment methods or
-guidelines available with respect to their design. ISO~2631~\cite{ISO2631}, the
+thresholds to assess IHI-ST risks~\cite{hutchinson2024modeling}. Similarly, even
+if there are indications that vibration affects comfort in bicycles or
+strollers, there are no standard vibration assessment methods or guidelines
+available with respect to their design. ISO~2631~\cite{ISO2631}, the
 international standard for assessing whole-body vibrations, was derived using
 data sets on motion platforms, with adults as participants and sitting postures
-as adopted in passenger vehicles rather than on bicycles.
-Gao~et~al.~\cite{Gao2018} therefore derived vibration
-comfort limits for adults riding bicycles, based on their
-subjective feedback.
-Furthermore, in ISO~2631-1 the exposure time to vibrations is not considered a factor
-in the determination of comfort, despite having a clear impact on health risks
-according to the European Directive (2002/44/EC, 2002)
-\cite{directive2002directive}.
+adopted in passenger vehicles rather than on bicycles. Gao~et~al.~\cite{Gao2018}
+show this discrepancy with vibration comfort limits for adults riding bicycles,
+based on their subjective feedback, tolerating more than the the vibration
+limits suggested by ISO~2631-1. Furthermore, in ISO~2631-1 the exposure time to
+vibrations is not considered a factor in the determination of comfort, despite
+having a clear impact on health risks according to the European Directive
+(2002/44/EC, 2002)~\cite{directive2002directive}.
 
 % Paragraph Potential effects of vibrations on adults
-Despite the lack of knowledge and test methods with regard to comfort or inflicted head
-injury by shaking trauma for children/infants on bicycles, there are clear
-indications in the literature that these should be considered.
-About 36\% of males and 42\% of females in a total sample of 900 cyclists had
-various discomfort complaints~\cite{groenendijk1992sitting}.
-Discomfort of both men and women occurred even during short bicycle trips
-(\SIrange{3}{10}{\kilo\meter}). However, results from research into comfort of active
-adult cyclists cannot be applied directly to infants or children sitting or
-lying in transportation systems.
-
-Schwanitz~et~al.~\cite{Schwanitz2020} tested a child bicycle
-trailer on smooth asphalt, gravel, and cobblestones using child shaped sandbag dummies (baby and toddler sizes) using ISO~2631-1
-weightings. Tyre pressure and number of
-passengers had no significant effect on vibration magnitude, but road surface
-and travel speed did. 
-The baby-sized dummy (5~\si{\kilo\gram}) experienced 20\% higher vibration than
-the toddler-sized dummy (10~\si{\kilo\gram}), while the measured values
-generally exceeded the ISO~2631-1 limit for vibrational comfort of adults.
-Rothhämel~et~al.~\cite{MalteChildComfort2022} tested a
-trailer seat and a tadpole configuration three-wheel cargo bicycle on smooth
-asphalt and cobblestones for speeds from \SIrange{10}{20}{\kph} using ISO~2631-1 weightings. They found a large
-increase in vibration amplitude on cobblestones compared to asphalt in the
-same speed range. The child trailer exhibited larger accelerations
-than the cargo bicycle with the child seat between the front wheels. 
-Child seats in trailers and cargo bicycles generally had
-vibrations of higher magnitude than those experienced in a car seat travelling at 30~\si{\kph} on a rough road \cite{gromadowski2013analysis}. Rothhämel and
-Liu~\cite{rothhamel2023comfort} conducted measurements with a
-6.5~\si{\kilo\gram} mass representing an infant with various tyre pressures. All
-their values fell into the ``extremely uncomfortable'' zone for ISO~2631-1.
-
-In addition to studies with dummies or lumped masses representing
-infants, Kanya-Forstner~\cite{Kanya-Forstner2020} measured acceleration in
-bicycle child trailers with human subjects aged 12 months to 6 years over
-asphalt and gravel terrain (average speed of 12~\si{\kph} over a
-20~\si{\minute} ride). 
-According to the health assessment using ISO~2631-1, the vibrations are similar
-to those experienced in child seats in cars and illustrate moderate or low
-health risk for a 2~\si{\hour} duration.
-On the other hand, if not corrected for duration, the values point to moderate
-and high risks. The type of road surface had the greatest influence on the levels of vibration
-exposure, followed by type of trailer, while gel cushions as support did not
+Despite the lack of knowledge and test methods with regard to comfort or
+inflicted head injury by shaking trauma for children/infants on bicycles, there
+are clear indications in the literature that these should be considered. About
+36\% of males and 42\% of females in a total sample of 900 cyclists had various
+discomfort complaints~\cite{groenendijk1992sitting}. Discomfort occurred even
+during short bicycle trips (\SIrange{3}{10}{\kilo\meter}). However, the
+results of research on the comfort of active adult cyclists cannot be applied
+directly to infants or children sitting or lying in transportation systems.
+
+Schwanitz~et~al.~\cite{Schwanitz2020} tested a child bicycle trailer on smooth
+tarmac, gravel, and cobblestones using child shaped sandbag dummies (baby and
+toddler sizes) using ISO~2631-1 weightings. Tyre pressure and number of
+passengers had no significant effect on vibration magnitude, but the road
+surface and travel speed did. The infant dummy (5~\si{\kilo\gram}) experienced a
+20\% higher vibration than the toddler dummy (10~\si{\kilo\gram}), while the
+measured values generally exceeded the ISO~2631-1 limit for vibrational comfort
+of adults. Rothhämel~et~al.~\cite{MalteChildComfort2022} tested a trailer seat
+and a tadpole configuration three-wheel cargo bicycle on smooth tarmac and
+cobblestones for speeds from \SIrange{10}{20}{\kph} using ISO~2631-1 assessment.
+They found a large increase in vibration amplitude on cobblestones compared to
+tarmac in the same speed range. The child trailer exhibited larger
+accelerations than the cargo bicycle with the child seat between the front
+wheels. Child seats in trailers and cargo bicycles generally had vibrations of
+higher magnitude than those experienced in a car seat travelling at 30~\si{\kph}
+on a rough road \cite{gromadowski2013analysis}. Rothhämel and
+Liu~\cite{rothhamel2023comfort} also conducted laboratory measurements with a
+6.5~\si{\kilo\gram} mass representing an infant in a bicycle trailer with
+various tyre pressures. All their values fell into the ``extremely
+uncomfortable'' zone for ISO~2631-1.
+
+In addition to studies with dummies or lumped masses representing infants,
+Kanya-Forstner~\cite{Kanya-Forstner2020} measured acceleration in bicycle child
+trailers with human subjects aged 12 months to 6 years over tarmac and gravel
+terrain (average speed of 12~\si{\kph} over a 20~\si{\minute} ride). According
+to the health assessment using ISO~2631-1, the vibrations are similar to those
+experienced in child seats in cars and illustrate moderate or low health risk
+for a 2~\si{\hour} duration. She points out the importance of correcting for
+duration, otherwise the values point to moderate and high risks. The type of
+road surface had the greatest influence on the levels of vibration exposure,
+followed by the type of trailer, while the gel cushions as support did not
 significantly influence the vibration measured at the seat/pan interface. Hence,
-there is a need to refocus on the impact of vibrations on infants and
-children's health and comfort~\cite{rybarczyk2020physiological} to ensure 
-safe, comfortable and wide use of bicycles.
-
-% Don't edit, working to change the following paragraph
-In the context of infants transportation with stroller seats, Kok
+there is a need to refocus on the impact of vibrations on infants and children's
+health and comfort~\cite{rybarczyk2020physiological} to ensure safe, comfortable
+and widespread use of bicycles.
+
+In the context of infant transportation with stroller seats, Kok
 Siong~\cite{lim2018study} carried out an indoor and an outdoor experiment to
-capture the vibrations at the seat and backrest of a baby
-stroller, using weights from \SIrange{4}{14.14}{\kilo\gram}, and  a child
-subject of 10.30~\si{\kilo\gram} as well as a dummy weighing
-10.30~\si{\kilo\gram}. 
-Comfort levels (ISO~2631-1) for indoor testing were  `Fairly
-uncomfortable' to `A little uncomfortable', where outdoor testing resulted in
-`Extremely uncomfortable' and `Fairly uncomfortable' values.
-The child and dummy provided similar results.
-%However, the results still consider ISO~2631-1 standard, which is designed for adults and specific postures.
-Sierzputowski~
-et~al.~\cite{sierzputowski2021pilot} tested a modern
-and
-an older stroller on asphalt road, concrete
-paving blocks, concrete plates, dirt road, lawn and damaged concrete. Several conditions resulted in the highest discomfort levels ($>$2~\si{\mps\squared} according to ISO~2631-1). 
-Okajima~et~al.~\cite{okajima2020dynamic} tested seven
-children, sitting upright in a stroller, riding over a protrusion
-(13x60 mm) with either one wheel or two wheels. 
-The children were 3 to 6 years old, boys and girls, weighing
-\SIrange{15.94}{19.96}{\kilo\gram} with a length of
-\SIrange{98.0}{112.4}{\centi\meter}. 
-The infant’s head and chest exhibited strong vibrations at
-1~\si{\hertz} along all three axes (x, y and z), vibration along the
-y-direction at 2~\si{\hertz}, with limited vibration above
+capture the vibrations at the seat and backrest of a baby stroller, using
+weights from \SIrange{4}{14}{\kilo\gram}, and a child subject of
+10.30~\si{\kilo\gram} as well as a dummy weighing 10.30~\si{\kilo\gram}. Comfort
+levels (ISO~2631-1) for indoor testing were  `Fairly uncomfortable' to `A little
+uncomfortable', where outdoor testing resulted in `Extremely uncomfortable' and
+`Fairly uncomfortable' values. The child and dummy provided similar results.
+Sierzputowski~et~al.~\cite{sierzputowski2021pilot} tested a modern and an older
+stroller on tarmac road, concrete paving blocks, concrete plates, dirt road,
+lawn, and damaged concrete. Several conditions resulted in the highest
+discomfort levels ($>$2~\si{\mps\squared} according to ISO~2631-1).
+Okajima~et~al.~\cite{okajima2020dynamic} tested seven children, sitting upright
+in a stroller, riding over a protrusion (13$\times$60~\si{\milli\meter}) with
+either one wheel or two wheels. The children were 3 to 6 years old, boys and
+girls, weighing \SIrange{15.94}{19.96}{\kilo\gram} with a length of
+\SIrange{98.0}{112.4}{\centi\meter}. The heads and chests of the children
+exhibited strong vibrations at 1~\si{\hertz} along all three axes (x, y, and z),
+vibration along the y-direction at 2~\si{\hertz}, with limited vibration above
 8~\si{\hertz}.
-%This result is critical as this range of frequencies is very common in bicycles and strollers. 
-However, they did not assess comfort and health risk.
-
-The above studies provide experimental evidence of strong vibrations in real children, dummies, or simple masses transported in cargo bicycles, bike trailers, and strollers.
-Most studies use ISO~2631-1 frequency weighting and report very or extremely uncomfortable conditions with higher speeds and rough surfaces, while only one study evaluated health effects.
-Only a few studies focus on the effect of vibration on babies and infants under 12 months of age.
-
-This paper addresses both comfort and potential health effects for babies and infants.
-We equipped five
-strollers and two cargo bicycles with inertial measurement units (IMU) and
-carried out 78 experiments on different road surfaces and with different travel speeds, using
-dummies representing 0, 3, and 9 month-old infants.
-We present results using ISO~2631-1
-frequency weightings. 
-Given that ISO-2631-1 is neither validated for children nor for lying postures, we also report unweighted results to assess power spectrum and bandwidth.
-We investigated the influence of vehicle, seat, body size, speed, and road surface
-and provide recommendations to users, designers, and future researchers.
-
-\section{Methods}
+
+The above studies provide experimental evidence of potentially worrying
+vibrations in real children, dummies, or simple masses transported in cargo
+bicycles, bike trailers, and strollers. Most studies use ISO~2631-1 frequency
+weighting and report very or extremely uncomfortable conditions with higher
+speeds and rough surfaces, while only one study evaluated health effects. Only a
+few studies focus on vibrations experienced by infants under 12 months of age.
+
+This paper addresses both comfort and potential health effects for infants. We
+equipped five strollers and two cargo bicycles with inertial measurement units
+(IMU) and carried out 67 experiments on different road surfaces and with
+different travel speeds, using dummies representing 0, 3, and 9-month-old
+infants. We assessed the data and derived results using ISO~2631-1 frequency
+weightings and procedures. Given that ISO-2631-1 is neither validated for
+children nor for lying postures, we also report unweighted results to assess
+power spectrum and bandwidth. We investigated the influence of vehicle, seat,
+body size, speed, and road surface and provided recommendations to users,
+designers, and for future research.
+
+\section{Materials and Methods}
 %
@@
 %
-Vibration measurements were conducted at approximately constant speed using five
-different strollers and two cargo bicycles with two baby seats, chosen for their
-popularity and/or distinctive features. The strollers consisted of three modern
-strollers: Maxi-Cosi Street Plus (Dorel Juvenile, Foxborough, USA), BABYZEN YOYO
-0+ (Stokke, Ålesund, Norway), Fox 5 (Bugaboo, Amsterdam, The Netherlands) and
-two vintage strollers from unknown manufacturers ``Green Machine'' cot-style and
-``Old Rusty'' seat-style. The cargo bicycles were a two-wheel UrbanArrow (Pon,
-Amsterdam, The Netherlands) and a delta configuration tricycle (Keiler Bakfiets, The Netherlands) which were each fitted with the two seats: Joolz Pebble Pro (Dorel Juvenile, Foxborough, USA), Melia Baby Shell (Melia, Rotterdam, The Netherlands).
-~\footnote{Appendix~\ref{app:equipment} provides.
-figures and technical descriptions of all strollers and cargo bicycles.}
+Vibration measurements were conducted using five different strollers and two
+cargo bicycles with two baby seats, chosen for their popularity and/or
+distinctive features. The strollers included three modern strollers:
+\underline{Bugaboo} Fox 5 (Bugaboo, Amsterdam, The Netherlands),
+\underline{Maxi-Cosi} Street Plus (Dorel Juvenile, Foxborough, USA), and
+\underline{Stokke} BABYZEN YOYO 0+ (Stokke, Ålesund, Norway) and two vintage
+strollers from unknown manufacturers ``\underline{Green Machine}'' cot-style and
+``\underline{Old Rusty}'' seat-style. The cargo bicycles were a delta
+configuration tricycle \underline{Keiler} (Keiler Bakfiets, The Netherlands) and
+a two-wheel \underline{Urban Arrow} (Pon Bicycle Holding B.V., Amsterdam, The
+Netherlands). Each was tested with both seats: Maxi-Cosi X Joolz
+\underline{Pebble} Pro i-Size (Dorel Juvenile, Foxborough, USA) and
+\underline{Melia} Baby Shell (Melia, Rotterdam, The Netherlands). The underlined
+words for each product designate an abbreviated name used in figures and tables
+in the paper and Figure~\ref{fig:equipment} shows the tested
+products.~\footnote{Appendix~\ref{app:equipment} provides more detailed figures
+and technical descriptions of all tested strollers and cargo bicycles.}
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/equipment.png}
+  \caption{Tested products: cargo bicycles with baby seats, strollers, and
+  dummies. Images are reproduced from manufacturer's websites except for the
+  vintage strollers and dummies.}
+  \label{fig:equipment}
+\end{figure}
 
 The tests involved three baby dummies with sizes and weights representative of
-newborns and infants 3 and 9 months of age. Newborns (`0 months') are the
-youngest (smallest, lightest) children that are transported in strollers with a
-cot. Three-month-old infants are the youngest (smallest, lightest) children that
-are transported in cargo bicycles, fixed in a baby car seat or baby shell.
-Nine month old infants are the youngest (smallest, lightest) that can sit up
-straight by themselves and thus can be transported sitting up straight, in a
-stroller with a seat or on the bench of a cargo bicycle.
-
-We considered the use of ``crash test dummies'' (also known as anthropomorphic
-test devices or ATDs), which are designed and commonly used to test child seats
-in car crash tests. However, the closest available body sizes for crash test
-dummies do not meet the body sizes desired for this investigation. Furthermore, crash test dummies are of a fundamentally
-different design, based on scaling of adult biomechanical data
-rather than child data and with dynamic properties designed for crash
-conditions, not for vibration testing. Therefore crash test dummies were not considered a good option to use for the envisaged vibration testing.
-
-Testing with real infants would be unethical for the most severe conditions and create challenges in
-terms of reproducibility. Hence we bought and adapted ``reborn'' dummies
-available in a wide range of postures from a webshop specialising in dolls and
-dummies (\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). The dummies were
-filled with a mixture of cat litter, sand, and water to reproduce the exact
-weights needed. Cat litter sand features smooth and round shapes
-grains, which do not damage the dummies' materials (fabric and plastic). The
-weight and body height of the dummies were made to match the average measures
-for children of 0, 3 and 9 months old: 3.48~\si{\kg}|50~\si{\cm}
-5.90~\si{\kg}|62.5~\si{\cm}, and 8.90~\si{\kg}|70~\si{\cm}, respectively.
-
-%We wanted to use the measurements from Steenbekkers~\cite{Steenbekkers1993}. However, this research provided the results only per three-month group, which did not fit our age categories. 
-We used Dutch infant growth charts to determine the average weight and body
-height at age 0 months [reference needed!] and French growth charts for 3 and 9
-months. French children are the smallest in Europe, and Dutch children are the
-tallest. At 3 months, average Dutch children weigh 113 grams more than average
-French children and at 9 months, the difference is 85 grams.
-
-To achieve a realistic mass distribution, each limb
-was filled with a proper amount of wet sand (for the 0-month dummy, water was
-added to achieve the correct weight). To do this, we simplified the geometry of
-each body segment according to the defined basic geometric shapes: a sphere for
-the head, and cylinders for the torso, upper arms, upper legs and lower legs,
-according to~\cite{Snyder1977}. We assumed equal
-density for each limb (1000~\si{\kg\per\cubic\meter}), and rescaled the limb segments
-in \cite{Snyder1977} to match the dimensions of our dummies. %In doing so, we were able to calculate the volume of each segment, thus the mass of each limb of the dummies.
+infants 0, 3 and 9 months of age. Newborns (`0 months') are the youngest
+(smallest, lightest) children that are transported in strollers with a cot.
+3-month-old infants are the youngest (smallest, lightest) children that are
+transported in cargo bicycles, fixed in a baby car seat or baby shell. At nine
+months on average, infants can sit up straight by themselves and thus can be
+transported sitting up straight, in a stroller with a seat or on the bench of a
+cargo bicycle. Testing with real infants would be unethical for the most severe
+conditions and create challenges in terms of reproducibility. Hence we bought
+and adapted commercially available ``Reborn'' dummies
+(\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}), see
+Figure~\ref{fig:equipment}~where Appendix  {\ref{app:equipment} provides full
+details}.
+
+The weight and body height of the dummies were made to match the average
+measures for children of 0, 3 and 9 months old: 3.48~\si{\kg}|50~\si{\cm}
+5.90~\si{\kg}|62.5~\si{\cm}, and 8.90~\si{\kg}|70~\si{\cm}, respectively. We
+used Dutch infant growth charts to determine the average weight and body height
+at age 0 months~\cite{TNO/LUMC1998} and French growth charts for 3 and 9
+months~\cite{FrenchGrowthChart} as requested by the funder; with French children
+being the smallest in Europe, while the Dutch are the tallest . The dummies were
+filled with a mixture of cat litter, sand, and water to reproduce the mass and
+mass distribution according to the body segment information reported
+in~\cite{Snyder1977}.
 
@@
 with Microsoft Windows 10. We 3D printed supports (material: PLA) for the
-sensors to ensure a firm clamp between the sensor and the bicycle/stroller
-tested (Small white and orange boxes visible in Figure~\ref{fig:sensors_UA}).
-Each vehicle was equipped with five IMUs, as listed below. Drawings
-showing the vehicles and the sensors' location are in
-Appendix~\ref{app:equipment}.
-%
-\begin{enumerate}
-  \item \textbf{Rear Wheel} This IMU was placed on the wheel hub (cargo
-  bicycles) or clamped to the wheel (strollers) for measuring travel speed. The
-  travelling (longitudinal) speed was derived according to the wheel radius and
-  the IMU angular speed.
-  \item \textbf{Front Wheel} This IMU was mounted on the front wheel fork (the
-  caster wheel for the stroller). This was the non-rotating measurement point
-  closest to the ground. The purpose of this sensor was to measure the road
-  roughness filtered out only by the tyres.  
-  \item \textbf{Frame} On the cargo bicycle, an IMU was placed below the frontal
-  cargo bay and clamped to the frame. This was to provide an understanding of
-  the damping characteristics of the bicycle frame, together with an estimation
-  of the effect of the suspension system. On the stroller, the IMU was taped
-  under the baby seat.
-  \item \textbf{Seat Head} IMU taped into the baby seat (on the soft mattress),
-  directly in contact with the dummy's head. This IMU measured the vibration
-  transmitted to the head contact point.
-  \item \textbf{Seat Pan} This IMU was taped into the baby seat, at the
-  interface between the dummy's buttock and the baby seat. It measured the
-  vibration transmitted to the dummy's buttock.
-\end{enumerate}
-
+sensors to firmly fix the sensors on the tested bicycle/stroller (small white
+and orange boxes visible in Figure~\ref{fig:sensors_UA}). Each vehicle was
+equipped with five IMUs. The IMUs under the head and buttocks contacting the
+dummy were placed according to the recommended practice in vibration testing
+standard ISO-2631-1.~\footnote{Only two sensors were used in this study and
+descriptions of the remaining three sensors and detailed drawings showing the
+vehicles and the sensors' location are in Appendix~\ref{app:equipment}.} This
+generates acceleration data representative of the mechanical load transferred
+from the seat to the human body taking into account the compliance of the seat
+foams and the inertia and compliance of the dummy. 
+%
 \begin{figure}
   \centering
-  \subcaptionbox{IMU on the front fork}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/FW_UA.jpg}}
-  \subcaptionbox{IMU on the rear wheel hub}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/RW_UA.jpg}}
-  \subcaptionbox{IMU under the cargo bay}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/BT_UA.jpg}}
-  \subcaptionbox{two IMUs on the baby seat surface}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/Maxicosi_sensors_UA.jpg}}
-  \caption{IMU locations on the Urban Arrow cargo bicycle. The white 3D printed
-  sensor supports are visible in (a) and (c). The last figure (d) shows how the
-  sensors were taped to the seat pan and backrest.}
+  \subcaptionbox{IMU on Urban Arrow rear hub.}{
+    \includegraphics[width=65mm, angle=-90]{fig/RW_UA.jpg}}
+  \subcaptionbox{IMUs on the Pebble seat.}{
+    \includegraphics[width=65mm, angle=-90]{fig/Maxicosi_sensors_UA.jpg}}
+  \subcaptionbox{Stokke, dummy, and camera.}{
+    \includegraphics[height=65mm]{fig/stroller-dummy-camera.jpg}}
+  \caption{Example equipment set up. a) An IMU was placed on the wheel hub
+  (cargo bicycles) or clamped to the wheel (strollers) for measuring travel
+  speed. The travel (longitudinal) speed was derived according to the wheel
+  radius and the IMU's angular speed about the wheel axis. In b) the IMUs were
+  taped into the baby seat at the interface between the dummy's buttocks or head
+  and the baby seat. In c) the camera is mounted to the stroller handlebar and
+  IMUs are on the wheels.}
   \label{fig:sensors_UA}
@@
 
-The IMUs for the seat head and seat buttock positions contacting the dummy were
-placed according to the recommended practice in vibration testing standard
-ISO-2631-1. This generates acceleration data representative of the mechanical
-load transferred from the seat to the human body taking into account the
-compliance of the seat foams and the inertia and compliance of the dummy.
-
-The target sampling frequency was 910.22~\si{\hertz} for all IMUs. The
-full-scale range was set to \(\pm\)16~g for the accelerometer (``WR: wide
-range'' configuration on Consensys Shimmer software), and
-\(\pm\)2000~\si{\degree\per\second} for the gyroscope. All tests were recorded
-with two GoPro Hero7 cameras: one directly mounted on the strollers/bicycles to
-record the dummy-seat relative motion, while the other was held by an
-experimenter walking or riding alongside the vehicle to have a complete overview
-of the experiment.
-
-\subsection{Experimental Protocol}
-%
-All tests were conducted in Delft, The Netherlands, on public roads near the
-Delft University of Technology.
-After mounting the sensors and reaching the location of the experiment, we
-turned on the sensors to start the experimental session. Before each trial, we
-pushed the vehicle back and forth on level ground to mark the beginning of the
-trial as an extra time-synchronization measure.
-For the cargo bicycle, a single rider conducted all trials to be consistent
-across different sessions (rider mass: 59~\si{\kg}; rider height:
-1.70~\si{\m}).
-We tested three types of road surfaces with the cargo bicycles and repeated
-those at different speeds.
-The stroller tests were conducted on six different surfaces with the pusher
-manually keeping a consistent walking speed of approximately
-5~\si{\kilo\meter\per\hour}.
-In all tests, speed was controlled by the pusher or cyclist using a speedometer
-mounted on the stroller handle bar or the steer of the cargo bicycle. We
-gathered data from multiple trials within the same session.
-The test ``scenarios'' combining vehicle type, body size, speed and test surfaces are listed below.
-All test locations and surfaces are shown in
-  Appendix~\ref{app:location}.
-%
-\begin{itemize}
-  \item \textbf{Strollers} were tested with dummies of 0 months and 9 months at
-  5~\si{\kph} at:
-  \begin{itemize}
-      \item Tarmac
-      \item Paver bricks % Klinkers
-      \item Sidewalk pavers % Stoeptegels
-      \item Cobblestones 
-      \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
-      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar 
-  \end{itemize}
-  \item \textbf{Cargo bicycles} were tested with dummies of 0 months and 3
-  months. Test were performed at 12~\si{\kph} for both vehicles. The Urban Arrow
-  was also tested at 25~\si{\kph} whereas the Keiler was tested at
-  20~\si{\km\per\hour} for safety reasons (due to wobbling). The test surfaces
-  are:
-  \begin{itemize}
-      \item Tarmac
-      \item Paver bricks
-      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar (also tested at 5~\si{\kph})
-      \end{itemize}
-  \item \textbf{Baby seats} Both the Maxi-Cosi X Joolz Pebble Pro i-Size and the
-  Melia baby shell were tested on each cargo bicycle using the same mounting
-  systems.
-\end{itemize}
+The sampling frequency was set to 910.22~\si{\hertz} for all IMUs. The
+full-scale range was set to the sensors' maximum: \(\pm\)16~g for the
+accelerometer and \(\pm\)2000\si{\degree\per\second} for the gyroscope. All
+tests were recorded with two GoPro Hero7 cameras: one directly mounted on the
+strollers/bicycles to capture the dummy-seat relative motion, while the other
+was held by an experimenter who was walking or riding along with the vehicle to
+have a complete overview of the experiment.
 
@@
 %
-All tested systems provided full support for back and head and allowed usage in
-lying or at least reclined postures. Nine month old infants would be able to sit
+All tested equipment provided full support for the back and head, allowing usage
+in lying or reclined postures. Nine-month-old infants are generally able to sit
 erect, but will often rest their heads or be asleep. Although sitting upright is
@@
 while the head was always supported by the headrest. We tested all systems with
-horizontal or reclined postures. The inclination angle with respect to the
+horizontal or reclined postures. The angle of inclination with respect to the
 ground is listed in Table~\ref{tab:baby-posture} for each condition tested.
@@
   \caption{Inclination angles of the IMUs ``Seat Head'' and ``Seat Pan'', per
-  each tested configuration.
-%We report the angles defined by the axis of the human body reference system (a reference system connected to the dummy, whose z-axis is aligned with the body spine and x-axis points to the front of the body) and the ground plane.
-  For the head positive angles represent forward head rotation with 0~\si{\degree} indicating a fully supine posture (lying horizontally) and 90~\si{\degree} fully erect.
-For the seat pan  0~\si{\degree} is horizontal and positive angles indicate elevated legs, see Figures in Appendix \ref{app:equipment}.
-RF is rearward facing, and FF is forward facing.}
+  each tested configuration (without rider and dummy). For the head, positive
+  angles represent forward head rotation with 0\si{\degree} indicating a fully
+  supine posture (lying horizontally) and 90\si{\degree} fully erect. For the
+  seat pan, 0\si{\degree} is horizontal and positive angles indicate elevated
+  legs, see Figures in Appendix \ref{app:equipment}. RF indicates rearward
+  facing and FF indicates forward-facing.}
+\small
 \begin{tabular}{lllrrr}
@@
 \midrule
-\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Maxi-Cosi X Joolz (RF)& 41
-& 2 \\
- &  & 3 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
+\multirow[t]{5}{*}{Stroller}
+ & Bugaboo & 0 mo & Baby cot (RF)& 0 & 0 \\
+ & Bugaboo & 9 mo & Baby seat (FF) & 49 & 24\\
+ \cline{2-6}
+ & Green Machine & 0 mo & Baby cot (RF) & 0 & 0\\
+ \cline{2-6}
+ & Maxi-Cosi & 0 mo & Baby cot (RF)& 0 & 0\\
+ & Maxi-Cosi & 9 mo & Baby seat (FF)& 40 & 10 \\
+ \cline{2-6}
+ & Old Rusty & 9 mo & Baby seat (FF) & 48 & 5\\
+ \cline{2-6}
+ & Stokke & 0 mo & Baby cot (RF)& 12 & 12 \\
+ & Stokke & 9 mo & Baby seat (FF)& 45 & 4 \\
+ \cline{1-6} \cline{2-6}
+ \multirow[t]{6}{*}{Cargo Bicycle} 
+ & \multirow[t]{3}{*}{Keiler} & 0 mo & Pebble (RF)& 41 & 2 \\
+ &  & 3 mo & Pebble (RF)& 41 & 2 \\
  &  & 3 mo & Melia (FF)& 64 & 2 \\
  \cline{2-6}
- & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
- &  & 3 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
+ & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Pebble (RF)& 41 & 2 \\
+ &  & 3 mo & Pebble (RF)& 41 & 2 \\
  &  & 3 mo & Melia (FF)& 64 & 2 \\
-\cline{1-6} \cline{2-6}
-\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street Plus & 0 mo & Baby cot (RF)& 0 & 0\\
-\cline{2-6}
- & Maxi-Cosi Street Plus & 9 mo & Baby seat (FF)& 40 & 10 \\
-\cline{2-6}
- & Babyzen YOYO 0+ & 0 mo & Baby cot (RF)& 12 & 12 \\
-\cline{2-6}
-& Babyzen YOYO 6+ & 9 mo & Baby seat (FF)& 45 & 4 \\
-\cline{2-6}
-& Bugaboo Fox 5 & 0 mo & Baby cot (RF)& 0 & 0 \\
-\cline{2-6}
- & Bugaboo Fox 5 & 9 mo & Baby seat (FF) & 49 & 24\\
- & Green Machine & 0 mo & Baby cot (RF) & 0 & 0\\
- & Old Rusty & 9 mo & Baby seat (FF) & 47.8 & 5\\
 \bottomrule
@@
 
+\subsection{Experimental Protocol}
+%
+All tests were conducted in Delft, The Netherlands, on public roads near Delft
+University of Technology~\footnote{Details of all test locations and surfaces
+are shown in Appendix~\ref{app:location}.}. After mounting the sensors and
+reaching the location of the experiment, we turned on the sensors to start the
+experimental ``session'', where a session is a continuous data collection period
+from a single vehicle that may include different road surfaces or speeds. Before
+each trial, we pushed the vehicle back and forth on level ground to mark the
+beginning of the session as an extra time-synchronization measure. For the cargo
+bicycle, a single rider conducted all trials to be consistent across different
+sessions (rider mass: 59~\si{\kg}; rider height: 1.70~\si{\m}). We tested
+cargo bicycles on tarmac and paver bricks road surfaces at target speeds of
+12~\si{\kph}, 20~\si{\kph}, and 25~\si{\kph}. The stroller tests were conducted
+on tarmac, paver bricks, sidewalk pavers, cobblestones, and sidewalk slabs
+(concrete blocks with gaps in between) road surfaces. Figure~\ref{fig:surfaces}
+shows the road surfaces used for each vehicle type. In all tests, the speed was
+manually controlled by the pusher or cyclist by observing a speedometer mounted
+on the handlebar of the stroller or cargo bicycle. 
+%
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/surfaces.png}
+  \caption{Road surfaces tested: tarmac and paver bricks (cargo bicycles and
+  strollers), sidewalk pavers, cobblestones, sidewalk slabs (strollers).}
+  \label{fig:surfaces}
+\end{figure}
+
 \subsection{Data Processing}
 %
-We analysed the raw data with a custom data processing pipeline. The open source code (MIT license) is hosted at
+We analysed the raw data with a custom data processing pipeline. The open source
+MIT licensed code is hosted at
 \href{https://github.com/mechmotum/baby-vibration}{github.com/mechmotum/baby-vibration}
-implemented in Python 3.13.1 using the following software:
+and implemented in Python 3.13.1 using the following libraries:
 DynamicistToolKit 0.6.1, Matplotlib 3.9.3, NumPy 2.2.0, Pandas 2.2.3, pyyaml
@@
 generates a website at
-\href{https://mechmotum.github.io/baby-vibration}{mechmotum.github.io/baby-vibration} with an exhaustive collection of figures for examining the
-quality of the data and general results for all trials including the selected
-tables and figures in this paper.
-
-We define a ``session'' as a continuous data collection period from a single
-vehicle. Each session is segmented into ``trials'' corresponding to a different
-road surface or activity and each trial is divided into subsequent, back-to-back
-``repetitions''.
-The raw data consists of a single comma-separated value (CSV) file per session
-per IMU, along with metadata for the sessions and vehicles. The CSV file contains
-the time series data from each IMU: linear acceleration along and angular speed
-about each of the body-fixed orthogonal axes of the IMU alongside Epoch Unix
-timestamps. We segment the sessions into trials representing a motion state of
-the vehicle: either static on level ground or being propelled over one of the
-surfaces of interest at a constant speed. Figure~\ref{fig:session} gives an
-example of segmenting a session in different trials. The data were processed per
-session as follows:
+\href{https://mechmotum.github.io/baby-vibration}{mechmotum.github.io/baby-vibration}
+with an exhaustive collection of figures to examine the quality of the data and
+general results for all trials, including the selected tables and figures in
+this paper.
+
+Each session was segmented into ``trials'' corresponding to a different road
+surface or activity and each trial was divided into subsequent, back-to-back
+``repetitions''. We divided into repetitions to capture the variation of road
+surface features within a trial. The raw data consists of a single
+comma-separated value (CSV) file per session per IMU, along with metadata for
+the sessions and vehicles. The CSV file contains the time series data from each
+IMU: linear acceleration along and angular speed about each of the body-fixed
+orthogonal axes of the IMU alongside Epoch Unix timestamps. We segmented the
+sessions into trials representing a motion state of the vehicle: either static
+on level ground or being propelled over one of the surfaces of interest at a
+constant speed. Figure~\ref{fig:session} gives an example of segmenting a
+session in different trials. The data were processed per session as follows:
+%
+% NOTE : Putting the figure before the enumeration causes a slightly better
+% layout.
+\begin{figure}
+  \centering
+  \includegraphics[width=160mm]{fig/session015.png}
+  \caption{Vehicle speed versus time derived from the wheel hub IMU for an
+  entire session (015) showing the trials in the shaded grey areas. Gold
+  horizontal lines depict the mean speed during trials bounded by its standard
+  deviation.}
+  \label{fig:session}
+\end{figure}
 %
@@
   \item Split the trials with durations longer than 40~\si{\second} into
-    repetitions of \SIrange{20}{39}{\second}.
+    repetitions of \SIrange{20}{39}{\second}. Trials less than 20~\si{\second}
+    are not split.
   \item Rotate the accelerometer data for each sensor from body-fixed sensor
-    coordinates to body-fixed vehicle coordinates and subtract the constant
-    standard gravity component. This is achieved by rotating the coordinate axes
-    about the sensor's body-fixed axis, which was manually aligned with the
-    vehicle's pitch axis. We subtracted the mean measured acceleration due to
-    gravity giving linear acceleration of each sensor projected into the
-    vehicle's SAE body-fixed axes~\cite{SocietyofAutomotiveEngineers2008},
-    named: longitudinal $x$, lateral $y$, and vertical $z$.
+    coordinates to body-fixed vehicle coordinates. This is achieved by rotating
+    the coordinate axes about the sensor's body-fixed axis, which was manually
+    aligned with the vehicle's pitch axis. We subtracted the mean measured
+    acceleration due to gravity (standard gravity) giving linear acceleration of
+    each sensor projected into the vehicle's SAE body-fixed
+    axes~\cite{SocietyofAutomotiveEngineers2008}, named: longitudinal $x$,
+    lateral $y$, and vertical $z$.
   \item Extract each motion trial segment and select the vehicle body-fixed
@@
 %
-This resulted in acceleration-time recordings of 220 total repetitions. The
-non-shock repetitions have durations in the range of \SIrange{10}{40}{\second}
-(mean: 25~\si{\second}), see Table~\ref{tab:num-trials}.
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/session015.png}
-  \caption{Vehicle speed versus time for an entire session (015) showing the
-  trials in the shaded grey areas. Gold horizontal lines depict the mean speed
-  during trials bounded by its standard deviation.}
-  \label{fig:session}
-\end{figure}
-%
-% NOTE : This table is autogenerated from the data pipeline scripts and pasted in. I move the units to a second row manually for width conservation.
+This resulted in acceleration versus time recordings of 154 total repetitions.
+The repetitions have durations in the range of \SIrange{20}{40}{\second} (mean:
+25~\si{\second}), see Table~\ref{tab:num-trials}.
+
+% NOTE : This table is autogenerated from the data pipeline scripts and pasted
+% in. Do not edit manually. I move the units to a second row manually for width
+% conservation.
+% file: trial-count-data-frame.txt
 \begin{table}
   \centering
-  \caption{Number of repetitions performed on each road surface, excluding
-  shock, and speed along with the mean duration and its standard
-  deviation.}
+  \caption{Number of repetitions performed on each road surface and speed along
+  with the mean duration and its standard deviation. Tables
+  \ref{tab:summary-stroller} and \ref{tab:summary-bicycle} provide metrics for
+  repetition sets.}
 \begin{tabular}{llcccc}
@@
 \midrule
-\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 13 & 25.1 & 7.0 \\
+\multirow[t]{6}{*}{Bicycle} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 13 & 25.1 & 7.0 \\
  &  & 20 & 8 & 28.8 & 7.6 \\
@@
 
-\subsection{Analysis}
+\subsection{Data Analysis}
 %
 Figure~\ref{fig:vert-acc-example} shows an example time history of the vertical
-acceleration of the seat pan during a single repetition. To perform the
+(\(z\)) acceleration of the seat pan during a single repetition. To perform the
 ISO~2631-1 recommended health and comfort analysis, we first downsampled the
@@
 minimum, respectively, given that values outside the range may be unreliable.
-Values that exceed the range are rare and only present in some of the cargo
-bicycle paver brick trials, but more common in the shock tests. Following the
-ISO~2631-1 recommendation, we low-pass filtered the signal at
-\(1.5\times80~\si{\hertz}=120~\si{\hertz}\) using a zero-lag
-2\textsuperscript{nd} order Butterworth filter, given that the standard only
-applies to frequencies up to 80~\si{\hertz}.
+Values that exceeded the range only present rarely in nine of the cargo bicycle
+paver brick repetitions. Following the ISO~2631-1 recommendation, we low-pass
+filtered the signal at \(1.5\times80~\si{\hertz}=120~\si{\hertz}\) using a
+zero-lag 2\textsuperscript{nd} order Butterworth filter, given that the standard
+only applies to frequencies up to 80~\si{\hertz}.
 %
@@
   \caption{Raw seat pan vertical acceleration versus time from session 001:
-  Maxi-Cosi Street Plus Stroller over the Sidewalk Slabs. Black horizontal lines
-  indicate the \(\pm\)root mean square (RMS) about the mean. The vibration dose
-  value (VDV) for the printed duration is shown in the bottom left.}
+  Maxi-Cosi stroller over the Sidewalk Slabs. Black horizontal lines indicate
+  the \(\pm\)root mean square (RMS) about the mean. The vibration dose value
+  (VDV) for the first 10~\si{\second} of the printed duration is shown in the
+  bottom left.}
   \label{fig:vert-acc-example}
@@
 
-ISO~2631-1 provides weighting filters that highlight those frequencies adults
-are most sensitive to. To apply them, we calculated the amplitude spectra of the
+ISO~2631-1 provides weighting filters that highlight frequencies that adults are
+most sensitive to. To apply them, we calculated the amplitude spectra of the
 acceleration time histories of each trial using the Fast Fourier Transform
 (FFT). Figure~\ref{fig:freq-spectrum} gives an example of a raw amplitude
-spectrum along with smoothened versions of the raw and ISO 2631-1 weighted
-signals.
-
-In almost all trials, there is a single dominant peak frequency in the
-ISO weighted and smoothed spectra. For the few trials that had two or more peaks
-at approximately the same amplitude, the second peak was sometimes selected.
-After ISO weighting, the area under the spectrum curve was calculated, and the
-frequency below which 80\% of the amplitude content falls marked as an indicator
-of bandwidth.
-
+spectrum along with smoothed versions of the raw and ISO~2631-1 weighted
+signals.  In almost all repetitions, there is a single dominant peak frequency
+in the ISO weighted and smoothed spectra. A handful of trials had two or more
+peaks at adjacent frequencies of approximately the same amplitude. We selected
+the maximum amplitude peak in those cases. Before ISO weighting, the area under
+the spectrum curve was calculated and the frequency below which 80\% of the
+amplitude content falls marked as an indicator of bandwidth.
+%
 \begin{figure}
@@
   \caption{Seat pan vertical acceleration amplitude spectrum from session 004:
-  Maxi-Cosi Street Plus over cobblestones. The gray curve shows the result of
-  the FFT, the black line is a smoothed version of the FFT (zero-lag Butterworth
+  Maxi-Cosi stroller over cobblestones. The gray curve shows the result of
+  the FFT, the black line is a smoothened version of the FFT (zero-lag Butterworth
   low pass), and the blue line is the smoothed ISO weighted FFT. The blue dashed
@@
 low-pass filtered, and ISO 2631-1 weighted vertical component of acceleration
-\(a_{w,z}\) at the seat pan for each trial using Equation~\ref{eq:rms-acc} to
-use for the health assessment and the RMS of the magnitude of the 3D acceleration
-vector at the seat pan using Equation~\ref{eq:rms-acc-mag} for the comfort
-assessment, as per ISO 2631-1 guidelines. We set the ISO~2631-1 adjustment
-factors \(k_x,k_y,k_z\) equal to 1 for all acceleration components. RMS gives an
-indication of the average vertical acceleration experienced at the infant's
-buttocks-seat interface for the duration of the trial and can be seen in
-Figure~\ref{fig:vert-acc-example}. It is the primary metric recommended by
-ISO-2631-1 for evaluation of health and comfort in adult whole-body vibration.
-We also calculated the vibration dose value (VDV) of the \(M\) raw data vertical
-acceleration \(a_{z}\) samples with Equation~\ref{eq:vdv-acc}, seen in
-Figure~\ref{fig:vert-acc-example}. Lastly, we compute the crest factor and
-absolute maximum of the downsampled and low pass filtered vertical
-acceleration\footnote{Some scenarios have crest factors larger than 9, but we
-do not report metrics other than RMS as ISO~2631-1 recommends for this study.}
-with Equations~\ref{eq:crest-factor} and \ref{eq:max-acc}, respectively. All of
-these per-repetition metrics are reported as mean values over the repetitions
-corresponding to a scenario in Table~\ref{tab:summary-stroller} and Table~\ref{tab:summary-bicycle} in
-Appendix~\ref{app:results}. Regarding the shock test, the analysis presented in Appendix~\ref{app:shock} was conducted
-on unfiltered data (not downsampled). We selected the maximum (absolute) peak
-from the time history of the vertical acceleration of the seat pan starting from
-the events' time histories (Figure \ref{fig:shock_time-history}), limiting it to
-16~g when the peak exceeded that maximum. The following equations give the
-details of the metrics calculations:
+\(a_{w,z}\) at the seat pan for each repetition using Equation~\ref{eq:rms-acc}
+to use for the health assessment and the RMS of the magnitude of the 3D
+acceleration vector at the seat pan \(\textrm{RMS}_{a_{w,xyz}}\) using
+Equation~\ref{eq:rms-acc-mag} for the comfort assessment, as per ISO 2631-1
+guidelines. We set the ISO~2631-1 adjustment factors \(k_x,k_y,k_z\) equal to 1
+for all acceleration components. RMS gives an indication of the average vertical
+acceleration experienced at the infant's buttocks-seat interface for the
+duration of the trial and can be seen in Figure~\ref{fig:vert-acc-example}. It
+is the primary metric recommended by ISO-2631-1 for evaluation of health and
+comfort in adult whole-body vibration. We also calculated the vibration dose
+value \(\textrm{VDV}_{a_{z}}\) of the \(M\) raw data vertical acceleration
+\(a_{z}\) samples corresponding to the first 10~\si{\second} of the repetition
+with Equation~\ref{eq:vdv-acc}, seen in Figure~\ref{fig:vert-acc-example}.
+Lastly, we computed the crest factor \(\textrm{CF}_{a_{z}}\) of the downsampled
+and low pass filtered vertical acceleration\footnote{Some scenarios have crest
+factors larger than 9, but we do not report metrics other than RMS as ISO~2631-1
+recommends for this study.} with Equations~\ref{eq:crest-factor}, respectively.
+All of these per-repetition metrics are reported as mean values over the
+repetitions corresponding to a scenario in Table~\ref{tab:summary-stroller} and
+Table~\ref{tab:summary-bicycle}.
+The following
+equations describe the metrics:
 %
@@
 \begin{align}
-  \textrm{Crest Factor}_{a_{z}} =\frac{\max|a_{z}(t_m)|}{\sqrt{\frac{1}{M}\sum_{m=1}^{M} a_{z}^2(t_m)}}
+  \textrm{CF}_{a_{z}} =\frac{\max|a_{z}(t_m)|}{\sqrt{\frac{1}{M}\sum_{m=1}^{M} a_{z}^2(t_m)}}
   \label{eq:crest-factor}
@@
 
-\begin{align}
-  \textrm{MAX}_{a_{z}} =\max|a_{z}(t_n)|
-  \label{eq:max-acc}
-\end{align}
-
 \subsection{Statistical Modelling}
@@
 To determine how road surface and stroller setup predict ISO~2631-1 weighted
-vertical RMS acceleration, we fit an ordinary linear least squares model to the
-data using:
+vertical RMS acceleration, we fitted an ordinary linear least squares model to
+the data using:
 %
@@
 Both \(x_\textrm{Road Surface}\) and \(x_\textrm{Stroller}\) are categorical
-variables, and we select tarmac and the Green Machine as the reference values
-when coding the categorical variables, respectively. We do not consider the
-interaction of road surface and stroller.
+variables, and we selected tarmac and the Green Machine as reference values when
+coding the categorical variables, respectively. We did not consider the
+interaction of road surface and stroller given no expectation of such an effect.
 
@@
 categorical variables and \(x_\textrm{Speed}\) is a continuous variable. We
-select tarmac and the `Keiler, Maxi-Cosi seat, 0 mo' setup as the reference
-values when coding the categorical variables, respectively. We do not consider
-the interaction of road surface and cargo bicycle setup, but we do consider the
-interaction of speed with road surface. 
-Both for strollers and cargo bicycles each tested combination of vehicle, seat and body size is considered as a different vehicle type.
-We use \(p<0.05\) to indicate
-significant differences for both models. Following fitting the two statistical
-models, we apply Tukey's Range Test to compare vehicle setups among each other
-for the different road surfaces and speed ranges with \(p=0.05\) for the
-adjusted limit for significance.
+selected tarmac and the `Keiler, Pebble, 0 mo' setup as the reference values
+when coding the categorical variables, respectively. We did not consider the
+interaction of road surface and cargo bicycle setup given no expectation of such
+an effect but we did consider the interaction of speed with road surface. For
+both strollers and cargo bicycles, each tested combination of vehicle, seat, and
+dummy size was considered as a different vehicle type. We use \(p<0.05\) to
+indicate significant differences for both models. Following fitting of the two
+statistical models, we applied Tukey's Range Test to compare vehicle setups
+among each other for the different road surfaces and speed ranges with
+\(p=0.05\) for the adjusted limit for significance.
 
@@
 %
-Results for all 67 combinations of vehicle setup, road surface, and target speed are shown in
-Table~\ref{tab:summary-stroller} for strollers and Table~\ref{tab:summary-bicycle} for cargo bicycles.
-The magnitude (combining x,y,z) ISO weighted RMS is only a bit higher ($<$4\% in  modern strollers and cargo bicycles) than the vertical (z) ISO weighted RMS, indicating that vertical vibration is dominant.
-This holds also for the three-wheeled Keiler which will roll due to differing road unevenness at left and right wheels, resulting in lateral seat motion, but this seems hardly relevant in the current data.
-An exception is the vintage green machine stroller where the magnitude is up to 24\% higher indicating relevant contributions of horizontal seat pan motion. 
-As expected, in all cases the vertical ISO weighted RMS acceleration is below the vertical unweighted RMS, and this reduction is on average 10\% for modern strollers, 13\% for the vintage green machine, and even 56\% for the vintage old rusty which sees the highest bandwidth (105 Hz).
-For cargo bicycles the ISO weighting leads to an average reduction of 16\%. 
-The Keiler cargo tricycle with Melia seat on paver bricks at 20 km/h sees a 29\% reduction with a bandwidth of 83 Hz. 
-These strong effects of ISO frequency weighting in some vehicle and speed combinations are addressed further in the discussion.
-Below we present ISO weighted results for which guidelines have been published using magnitude for discomfort and vertical for health.
+Results for all 67 combinations of vehicle setup, road surface, and target speed
+are shown in Table~\ref{tab:summary-stroller} for strollers and
+Table~\ref{tab:summary-bicycle} for cargo bicycles. These tables show the mean
+values over scenario repetitions. They report the unweighted and ISO~2631-1
+weighted seat pan vertical RMS acceleration, weighted seat pan magnitude RMS
+acceleration, unweighted seat pan vertical VDV for the first 10 seconds of the
+repetition, crest factor, peak frequency, bandwidth, and duration for all
+combinations of vehicle setup, road surface, and target speed.
+
+The magnitude (combining \(x,y,z\)) ISO weighted RMS is only a bit higher
+(\(<\)4\% in  modern strollers and cargo bicycles) than the vertical (\(z\)) ISO
+weighted RMS, indicating that vertical vibration is dominant. This also holds
+for the Keiler tricycle, which will roll due to differing road unevenness at
+left and right wheels, resulting in lateral seat motion, but this seems hardly
+relevant in the current data. An exception is the Green Machine where the
+magnitude is up to 24\% higher, indicating relevant contributions of horizontal
+seat pan motion, which may be due to the lack of rigid horizontal constraint on
+the cot. As expected, in all cases the vertical ISO weighted RMS acceleration is
+below the vertical unweighted RMS, and this reduction is on average 10\% for
+modern strollers, 13\% for the vintage Green Machine, and even 56\% for the
+vintage Old Rusty which sees the highest bandwidth (105 Hz). For cargo bicycles,
+ISO weighting leads to an average reduction of 16\%. The Keiler with Melia on
+paver bricks at 20~\si{\kph} sees a 29\% reduction with a bandwidth of
+83~\si{\hertz}. These strong effects of ISO frequency weighting in some vehicle
+and speed combinations are addressed further in the discussion. Below we present
+ISO weighted results for which guidelines have been published using magnitude
+for discomfort and vertical for health. 
+%
+% NOTE : These tables are generated automatically from the Python scripts. I
+% manually edit the header rows to fit on the page width. Save the edits between
+% toprule and midrule!
+% stroller-summary-data-frame.tex
+\bgroup
+\setlength\tabcolsep{0.4mm}  % reduces horiztonal padding between columns
+\begin{table}[!ht]
+  \centering
+  \caption{Mean computed metrics of the strollers for all 40 non-shock
+  scenarios, using seat pan acceleration.}
+  \label{tab:summary-stroller}
+  \scriptsize
+\begin{tabular}{lllcccccccccc}
+\toprule
+        &            &         &        & .     &     & ISO      & ISO      & 10~\si{\second}    &        &      &       &       \\
+        &            &         & Target & Rep.  & RMS & Weighted & Weighted & VDV & Crest  & Peak & Band- & Dur-  \\
+        &            & Road    & Speed  & Count & Acc & RMS Acc  & RMS Mag  & Acc & Factor & Freq & width & ation \\
+Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\meter\second}\(^{-1.75}\)] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\
+\midrule
+\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.4 & 4.3 & 4.5 & 11.5 & 6.2 & 6.5 & 20.5 & 20.4 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 3 & 2.6 & 2.4 & 2.5 & 6.1 & 4.1 & 9.5 & 23.4 & 23.3 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 2.9 & 2.7 & 2.9 & 15.6 & 13.5 & 6.1 & 49.8 & 25.4 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 4.8 & 4.7 & 4.8 & 12.5 & 6.4 & 5.8 & 30.6 & 20.2 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.7 & 0.6 & 0.7 & 1.7 & 3.3 & 10.1 & 33.3 & 23.1 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 4 & 2.5 & 2.3 & 2.5 & 6.2 & 4.7 & 6.6 & 37.9 & 22.5 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 3 & 2.3 & 1.8 & 1.8 & 5.2 & 3.8 & 9.4 & 43.2 & 22.6 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 3 & 1.7 & 1.4 & 1.6 & 4.5 & 5.5 & 7.7 & 39.5 & 24.7 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 2.4 & 2.2 & 2.3 & 5.9 & 5.3 & 6.0 & 36.6 & 24.5 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.6 & 0.4 & 0.5 & 1.6 & 6.5 & 8.4 & 51.2 & 34.6 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{5}{*}{greenmachine} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 3.2 & 2.9 & 3.4 & 7.2 & 5.3 & 4.1 & 38.1 & 23.7 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 2 & 1.6 & 1.3 & 1.6 & 3.2 & 4.5 & 4.2 & 47.4 & 29.6 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 2.7 & 2.5 & 2.9 & 7.4 & 6.5 & 4.1 & 41.3 & 28.2 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 3.5 & 3.2 & 3.4 & 7.6 & 6.7 & 3.9 & 36.0 & 23.9 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.5 & 0.4 & 0.7 & 1.1 & 4.1 & 4.2 & 52.5 & 22.1 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.6 & 4.4 & 4.5 & 11.3 & 4.9 & 8.1 & 51.2 & 20.7 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 2 & 3.2 & 2.8 & 2.9 & 7.5 & 3.9 & 10.4 & 53.6 & 27.2 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 3 & 3.0 & 2.9 & 3.0 & 8.3 & 5.5 & 7.6 & 40.1 & 21.4 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 5.0 & 4.6 & 4.7 & 13.8 & 8.2 & 5.1 & 70.3 & 16.3 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.9 & 0.8 & 0.8 & 2.1 & 8.0 & 9.6 & 43.4 & 34.3 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 4.1 & 3.7 & 3.8 & 10.4 & 5.8 & 8.0 & 46.9 & 25.9 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 2 & 3.0 & 2.4 & 2.4 & 6.9 & 3.4 & 9.7 & 57.4 & 27.8 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 2.6 & 2.3 & 2.5 & 7.2 & 5.5 & 7.3 & 47.2 & 27.8 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 3.1 & 2.9 & 3.0 & 7.8 & 5.4 & 6.9 & 51.4 & 25.6 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 1.0 & 0.7 & 0.8 & 2.6 & 5.8 & 10.2 & 55.5 & 36.1 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{5}{*}{oldrusty} & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 4.7 & 2.0 & 2.3 & 13.0 & 6.0 & 5.1 & 105.1 & 29.9 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 3 & 3.4 & 1.2 & 1.4 & 8.7 & 6.1 & 5.2 & 106.1 & 21.9 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 3.3 & 1.4 & 1.7 & 9.7 & 9.7 & 5.4 & 104.2 & 27.3 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 3.2 & 1.6 & 1.7 & 10.5 & 11.6 & 5.3 & 103.9 & 23.8 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 1.1 & 0.5 & 0.6 & 2.7 & 5.7 & 7.0 & 105.5 & 22.6 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{10}{*}{stokke} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 4.0 & 4.1 & 10.5 & 4.8 & 6.4 & 66.3 & 21.3 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 2 & 3.0 & 2.1 & 2.2 & 6.9 & 4.1 & 9.4 & 97.7 & 29.5 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 3 & 2.8 & 2.6 & 2.7 & 7.0 & 5.5 & 6.7 & 69.9 & 22.2 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 2 & 4.0 & 3.8 & 3.9 & 11.6 & 6.4 & 5.2 & 79.1 & 25.7 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.9 & 0.6 & 0.6 & 2.8 & 7.4 & 7.7 & 89.3 & 19.5 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 5.2 & 4.9 & 5.0 & 12.4 & 4.4 & 7.7 & 69.1 & 21.5 \\
+\cline{3-13}
+ &  & Paver Bricks & 5 & 3 & 3.6 & 3.0 & 3.0 & 8.2 & 3.8 & 10.4 & 93.4 & 22.5 \\
+\cline{3-13}
+ &  & Sidewalk Pavers & 5 & 2 & 3.1 & 2.7 & 2.8 & 11.9 & 9.9 & 8.3 & 78.3 & 28.5 \\
+\cline{3-13}
+ &  & Sidewalk Slabs & 5 & 3 & 4.0 & 3.7 & 3.8 & 9.7 & 6.2 & 5.3 & 69.7 & 23.3 \\
+\cline{3-13}
+ &  & Tarmac & 5 & 2 & 0.7 & 0.4 & 0.5 & 1.9 & 6.3 & 11.1 & 95.6 & 39.1 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\bottomrule
+\end{tabular}
+\end{table}
+\egroup
+
+% bicycle-summary-data-frame.tex
+\bgroup
+\setlength\tabcolsep{0.4mm}  % reduces horiztonal padding between columns
+\begin{table}[!ht]
+  \centering
+  \caption{Mean computed metrics of the cargo bicycles for all 27 non-shock scenarios, using seat pan
+  acceleration.}
+  \label{tab:summary-bicycle}
+  \scriptsize
+\begin{tabular}{lllcccccccccc}
+\toprule
+        &            &         &        & .     &     & ISO      & ISO      & 10~\si{\second}    &        &      &       &       \\
+        &            &         & Target & Rep.  & RMS & Weighted & Weighted & VDV & Crest  & Peak & Band- & Dur-  \\
+        &            & Road    & Speed  & Count & Acc & RMS Acc  & RMS Mag  & Acc & Factor & Freq & width & ation \\
+Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\meter\second}\(^{-1.75}\)] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\
+\midrule
+\multirow[t]{12}{*}{keiler} & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 5.4 & 4.9 & 5.0 & 12.9 & 8.1 & 7.9 & 62.5 & 26.3 \\
+ &  &  & 20 & 2 & 9.5 & 6.7 & 6.9 & 31.9 & 10.2 & 6.8 & 82.6 & 23.0 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.2 & 1.2 & 1.3 & 2.7 & 8.2 & 7.8 & 41.6 & 25.4 \\
+ &  &  & 20 & 2 & 1.6 & 1.5 & 1.6 & 3.6 & 3.8 & 8.3 & 28.9 & 22.6 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{4}{*}{pebble, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 7.0 & 6.9 & 7.1 & 15.7 & 7.2 & 7.6 & 36.6 & 23.8 \\
+ &  &  & 20 & 1 & 12.6 & 10.7 & 10.9 & 26.6 & 9.9 & 6.8 & 74.8 & 34.0 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 1.8 & 1.8 & 1.9 & 6.4 & 8.3 & 8.1 & 18.7 & 24.6 \\
+ &  &  & 20 & 2 & 2.8 & 2.8 & 2.8 & 6.7 & 5.1 & 7.8 & 16.7 & 29.2 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{4}{*}{pebble, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 6.3 & 5.7 & 5.9 & 14.7 & 11.0 & 8.0 & 47.5 & 28.9 \\
+ &  &  & 20 & 2 & 9.8 & 7.8 & 8.0 & 28.7 & 14.4 & 7.2 & 68.3 & 21.4 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.5 & 1.5 & 1.6 & 4.9 & 8.1 & 7.6 & 18.5 & 27.8 \\
+ &  &  & 20 & 2 & 2.1 & 2.1 & 2.2 & 5.1 & 3.9 & 6.4 & 16.0 & 23.8 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\multirow[t]{15}{*}{urbanarrow} & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 4.1 & 4.1 & 12.0 & 8.3 & 7.5 & 31.9 & 24.1 \\
+ &  &  & 20 & 1 & 6.9 & 6.2 & 6.3 & 15.2 & 8.6 & 7.9 & 40.1 & 36.8 \\
+ &  &  & 25 & 1 & 7.6 & 6.8 & 6.8 & 15.1 & 7.2 & 9.2 & 47.7 & 31.7 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 0.9 & 0.9 & 0.9 & 3.6 & 9.3 & 9.4 & 33.2 & 20.4 \\
+ &  &  & 25 & 2 & 1.4 & 1.3 & 1.3 & 3.4 & 5.8 & 9.4 & 27.8 & 23.0 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{pebble, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 3 & 6.5 & 5.7 & 5.7 & 26.1 & 9.6 & 7.6 & 58.5 & 20.8 \\
+ &  &  & 20 & 1 & 9.2 & 8.5 & 8.6 & 15.5 & 9.9 & 8.0 & 53.1 & 39.1 \\
+ &  &  & 25 & 1 & 11.6 & 8.2 & 8.3 & 31.8 & 13.7 & 6.9 & 85.0 & 38.3 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.3 & 1.2 & 1.2 & 4.8 & 8.3 & 9.3 & 24.8 & 29.0 \\
+ &  &  & 25 & 2 & 2.1 & 1.9 & 1.9 & 4.7 & 5.2 & 9.7 & 24.6 & 21.5 \\
+\cline{2-13} \cline{3-13}
+ & \multirow[t]{5}{*}{pebble, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 3.9 & 3.9 & 11.5 & 13.5 & 5.8 & 46.0 & 29.1 \\
+ &  &  & 20 & 1 & 10.8 & 7.4 & 7.5 & 15.2 & 14.7 & 5.0 & 71.9 & 32.1 \\
+ &  &  & 25 & 1 & 10.6 & 7.7 & 7.8 & 36.3 & 14.7 & 6.3 & 71.0 & 30.3 \\
+\cline{3-13}
+ &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.1 & 1.0 & 1.0 & 3.8 & 9.6 & 8.8 & 28.3 & 25.3 \\
+ &  &  & 25 & 2 & 1.6 & 1.5 & 1.5 & 3.8 & 4.9 & 9.5 & 25.4 & 21.6 \\
+\cline{1-13} \cline{2-13} \cline{3-13}
+\bottomrule
+\end{tabular}
+\end{table}
+\egroup
 
@@
 %
-Figure~\ref{fig:bicycle-type-compare} compares the two cargo bicycle models which were both  fitted with the same set of two baby seats (Melia baby shell and Maxi-Cosi Pebble Pro baby seat).
-The three-wheeled Keiler sees higher accelerations compared to the two-wheeled Urban Arrow, with a pronounced increase on asphalt and a modest increase on paver bricks.
-%Both vehicles show increasing accelerations with speed.%
-
+Figure~\ref{fig:bicycle-type-compare} compares the two cargo bicycle models
+which were both fitted with the same set of two baby seats (Melia and Pebble).
+Keiler sees higher accelerations compared to the two-wheeled Urban Arrow, with a
+pronounced increase on tarmac and a modest increase on paver bricks. Both
+vehicles show increasing accelerations with speed.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-bicycle-type-compare.png}
-  \caption{Seat pan ISO 2631-1 weighted vertical RMS acceleration versus speed
+  \caption{Seat pan ISO~2631-1 weighted vertical RMS acceleration versus speed
   grouped by road surface and cargo bicycle model. Slanted lines indicate a
@@
 each road surface for each of the five strollers, lumping seat configurations
-and dummy sizes. The Maxi-Cosi Street Plus and Stokke BABYZEN YOYO 0+ strollers
-have similar mean values. The Bugaboo Fox 5 has a slightly
-lower mean for cobblestones, paver bricks, and sidewalk pavers. The Green
-Machine performs better than the modern strollers on paver bricks, but similarly
-otherwise. The Old Rusty performs better than the modern strollers on all
-surfaces except tarmac. All strollers seem to experience the same acceleration
-on tarmac. %There may be no significant difference in the acceleration experienced in each modern stroller model. 
-All road surfaces compared to tarmac
-at least double the RMS acceleration.
+and dummy sizes. The Maxi-Cosi and Stokke strollers have similar mean values.
+The Bugaboo has a slightly lower mean for cobblestones, paver bricks, and
+sidewalk pavers. The Green Machine performs better than the modern strollers on
+paver bricks, but similarly otherwise. The Old Rusty performs better than the
+modern strollers on all surfaces except tarmac. All strollers seem to experience
+similar accelerations on tarmac. All road surfaces compared to tarmac at least
+double the RMS acceleration.
 %
@@
 
+\subsection{Dominant Frequency and Bandwidth}
+%
+Figure~\ref{fig:spectra-compare} shows frequency spectra averaged over body size
+and posture for all strollers on sidewalk pavers (left) and cargo bicycles on
+paver bricks. These surfaces are highly relevant as they are common in the
+Netherlands. Apparently, the two vintage strollers show a lower peak frequency,
+which is 4.1~\si{\hertz} for Green Machine and 5.6~\si{\hertz} for Old Rusty
+whereas modern systems peak around \SIrange{7}{9}{\hertz}. This can be explained
+by the more compliant suspension of the vintage strollers. The Old Rusty shows
+the lowest acceleration peak, and the lowest RMS weighted acceleration, but
+above 30 Hz it shows the highest power of all strollers. The Keiler sees much
+higher peak values as compared to the Urban Arrow. In both cargo bicycles, the
+peak frequencies range from \SIrange{6}{10}{\hertz} and hardly depend on vehicle
+and speed. Figure~\ref{fig:peak-freq-dist} shows the distributions of the
+dominant (peak) frequency across road surface types for each of the target
+speeds. Peak frequencies range from about \SIrange{4}{11}{\hertz} across all
+trials. For strollers (5~\si{\kph}), the median frequency increases from
+sidewalk slabs to cobblestones and sidewalk pavers and then to tarmac and paver
+bricks. For cargo bicycles, the difference in peak frequency between the two
+road surfaces is not as apparent or consistent.
+%
 \begin{figure}
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-spectra-compare.png}
-  \caption{Mean amplitude spectra of each vehicle for strollers on sidewalk pavers (left) and cargo bicycles on paver bricks (right).} 
+  \caption{Mean vertical seat pan amplitude spectra of each vehicle for
+  strollers on sidewalk pavers (left) and cargo bicycles on paver bricks
+  (right).} 
   \label{fig:spectra-compare}
 \end{figure}
-
-\subsection{Dominant Frequency and Bandwidth}
-%
-Figure~\ref{fig:spectra-compare} shows frequency spectra averaged over body size and posture for all strollers on sidewalk pavers (left) and cargo bicycles on paver bricks.
-These surfaces are highly relevant as they are common in the Netherlands.
-Apparently, the two vintage strollers show a lower peak frequency, which is 4.1 Hz for green machine and 5.6 Hz for old rusty whereas modern systems peak around 7-9 Hz.
-This can be explained by the more compliant suspension of the vintage strollers.
-The old rusty shows the lowest acceleration peak, and the lowest RMS weighted acceleration, but above 30 Hz it shows the highest power of all strollers.
-The Keiler tricycle sees much higher peak values as compared to the Urban Arrow bicycle. In both cargo bicycles peak frequencies range from 6-10 Hz and hardly depend on vehicle and speed.
-Figure~\ref{fig:peak-freq-dist} shows the distributions of dominant (peak)
-frequency across road surface types for each of the target speeds. Peak
-frequencies range from about \SIrange{4}{11}{\hertz} across all trials. For
-strollers (5~\si{\kilo\meter\per\hour}), the median frequency increases from
-sidewalk slabs to cobblestones and sidewalk pavers and then to tarmac and paver
-bricks.
-%The peak frequency median does not correlate sequentially with the geometric width of the dimension of the road surface feature.
-For the cargo bicycles, the difference in peak frequency between the two road surfaces is not so apparent or consistent.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-peak-freq-dist.png}
-  \caption{Peak frequency distributions comparisons among road surfaces for each
+  \caption{Seat pan vertical peak frequency distributions comparisons among road surfaces for each
   target speed group for non-shock repetitions. The boxes bound the quartiles
   and indicate the median. The whiskers indicate the 95\textsuperscript{th}
-  percentile and circles are any outliers.}
+  percentile and circles are outliers.}
   \label{fig:peak-freq-dist}
@@
 
-Figure~\ref{fig:bandwidth-dist} gives a general indication of bandwidth (80\% of
-the amplitude spectrum content) for each of the target speed
-groups.
-On average the bandwidth is 56 Hz for modern strollers, 46 Hz for Green Machine, 105 Hz for Old Rusty, and 44 Hz for cargo bicycles.%Most frequency content is below 45~\si{\hertz} for all trials.
-%The median bandwidth across all trials is 20~\si{\hertz}.
-For the cargo bicycles, the frequency content is spread wider for paver bricks than for tarmac, but for strollers there is likely no significant difference in these surfaces.
-For strollers, sidewalk pavers, sidewalk slabs, and cobblestones have similar bandwidths.
-%However this is based on the ISO filtering which attenuated the higher frequencies.
-For the tested lying postures this weighting may have to be reconsidered, as will be addressed further in the discussion.
+Figure~\ref{fig:bandwidth-dist} gives a general indication of the bandwidth (80\% of
+the amplitude spectrum content) for each of the target speed groups. On average,
+the bandwidth is 56 Hz for modern strollers, 46 Hz for Green Machine, 105 Hz for
+Old Rusty, and 44 Hz for cargo bicycles.
 %
@@
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-bandwidth-dist.png}
-  \caption{Bandwidth (based on 80\% of the area under the ISO~2631-1 filtered
-  amplitude spectrum) for each target speed group for non-shock repetitions. The
-  boxes bound the quartiles and indicate the median. The whiskers indicate the
-  95\textsuperscript{th} percentile and circles are any outliers.}
+  \caption{Bandwidth (based on 80\% of the area under the unfiltered seat pan
+  vertical amplitude spectrum) for each target speed group for non-shock
+  repetitions. The boxes bound the quartiles and indicate the median. The
+  whiskers indicate the 95\textsuperscript{th} percentile and circles are
+  outliers.}
   \label{fig:bandwidth-dist}
@@
 the stroller and cargo bicycles, respectively. The horizontal lines in the
-figure correspond to the boundary of the ``health caution'' and  ``health risk''
-zones in the standard, which has a dependence on exposure duration. If
+figure correspond to the boundaries of the ``health caution'' and  ``health
+risk'' zones in the standard, which depend on the duration of exposure. If
 acceleration values are above the health caution zone, ISO~2631-1 states that
 ``health risks are likely'' for adults in erect seating postures for a
-continuous daily dose. It must be emphasised that the ISO~2631-1 is based on
-adults and may not result in a representative risk for infants or older
-children.
-
+continuous daily dose. It must be emphasised that ISO~2631-1 is based on adults
+and may not result in a representative risk for infants or older children.
+%
 \begin{figure}
@@
   stroller repetitions with colour representing road surface. The horizontal
-  dashed grey lines with time duration indicators are the upper bound of the
-  ISO~2631-1 ``health caution zone'' at for adults seated erectly experiencing
-  vibrations for continuous duration in a daily dose.}
+  dashed grey lines with time duration indicators are the upper bounds of the
+  ISO~2631-1 ``health caution zones'' for long-term exposure of adults seated
+  erectly, daily experiencing these vibrations with continuous duration.}
   \label{fig:health-stroller}
@@
   indicating the target speed. The horizontal dashed grey lines with time
-  duration indicators are the upper bound of the ISO~2631-1 ``health caution
-  zone'' for adults seated erectly experiencing vibrations for continuous
-  duration in a daily dose.}
+  duration indicators are the upper bounds of the ISO~2631-1 ``health caution
+  zones'' for long-term exposure of adults seated erectly, daily experiencing
+  these vibrations with continuous duration.}
   \label{fig:health-bicycle}
@@
 For the strollers, all vibration measurements were below the health caution zone
-boundary if the daily continuous exposure is less than 10~\si{\minute}.
-Additionally, all strollers pushed over tarmac were below the zone if the daily
-continuous exposure is less than 4~\si{\hour}. Pushing the Bugaboo Fox 5 and
-Maxi-Cosi Street Plus with a 0 month infant or the Stokke BABYZEN YOYO 0+ with a
-9 month infant over cobblestones and sidewalk slabs may have health risks if the
-duration exceeds 20~\si{\minute}. For almost all of the strollers pushing over
-any surface except tarmac exceeded the 1~\si{\hour} risk boundary. Notably the
-Bugaboo Fox 5 and Old Rusty with a 9 mo infant fell under the 1~\si{\hour}
-threshold for all surfaces. The 0 month dummy experienced worse accelerations
-than the 9 month dummy in the Bugaboo Fox 5 and Maxi-Cosi Street Plus, but that
-was opposite for the Stokke YOYO 0+. Old rusty showed the least overall
-acceleration magnitudes.
-
-For both cargo bicycles, the accelerations exceeded the 10~\si{\minute} health
-risk threshold when ridden above 20~\si{\kilo\meter\per\hour} on paver bricks
-and exceeded the 1~\si{\hour} health risk threshold when ridden more than
-1~\si{\hour} above 12~\si{\kilo\meter\per\hour} on paver bricks. All but the
-Keiler with the Maxi-Cosi seat and the 0 mo dummy were under the 1~\si{\hour}
-threshold for riding on tarmac at any target speed. Only the Urban Arrow with
-the 3 month dummy is (mostly) under the 4~\si{\hour} threshold when ridden at
-either speed over tarmac. The accelerations may be less when using the Meila
-Baby Shell seat versus the Maxi-Cosi car seat, this is statistically considered
-later in the results.
+boundary if the long-term daily continuous exposure is under 10~\si{\minute}.
+Additionally, all strollers pushed over tarmac were below the zone for long-term
+daily continuous exposure under 4~\si{\hour}. Pushing the Bugaboo and Maxi-Cosi
+with a 0-month-old infant or the Stokke with a 9-month-old infant over
+cobblestones and sidewalk slabs may have health risks for long-term daily
+continuous exposures exceeding 20~\si{\minute}. For almost all strollers,
+pushing over any surface except tarmac exceeded the 1~\si{\hour} risk boundary.
+Notably the Bugaboo and Old Rusty with a 9-month-old infant fell at or under the
+1~\si{\hour} threshold for all surfaces. The 0-month dummy experienced worse
+accelerations than the 9-month dummy in the Bugaboo and Maxi-Cosi, but that was
+opposite for the Stokke. Old Rusty showed the lowest overall acceleration
+magnitudes.
+
+For both cargo bicycles, accelerations exceeded the 10~\si{\minute} health risk
+threshold when ridden above 20~\si{\kilo\meter\per\hour} on paver bricks and
+exceeded the health risk threshold when ridden more than 1~\si{\hour} above
+12~\si{\kilo\meter\per\hour} on paver bricks. All but the Keiler with the Pebble
+and the 0-month dummy were below the 1~\si{\hour} threshold for riding on tarmac
+at any target speed. Only the Urban Arrow with the 3-month dummy was (mostly)
+under the 4~\si{\hour} threshold when ridden at either speed over tarmac. The
+accelerations were lower for the Melia versus the Pebble, which is statistically
+confirmed in Section~\ref{sec:statistical-results}.
 
@@
 ISO~2631-1 recommends using the magnitude of the weighted seat pan acceleration
-vector for comfort assessment. Figures \ref{fig:comfort-stroller} and
+3D vector for comfort assessment. Figures \ref{fig:comfort-stroller} and
 \ref{fig:comfort-bicycle} plot RMS of the acceleration magnitude along with the
@@
 public transit for an unspecified duration. It must be emphasised that the
-ISO~2631-1 comfort assessment is designed for adults and may not result in a
-representative comfort assessment for infants or older children. We also include
-a line representing cyclists' discomfort threshold reported by
-Gao~et.~al~\cite{Gao2018}. It is important to recognize that cyclists perched on
-a bicycle seat seem to tolerate more vibration discomfort than the public
-transit riders who were surveyed for the ISO ratings. This points to possible
-weakness in the ISO recommendations or to other factors affecting cycling
-discomfort (e.g., the ability to stand on the pedals to lower vibration to the
-body and the head).
+ISO~2631-1 comfort assessment was compiled for adults, with many warnings and
+limitations, and may not be applicable for other contexts or populations, like
+infants or older children. We also include a line representing cyclists'
+discomfort threshold reported by Gao~et.~al~\cite{Gao2018}. It is important to
+recognise that cyclists perched on a bicycle seat seem to tolerate higher
+vibration amplitudes than the public transit riders who were surveyed for the
+ISO ratings. This points to possible weakness in the ISO recommendations or to
+other factors affecting cycling discomfort (e.g., the ability to stand on the
+pedals to lower vibration to the body and the head).
 
@@
 strollers, all are at least ``a little uncomfortable'' on all surfaces. All
-strollers are ``fairly uncomfortable'' on tarmac. All other road surfaces are at
-least ``very uncomfortable''. The `Bugaboo, seat, 9 mo' and `Green Machine, cot,
-0 mo' over paver bricks and `Old Rusty, seat, 9 mo' over paver bricks, sidewalk
-pavers, and sidewalk slabs are ``very uncomfortable'', but all other strollers
-and surfaces are ``extremely uncomfortable''. The Old Rusty is the only stroller
-that falls under the cyclist threshold discomfort line for all surfaces.
+strollers but the Stokke are ``fairly uncomfortable'' on tarmac. All other road
+surfaces are at least ``very uncomfortable''. The `Bugaboo, seat, 9 mo' and
+`Green Machine, cot, 0 mo' over paver bricks and `Old Rusty, seat, 9 mo' over
+paver bricks, sidewalk pavers, and sidewalk slabs are ``very uncomfortable'',
+but all other strollers and surfaces are ``extremely uncomfortable''. The Old
+Rusty generally shows the lowest discomfort levels.
 %
@@
   \caption{ISO~2631-1 weighted seat pan magnitude RMS acceleration of all
-  stroller repetitions with colour representing road surface. The horizontal
+  stroller repetitions with colour representing the road surface. The horizontal
   dashed lines are the lower bound of the ISO~2631-1 ``comfort zones'' for
@@
 
-Both of the two cargo bicycles ridden at any tested speed over paver bricks, as
-well as the Keiler with the Maxi-Cosi seat ridden over tarmac at high speed fall
-into the category ``extremely uncomfortable''. Those are also above the the
-cyclist discomfort threshold. The other vehicle setups fall between ``fairly
-uncomfortable'' and ``very uncomfortable'' over tarmac for the range of speeds.
-The Urban Arrow with the Melia Baby Shell performs, on average, the best on
-paver bricks and tarmac at all speeds tested.
+Both cargo bicycles ridden at any tested speed over paver bricks, as well as the
+Keiler with Pebble ridden over tarmac at high speed fall into the category
+``extremely uncomfortable''. Those are also above the cyclist discomfort
+threshold. The other vehicle setups fall between ``fairly uncomfortable'' and
+``very uncomfortable'' over tarmac for all tested speeds. The Urban Arrow with
+Melia performs, on average, the best on paver bricks and tarmac at all tested
+speeds.
 %
@@
   bicycle repetitions with colour representing road surface and marker style
-  representing the target speed. The horizontal dashed lines with the upper bound of
-  the ISO~2631-1 ``comfort zones'' for adults seated erectly experiencing
-  vibrations in public transit. The horizontal dashed-dotted line is the
-  cyclists' vibration discomfort threshold as reported by
+  representing the target speed. The horizontal dashed lines with the upper
+  bound of the ISO~2631-1 ``comfort zones'' for adults seated erectly
+  experiencing vibrations in public transit. The horizontal dashed-dotted line
+  is the cyclists' vibration discomfort threshold as reported by
   Gao~et.~al~\cite{Gao2018}.}
@@
 \subsection{Statistical Results}
-%
-For strollers, Table~\ref{tab:stroller-ols} shows the results of the 11 degrees of freedom
-statistical model for the 104 repetitions~(\(R^2=0.867,F=54.69\)). Both categorical
-variables have significant effects. The intercept gives the mean acceleration of
-the Green Machine stroller pushed over tarmac, which is not significant. All
-road surfaces cause significantly more acceleration than tarmac with
-cobblestones having the largest relative effect (3.0~\si{\mps\squared} larger),
-followed by sidewalk slabs (2.7~\si{\mps\squared} larger), sidewalk pavers
-(1.8~\si{\mps\squared} larger), and paver bricks (1.6~\si{\mps\squared} larger).
-The `Bugaboo, Seat, 9 mo' and `Maxi-Cosi, Seat, 9 mo' are not significantly
-different than the `Green Machine, Cot, 0 mo' but the other strollers are. The
-`Old Rusty, Seat, 9 mo' and `Bugaboo, Cot, 0 mo' showed lower RMS acceleration
-than `Green Machine, Cot, 0 mo' by 0.8 and 0.5~\si{\mps\squared}, respectively.
-The remaining strollers have larger accelerations than the `Green Machine, Cot,
-0 Mo' on tarmac: `Maxi-Cosi, Cot, 0 mo' (1.1~\si{\mps\squared}), `Bugaboo, Cot,
-0 mo' (1.0~\si{\mps\squared}), `YOYO, Seat, 9 mo' (1.0~\si{\mps\squared}), and
-`YOYO, Seat, 0 mo' (0.6~\si{\mps\squared}).
+\label{sec:statistical-results}
+%
+For strollers, Table~\ref{tab:stroller-ols} shows the results of the 11 degrees
+of freedom statistical model for the 104 repetitions~(\(R^2=0.867,F=54.69\)).
+Both categorical variables have significant effects. The intercept gives the
+mean acceleration of the Green Machine pushed over tarmac, which is not
+significant. All road surfaces cause significantly higher acceleration than
+tarmac, with cobblestones having the largest relative effect
+(3.0~\si{\mps\squared} larger), followed by sidewalk slabs
+(2.7~\si{\mps\squared} larger), sidewalk pavers (1.8~\si{\mps\squared} larger),
+and paver bricks (1.6~\si{\mps\squared} larger). The `Bugaboo, Seat, 9 mo' and
+`Maxi-Cosi, Seat, 9 mo' are not significantly different from the `Green Machine,
+Cot, 0 mo' but the other strollers are. The `Old Rusty, Seat, 9 mo' and
+`Bugaboo, Cot, 0 mo' showed significantly lower RMS acceleration than `Green
+Machine, Cot, 0 mo' by 0.8 and 0.5~\si{\mps\squared}, respectively. The
+remaining strollers have higher accelerations than the `Green Machine, Cot, 0
+Mo' on tarmac: `Maxi-Cosi, Cot, 0 mo' (1.1~\si{\mps\squared}), `Bugaboo, Cot, 0
+mo' (1.0~\si{\mps\squared}), `Stokke, Seat, 9 mo' (1.0~\si{\mps\squared}), and
+`Stokke, Seat, 0 mo' (0.6~\si{\mps\squared}).
 %
@@
   \label{tab:stroller-ols}
-  \footnotesize
 \begin{tabular}{lcccccc}
@@
 Sidewalk Slabs                                   &       2.7754  &        0.167     &    16.637  &         0.000        &        2.444    &        3.107     \\
-bugaboo, cot, 0 mo   &       0.9706  &        0.202     &     4.813  &         0.000        &        0.570    &        1.371     \\
-bugaboo, seat, 9 mo  &      -0.5065  &        0.199     &    -2.551  &         0.012        &       -0.901    &       -0.112     \\
-maxicosi, cot, 0 mo  &       1.0795  &        0.202     &     5.353  &         0.000        &        0.679    &        1.480     \\
-maxicosi, seat, 9 mo &       0.3012  &        0.209     &     1.441  &         0.153        &       -0.114    &        0.716     \\
-oldrusty, seat, 9 mo &      -0.7551  &        0.209     &    -3.605  &         0.001        &       -1.171    &       -0.339     \\
-yoyo, cot, 0 mo     &       0.5766  &        0.209     &     2.753  &         0.007        &        0.161    &        0.993     \\
-yoyo, seat, 9 mo     &       0.9706  &        0.205     &     4.731  &         0.000        &        0.563    &        1.378     \\
+Bugaboo, cot, 0 mo   &       0.9706  &        0.202     &     4.813  &         0.000        &        0.570    &        1.371     \\
+Bugaboo, seat, 9 mo  &      -0.5065  &        0.199     &    -2.551  &         0.012        &       -0.901    &       -0.112     \\
+Maxi-Cosi, cot, 0 mo  &       1.0795  &        0.202     &     5.353  &         0.000        &        0.679    &        1.480     \\
+Maxi-Cosi, seat, 9 mo &       0.3012  &        0.209     &     1.441  &         0.153        &       -0.114    &        0.716     \\
+Old Rusty, seat, 9 mo &      -0.7551  &        0.209     &    -3.605  &         0.001        &       -1.171    &       -0.339     \\
+Stokke, cot, 0 mo     &       0.5766  &        0.209     &     2.753  &         0.007        &        0.161    &        0.993     \\
+Stokke, seat, 9 mo     &       0.9706  &        0.205     &     4.731  &         0.000        &        0.563    &        1.378     \\
 \bottomrule
@@
 
-For cargo bicycles, Table~\ref{tab:bicycle-ols} shows the results of the 8 degree of freedom statistical model for the 50 repetitions~(\(R^2=0.925,F=63.17\)). The vehicle setup
-categorical variable has significant effects, the road surface categorical
-variable alone does not, but the speed and interaction of speed with road
-surface do have significant effects. The intercept should theoretically be zero,
-because there is no vertical vibration when the speed is zero and the intercept
-is not significantly different than zero. Speed is not a significant predictor
-on tarmac, but the interaction variable shows that 0.8~\si{\mps\squared} is
-gained in acceleration for each 1~\si{\kph} increase on paver bricks. Only the
-Urban Arrow with the 3 mo infant in either seat has significant difference to
-the `Keiler, Maxi-Cosi, 3 mo', both showing reduction in relative acceleration.
+For cargo bicycles, Table~\ref{tab:bicycle-ols} shows the results of the 8
+degree of freedom statistical model for the 50
+repetitions~(\(R^2=0.925,F=63.17\)). The categorical variable for vehicle setup
+has significant effects, the categorical variable for road surface alone does
+not, but the interaction of speed with road surface does have significant
+effects. The intercept should be zero because there is no vertical vibration
+when the speed is zero which aligns with the intercept not being significantly
+different than zero. Speed is not a significant predictor on tarmac, but the
+interaction variable shows that 0.8~\si{\mps\squared} is gained in acceleration
+for each 1~\si{\kph} increase on paver bricks. The Urban Arrow with the 3~mo
+infant in either seat has significant difference to the `Keiler, Pebble, 3~mo',
+both showing reduction in relative acceleration. If the 0~mo dummy is used in
+the Keiler with the Pebble there is significantly higher vibration.
 %
@@
   \caption{Ordinary Linear Regression Results for Cargo Bicycles. Tarmac and
-  `Keiler, Maxi-Cosi, 3 mo' are the references for the categorical Road Surface
+  `Keiler, Pebble, 3 mo' are the references for the categorical Road Surface
   and Cargo Bicycle variables, respectively. The columns give the effect
@@
   \label{tab:bicycle-ols}
-  \footnotesize
 \begin{tabular}{lcccccc}
@@
 Paver Bricks                                          &       1.2956  &        0.889     &     1.457  &         0.153        &       -0.500    &        3.091     \\
-keiler, maxicosi, 0 mo     &       0.8664  &        0.415     &     2.085  &         0.043        &        0.027    &        1.705     \\
-keiler, melia, 3 mo        &      -0.5060  &        0.415     &    -1.219  &         0.230        &       -1.344    &        0.332     \\
-urban arrow, maxicosi, 0 mo &      -0.0512  &        0.404     &    -0.127  &         0.900        &       -0.867    &        0.764     \\
-urban arrow, maxicosi, 3 mo &      -0.8895  &        0.415     &    -2.141  &         0.038        &       -1.728    &       -0.051     \\
-urban arrow, melia, 3 mo    &      -1.1357  &        0.403     &    -2.819  &         0.007        &       -1.949    &       -0.322     \\
+Keiler, Pebble, 0 mo     &       0.8664  &        0.415     &     2.085  &         0.043        &        0.027    &        1.705     \\
+Keiler, Melia, 3 mo        &      -0.5060  &        0.415     &    -1.219  &         0.230        &       -1.344    &        0.332     \\
+Urban Arrow, Pebble, 0 mo &      -0.0512  &        0.404     &    -0.127  &         0.900        &       -0.867    &        0.764     \\
+Urban Arrow, Pebble, 3 mo &      -0.8895  &        0.415     &    -2.141  &         0.038        &       -1.728    &       -0.051     \\
+Urban Arrow, Melia, 3 mo    &      -1.1357  &        0.403     &    -2.819  &         0.007        &       -1.949    &       -0.322     \\
 Mean Speed [m/s]                                                                              &       0.2034  &        0.116     &     1.747  &         0.088        &       -0.032    &        0.439     \\
@@
 
-\paragraph{Vehicle Comparisons}
-%
 Given that the vehicle setup (\(x_\textrm{Stroller}\) and \(x_\textrm{Cargo
-Bicycle}\)) has a significant effect, we perform a post-hoc analysis to compare
-vehicles on each road surface. Table~\ref{tab:sig-group-stroller}, derived from
-Figure~\ref{fig:tukey-stroller} in Appendix~\ref{app:compare}, shows the
-groupings of non-significant comparisons for a Tukey Range Test among the
-strollers.
+Bicycle}\)) has a significant effect, we performed a post-hoc analysis to
+compare vehicles on each road surface. Table~\ref{tab:sig-group-stroller},
+derived from Figure~\ref{fig:tukey-stroller} in Appendix~\ref{app:compare},
+shows the groupings of non-significant comparisons for a Tukey Range Test among
+the strollers.
 Old Rusty and `Bugaboo, Seat, 9 mo' and the Green Machine perform generally
@@
 ranking.
-For cobblestones, this is also true as well as: 1) the `YOYO, Seat, 9 mo' is the
-worst stroller tested and, interestingly, the heavier dummy performs worse
-than the lighter one, 2) the 9 mo dummy experiences less acceleration in the
+For cobblestones, this is also true as well as: 1) the `Stokke, Seat, 9 mo' is
+the worst stroller tested and, interestingly, the heavier dummy performs worse
+than the lighter one; 2) the 9-month dummy experiences lower acceleration in the
 Bugaboo and Maxi-Cosi.
 For paver bricks: 1) Old Rusty, `Bugaboo, Seat, 9 mo', and Green Machine are
-again the best and 2) `YOYO, Seat, 9 mo' sees more acceleration than the 0 mo
-configuration.
-For sidewalk pavers, there is no significant difference among the strollers.
-For side walk slabs: 1) Old Rusty is the best and Bugaboo the second best,
-2) the 0 month in the Bugaboo and Maxi-Cosi see more than the 9 month in the
-same vehicle, respectively, and 3) no difference in the YOYO when comparing
-dummy sizes.
-For tarmac: the Green Machine, `Bugaboo, Seat, 9 mo', and `YOYO, Seat, 9 mo' are
-better than Maxi-cosi with either dummy size and 2) the Green Machine is better
-than the `Bugaboo, Cot, 0 mo'.
+again the best and 2) `Stokke, Seat, 9 mo' sees higher acceleration than the
+0-month configuration.
+For sidewalk pavers, there was no significant difference among all the
+strollers. For sidewalk slabs: 1) Old Rusty is the best and Bugaboo the second
+best; 2) the 0-month in the Bugaboo and Maxi-Cosi see more than the 9-month in
+the same vehicle, respectively; and 3) no difference in Stokke when comparing
+dummy sizes. For tarmac: 1) the Green Machine, `Bugaboo, Seat, 9 mo', and
+`Stokke, Seat, 9 mo' are better than Maxi-Cosi with either dummy size; and 2)
+the Green Machine is better than the `Bugaboo, Cot, 0 mo'.
 %
@@
   \midrule
-  yoyo, seat, 9 mo        & 7 & 8   & 6-8 & 1-8 & 5-6 & 1-6 \\
-  yoyo, cot, 0 mo         & 4 & 4-5 & 3-5 & 1-8 & 5-6 & 1-8 \\
-  oldrusty, seat, 9 mo    & 1 & 1-2 & 1-3 & 1-8 & 1   & 1-8 \\
-  maxicosi, seat, 9 mo    & 4 & 4-5 & 3-6 & 1-8 & 3-4 & 4-8 \\
-  maxicosi, seat, 0 mo    & 8 & 6-7 & 6-8 & 1-8 & 7-8 & 4-8 \\
-  greenmachine, cot, 0 mo & 3 & 3   & 1-3 & 1-8 & 3-4 & 1-4 \\
-  bugaboo, seat, 9 mo     & 1 & 1-2 & 1-3 & 1-8 & 2   & 1-6 \\
-  bugaboo, cot, 0 mo      & 6 & 6-7 & 3-6 & 1-8 & 7-8 & 2-8 \\
+  Bugaboo, cot, 0 mo        & 7 & 5-7 & 4-8 & 1-8 & 7-8 & 2-8 \\
+  Bugaboo, seat, 9 mo       & 2 & 1-2 & 1-5 & 1-8 & 2   & 1-6 \\
+  Green Machine, cot, 0 mo  & 3 & 3   & 1-3 & 1-8 & 3-4 & 1-5 \\
+  Maxi-Cosi, seat, 0 mo     & 8 & 5-7 & 5-8 & 1-8 & 7-8 & 4-8 \\
+  Maxi-Cosi, seat, 9 mo     & 4 & 4-5 & 3-8 & 1-8 & 3-4 & 4-8 \\
+  Old Rusty, seat, 9 mo     & 1 & 1-2 & 1-3 & 1-8 & 1   & 1-8 \\
+  Stokke, cot, 0 mo         & 5 & 4-7 & 3-6 & 1-8 & 5-6 & 1-8 \\
+  Stokke, seat, 9 mo        & 6 & 8   & 6-8 & 1-8 & 5-6 & 1-6 \\
   \bottomrule
@@
 
-When comparing the cargo bicycles, Table~\ref{tab:sig-group-bicycle}, most
+When comparing cargo bicycles (Table~\ref{tab:sig-group-bicycle}), most
 vehicle setups deliver similar acceleration to the seat pan when ridden over the
 same surface at the same target speed. For low speed on tarmac, the Urban Arrow
-with the Meila Baby Shell and a 3 mo dummy has significantly less acceleration
-than the Keiler with the Maxicosi and 0 mo dummy. There is no significant
+with Melia and a 3-month dummy has significantly less acceleration
+than the Keiler with Pebble and 0-month dummy. There is no significant
 difference in any vehicle setups at low speed on paver bricks. At higher speeds,
-the Urban Arrow and Keiler with the Meila seat and the 3 mo dummy are
-significantly better than the Keiler with the Maxicosi and the 0 mo on paver
+the Urban Arrow and Keiler with Melia and the 3-month dummy are
+significantly better than the Keiler with Pebble and the 0-month dummy on paver
 bricks and on tarmac. It is important to point out that there is no significant
-difference when simply swapping the seat for the 3 mo dummy, which does not
+difference when simply swapping the seat for the 3-month dummy, which does not
 support the hypothesis in Section~\ref{sec:health-assesment}.
@@
      \midrule
-     urban arrow, melia, 3 mo    & 1 & 1-6 & 1-5 & 1-5 & 1-5\\
-     urban arrow, maxicosi, 3 mo & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
-     urban arrow, maxicosi, 0 mo & 4 & 1-6 & 1-6 & 1-6 & 1-5\\
-     keiler, melia, 3 mo        & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
-     keiler, maxicosi, 3 mo     & 5 & 1-6 & 1-6 & 1-6 & 1-6\\
-     keiler, maxicosi, 0 mo     & 6 & 1-6 & 2-6 & 3-6 & 4-6\\
+     Keiler, Melia, 3 mo       & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
+     Keiler, Pebble, 0 mo      & 6 & 1-6 & 2-6 & 3-6 & 5-6\\
+     Keiler, Pebble, 3 mo      & 5 & 1-6 & 1-6 & 1-6 & 1-6\\
+     Urban Arrow, Melia, 3 mo  & 1 & 1-6 & 1-5 & 1-5 & 1-5\\
+     Urban Arrow, Pebble, 0 mo & 4 & 1-6 & 1-6 & 1-6 & 1-5\\
+     Urban Arrow, Pebble, 3 mo & 2 & 1-6 & 1-6 & 1-5 & 1-5\\
      \bottomrule
@@
 We have presented a comprehensive set of acceleration measurements from
-experiments that simulate vibrations experienced by infants in the 0-9
-month mass range during transportation in strollers and cargo bicycles. We
-compared the average magnitude of vertical and total acceleration at the seat
-pan across a variety of road surfaces and seats at typical 
-travel speeds. ISO~2631-1 weighted average
-acceleration can range from \SIrange{0.4}{10.7}{\mps\squared} across all tested
-scenarios. Strollers induced \SIrange{0.4}{5.0}{\mps\squared}  for a mean walking speed of 5.3~\si{\kph}. Cargo bicycles induced
+experiments that simulate vibrations experienced by infants in the 0-9-month age and mass range during transportation in strollers and cargo bicycles. We compared
+the average magnitude of vertical and total acceleration at the seat pan across
+a variety of road surfaces and seats at typical travel speeds. ISO~2631-1
+weighted average acceleration ranged from \SIrange{0.4}{10.7}{\mps\squared}
+across all tested scenarios. Strollers induced \SIrange{0.4}{5.0}{\mps\squared}
+for a mean walking speed of 5.3~\si{\kph}. Cargo bicycles induced
 \SIrange{0.6}{10.7}{\mps\squared} over a speed range of \SIrange{12}{25}{\kph}.
@@
 %
-Travelling over a tarmac surface offers the least vibration in all vehicle types
-at any speed with a maximum average acceleration of
-1.2~\si{\meter\per\second\squared}. For strollers, the roughest surfaces being cobblestones and the sidewalk slabs with large gaps cause 5\(\times\) the acceleration experienced on tarmac reaching
-5.0~\si{\meter\per\second\squared}. More common surfaces being sidewalk pavers and paver bricks, reach values up 3~\si{\meter\per\second\squared}.
+Travelling over a tarmac surface showed the least vibration in all types of
+vehicles at any speed with a range of \SIrange{0.4}{1.2}{\mps\squared}. For
+strollers, the roughest surfaces being cobblestones and sidewalk slabs with
+large gaps caused 5\(\times\) the acceleration experienced on tarmac, reaching
+5.0~\si{\mps\squared}. More common surfaces, sidewalk pavers and
+paver bricks, reach values up to 3~\si{\mps\squared}.
 
 For cargo bicycles, travelling over paver bricks at the same speeds can
-quadruple accelerations relative to asphalt.
-Travelling at the maximum allowed speed of an electric cargo bicycle (25
-\si{\kph}) over paver bricks caused average
-accelerations exceeding 8~\si{\mps\squared}. %The effect of speed on vibration is significant for paver bricks but not for tarmac.
-
-Whereas speed strongly affected the acceleration amplitude it does not strongly
-affect the peak frequency and the bandwidth below which 80\% of power is
-contained. This suggests that peak frequencies represent oscillations induced by
-the systems tested rather than dominant frequencies resulting from the road
-surface.
+quadruple average acceleration relative to tarmac. Travelling at the maximum
+allowed speed of an electric cargo bicycle (25 \si{\kph}) over paver bricks
+caused average accelerations that exceeded 8~\si{\mps\squared}. Additionally, the
+effect of speed on vibration was significant for paver bricks but not for tarmac.
+
+Whereas speed strongly affected the acceleration amplitude, it had lesser effect
+on the peak frequency and the bandwidth. Peak frequency at the highest speed was
+1.25\(\times\) higher for tarmac than paver bricks and bandwidth approximately
+doubled for paver bricks relative to tarmac at high speeds. This suggests that
+oscillations induced by the systems tested may have strong influence relative to
+dominant frequencies resulting from the road surface.
 
@@
 %
-The size of the dummy (mass and build) had no obvious and systematic effect on
-the average acceleration at the seat pan to body interface. These vibrations
-are transmitted to an infant's body, and the physical properties (mass,
-stiffness, and damping) of the infant's body determine whether this excitation is
-amplified or not and which body segment is more affected. Tests with more
-realistic dummies or real infants are necessary to investigate how the infant
-itself moves when excited by this level of vibration. This information is not
-readily available in the literature and may be hard to acquire due to ethical
-limitations and the absence of validated infant dummies. The only effect that
-stood out for mass was that, counter-intuitively, the lighter dummy has less
-acceleration than the heavier dummy for the Stokke BABYZEN YOYO 0+ stroller.
+The size of the dummy (mass and build) had no obvious systematic effect on the
+average acceleration at the seat pan. These vibrations are transmitted to
+infant's body, and the physical properties (mass, stiffness, and damping) of the
+infant's body determine whether this excitation is amplified or not and which
+body segment is more affected. Tests with more realistic dummies or real infants
+along with comparisons of equivalent vehicle setups are necessary to investigate
+how the infant itself moves when excited by this level of vibration. This
+information is not readily available in the literature and may be difficult to
+acquire due to ethical limitations and the absence of validated infant dummies.
+The only effect that stood out for mass was that, counter-intuitively, the
+lighter dummy had less acceleration than the heavier dummy for the Stokke
+stroller, but this may well be explained by the different stroller
+configurations tested for the two body sizes.
 
@@
 %
-The vibrations measured in the different scenarios showed that RMS acceleration
-can be relatively large when compared to the smoothest experience on tarmac.
-There is a large gap in the literature connecting acceleration magnitude to
-discomfort and/or health consequences, which is particularly absent for infants.
-The most used health and comfort assessment tool for whole-body vibration is the
-ISO~2631-1 standard. When we investigated health risks using the standard, we
-found that:
+Vertical RMS acceleration on uneven surfaces can be relatively large compared to
+the smoothest experience on tarmac. When we compare the vibration measured for
+infants in strollers and cargo bicycles with the ISO~2631-1 standard vibration
+``health risk zone'' as defined for long-term exposure of adults seated erectly,
+we see that:
 %
@@
     acceleration below the ``health risk zone" for 4~\si{\hour} daily duration,
-    \item strollers pushed over cobblestones and sidewalk slabs can deliver
-    accelerations in the ``health risk zone'' with durations less than
-    20~\si{\min},
-    \item cargo bicycles ridden at \SIrange{12}{25}{\kph} over tarmac
-    overwhelmingly delivered accelerations below the 1~\si{\hour} ``health risk
-    zone'', and
-    \item cargo bicycles ridden at \SIrange{12}{25}{\kph} over paver bricks
-    delivered accelerations well into the 10~\si{\min} ``health risk zone''.
+    \item walking with an infant in a stroller on cobblestones and sidewalk
+    slabs can exceed the ``health risk zone'' within 20~\si{\min} to
+    1~\si{\hour}, depending on the stroller model and the age of the child,
+    \item cargo bicycles ridden at \SIrange{12}{25}{\kph} over tarmac delivered
+    accelerations below the 1~\si{\hour} ``health risk zone'' for all but the
+    Keiler with the newborn,
+    \item cycling with an infant in a cargo bicycle on tarmac at 12~\si{\kph}
+    can be maintained for approximately two hours before exceeding the ``health
+    risk zone'',
+    \item cargo bicycles ridden at \SI{12}{\kph} over paver bricks delivered
+    accelerations exceed the 10~\si{\min} ``health risk zone'' for three of the
+    6 vehicle setups and range between \SI{1}{\hour} to \SI{20}{\minute}
+    otherwise, and
+    \item cycling with an infant in a cargo bicycle on paver bricks at
+    \SIrange{20}{25}{\kph} for 10~\si{\min} gives the infant a vibration load
+    that equals or exceeds the ``health risk zone''. 
 \end{itemize}
-%
-When we compare the vibration measured for infants in strollers and cargo
-bicycles with the vibration ``health risk zone'' as defined for adults in the
-ISO~2631-1 standard, we see that:
-%
-\begin{itemize}
-    \item cycling with an infant in a cargo bicycle on paver bricks with
-    20~\si{\kph} for 10~\si{\min} gives the infant a vibration load that equals
-    or exceeds the ``health risk zone'' for adults seated erectly experiencing
-    vibrations,
-    \item cycling with an infant in a cargo bicycle on tarmac at 12~\si{\kph} can
-    be maintained for approximately two hours before exceeding the ``health risk
-    zone'' for adults seated erectly experiencing vibrations,
-    \item walking with an infant in a stroller on cobblestones can exceed the
-    ``health risk zone'' for adults seated erectly experiencing vibrations
-    within 15~\si{\min} to 1~\si{\hour}, depending on the stroller model and the
-    age of the child, and
-    \item walking with an infant in a stroller on tarmac can be continued for
-    four hours without exceeding the ``health risk zone'' for adults seated
-    erectly experiencing vibrations.
-\end{itemize}
-
-We can conclude that strollers can be pushed over paver bricks and sidewalk
-pavers continuously for no more than half an hour. On extreme surfaces like
-cobblestones and sidewalk slabs, strollers should be pushed slower than
-5~\si{\kph} with a duration of maximal 10~\si{\min}. A stroller
-can be walked continuously for four hours only on tarmac, and only if the infant is lying in the cot.
-If the infant is sitting, the parent/caregiver would need to consider appropriate breaks to allow the infant to move. Cargo
-bicycles carrying infants over paver bricks should slow down to 12~\si{\kph} or
-preferably less, and the duration should be kept under 10~\si{\min}. When riding
-a cargo bicycle over tarmac at 20\si{\kph}, the duration should be kept under
-1~\si{\hour}. At 12~\si{\kph}, cargo bicycles can ride over tarmac for maximal
-2~\si{\hour}.
+
+When utilizing the ISO~2631-1 guidance, we can conclude that strollers can be
+pushed over paver bricks and sidewalk pavers continuously for no more than half
+an hour. On extreme surfaces like cobblestones and sidewalk slabs, strollers
+should be pushed slower than 5~\si{\kph} with a duration of maximal
+10~\si{\min}. A stroller can be walked continuously for four hours only on
+tarmac, and only if the infant is lying in the cot. If the infant is sitting,
+the parent/caregiver would need to consider appropriate breaks to allow the
+infant to move. Cargo bicycles carrying infants over paver bricks should slow
+down to 12~\si{\kph} or preferably less, and the duration should be kept under
+10~\si{\min}. When riding a cargo bicycle over tarmac at 20~\si{\kph}, the
+duration should be kept under 1~\si{\hour}. At 12~\si{\kph}, cargo bicycles can
+ride over tarmac for maximal 2~\si{\hour}.
+
+The largest unweighted RMS vertical acceleration we recorded at the seat pan was
+\SI{12.6}{\mps\squared}. Tsuijuchi et~al.~\cite{Tsujiuchi2014} studied inflicted
+head injury by shaking trauma and give evidence based on finite element
+modelling that shaking an infant at the chest with an unsupported head at
+\SI{14}{\mps\squared} for \SI{2}{\second} could rupture brain bridging veins.
+This is a largely different scenario with an unsupported head and accelerations
+acting in different directions than in our experiments, yet it is worrisome that
+the acceleration magnitudes are of the same order of magnitude.
 
@@
 %
-When considering comfort, the ISO~2631-1 guidelines indicate that adults would
+When considering comfort, the ISO~2631-1 guidelines estimate that adults would
 report the vibrations experienced in strollers and bicycles as uncomfortable.
@@
 subjective ratings of vibrations felt when riding public transit for an
-unspecified duration, so this scale is unlikely to be appropriate to apply to our
-situation. Gao~et~al.~\cite{Gao2018} report that cyclists do not rate
-vibrations as extremely uncomfortable on normal road surfaces, indicating some
-contradiction.
+unspecified duration, so we question whether the scale is appropriate for
+typical strolling and cycling durations. Furthermore, the standard extensively
+emphasises that comfort perception depends on many interacting factors.
+Gao~et~al.~\cite{Gao2018} report that cyclists do not rate vibrations as
+extremely uncomfortable on normal road surfaces, indicating a possible
+contradiction, especially given a bicycle saddle is generally perceived less
+comfortable than a chair-style seat used in the standard development. Lastly, it
+is not readily possible to assess subjective comfort directly from infants so we
+can only extrapolate from children and adult experience.
 
@@
 %
-Different vehicle, seat, and baby mass combinations cause different average
+Different combinations of vehicle, seat, and baby mass cause different average
 vertical accelerations at the seat pan. We are only able to compare vehicle
-setups, other than comparing the same two different baby seats
-in both cargo bicycles. A striking discovery is that the two 1970s strollers we
-tested were significantly better than many of the modern stroller setups on most
-road surfaces. The vintage strollers actually had more sophisticated suspension
-systems that used springs, straps, and mechanisms, and they also had larger
-wheels. Stroller manufacturers may have reduced suspension as a side effect to
-decreasing the size and weight of strollers and introducing swivelling front
-wheels (which makes steering lighter but can technically not be combined with
-the design of vintage suspension types). As an example, the ``Old Rusty'' stroller
-was the only one that did not exceed the 1~\si{\hour} health risk line for all
-road surfaces.
-
-Both the Bugaboo Fox 5 and Maxi-Cosi Street Plus stroller showed lower
-acceleration for the heavier baby, as expected, but the Stokke BABYZEN YOYO 0+
-showed the opposite trend for cobblestones and paver bricks. This points to
-design choices that may cause resonance on certain surface profiles. The
+setups, other than comparing the same two different baby seats in both cargo
+bicycles. A striking discovery is that the two tested 1970s strollers
+significantly outperformed many of the modern stroller setups on most road
+surfaces. The vintage strollers had more sophisticated suspension systems that
+used springs, straps, and larger wheels. Stroller manufacturers may have reduced
+suspension as a side effect of decreasing the size and weight of strollers and
+introducing swivelling front wheels (which makes steering lighter but which made
+manufacturers drop suspension solutions like these in the vintages products). As
+an example, the ``Old Rusty'' stroller was the only one that did not exceed the
+1~\si{\hour} health risk line for any road surface.
+
+Both the Bugaboo and Maxi-Cosi strollers showed lower accelerations for the
+heavier baby, as expected, but the Stokke stroller showed the opposite trend for
+cobblestones and paver bricks. This points to design choices in the seated
+configuration that may excite resonance on certain surface profiles. The
 `Bugaboo, Seat, 9 mo' configuration performed better than the other modern
-strollers for all non-tarmac road surfaces. Urban Arrow performed better than
-Keiler on tarmac but there is no difference on paver bricks. Additionally, there
-was no difference in the different seats for the 3 month infant. Performance of
-a vehicle setup is not necessarily constant with respect to cot or seat
-configuration; contrarily, performance is often significantly different when
-converting for different baby ages. This points towards designs that are only
-optimized for one configuration.
+strollers for all non-tarmac road surfaces. The Urban Arrow performed better
+than Keiler on tarmac but there was no difference on paver bricks. Additionally,
+there was no difference between different seats for the 3-month-old infant. The
+performance of a vehicle setup was not necessarily constant with respect to cot
+or seat configuration; contrarily, performance was often significantly different
+when converting for different baby ages. This may be due to designs being
+optimised for one configuration.
 
@@
 %
-We report RMS accelerations as well as accelerations
-weighted according to the ISO standards for vibration (VDV). Vibrations at
-frequencies between \SIrange{4.9}{10.7}{\hertz} showed to have the largest
-magnitude, but there are substantial accelerations at higher frequencies. Our results show
-substantial differences between RMS and VDV, highlighting the importance of
+We report RMS accelerations as well as the ISO~2631-1 weighted accelerations for
+comparison. Vibrations at frequencies between \SIrange{4}{11}{\hertz} showed to
+have the largest unweighted magnitude, but there are substantial accelerations
+at higher frequencies, as shown by the unweighted 80\% bandwidth. Our results
+show substantial differences between RMS and VDV, highlighting the importance of
 reviewing their meaning. These differences emerge from the high bandwidth of the
 accelerations now measured, which greatly exceed the bandwidth of accelerations
-measured with adults seated in cars (see e.g Figure 2 in
+measured with adults seated in cars (see e.g. Figure 2 in
 \cite{griffin2004experimental}). Adult experiments show that significant
@@
 is associated with the vertical dynamics of erect seated subjects, and filter
-out such high frequencies \cite{toward2011transmission,mirakhorlo2022effects}.
-However, adult experiments show higher discomfort for frequencies above
+out such high frequencies~\cite{toward2011transmission,mirakhorlo2022effects}.
+However, adult experiments show greater discomfort for frequencies above
 8~\si{\hertz} when lying with head supported with \SIrange{30}{90}{\degree} back
-inclination as compared to erect without head support \cite{BASRI2013inclined}. Higher frequencies have
-also been associated with effects on the central nervous system. For instance,
-experiments on rats showed brain injury visible in behaviour through functional
-impairment and in visual changes of brain structures in postmortem dissection
-after exposure to prolonged whole-body vibration at 30~\si{\hertz} and
+inclination compared to sitting erect without head support
+\cite{BASRI2013inclined}. Higher frequencies have also been associated with
+effects on the central nervous system. For instance, experiments on rats showed
+brain injury visible in behaviour through functional impairment and in visual
+changes of brain structures in postmortem dissection after exposure to prolonged
+whole-body vibration at 30~\si{\hertz} and
 5~\si{\mps\squared}~\cite{Yan2015_cumulative_brain_injury/j.jstrokecerebrovasdis.2015.08.007}.
@@
 warranting further research on the effects of higher frequencies, in particular
-for head supported conditions, and for children.
-Meanwhile, a conservative approach is to (also) consider the unweighted RMS in the design and evaluation of transport means for very young children.
-%The VDV showed even higher values warranting further research on the relevance of peaks and transients.
+for conditions where the head is supported and for children. Meanwhile, a
+conservative approach is to (also) consider the unweighted RMS in the design and
+evaluation of transport means for very young children.
 
@@
 cargo bicycles. If the user's behaviour is not adjusted to avoid rough surfaces
-or to travel very slowly over them when transporting an infant, there are potential
-health risks from daily and repeated exposure to large vibrations over a
-longer time. However, this has yet to be studied. There is no direct evidence that connects whole-body vibration as
-measured in this study to infant harm or negative health effects, thus we can only
-extrapolate from the limited guidelines on adults in occupational settings. We did measure vibrations that would not be permitted for adults to maintain
-long-term occupational health, and it is reasonable to believe we should not
-subject our infants to the same.
-
-It is well known that whole-body vibration can be controlled with good
-suspension design. We see this in the drastic historical evolution of suspension
-in automobiles. We do not see this same kind of attention to suspension in
-strollers, cargo bicycles, and baby seats for these vehicles. Both walking and
-cycling are well known to offer great societal and personal benefits over
-travelling by car, so it behoves us all to make transport for infants
-optimal in these two modes of transportation.
+or to travel slowly over them when transporting an infant, there are potential
+health risks and discomfort from daily and repeated exposure to large vibrations
+over a longer time. However, there is no direct evidence that connects
+whole-body vibration as measured in this study to infant harm or negative health
+effects and discomfort, thus we can only extrapolate from the limited guidelines
+on adults in occupational settings. We did measure vibrations that would not be
+permitted for adults to maintain long-term occupational health, and it is
+reasonable to believe we should not subject our infants to the same. Further
+research to establish direct evidence to infant health and comfort would
+possibly permit less conservative caution than we conclude below.
+
+It is well known that whole-body vibration can be attenuated with good
+suspension design. We see this in the drastic historical evolution of
+suspensions in automobiles, buses, trucks, and trains. We do not see this same
+kind of attention to suspension in strollers, cargo bicycles, and baby seats for
+these vehicles. Both walking and cycling are well known to offer great societal
+and personal benefits over travelling by car, so it behoves us all to optimise
+transport for infants in these two modes of transportation.
 
@@
 Our conclusions result primarily from the recommended application of ISO~2631-1.
-It is of utmost importance to recognize that this standard cautions against extending
-the use of the standard to situations for which its supporting data was not
-derived. The standard is based primarily on pre-1997 studies of adult whole-body
-vibration in occupational durations (\SIrange{4}{8}{\hour} daily dose) or during
-public transportation.
+It is of utmost importance to recognise that this standard cautions against
+extending the use of the standard to situations for which its supporting data
+were not derived. The standard is based primarily on pre-1997 studies of adult
+whole-body vibration in occupational durations (\SIrange{4}{8}{\hour} daily
+dose) or during public transport.
 %
@@
   \textbf{The recommendations in standard ISO~2631-1 have not been based on or
-  validated for infants, children, or young adults, nor for recumbent or reclined
-  seating postures with the head supported. Additionally, the admissible
-  durations for health are not validated for daily short durations or shorter
-  lifetime accumulation that dominate stroller and cargo bicycle travel with
-  infants. So our recommendations must be taken with caution, at least until
-  more research is done to improve the standard guidance.}
+  validated for infants, children, or young adults, nor for recumbent or
+  reclined seating postures with the head supported. Additionally, the
+  admissible durations for health are not validated for daily short durations or
+  shorter lifetime accumulation that dominate stroller and cargo bicycle travel
+  with infants. So, our recommendations must be taken with caution, at least
+  until more research is done to improve the standard guidance.}
 \end{quote}
@@
 \begin{enumerate}
-    \item Stroller, cargo bicycle, and seat manufacturers should test for
-    vibration for all expected surface types and ranges of relevant body sizes
-    and posture to ensure their designs isolate vibrations well for all use
+    \item Manufacturers of strollers, cargo bicycles, and seats should test for
+    vibrations for all expected surface types and ranges of relevant body sizes
+    and posture to ensure that their designs isolate vibrations well for all use
     conditions. Testing across relevant body sizes is especially important for
-    strollers, due to the high mass of the infant relative to the stroller mass.
+    strollers, due to the high mass of the infant relative to the mass of the
+    stroller.
     \item Manufacturers should collaborate in testing and report their results
-    publicly, similar to the automobile industry safety ratings. For the
+    publicly, similar to the safety ratings of the automobile industry. For the
     combined use of cargo bicycles and baby seats, manufacturers should
@@
     Useful information may be derived from past designs with better suspension.
-    \item Cycling roads should have a tarmac-like smoothness. Cobblestones
-    should be avoided.
-    \item Sidewalks should have a tarmac-like smoothness. Cobblestones should be
-    avoided for strollers.
-    \item Users should limit their speed when walking with strollers or riding
-    over surfaces rougher than tarmac, as bumpier surfaces can quickly multiply
-    the experienced accelerations.
+    \item New cycling roads and sidewalks should have a tarmac-like smoothness.
+    Cobblestones should be avoided.
+    \item Users should consider limiting their speed when walking with strollers
+    or riding over surfaces rougher than tarmac, as bumpier surfaces aggravate
+    accelerations.
     \item Users are suggested to limit the duration of transport over surfaces
     rougher than tarmac to periods that do not exceed 10-30 continuous minutes
-    depending on the system (existence of suspension, larger tyres or wheels)
-    and other countermeasures like adequate non-vibration breaks in between.
-    When transporting over tarmac, continuous durations should not exceed
-    4 hours, and need to include regular breaks, if only to give the infant
-    an opportunity to move.
-    \item Preferably ride any cargo bicycle at a speed of maximal 12~\si{\kph}
-    over surfaces rougher than tarmac. E-cargo bicycles can easily reach the
-    maximum speed of 25~\si{\kph}. Infants should only be transported for short
-    durations when riding over non-tarmac surfaces at these speeds.
-    \item Standard ISO~2631-1 is not validated to characterize health and
+    depending on the system (quality of suspension, larger tyres or wheels) and
+    other countermeasures like adequate non-vibration breaks in between. When
+    transporting over tarmac, continuous durations should not exceed 4 hours,
+    and need to include regular breaks, if only to allow the infant to move free
+    from the seat harness.
+    \item Users should preferably ride any cargo bicycle at a speed of maximal
+    12~\si{\kph} over surfaces rougher than tarmac. E-cargo bicycles can easily
+    reach the maximum speed of 25~\si{\kph}. Infants should only be transported
+    for short durations when riding over non-tarmac surfaces at these speeds.
+    \item Standard ISO~2631-1 is not validated to characterise health and
     comfort effects of vibration for infants or children, for short travel
@@
     literature assessing health and comfort levels on vibrations, and should be
-    used as a benchmark.
+    used as a benchmark. More research should be done to enable the design of a
+    standard on vibration that is applicable for infant transportation.
 \end{enumerate}
@@
 %
-We acknowledge the advice and financial support of VeiligheidNL.
+Niel Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, Idsart
+Kignma, Darek Wieckowksi, Aernout Dijkstra-Hellinga, and  Clement Moe all
+provided important feedback on the preprint that helped improve the paper. This
+work was financially supported by VeiligheidNL under the ``Project Trillingen
+bakfiets en wandelwagen.''
+
+\subsection{Declaration of Interest Statement}
+%
+The authors report there are no competing interests to declare.
+
+\subsection{Data Availability Statement}
+%
+TODO
 
@@
 %
-Figure~\ref{fig:compare-bicycle-speed} shows the variation in ISO~2631-1 weighted vertical RMS acceleration across the tested speeds. Paver bricks result in about  4-5\(\times\) higher
-accelerations compared to tarmac. On paver bricks, the RMS acceleration
-increased by about 1.6\(\times\) when increasing the speed from
-\SIrange{12}{25}{\kilo\meter\per\hour}. The effect of speed while cycling over
-tarmac was less drastic, but also shows a slight increase.
+Figure~\ref{fig:compare-bicycle-speed} shows the variation in ISO~2631-1
+weighted vertical RMS acceleration across the tested speeds. On paver
+bricks, the RMS acceleration increased by approximately 1.6\(\times\) when increasing
+the speed from \SIrange{12}{25}{\kilo\meter\per\hour}.The effect of speed while cycling on tarmac was less drastic, but still showed a slight increase.
 
@@
 Figure~\ref{fig:compare-baby-mass} shows the ISO~2631-1 weighted vertical RMS
-acceleration for each repetition for all vehicles, comparing among dummy sizes.
-The substantial variation has been shown to relate significantly to surface and within cargo bicycles also to speed (see tables \ref{tab:sig-group-stroller},\ref{tab:sig-group-bicycle}).
+acceleration for each repetition for all vehicles, and compares the dummy sizes.
+Substantial variation has been shown to relate significantly to the surface and
+within cargo bicycles, as well as to speed (see tables
+\ref{tab:sig-group-stroller},\ref{tab:sig-group-bicycle}).
 %There were larger accelerations in the bicycle (high speeds) versus the stroller (low speeds), likely mostly attributed to the different testing speeds. 
 When comparing the vertical RMS acceleration values between cargo bicycles and
-strollers there are no obvious differences due to baby size, i.e. each dummy
-size experienced a similar range of acceleration magnitudes when vehicle type
-and road surface are ignored. For the bicycles, the lightest dummy sometimes
-experienced higher acceleration than the heavier dummy, but high and low
-accelerations are seen across the speed range tested.
+strollers, there are no obvious differences due to baby size, i.e. each dummy
+size experienced a similar range of acceleration magnitudes when the vehicle type
+and the road surface are ignored. For bicycles, the lightest dummy sometimes
+experienced a higher acceleration than the heavier dummy, but high and low
+accelerations were observed across the tested speed range.
 %
@@
 acceleration from repetitions grouped into the various road surfaces tested. All
-vehicles were tested on paver bricks and tarmac but only strollers were tested
-on cobblestones and sidewalk pavers and sidewalk slabs, i.e. light colour dots
+vehicles were tested on paver bricks and tarmac, but only strollers were tested
+on cobblestones, sidewalk pavers, and sidewalk slabs, i.e. light colour dots
 (strollers are present in each column).
@@
 all strollers.
-Paver bricks and sidewalk pavers seem to have a similar range of RMS
+Paver bricks and sidewalk pavers appear to have a similar range of RMS
 acceleration for the same 5~\si{\kilo\meter\per\hour} walking speeds.
-Paver bricks cause relatively large accelerations at high travel speeds in the
-cargo bicycles.
+Paver bricks cause relatively large accelerations at high travel speeds in
+cargo bicycles. Paver bricks result in approximately 4-5\(\times\) higher accelerations compared to tarmac.
 %
@@
 \end{figure}
-
-\section{Experimental Equipment}
-\label{app:equipment}
- The following lists the dummies used:
-%
-\begin{description}
-  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
-  ``Andi Asleep'' (product code AW380008).
-  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
-
-  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
-  ``Asia - Limited Edition'' (product code 300287).
-  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
-  \item[Dummy 9 months] weight 8.90~\si{\kg}, size 70~\si{\cm}. Dollkit 28'',
-  ``Hailey'' (product code 304137).
-  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
-\end{description}
-%
-In this section, we report the pictures of the strollers and bicycles used for
-the experiments. The reader can find the measurements, wheelbase, wheel
-diameter, sensor location and orientation for all the tested vehicles.
-
-\begin{description}
-\item[Strollers] A selection of vintage and modern strollers for carrying
-infants. The modern strollers are configurable as cots for newborns and as seats
-for older infants.
-%
-\begin{description}
-  \item[Maxi-Cosi Street Plus] This stroller comes with a cot configuration (0-6
-  months) and an infant seat option. It has large wheels with only a marginal suspension system.
-  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
-  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the market. It has only a marginal suspension system and smaller wheels compared to other strollers available on the market.
-  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
-  rented for the experiment})
-  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system that makes
-  it an all-terrain stroller according to the manufacturer. It has large
-  puncture-resistant tyres and an air-permeable mattress.
-  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
-  website})
-  \item[Green Machine] An unknown brand vintage perambulator with a cot, dating
-  approximately from the 1970s that includes a leather strap suspended cot in a
-  metal frame. The wheels are relatively large compared to modern strollers.
-  \item[Old Rusty] An unknown brand vintage seat-style stroller dating approximately from the 1970s that includes a metal spring suspension system and wheels that are slightly larger than those on modern strollers.
-\end{description}
-\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
-seats can be mounted.
-%
-\begin{description}
-  \item[Urban Arrow Cargo Bicycle] An electric cargo bicycle that is popular in The Netherlands.
-This vehicle has two inline wheels, which makes it roll into curves like a regular bicycle.
-It is featured by a long frame that can carry loads (e.g., a child in a car seat or a baby shell) placed in between the rider and the front wheel.
-  (\href{https://urban arrow.com/}{Urban Arrow website})
-  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
-  rear) cargo tricycle without electric assist. This vehicle will not roll into
-  curves. However, differing road surface unevenness at the left and right front
-  wheels will induce lateral roll and lateral acceleration in infants. We added
-  masses in specific locations to simulate the presence of an electric motor and
-  battery package, in order to compare the results with those of the Urban Arrow cargo bike. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
-  Webpage}) 
-\end{description}
-\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
-cargo bicycles.
-%
-\begin{description}
-  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
-  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
-  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
-  adapter was used in both cargo bicycles.
-    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
-    Webpage})
-  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
-  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
-  cargo bicycles.
-    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
-    Webpage})
-\end{description}
-\end{description}
-\begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Joolz_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_UA-Joolz_front.pdf}}
-  \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
-  Maxicosi-Joolz baby Pebble.}
-  \label{fig:tech_drawing_UA_Joolz}
-\end{figure}
-
-\begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_UA-Melia_front.pdf}}
-  \caption{IMU locations on the Urban Arrow cargo bicycle, equipped with the
-  Melia baby shell.}
-  \label{fig:tech_drawing_UA_Melia}
-\end{figure}
-
-\clearpage
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Joolz_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_Trike-Joolz_front.pdf}}
-  \caption{IMU locations on the Keiler Tricycle, equipped with the
-  Maxicosi-Joolz baby pebble.}
-  \label{fig:tech_drawing_Trike_Joolz}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Melia_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Melia_front.pdf}}
-  \caption{IMU locations on the Keiler Tricycle, equipped with the
-  Melia baby shell.}
-  \label{fig:tech_drawing_Trike_Melia}
-\end{figure}
-
-\clearpage
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_front.pdf}}
-  \caption{IMU locations on the stroller Bugaboo Fox 5, configured for 0-months baby.}
-  \label{fig:tech_drawing_Bugaboo0}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Bugaboo9_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo9_front.pdf}}
-  \caption{IMU locations on the stroller Bugaboo Fox 5, configured for 9-months baby.}
-  \label{fig:tech_drawing_Bugaboo9}
-\end{figure}
-
-\clearpage
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Maxicosi0_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Maxicosi0_front.pdf}}
-  \caption{IMU locations on the stroller Maxi-Cosi Street Plus, configured for 0-months baby.}
-  \label{fig:tech_drawing_Maxicosi0}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Maxicosi9_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=70mm,angle=-90]{fig/TechDraw_Maxicosi9_front.pdf}}
-  \caption{IMU locations on the stroller Maxi-Cosi Street Plus, configured for 9-months baby.}
-  \label{fig:tech_drawing_Maxicosi9}
-\end{figure}
-
-\clearpage
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_YOYO0_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO0_front.pdf}}
-  \caption{IMU locations on the stroller Stokke BABYZEN YOYO 0+, configured for 0-months baby.}
-  \label{fig:tech_drawing_YOYO0}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_YOYO9_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO9_front.pdf}}
-  \caption{IMU locations on the stroller Stokke BABYZEN YOYO 0+, configured for 9-months baby.}
-  \label{fig:tech_drawing_YOYO9}
-\end{figure}
-
-\clearpage
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_GreenM0_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_GreenM0_front.pdf}}
-  \caption{IMU locations on the vintage stroller Green Machine, configured for 0-months baby.}
-  \label{fig:tech_drawing_GreenM0}
-\end{figure}
-
-\begin{figure}[htbp]
-  \centering
-  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_OldR9_lat.pdf}}
-  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_OldR9_front.pdf}}
-  \caption{IMU locations on the vintage stroller Old Rusty, configured for 9-months baby.}
-  \label{fig:tech_drawing_OldR9}
-\end{figure}
-
-\clearpage
-\newpage
-
-\section{Location and pictures of the experiment areas}
-\label{app:location}
-
-\subsection{For Bicycles}
-
-\begin{itemize}
-    \item Tarmac
-\begin{figure}[htbp]
-  \centering
-  {\includegraphics[width=70mm, angle=-90]{fig/Tarmac_bicycle.pdf}}
-  \caption{Tarmac surface where we tested bicycles.}
-  \label{fig:tarmac_bicycle}
-\end{figure}
-
-The bicycle experiment on the tarmac was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands (GPS coordinates: 52.001053, 4.369071).
-
-    \item Paver bricks
-\begin{figure}[htbp]
-  \centering
- {\includegraphics[width=70mm, angle=-90]{fig/Paver_bricks_bicycle.pdf}}
-  \caption{Paver bricks surface where we tested bicycles.}
-  \label{fig:paver_bricks_bicycle}
-\end{figure}
-
-The bicycle experiment on the paver bricks was conducted along Kanaalweg, 2611 DD Delft, The Netherlands (GPS coordinates: 52.006264, 4.363013).\\
-Details of paver brick: rectangular shape, dimensions 195 x 95 mm (gap in between: 7±2 mm).
-
-\clearpage
-
-    \item Shock
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=70mm, angle=0]{fig/Shock_bicycle.pdf}
-  \caption{We performed a shock test with bicycles riding over a 30x30 mm square section bar.}
-  \label{fig:shock_bicycle}
-\end{figure}
-
-The bicycle shock experiment was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands (same location of the experiment on the tarmac, GPS coordinates: 52.001053, 4.369071).\\
-Details of the shock experiment: we rode over a squared section aluminium bar 30 x 30 mm.
-
-\end{itemize}
-
-\subsection{For Strollers}
-
-\begin{itemize}
-    \item Tarmac
-
-\begin{figure}[htbp]
-  \centering
-    \includegraphics[width=70mm, angle=-90]{fig/Tarmac_stroller.pdf}
-  \caption{Tarmac test area.}
-  \label{fig:tarmac_stroller}
-\end{figure}
-
-The bicycle experiment on the tarmac was conducted along Julianalaan Straat, 2628 BG Delft, The Netherlands (GPS coordinates: 52.002727, 4.366845).
-
-\clearpage
-
-    \item Cobblestone
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=60mm, angle=-90]{fig/Cobblestone_stroller.pdf}
-  \caption{Cobblestone surface where we tested strollers.}
-  \label{fig:cobblestone_area_stroller}
-\end{figure}
-
-The bicycle experiment on the cobblestone was conducted along Julianalaan Straat, 2628 BG Delft, The Netherlands (GPS coordinates: 52.002727, 4.366845).
-Details of cobblestone: rectangular shape, dimensions 180 x 125 mm (gap in between: 20±4 mm).
-
-    \item Sidewalk pavers
-
-\begin{figure}[htbp]
-  \centering
-    \includegraphics[width=60mm, angle=-90]{fig/Sidewalk_pavers_stroller.pdf}
-  \caption{Sidewalk pavers test area for strollers.}
-  \label{fig:sidewalkpavers_area_stroller}
-\end{figure}
-
-The experiment was conducted along Prins Bernhardlaan, 2628 CN Delft, The Netherlands (same location as Paver bricks test, GPS coordinates: 52.003147, 4.369530).\\
-Details of sidewalk bricks: rectangular shape, dimensions 290 x 290 mm (gap in between: 12±2 mm).
-
-\clearpage
-
-    \item Sidewalk slabs
-
-\begin{figure}[htbp]
-  \centering
-    \includegraphics[width=70mm, angle=-90]{fig/Sidewalk_slabs_stroller.pdf}
-  \caption{Sidewalk slab test area where we conducted test with strollers.}
-  \label{fig:sidewalkslabs_area_stroller}
-\end{figure}
-
-The experiment was conducted in front of TU Delft Aula Conference Centre (Building 20), Mekelweg 5, 2628 CC Delft, The Netherlands (GPS coordinates: 52.002250, 4.372665).\\
-Details of sidewalk slab: made of concrete, rectangular shape, dimensions 2000 x 990 mm (gap in between: 160±3 mm).
-
-    \item Paver bricks
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=50mm, angle=-90]{fig/Paver_bricks_stroller.pdf}
-  \caption{Details of the paver bricks test area.}
-  \label{fig:paverbrick_area_stroller}
-\end{figure}
-
-The experiment was conducted along Prins Bernhardlaan, 2628 CN Delft, The Netherlands (same location as Sidewalk paver test, GPS coordinates: 52.003147, 4.369530).\\
-Details of paver brick: rectangular shape, dimensions 195 x 95 mm (gap in between: 7±2 mm).
-
-\clearpage
-
-    \item Shock
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=60mm, angle=-90]{fig/Shock_stroller.pdf}
-  \caption{Area where we tested strollers during the shock experiment.}
-  \label{fig:shock_area_stroller}
-\end{figure}
-
-The experiment was conducted inside TU Delft Mechanical Engineering faculty (Building 34 - Ground floor, aisle in front of Gezelschap Leeghwater office), Mekelweg 2, 2628 CD Delft, The Netherlands (GPS coordinates: 52.000587, 4.372224).\\
-Details of the shock experiment: we pushed the stroller over a squared section aluminium bar 30 x 30 mm.
-
-\end{itemize}
-
-\newpage
-\section{Table of Metrics - move to main text?}
-\label{app:results}
-%
-Table~\ref{tab:summary-stroller} and Table~\ref{tab:summary-bicycle} show mean
-values over the scenario repetitions. They report the unweighted and ISO~2631-1
-weighted seat pan vertical RMS acceleration, weighted seat pan magnitude RMS
-acceleration, unweighted seat pan vertical VDV for the first 10 seconds of the
-repetition, crest factor, peak frequency, bandwidth, and duration for all 67
-combinations of vehicle setup, road surface, and target speed.
-% NOTE : These tables are generated automatically from the Python scripts. I manually edit the header rows to fit on the page width. Save the edits between toprule and midrule!
-\bgroup
-\setlength\tabcolsep{0.4mm}  % reduces horiztonal padding between columns
-\begin{table}[!ht]
-  \centering
-  \caption{Mean computed metrics of the strollers for all 40 non-shock
-  scenarios, using seat pan acceleration.}
-  \label{tab:summary-stroller}
-  \scriptsize
-\begin{tabular}{lllcccccccccc}
-\toprule
-        &            &         &        & .     &     & ISO      & ISO      &     &        &      &       &       \\
-        &            &         & Target & Rep.  & RMS & Weighted & Weighted & VDV & Crest  & Peak & Band- & Dur-  \\
-        &            & Road    & Speed  & Count & Acc & RMS Acc  & RMS Mag  & Acc & Factor & Freq & width & ation \\
-Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\meter\second}\(^{-1.75}\)] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\
-\midrule
-\multirow[t]{10}{*}{bugaboo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.4 & 4.3 & 4.5 & 11.5 & 6.2 & 6.5 & 20.5 & 20.4 \\
-\cline{3-13}
- &  & Paver Bricks & 5 & 3 & 2.6 & 2.4 & 2.5 & 6.1 & 4.1 & 9.5 & 23.4 & 23.3 \\
-\cline{3-13}
- &  & Sidewalk Pavers & 5 & 2 & 2.9 & 2.7 & 2.9 & 15.6 & 13.5 & 6.1 & 49.8 & 25.4 \\
-\cline{3-13}
- &  & Sidewalk Slabs & 5 & 3 & 4.8 & 4.7 & 4.8 & 12.5 & 6.4 & 5.8 & 30.6 & 20.2 \\
-\cline{3-13}
- &  & Tarmac & 5 & 2 & 0.7 & 0.6 & 0.7 & 1.7 & 3.3 & 10.1 & 33.3 & 23.1 \\
-\cline{2-13} \cline{3-13}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 4 & 2.5 & 2.3 & 2.5 & 6.2 & 4.7 & 6.6 & 37.9 & 22.5 \\
-\cline{3-13}
- &  & Paver Bricks & 5 & 3 & 2.3 & 1.8 & 1.8 & 5.2 & 3.8 & 9.4 & 43.2 & 22.6 \\
-\cline{3-13}
- &  & Sidewalk Pavers & 5 & 3 & 1.7 & 1.4 & 1.6 & 4.5 & 5.5 & 7.7 & 39.5 & 24.7 \\
-\cline{3-13}
- &  & Sidewalk Slabs & 5 & 3 & 2.4 & 2.2 & 2.3 & 5.9 & 5.3 & 6.0 & 36.6 & 24.5 \\
-\cline{3-13}
- &  & Tarmac & 5 & 2 & 0.6 & 0.4 & 0.5 & 1.6 & 6.5 & 8.4 & 51.2 & 34.6 \\
-\cline{1-13} \cline{2-13} \cline{3-13}
-\multirow[t]{5}{*}{greenmachine} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 3.2 & 2.9 & 3.4 & 7.2 & 5.3 & 4.1 & 38.1 & 23.7 \\
-\cline{3-13}
- &  & Paver Bricks & 5 & 2 & 1.6 & 1.3 & 1.6 & 3.2 & 4.5 & 4.2 & 47.4 & 29.6 \\
-\cline{3-13}
- &  & Sidewalk Pavers & 5 & 2 & 2.7 & 2.5 & 2.9 & 7.4 & 6.5 & 4.1 & 41.3 & 28.2 \\
-\cline{3-13}
- &  & Sidewalk Slabs & 5 & 3 & 3.5 & 3.2 & 3.4 & 7.6 & 6.7 & 3.9 & 36.0 & 23.9 \\
-\cline{3-13}
- &  & Tarmac & 5 & 2 & 0.5 & 0.4 & 0.7 & 1.1 & 4.1 & 4.2 & 52.5 & 22.1 \\
-\cline{1-13} \cline{2-13} \cline{3-13}
-\multirow[t]{10}{*}{maxicosi} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 4 & 4.6 & 4.4 & 4.5 & 11.3 & 4.9 & 8.1 & 51.2 & 20.7 \\
-\cline{3-13}
- &  & Paver Bricks & 5 & 2 & 3.2 & 2.8 & 2.9 & 7.5 & 3.9 & 10.4 & 53.6 & 27.2 \\
-\cline{3-13}
- &  & Sidewalk Pavers & 5 & 3 & 3.0 & 2.9 & 3.0 & 8.3 & 5.5 & 7.6 & 40.1 & 21.4 \\
-\cline{3-13}
- &  & Sidewalk Slabs & 5 & 3 & 5.0 & 4.6 & 4.7 & 13.8 & 8.2 & 5.1 & 70.3 & 16.3 \\
-\cline{3-13}
- &  & Tarmac & 5 & 2 & 0.9 & 0.8 & 0.8 & 2.1 & 8.0 & 9.6 & 43.4 & 34.3 \\
-\cline{2-13} \cline{3-13}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 4.1 & 3.7 & 3.8 & 10.4 & 5.8 & 8.0 & 46.9 & 25.9 \\
-\cline{3-13}
- &  & Paver Bricks & 5 & 2 & 3.0 & 2.4 & 2.4 & 6.9 & 3.4 & 9.7 & 57.4 & 27.8 \\
-\cline{3-13}
- &  & Sidewalk Pavers & 5 & 2 & 2.6 & 2.3 & 2.5 & 7.2 & 5.5 & 7.3 & 47.2 & 27.8 \\
-\cline{3-13}
- &  & Sidewalk Slabs & 5 & 3 & 3.1 & 2.9 & 3.0 & 7.8 & 5.4 & 6.9 & 51.4 & 25.6 \\
-\cline{3-13}
- &  & Tarmac & 5 & 2 & 1.0 & 0.7 & 0.8 & 2.6 & 5.8 & 10.2 & 55.5 & 36.1 \\
-\cline{1-13} \cline{2-13} \cline{3-13}
-\multirow[t]{5}{*}{oldrusty} & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 2 & 4.7 & 2.0 & 2.3 & 13.0 & 6.0 & 5.1 & 105.1 & 29.9 \\
-\cline{3-13}
- &  & Paver Bricks & 5 & 3 & 3.4 & 1.2 & 1.4 & 8.7 & 6.1 & 5.2 & 106.1 & 21.9 \\
-\cline{3-13}
- &  & Sidewalk Pavers & 5 & 2 & 3.3 & 1.4 & 1.7 & 9.7 & 9.7 & 5.4 & 104.2 & 27.3 \\
-\cline{3-13}
- &  & Sidewalk Slabs & 5 & 3 & 3.2 & 1.6 & 1.7 & 10.5 & 11.6 & 5.3 & 103.9 & 23.8 \\
-\cline{3-13}
- &  & Tarmac & 5 & 2 & 1.1 & 0.5 & 0.6 & 2.7 & 5.7 & 7.0 & 105.5 & 22.6 \\
-\cline{1-13} \cline{2-13} \cline{3-13}
-\multirow[t]{10}{*}{yoyo} & \multirow[t]{5}{*}{cot, 0 mo} & Cobblestones & 5 & 3 & 4.1 & 4.0 & 4.1 & 10.5 & 4.8 & 6.4 & 66.3 & 21.3 \\
-\cline{3-13}
- &  & Paver Bricks & 5 & 2 & 3.0 & 2.1 & 2.2 & 6.9 & 4.1 & 9.4 & 97.7 & 29.5 \\
-\cline{3-13}
- &  & Sidewalk Pavers & 5 & 3 & 2.8 & 2.6 & 2.7 & 7.0 & 5.5 & 6.7 & 69.9 & 22.2 \\
-\cline{3-13}
- &  & Sidewalk Slabs & 5 & 2 & 4.0 & 3.8 & 3.9 & 11.6 & 6.4 & 5.2 & 79.1 & 25.7 \\
-\cline{3-13}
- &  & Tarmac & 5 & 2 & 0.9 & 0.6 & 0.6 & 2.8 & 7.4 & 7.7 & 89.3 & 19.5 \\
-\cline{2-13} \cline{3-13}
- & \multirow[t]{5}{*}{seat, 9 mo} & Cobblestones & 5 & 3 & 5.2 & 4.9 & 5.0 & 12.4 & 4.4 & 7.7 & 69.1 & 21.5 \\
-\cline{3-13}
- &  & Paver Bricks & 5 & 3 & 3.6 & 3.0 & 3.0 & 8.2 & 3.8 & 10.4 & 93.4 & 22.5 \\
-\cline{3-13}
- &  & Sidewalk Pavers & 5 & 2 & 3.1 & 2.7 & 2.8 & 11.9 & 9.9 & 8.3 & 78.3 & 28.5 \\
-\cline{3-13}
- &  & Sidewalk Slabs & 5 & 3 & 4.0 & 3.7 & 3.8 & 9.7 & 6.2 & 5.3 & 69.7 & 23.3 \\
-\cline{3-13}
- &  & Tarmac & 5 & 2 & 0.7 & 0.4 & 0.5 & 1.9 & 6.3 & 11.1 & 95.6 & 39.1 \\
-\cline{1-13} \cline{2-13} \cline{3-13}
-\bottomrule
-\end{tabular}
-\end{table}
-\egroup
-
-\bgroup
-\setlength\tabcolsep{0.4mm}  % reduces horiztonal padding between columns
-\begin{table}[!ht]
-  \centering
-  \caption{Mean computed metrics of the cargo bicycles for all 27 non-shock scenarios, using seat pan
-  acceleration.}
-  \label{tab:summary-bicycle}
-  \scriptsize
-\begin{tabular}{lllcccccccccc}
-\toprule
-        &            &         &        & .     &     & ISO      & ISO      &     &        &      &       &       \\
-        &            &         & Target & Rep.  & RMS & Weighted & Weighted & VDV & Crest  & Peak & Band- & Dur-  \\
-        &            & Road    & Speed  & Count & Acc & RMS Acc  & RMS Mag  & Acc & Factor & Freq & width & ation \\
-Vehicle & Seat, Baby & Surface & [\si{\kph}] & & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\mps\squared}] & [\si{\meter\second}\(^{-1.75}\)] & & [\si{\hertz}] & [\si{\hertz}]       & [\si{\second}]       \\
-\midrule
-\multirow[t]{12}{*}{keiler} & \multirow[t]{4}{*}{maxicosi, 0 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 7.0 & 6.9 & 7.1 & 15.7 & 7.2 & 7.6 & 36.6 & 23.8 \\
- &  &  & 20 & 1 & 12.6 & 10.7 & 10.9 & 26.6 & 9.9 & 6.8 & 74.8 & 34.0 \\
-\cline{3-13}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 1.8 & 1.8 & 1.9 & 6.4 & 8.3 & 8.1 & 18.7 & 24.6 \\
- &  &  & 20 & 2 & 2.8 & 2.8 & 2.8 & 6.7 & 5.1 & 7.8 & 16.7 & 29.2 \\
-\cline{2-13} \cline{3-13}
- & \multirow[t]{4}{*}{maxicosi, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 6.3 & 5.7 & 5.9 & 14.7 & 11.0 & 8.0 & 47.5 & 28.9 \\
- &  &  & 20 & 2 & 9.8 & 7.8 & 8.0 & 28.7 & 14.4 & 7.2 & 68.3 & 21.4 \\
-\cline{3-13}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.5 & 1.5 & 1.6 & 4.9 & 8.1 & 7.6 & 18.5 & 27.8 \\
- &  &  & 20 & 2 & 2.1 & 2.1 & 2.2 & 5.1 & 3.9 & 6.4 & 16.0 & 23.8 \\
-\cline{2-13} \cline{3-13}
- & \multirow[t]{4}{*}{melia, 3 mo} & \multirow[t]{2}{*}{Paver Bricks} & 12 & 2 & 5.4 & 4.9 & 5.0 & 12.9 & 8.1 & 7.9 & 62.5 & 26.3 \\
- &  &  & 20 & 2 & 9.5 & 6.7 & 6.9 & 31.9 & 10.2 & 6.8 & 82.6 & 23.0 \\
-\cline{3-13}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.2 & 1.2 & 1.3 & 2.7 & 8.2 & 7.8 & 41.6 & 25.4 \\
- &  &  & 20 & 2 & 1.6 & 1.5 & 1.6 & 3.6 & 3.8 & 8.3 & 28.9 & 22.6 \\
-\cline{1-13} \cline{2-13} \cline{3-13}
-\multirow[t]{15}{*}{urban arrow} & \multirow[t]{5}{*}{maxicosi, 0 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 3 & 6.5 & 5.7 & 5.7 & 26.1 & 9.6 & 7.6 & 58.5 & 20.8 \\
- &  &  & 20 & 1 & 9.2 & 8.5 & 8.6 & 15.5 & 9.9 & 8.0 & 53.1 & 39.1 \\
- &  &  & 25 & 1 & 11.6 & 8.2 & 8.3 & 31.8 & 13.7 & 6.9 & 85.0 & 38.3 \\
-\cline{3-13}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.3 & 1.2 & 1.2 & 4.8 & 8.3 & 9.3 & 24.8 & 29.0 \\
- &  &  & 25 & 2 & 2.1 & 1.9 & 1.9 & 4.7 & 5.2 & 9.7 & 24.6 & 21.5 \\
-\cline{2-13} \cline{3-13}
- & \multirow[t]{5}{*}{maxicosi, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 3.9 & 3.9 & 11.5 & 13.5 & 5.8 & 46.0 & 29.1 \\
- &  &  & 20 & 1 & 10.8 & 7.4 & 7.5 & 15.2 & 14.7 & 5.0 & 71.9 & 32.1 \\
- &  &  & 25 & 1 & 10.6 & 7.7 & 7.8 & 36.3 & 14.7 & 6.3 & 71.0 & 30.3 \\
-\cline{3-13}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 2 & 1.1 & 1.0 & 1.0 & 3.8 & 9.6 & 8.8 & 28.3 & 25.3 \\
- &  &  & 25 & 2 & 1.6 & 1.5 & 1.5 & 3.8 & 4.9 & 9.5 & 25.4 & 21.6 \\
-\cline{2-13} \cline{3-13}
- & \multirow[t]{5}{*}{melia, 3 mo} & \multirow[t]{3}{*}{Paver Bricks} & 12 & 2 & 4.5 & 4.1 & 4.1 & 12.0 & 8.3 & 7.5 & 31.9 & 24.1 \\
- &  &  & 20 & 1 & 6.9 & 6.2 & 6.3 & 15.2 & 8.6 & 7.9 & 40.1 & 36.8 \\
- &  &  & 25 & 1 & 7.6 & 6.8 & 6.8 & 15.1 & 7.2 & 9.2 & 47.7 & 31.7 \\
-\cline{3-13}
- &  & \multirow[t]{2}{*}{Tarmac} & 12 & 3 & 0.9 & 0.9 & 0.9 & 3.6 & 9.3 & 9.4 & 33.2 & 20.4 \\
- &  &  & 25 & 2 & 1.4 & 1.3 & 1.3 & 3.4 & 5.8 & 9.4 & 27.8 & 23.0 \\
-\cline{1-13} \cline{2-13} \cline{3-13}
-\bottomrule
-\end{tabular}
-\end{table}
-\egroup
 
@@
 results listed in Table~\ref{tab:shock} for different vehicles and
-configurations. There is a significant variation among tests, with the peaks for
-the bicycles sometimes reaching the accelerometer's full scale (\(\pm\)16~g).
-While the seat pan accelerations for the strollers are generally lower than
-those experienced with the bicycles, the configuration (0 or 9 months) may play
-a large role. Among bicycles, the Melia baby shell seems to transmit
-lower accelerations compared to Maxi-Cosi, 3 months, for both the Keiler
-tricycle and the Urban Arrow. Strollers with the baby seat configuration for 9
+configurations. There is a significant variation between tests, with the peaks for
+the bicycles sometimes reaching the full scale of the accelerometer (\(\pm\)16~g).
+The seat pan accelerations for strollers are generally lower than
+those experienced with bicycles, but in strollers the configuration (0 or 9 months) may play
+a large role. Among bicycles, the Melia seems to transmit
+lower accelerations compared to Pebble, 3 months, for both the Keiler and the Urban Arrow. Strollers with the baby seat configuration for 9
 months show much lower acceleration compared to the baby cot for 0 months
@@
 Machine) performed very well during the shock test, resulting in the lowest seat
-pan acceleration among all the tested vehicles.
+pan acceleration among all the vehicles tested.
 Figure~\ref{fig:shock_vehicle_comparison} shows the peaks of the vertical
@@
 Green Machine show lower acceleration values. We do not clearly distinguish any
-trend with speed for the bicycles (Keiler and Urban Arrow). During the tests
-involving Keiler tricycle and strollers, we cannot exclude that the front wheels
+trend with speed for the bicycles (Keiler and Urban Arrow). During tests
+involving Keiler and strollers, we cannot exclude that the front wheels
 (left and right) hit the bump at slightly different time instants.
+
+Regarding the
+shock test, the analysis presented in Appendix~\ref{app:shock} was conducted on
+unfiltered data (not downsampled). We selected the maximum (absolute) peak from
+the time history of the vertical acceleration of the seat pan starting from the
+events' time histories (Figure \ref{fig:shock_time-history}), limiting it to
+16~g when the peak exceeded that maximum.
+
+\begin{align}
+  \textrm{MAX}_{a_{z}} =\max|a_{z}(t_n)|
+  \label{eq:max-acc}
+\end{align}
+
 %
@@
     \cline{2-6}
+              & Green Machine & Cot, 0 mo & 5 & 4 & 17 \\
+    \cline{2-6}
               & Maxi-Cosi & Cot, 0 mo  & 5 & 2 & 131 \\
@@
     \cline{2-6}
-              & Stokke BABYZEN YOYO & Cot, 0 mo  & 5 & 4 & 35 \\
+              & Old Rusty & Seat, 9 mo & 5 & 4 & 31 \\
+    \cline{2-6}
+              & Stokke & Cot, 0 mo  & 5 & 4 & 35 \\
               &                     & Seat, 9 mo & 5 & 4 & 51 \\
-    \cline{2-6}
-              & Green Machine & Cot, 0 mo & 5 & 4 & 17 \\
-    \cline{2-6}
-              & Old Rusty & Seat, 9 mo & 5 & 4 & 31 \\
     \cline{1-6}
-    Bicycles & Keiler tricycle & Melia, 3 mo & 5 & 2 & 52 \\
+    Bicycles & Keiler & Melia, 3 mo & 5 & 2 & 52 \\
 
@@
     \cline{2-6}
-             &               & Maxi-Cosi, 0 mo & 5 & 2 & 113 \\
-
-             &               & Maxi-Cosi, 0 mo & 12 & 2 & 140 \\
-
-             &               & Maxi-Cosi, 0 mo & 20 & 2 & 115 \\
+             &               & Pebble, 0 mo & 5 & 2 & 113 \\
+
+             &               & Pebble, 0 mo & 12 & 2 & 140 \\
+
+             &               & Pebble, 0 mo & 20 & 2 & 115 \\
     \cline{2-6}
-             &               & Maxi-Cosi, 3 mo & 5 & 2 & 151 \\
-
-             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160 \\
-
-             &               & Maxi-Cosi, 3 mo & 20 & 2 & 145 \\
+             &               & Pebble, 3 mo & 5 & 2 & 151 \\
+
+             &               & Pebble, 3 mo & 12 & 2 & 160 \\
+
+             &               & Pebble, 3 mo & 20 & 2 & 145 \\
     \cline{2-6}
@@
     \cline{2-6}
-             &               & Maxi-Cosi, 0 mo & 5 & 1 & 50 \\
-
-             &               & Maxi-Cosi, 0 mo & 12 & 2 & 63 \\
-
-             &               & Maxi-Cosi, 0 mo & 25 & 2 & 130 \\
+             &               & Pebble, 0 mo & 5 & 1 & 50 \\
+
+             &               & Pebble, 0 mo & 12 & 2 & 63 \\
+
+             &               & Pebble, 0 mo & 25 & 2 & 130 \\
     \cline{2-6}
-             &               & Maxi-Cosi, 3 mo & 5 & 2 & 156 \\
-
-             &               & Maxi-Cosi, 3 mo & 12 & 2 & 160 \\
-
-             &               & Maxi-Cosi, 3 mo & 25 & 2 & 160 \\
+             &               & Pebble, 3 mo & 5 & 2 & 156 \\
+
+             &               & Pebble, 3 mo & 12 & 2 & 160 \\
+
+             &               & Pebble, 3 mo & 25 & 2 & 160 \\
     \bottomrule
@@
 
-\section{Future Work - can be one of the first appendices}
+\section{Future Work}
 % 
 There are four possible directions for future work: more in-depth analysis of
-the present measurements, more research on vibrations generated by infant
+the present measurements, more research on the vibrations transmitted by infant
 transport systems, more research on the effects of vibration on infants, and
@@
 %
-There are products and variables that have not yet been investigated for their
-effect on vibration. For example, running with an infant in a sports stroller is
-not tested. Investigating this is important because we expect that vibrations
-when running may quickly exceed health limits. In addition, recumbent postures in
-sports strollers are estimated to increase the vibration load on the head of the
+Some products, scenarios, and variables have not yet been investigated for their
+effect on vibration. For example, running with an infant in a jogging stroller is a subject of interest as vibrations are likely to exceed health limits. Furthermore, recumbent postures in
+jogging strollers are estimated to increase the vibration load on the head of the
 infant. It is important to establish the actual vibration load on the head in
@@
 At this moment, no requirements exist for the vibrational properties of child
-transport systems in the standards for strollers, cargo bicycles, bicycle seats,
+transport systems in the standards for strollers, cargo bicycles, bicycle seats, bicycle trailers,
 and car seats. Due to the magnitude of vibrations that can occur during child
-transport, it is imperative to include a requirement to the vibrational
+transport, it is imperative to include requirements for the vibrational
 properties in the standards for these products.
@@
 With the information resulting from more research on infant vibration, a benchmark for the vibration properties of infant transportation products needs to be developed.
-Tests as performed in this study, could serve as a first basis.
-Road surfaces, speeds, dummies, posture and metrics could be standardized.
-Over the years these could be refined building upon scientific research.
-Acceptance thresholds could be set to accept well performing current products.
+Tests as performed in this study mark a first milestone.
+Road surfaces, speeds, dummies, posture, and metrics could be standardised.
+Over the years, these could be refined building upon scientific research.
+Acceptance thresholds could be set to accept current products that perform well.
 This will enable the inclusion of (minimal) requirements for vibration
 properties in the standards, which would greatly increase the health and comfort
-of the infants who must use these products.
+of infants who must use these products.
+
+\section{Experimental Equipment}
+\label{app:equipment}
+
+We considered the use of ``crash test dummies'' (also known as anthropomorphic
+test devices or ATDs), which are designed and commonly used to test child seats
+in car crash tests. However, the closest available body sizes for crash test
+dummies do not meet the body sizes desired for this investigation. Furthermore,
+crash test dummies are of a fundamentally different design, based on scaling of
+adult biomechanical data rather than child data and with dynamic properties
+designed for crash conditions, not for vibration testing. Therefore, crash test
+dummies were not considered a good option to use for the envisaged vibration tests. 
+ The following lists the dummies used:
+%
+\begin{description}
+  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
+  ``Andi Asleep'' (product code AW380008).
+  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
+
+  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
+  ``Asia - Limited Edition'' (product code 300287).
+  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
+  \item[Dummy 9 months] weight 8.90~\si{\kg}, size 70~\si{\cm}. Dollkit 28'',
+  ``Hailey'' (product code 304137).
+  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
+\end{description}
+%
+The strollers and bicycles used for the experiments are shown below, along with their wheelbase, wheel diameter, sensor location, and orientation for all the tested vehicles.
+
+\begin{description}
+\item[Strollers] A selection of vintage and modern strollers for carrying
+infants. The modern strollers are configurable as cots for newborns and as seats
+for older infants.
+%
+\begin{description}
+  \item[Bugaboo Fox 5] Featuring large wheels and a suspension system that makes
+  it an all-terrain stroller, according to the manufacturer. It has large
+  puncture-resistant tyres and an air-permeable mattress.
+  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
+  website})
+  \item[Green Machine] An unknown brand vintage perambulator with a cot, dating
+  approximately from the 1970s that includes a leather strap suspended cot in a
+  metal frame. The wheels are relatively large compared to modern strollers.
+  \item[Maxi-Cosi Street Plus] This stroller comes with a cot configuration (0-6
+  months) and an infant seat option. It has large wheels with only a marginal suspension system.
+  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-Cosi website})
+  \item[Old Rusty] An unknown brand vintage seat-style stroller dating approximately from the 1970s that includes a metal spring suspension system and wheels that are slightly larger than those on modern strollers.
+  \item[Stokke BABYZEN YOYO 0+] Among the smallest foldable strollers on the market. It has only a marginal suspension system and smaller wheels compared to other strollers available on the market.
+  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
+  rented for the experiment})
+\end{description}
+\item[Cargo Bicycles] Two modern Dutch ``bakfietsen'' in which different baby
+seats can be mounted.
+%
+\begin{description}
+  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
+  rear) cargo tricycle without electric assist. This vehicle will not roll into
+  curves. However, differing road surface unevenness at the left and right front
+  wheels will induce lateral roll and lateral acceleration in infants. We added
+  masses in specific locations to simulate the presence of an electric motor and
+  battery package, in order to compare the results with those of the Urban Arrow. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
+  Webpage}) 
+  \item[Urban Arrow Cargo Bicycle] An electric cargo bicycle that is popular in the Netherlands.
+This vehicle has two inline wheels, which makes it roll into curves like a regular bicycle.
+It is featured by a long frame that can carry loads (e.g., a child in a car seat or a baby shell) placed in between the rider and the front wheel.
+  (\href{https://urban arrow.com/}{Urban Arrow website})
+\end{description}
+\item[Baby Seats] These two baby seats were mounted in the cargo bays of the two
+cargo bicycles.
+%
+\begin{description}
+  \item[Melia Baby Shell] Baby seat specifically designed for cargo bicycles
+  meant for babies from 2 to 9 months old. Mounted to the seat platform in both
+  cargo bicycles.
+    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia
+    Webpage})
+  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to be
+  mounted on cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow
+  Baby Car Seat Adapter''). Comes with an integrated suspension system. The same
+  adapter was used in both cargo bicycles.
+    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi
+    Webpage})
+\end{description}
+\end{description}
+
+Additional sensor locations are as follows.
+
+\begin{enumerate}
+  \item \textbf{Front Wheel} This IMU was mounted on the front wheel fork (the
+  caster wheel for the stroller). This was the non-rotating measurement point
+  closest to the ground. The purpose of this sensor was to measure the road
+  roughness filtered out only by the tyres.  
+  \item \textbf{Frame} On the cargo bicycle, an IMU was placed below the frontal
+  cargo bay and clamped to the frame. This was to provide an understanding of
+  the damping characteristics of the bicycle frame, together with an estimation
+  of the effect of the suspension system. On the stroller, the IMU was taped
+  under the baby seat.
+  \item \textbf{Seat Head} IMU taped into the baby seat (on the soft mattress),
+  directly in contact with the dummy's head. This IMU measured the vibration
+  transmitted to the head contact point.
+\end{enumerate}
+
+\begin{figure}
+  \centering
+  \subcaptionbox{IMU on the front fork}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/FW_UA.jpg}}
+  \subcaptionbox{IMU under the cargo bay}{\includegraphics[width=0.45\textwidth, angle=-90]{fig/BT_UA.jpg}}
+  \caption{IMU locations on the Urban Arrow. The white 3D printed
+  sensor supports are visible in (a) and (c). The last figure (d) shows how the
+  sensors were taped to the seat pan and backrest.}
+  \label{fig:sensors_UA2}
+\end{figure}
+
+\begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Joolz_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_UA-Joolz_front.pdf}}
+  \caption{IMU locations on the Urban Arrow, equipped with
+  Pebble.}
+  \label{fig:tech_drawing_UA_Joolz}
+\end{figure}
+
+\begin{figure}[htbp]    % use [htbp] to place the figures where I prefer
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_UA-Melia_front.pdf}}
+  \caption{IMU locations on the Urban Arrow, equipped with
+  Melia.}
+  \label{fig:tech_drawing_UA_Melia}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Joolz_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_Trike-Joolz_front.pdf}}
+  \caption{IMU locations on the Keiler, equipped with
+  Pebble.}
+  \label{fig:tech_drawing_Trike_Joolz}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Melia_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_Trike-Melia_front.pdf}}
+  \caption{IMU locations on the Keiler, equipped with
+  Melia.}
+  \label{fig:tech_drawing_Trike_Melia}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_front.pdf}}
+  \caption{IMU locations on the Bugaboo, configured for a 0-month-old baby.}
+  \label{fig:tech_drawing_Bugaboo0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Bugaboo9_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo9_front.pdf}}
+  \caption{IMU locations on the Bugaboo, configured for a 9-month-old baby.}
+  \label{fig:tech_drawing_Bugaboo9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Maxicosi0_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Maxicosi0_front.pdf}}
+  \caption{IMU locations on the Maxi-Cosi, configured for a 0-month-old baby.}
+  \label{fig:tech_drawing_Maxicosi0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_Maxicosi9_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm,angle=-90]{fig/TechDraw_Maxicosi9_front.pdf}}
+  \caption{IMU locations on the Maxi-Cosi, configured for a 9-month-old baby.}
+  \label{fig:tech_drawing_Maxicosi9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_YOYO0_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO0_front.pdf}}
+  \caption{IMU locations on the Stokke, configured for a 0-month-old baby.}
+  \label{fig:tech_drawing_YOYO0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_YOYO9_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO9_front.pdf}}
+  \caption{IMU locations on the Stokke, configured for a 9-month-old baby.}
+  \label{fig:tech_drawing_YOYO9}
+\end{figure}
+
+\clearpage
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_GreenM0_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_GreenM0_front.pdf}}
+  \caption{IMU locations on the Green Machine, configured for a 0-month-old baby.}
+  \label{fig:tech_drawing_GreenM0}
+\end{figure}
+
+\begin{figure}[htbp]
+  \centering
+  \subcaptionbox{Lateral view}{\includegraphics[width=70mm, angle=-90]{fig/TechDraw_OldR9_lat.pdf}}
+  \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_OldR9_front.pdf}}
+  \caption{IMU locations on the Old Rusty, configured for a 9-month-old baby.}
+  \label{fig:tech_drawing_OldR9}
+\end{figure}
+
+\clearpage
+\newpage
+
+\section{Location and pictures of the experiment areas}
+\label{app:location}
+%
+\begin{itemize}
+  \item \textbf{Strollers} were tested with dummies of 0 months and 9 months at
+  5~\si{\kph} at:
+  \begin{itemize}
+      \item Tarmac
+      \item Paver bricks % Klinkers
+      \item Sidewalk pavers % Stoeptegels
+      \item Cobblestones 
+      \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
+      \item Shock bump: A 30x30~\si{\mm} square section aluminium bar 
+  \end{itemize}
+  \item \textbf{Cargo bicycles} were tested with dummies of 0 months and 3
+  months. Test were performed at 12~\si{\kph} for both vehicles. The Urban Arrow
+  was also tested at 25~\si{\kph} whereas the Keiler was tested at
+  20~\si{\km\per\hour} for safety reasons (due to wobbling). The test surfaces
+  are:
+  \begin{itemize}
+      \item Tarmac
+      \item Paver bricks
+      \item Shock bump: A 30~\si{\mm} x 30~\si{\mm} square section aluminium bar (also tested at 5~\si{\kph})
+      \end{itemize}
+  \item \textbf{Baby seats} Both the Pebble and the
+  Melia was tested on each cargo bicycle using the same mounting
+  systems.
+\end{itemize}
+
+\subsection{For Bicycles}
+
+\begin{itemize}
+    \item Tarmac
+\begin{figure}[htbp]
+  \centering
+  {\includegraphics[width=70mm, angle=-90]{fig/Tarmac_bicycle.pdf}}
+  \caption{Tarmac surface where we tested bicycles.}
+  \label{fig:tarmac_bicycle}
+\end{figure}
+
+The bicycle experiment on the tarmac was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands (GPS coordinates: 52.001053, 4.369071).
+
+    \item Paver bricks
+\begin{figure}[htbp]
+  \centering
+ {\includegraphics[width=70mm, angle=-90]{fig/Paver_bricks_bicycle.pdf}}
+  \caption{Paver bricks surface where we tested bicycles.}
+  \label{fig:paver_bricks_bicycle}
+\end{figure}
+
+The bicycle experiment on the paver bricks was conducted along Hertog Govertkade and Kanaalweg, 2611 DD Delft, The Netherlands (GPS coordinates: 52.006264, 4.363013).\\
+Details of paver brick: rectangular shape, dimensions 195x95~\si{\mm} (gap in between: 7±2~\si{\mm}).
+
+\clearpage
+
+    \item Shock
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=70mm, angle=0]{fig/Shock_bicycle.pdf}
+  \caption{We performed a shock test with bicycles riding over a 30x30~\si{\mm} square section bar.}
+  \label{fig:shock_bicycle}
+\end{figure}
+
+The bicycle shock experiment was conducted along Leeghwaterstraat, 2628 CA Delft, The Netherlands (same location of the experiment on the tarmac, GPS coordinates: 52.001053, 4.369071).\\
+Details of the shock experiment: we rode over a square-sectioned aluminium bar 30x30~\si{\mm}.
+
+\end{itemize}
+
+\subsection{For Strollers}
+
+\begin{itemize}
+    \item Tarmac
+
+\begin{figure}[htbp]
+  \centering
+    \includegraphics[width=70mm, angle=-90]{fig/Tarmac_stroller.pdf}
+  \caption{Tarmac test area.}
+  \label{fig:tarmac_stroller}
+\end{figure}
+
+The bicycle experiment on the tarmac was conducted along Julianalaan, 2628 BG Delft, The Netherlands (GPS coordinates: 52.002727, 4.366845).
+
+\clearpage
+
+    \item Cobblestone
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=60mm, angle=-90]{fig/Cobblestone_stroller.pdf}
+  \caption{Cobblestone surface where we tested strollers.}
+  \label{fig:cobblestone_area_stroller}
+\end{figure}
+
+The bicycle experiment on the cobblestone was conducted along Julianalaan, 2628 BG Delft, The Netherlands (GPS coordinates: 52.002727, 4.366845).
+Details of cobblestone: rectangular shape, dimensions 180x125~\si{\mm} (gap in between: 20±4~\si{\mm}).
+
+    \item Sidewalk pavers
+
+\begin{figure}[htbp]
+  \centering
+    \includegraphics[width=60mm, angle=-90]{fig/Sidewalk_pavers_stroller.pdf}
+  \caption{Sidewalk pavers test area for strollers.}
+  \label{fig:sidewalkpavers_area_stroller}
+\end{figure}
+
+The experiment was conducted along Prins Bernhardlaan, 2628 CN Delft, The Netherlands (same location as Paver bricks test, GPS coordinates: 52.003147, 4.369530).\\
+Details of sidewalk bricks: rectangular shape, dimensions 290x290~\si{\mm} (gap in between: 12±2~\si{\mm}).
+
+\clearpage
+
+    \item Sidewalk slabs
+
+\begin{figure}[htbp]
+  \centering
+    \includegraphics[width=70mm, angle=-90]{fig/Sidewalk_slabs_stroller.pdf}
+  \caption{Sidewalk slab test area where we conducted the test with strollers.}
+  \label{fig:sidewalkslabs_area_stroller}
+\end{figure}
+
+The experiment was conducted in front of TU Delft Aula Conference Centre (Building 20), Mekelweg 5, 2628 CC Delft, The Netherlands (GPS coordinates: 52.002250, 4.372665).\\
+Details of sidewalk slab: made of concrete, rectangular shape, dimensions 2000x990~\si{\mm} (gap in between: 160±3~\si{\mm}).
+
+    \item Paver bricks
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=50mm, angle=-90]{fig/Paver_bricks_stroller.pdf}
+  \caption{Details of the paver bricks test area.}
+  \label{fig:paverbrick_area_stroller}
+\end{figure}
+
+The experiment was conducted along Prins Bernhardlaan, 2628 CN Delft, The Netherlands (same location as Sidewalk paver test, GPS coordinates: 52.003147, 4.369530).\\
+Details of paver brick: rectangular shape, dimensions 195x95~\si{\mm} (gap in between: 7±2~\si{\mm}).
+
+\clearpage
+
+    \item Shock
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=60mm, angle=-90]{fig/Shock_stroller.pdf}
+  \caption{Area where we tested strollers during the shock experiment.}
+  \label{fig:shock_area_stroller}
+\end{figure}
+
+The experiment was conducted inside TU Delft Mechanical Engineering faculty (Building 34 - Ground floor, aisle in front of Gezelschap Leeghwater office), Mekelweg 2, 2628 CD Delft, The Netherlands (GPS coordinates: 52.000587, 4.372224).\\
+Details of the shock experiment: we pushed the stroller over a square section aluminium bar 30x30~\si{\mm}.
+
+\end{itemize}
 

### 2025-09-21 src/website.py
Capitalize and increase figure height.

@@ -905,7 +905,7 @@ boxp_html.append(IMG.format('', fname) + '\n</br>')
 plt.close('all')
 
 #############################################
-# Figure: Shock test comparison -  All Trials
+# Figure: Shock Test comparison -  All Trials
 #############################################
 # Limit max_amp_shock values to a maximum of 160 (only for plotting, in the
 # table you will have uncut values)
@@ -913,7 +913,7 @@ shock_df['Peak Value [m/s/s]'] = shock_df['Peak Value [m/s/s]'].clip(
     upper=16*9.81)
 
 shock_html = []
-shock_html.append(H2.format('Shock test Comparison'))
+shock_html.append(H2.format('Shock Test Comparison'))
 msg = 'Compare maximum acceleration across vehicles and speed.'
 shock_html.append(P.format(msg))
 p = sns.stripplot(
@@ -922,7 +922,7 @@ p = sns.stripplot(
     y="Peak Value [m/s/s]",
     hue='Target Speed [km/h]',
 )
-p.set_ylabel(r'Vertical Acceleration Shock test [m/s$^2$]')
+p.set_ylabel(r'Vertical Acceleration Shock Test [m/s$^2$]')
 p.set_xticks(p.get_xticks())
 p.set_xticklabels(
     [label.get_text().replace("trike", "keiler")
@@ -930,7 +930,7 @@ p.set_xticklabels(
     rotation=30)
 p.set_xticklabels(p.get_xticklabels(), rotation=30)
 fname = '{}-shock-test-compare.png'.format(SIGNAL)
-p.figure.set_size_inches((MAXWIDTH*MM2INCH, 100*MM2INCH))
+p.figure.set_size_inches((MAXWIDTH*MM2INCH, 110*MM2INCH))
 p.figure.set_layout_engine('constrained')
 p.figure.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
 plt.clf()

### 2025-09-22 main.tex
Updated the tex files to v6.

@@
 \title{
-  DRAFT: v6.dev \\
+  DRAFT: v6 \\
   Vibration Characterisation of Strollers and\\
@@
   % NOTE: keep to 150 words max
-  We evaluated road-induced vibrations with dummies representing infants aged 0,
-  3, and 9 months with five strollers and two cargo bicycles on six common road
-  surfaces using the ISO standard for whole-body vibration. Strollers induced on
-  average 0.4~\si{\mps\squared} on tarmac and up to 5.0~\si{\mps\squared} on
-  cobblestones at a mean walking speed of 5.3~\si{\kph}. Cargo bicycles induced
-  induced as low as 0.6~\si{\mps\squared} on tarmac and up to
-  10.7~\si{\mps\squared} at 25~\si{\kph} on paver bricks. The standard suggests
-  that the highest accelerations for the strollers and cargo bicycles should be
-  limited to continuous duration less than 10~\si{\minute}. Effects of body size
-  and posture were minor. Two vintage stroller designs significantly reduced
-  vibrations compared to three modern strollers, indicating the benefits of
-  compliant suspensions. 
+  % Knowledge is lacking on road-induced vibrations for infants transported  in
+  % strollers and cargo  bicycles.
+  We evaluated vibrations with dummies representing infants aged 0, 3, and 9
+  months lying or sitting in five strollers and two cargo bicycles with
+  dedicated baby seats on six common road surfaces using the ISO standard for
+  whole-body vibration.
+  Strollers induced on average 0.4~\si{\mps\squared} on tarmac and up to
+  5.0~\si{\mps\squared} on cobblestones at a mean walking speed of
+  5.3~\si{\kph}.
+  Cargo bicycles induced on average 0.6~\si{\mps\squared} on tarmac and up to
+  10.7~\si{\mps\squared} at 25~\si{\kph} on paver bricks.
+  The standard suggests the highest accelerations for strollers and cargo
+  bicycles are extremely uncomfortable and continuous exposure should be limited
+  to less than 10~\si{\minute}.
+  % Effects of body size and posture were minor.
+  Two vintage strollers significantly reduced vibrations compared to three
+  modern strollers, indicating benefits of compliant suspensions. 
+  We recommend designers systematically consider vibration, users avoid
+  prolonged exposure to surfaces rougher than tarmac, and researchers to pursue
+  scientifically founded test procedures and standards for infant vibration.
 \end{abstract}
@@
 measured with adults seated in cars (see e.g. Figure 2 in
-\cite{griffin2004experimental}). Adult experiments show that significant
-discomfort can be measured across all tested frequencies being 80 Hz
-\cite{morioka2010frequency} or even 315~\si{\hertz}~\cite{morioka2006magnitude}
+\cite{griffin2004experimental}). Adult experiments investigating discomfort as a function of frequency, show that significant
+discomfort can be measured across all tested frequencies, being up to 80 Hz
+\cite{morioka2010frequency} or even up to 315~\si{\hertz}~\cite{morioka2006magnitude}
 albeit with reduced sensitivity.
@@
     vibrations for all expected surface types and ranges of relevant body sizes
-    and posture to ensure that their designs isolate vibrations well for all use
+    and postures to ensure that their designs isolate vibrations well for all use
     conditions. Testing across relevant body sizes is especially important for
@@
 %
-Niel Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, Idsart
-Kignma, Darek Wieckowksi, Aernout Dijkstra-Hellinga, and  Clement Moe all
+Neil Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, Idsart
+Kingma, Darek Wieckowksi, Aernout Dijkstra-Hellinga, and  Clement Moe all
 provided important feedback on the preprint that helped improve the paper. This
@@
 %
-TODO
+The data will be made publicly available alongside publication.
 
@@
 the speed from \SIrange{12}{25}{\kilo\meter\per\hour}.The effect of speed while cycling on tarmac was less drastic, but still showed a slight increase.
-
+%
 \begin{figure}
@@
 \end{figure}
-%
+
 \subsection{Effect of Dummy Size}
@@
 At this moment, no requirements exist for the vibrational properties of child
-transport systems in the standards for strollers, cargo bicycles, bicycle seats, bicycle trailers,
-and car seats. Due to the magnitude of vibrations that can occur during child
-transport, it is imperative to include requirements for the vibrational
-properties in the standards for these products.
-%At this moment, no new requirements can be defined because there is not enough information.
-With the information resulting from more research on infant vibration, a benchmark for the vibration properties of infant transportation products needs to be developed.
-Tests as performed in this study mark a first milestone.
-Road surfaces, speeds, dummies, posture, and metrics could be standardised.
-Over the years, these could be refined building upon scientific research.
-Acceptance thresholds could be set to accept current products that perform well.
-This will enable the inclusion of (minimal) requirements for vibration
-properties in the standards, which would greatly increase the health and comfort
-of infants who must use these products.
+transport systems in the standards for strollers, cargo bicycles, bicycle seats,
+bicycle trailers, and car seats. Due to the magnitude of vibrations that can
+occur during child transport, it is imperative to include requirements for the
+vibrational properties in the standards for these products. At this moment, it
+is difficult to develop new requirements because there is not enough
+information. With the information resulting from more research on infant
+vibration, a benchmark for the vibration properties of infant transportation
+products needs to be developed. Tests as performed in this study mark a first
+milestone. Road surfaces, speeds, dummies, posture, and metrics could be
+standardised. Over the years, these could be refined building upon scientific
+research. Acceptance thresholds could be set to accept current products that
+perform well.  This will enable the inclusion of (minimal) requirements for
+vibration properties in the standards, which would greatly increase the health
+and comfort of infants who must use these products.
 
@@
 in car crash tests. However, the closest available body sizes for crash test
-dummies do not meet the body sizes desired for this investigation. Furthermore,
-crash test dummies are of a fundamentally different design, based on scaling of
-adult biomechanical data rather than child data and with dynamic properties
-designed for crash conditions, not for vibration testing. Therefore, crash test
-dummies were not considered a good option to use for the envisaged vibration tests. 
+dummies do not meet the body sizes desired for this investigation.
+Furthermore, crash test dummies are of a fundamentally different design, based on scaling of adult biomechanical data rather than child data and with dynamic properties designed for crash conditions, not for vibration testing.
+Therefore, crash test dummies were not used for the envisaged vibration tests.
  The following lists the dummies used:
@@
 \begin{description}
-  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the
-  rear) cargo tricycle without electric assist. This vehicle will not roll into
+  \item[Keiler Tricycle] A tadpole (two wheels in the front, one in the rear)
+  cargo tricycle without electric assist. This vehicle will not roll into
   curves. However, differing road surface unevenness at the left and right front
@@
   masses in specific locations to simulate the presence of an electric motor and
-  battery package, in order to compare the results with those of the Urban Arrow. (\href{https://kashop.nl/product/keiler-bakfiets/}{Product
-  Webpage}) 
-  \item[Urban Arrow Cargo Bicycle] An electric cargo bicycle that is popular in the Netherlands.
-This vehicle has two inline wheels, which makes it roll into curves like a regular bicycle.
-It is featured by a long frame that can carry loads (e.g., a child in a car seat or a baby shell) placed in between the rider and the front wheel.
+  battery package, in order to compare the results with those of the Urban
+  Arrow. The tricycle was equipped with tyres CST XPEDIUM Safe 47-559
+  (Cheng Shin Tire, Yuanlin, Taiwan) on the rear, and Schwalbe Green Comfort Road Cruiser
+  K-Guard 3 47-507 (Ralf Bohle GmbH, Reichshof-Wehnrath, Germany) on
+  the front. We set both tyres to an inflation pressure of 300~\si{\kPa}.
+  (\href{https://kashop.nl/product/keiler-bakfiets/}{Product Webpage}) 
+  \item[Urban Arrow Cargo Bicycle] An electric cargo bicycle that is popular in
+  the Netherlands. This vehicle has two inline wheels, which makes it roll into
+  curves like a regular bicycle. It is featured by a long frame that can carry
+  loads (e.g., a child in a car seat or a baby shell) placed in between the
+  rider and the front wheel. We used the ''Family Performance Plus'' model, with
+  an electric drivetrain from Bosch Performance Line (65~\si{\N}\si{\m},
+  250~\si{\W}). It was equipped with tyres Schwalbe Big Ben Plus 55-559 on the
+  rear, and Schwalbe Big Ben Plus 55-406 on the front (Ralf Bohle GmbH, Reichshof-Wehnrath, Germany). We set both tyres to an
+  inflation pressure of 300~\si{\kPa}, according to the range recommended by the
+  manufacturer.
   (\href{https://urban arrow.com/}{Urban Arrow website})
@@
   \item \textbf{Cargo bicycles} were tested with dummies of 0 months and 3
-  months. Test were performed at 12~\si{\kph} for both vehicles. The Urban Arrow
+  months. Tests were performed at 12~\si{\kph} for both vehicles. The Urban Arrow
   was also tested at 25~\si{\kph} whereas the Keiler was tested at

### 2025-09-22 src/html_templates.py
Tidy up website, closes #58.

@@ -22,9 +22,8 @@ INDEX = """\
   <hr>
   <div class="alert alert-danger" role="alert">
     <p>
-      Warning: These results are a work-in-progress, we caution reliance on
-      them until a supporting paper is published. See the latest preprint for
-      more context: <a
+      Warning: These results are currently under peer review. See the latest
+      preprint for more context: <a
       href="https://doi.org/10.31224/4415">doi.org/10.31224/4415</a>.
     </p>
   </div>
@@ -36,11 +35,13 @@ INDEX = """\
     License: CC-BY 4.0
   </p>
   <p>
-    This page examines the signal: <strong>{signal}</strong>.
+    This page examines the signal from the strollers and cargo bicycles:
+    <strong>{signal}</strong>.
   </p>
 
   <h1>Table of Contents</h1>
   <ol>
+    <li><a href="#definitions">Definitions</a></li>
     <li><a href="#mean_table">Scenario Mean Table</a></li>
     <li><a href="#boxp">Comparison Plots</a></li>
     <li><a href="#shock">Shock Test</a></li>
@@ -54,6 +55,52 @@ INDEX = """\
     <li><a href="#sync">Sensor Time Synchronization Checks</a></li>
   </ol>
 
+  <h1 id="definitions">Definitions</h1>
+  <h2>Data Sectioning</h2>
+  <dl>
+    <dt>Scenario</dt>
+    <dd>We test a combination of vehicle, infant seat, infant dummy, road
+    surface (including shock), and speed. A unique combination of these factors
+    is called a "scenario".</dd>
+    <dt>Session</dt>
+    <dd>A "session" is a continuous collection of data from a set of Shimmer
+    IMUs which contains one or more scenarios. The IMU's internal clocks are
+    time synchronized on the base station, attached to the vehicle, and each
+    IMU is started. After a time period of collecting data of possibly multiple
+    trials and calibrations the IMUs are stopped. Each IMU produces a single
+    acquisition CSV file for that session.</dd>
+    <dt>Trial</dt>
+    <dd>A trial is defined as a continuous time segment selected from a session
+    that represents a specific scenario. The trial may be a static calibration
+    period, a time synchronization motion period, or a constant speed period of
+    vehicle motion.</dd>
+    <dt>Repetition</dt>
[…]

### 2025-09-22 src/website.py

@@ -254,7 +254,8 @@ boxp_html = []
 # Figure: Stroller and Bicycle Spectrum Comparison
 ##################################################
 boxp_html.append(H2.format("""Mean spectra of each vehicle at each speed."""))
-msg = """TODO"""
+msg = """Curves represent the average amplitude at each frequency over all
+repetitions of the same vehicle grouped by target speed."""
 boxp_html.append(P.format(msg))
 fig, axes = plt.subplots(ncols=2, nrows=2, layout='constrained',
                          figsize=(MAXWIDTH*MM2INCH, 0.6*MAXWIDTH*MM2INCH))

### 2025-10-17 main.tex
Version 7 of the paper.

@@
 \title{
-  DRAFT: v6 \\
+  DRAFT: v7 \\
   Vibration Characterisation of Strollers and\\
@@
 
-This paper addresses both comfort and potential health effects for infants. We
-equipped five strollers and two cargo bicycles with inertial measurement units
-(IMU) and carried out 67 experiments on different road surfaces and with
-different travel speeds, using dummies representing 0, 3, and 9-month-old
-infants. We assessed the data and derived results using ISO~2631-1 frequency
-weightings and procedures. Given that ISO-2631-1 is neither validated for
-children nor for lying postures, we also report unweighted results to assess
-power spectrum and bandwidth. We investigated the influence of vehicle, seat,
-body size, speed, and road surface and provided recommendations to users,
-designers, and for future research.
+This paper provides measurements of vibration exerted on infant dummies in
+strollers and cargo bicycles, which may be used as risk indicators for
+discomfort or health effects. We equipped five strollers and two cargo bicycles
+with inertial measurement units (IMU) and carried out 67 experiments on
+different road surfaces and with different travel speeds, using dummies
+representing 0, 3, and 9-month-old infants. We derived results using ISO~2631-1
+frequency weightings and procedures to enable comparison with previous studies.
+However, given that ISO~2631-1 is neither validated for children nor for lying
+postures, we also report unweighted results to assess power spectrum and
+bandwidth. We investigated the influence of vehicle, seat, body size, speed, and
+road surface and provided recommendations to users, designers, and for future
+research. Furthermore, as an example of how such measurements could be used for
+assessing discomfort and health effects, we discuss these in the light of
+thresholds suggested by ISO~2631-1 and Gao~et.~al~\cite{Gao2018}.
 
@@
 vibration amplitudes than the public transit riders who were surveyed for the
-ISO ratings. This points to possible weakness in the ISO recommendations or to
-other factors affecting cycling discomfort (e.g., the ability to stand on the
-pedals to lower vibration to the body and the head).
+ISO ratings. This points to possible weakness in or contradiction to the ISO
+recommendations or to other factors affecting cycling discomfort (e.g., the
+ability to stand on the pedals to lower vibration to the body and the head).
 

### 2025-10-21 main.tex
Version 8, added ALT TEXT to each image, author contrib statement, and practitioner summary.

@@
 \title{
-  DRAFT: v7 \\
+  DRAFT: v8 \\
   Vibration Characterisation of Strollers and\\
@@
   modern strollers, indicating benefits of compliant suspensions. 
-  We recommend designers systematically consider vibration, users avoid
-  prolonged exposure to surfaces rougher than tarmac, and researchers to pursue
+  We recommend that designers systematically consider vibration, users avoid
+  prolonged exposure to surfaces rougher than tarmac, and researchers pursue
   scientifically founded test procedures and standards for infant vibration.
 \end{abstract}
+
+\section*{Practitioner Summary}
+%
+Strollers pushed over cobblestones and cargo bicycles travelling over paver
+bricks at typical speeds induce infant seat pan accelerations up to 5 and
+11~\si{\mps\squared}, respectively. The adult whole-body vibration standard
+suggests these accelerations are extremely uncomfortable and continuous exposure
+should be limited to less than 10~\si{\minute}.
 
@@
   dummies. Images are reproduced from manufacturer's websites except for the
-  vintage strollers and dummies.}
+  vintage strollers and dummies. ALT TEXT: Photos of cargo bicycles, infant
+  seats, strollers, and infant dummies.}
   \label{fig:equipment}
@@
   and the baby seat. In c) the camera is mounted to the stroller handlebar and
-  IMUs are on the wheels.}
+  IMUs are on the wheels. ALT TEXT: Photos of IMU and camera locations on the
+  vehicles.}
   \label{fig:sensors_UA}
@@
   \caption{Road surfaces tested: tarmac and paver bricks (cargo bicycles and
-  strollers), sidewalk pavers, cobblestones, sidewalk slabs (strollers).}
+  strollers), sidewalk pavers, cobblestones, sidewalk slabs (strollers). ALT
+  TEXT: Photos of road surfaces.}
   \label{fig:surfaces}
@@
   horizontal lines depict the mean speed during trials bounded by its standard
-  deviation.}
+  deviation. ALT TEXT: Plot of vehicle speed during a session.}
   \label{fig:session}
@@
   (VDV) for the first 10~\si{\second} of the printed duration is shown in the
-  bottom left.}
+  bottom left. ALT TEXT: Plot of acceleration versus time during an example
+  repetition.}
   \label{fig:vert-acc-example}
@@
   curve. The black dashed-dotted vertical line indicates the bandwidth threshold
-  for 80\% of the area under the black curve.}
+  for 80\% of the area under the black curve. ALT TEXT: Plot of amplitude versus
+  frequency for an example repetition.}
   \label{fig:freq-spectrum}
@@
   linear regression, vertical lines are the standard deviation at those speeds,
-  and shaded regions show the 95\% confidence intervals for the regression.}
+  and shaded regions show the 95\% confidence intervals for the regression. ALT
+  TEXT: Plots of cargo bicycle acceleration versus speed for tarmac and paver
+  bricks.}
   \label{fig:bicycle-type-compare}
@@
   surface for each stroller. Vertical lines indicate the standard deviation for
-  categories that have more than one repetition.} 
+  categories that have more than one repetition. ALT TEXT: Plot of stroller
+  accelerations for each road surface.} 
   \label{fig:stroller-type-compare}
@@
   strollers on sidewalk pavers (left) and cargo bicycles on paver bricks
-  (right).} 
+  (right). ALT TEXT: Plot of amplitude versus frequency for each stroller and
+  cargo bicycle.} 
   \label{fig:spectra-compare}
@@
   and indicate the median. The whiskers indicate the 95\textsuperscript{th}
-  percentile and circles are outliers.}
+  percentile and circles are outliers. ALT TEXT: Box plots of peak frequencies
+  for strollers and bicycles on each road surface.}
   \label{fig:peak-freq-dist}
@@
   whiskers indicate the 95\textsuperscript{th} percentile and circles are
-  outliers.}
+  outliers. ALT TEXT: Box plots of bandwidth for strollers and bicycles on each
+  road surface.}
   \label{fig:bandwidth-dist}
@@
   ISO~2631-1 ``health caution zones'' for long-term exposure of adults seated
-  erectly, daily experiencing these vibrations with continuous duration.}
+  erectly, daily experiencing these vibrations with continuous duration. ALT
+  TEXT: Vertical acceleration for each stroller repetition with ISO health
+  duration limits.}
   \label{fig:health-stroller}
@@
   zones'' for long-term exposure of adults seated erectly, daily experiencing
-  these vibrations with continuous duration.}
+  these vibrations with continuous duration. ALT TEXT: Vertical acceleration for
+  each cargo bicycle repetition with ISO health duration limits.}
   \label{fig:health-bicycle}
@@
   horizontal dashed dotted line is the cyclists' vibration discomfort threshold
-  as reported by Gao et. al~\cite{Gao2018}.}
+  as reported by Gao et. al~\cite{Gao2018}. ALT TEXT: Acceleration magnitude for
+  each stroller repetition with ISO comfort limits.}
   \label{fig:comfort-stroller}
@@
   is the cyclists' vibration discomfort threshold as reported by
-  Gao~et.~al~\cite{Gao2018}.}
+  Gao~et.~al~\cite{Gao2018}. ALT TEXT: Acceleration magnitude for each cargo
+  bicycle repetition with ISO comfort limits.}
   \label{fig:comfort-bicycle}
@@
 
-\subsection{Acknowledgement}
-%
-Neil Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, Idsart
-Kingma, Darek Wieckowksi, Aernout Dijkstra-Hellinga, and  Clement Moe all
-provided important feedback on the preprint that helped improve the paper. This
-work was financially supported by VeiligheidNL under the ``Project Trillingen
-bakfiets en wandelwagen.''
-
-\subsection{Declaration of Interest Statement}
+\section*{Acknowledgement}
+%
+Neil Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, and Aernout
+Dijkstra-Hellinga all provided important feedback on the preprint that helped
+improve the paper. This work was financially supported by VeiligheidNL under the
+``Project Trillingen bakfiets en wandelwagen'' and we thank VeiligheidNL
+employee Mieke Cotterink for advice, support, and review of our work.
+
+\section*{Author Contribution Statement}
+%
+All authors were involved in the conception and design, or analysis and
+interpretation of the data; the drafting of the paper; revising it critically
+for intellectual content; and the final approval of the version to be published;
+and all authors agree to be accountable for all aspects of the work.
+
+\section*{Declaration of Interest Statement}
 %
@@
 
-\subsection{Data Availability Statement}
+\section*{Data Availability Statement}
 %
@@
   confidence intervals from a simple linear regression that ignores
-  \(x_\textrm{Cargo Bicycle}\).}
+  \(x_\textrm{Cargo Bicycle}\). ALT TEXT: Cargo bicycle vertical acceleration
+  versus speed for each road surface.}
   \label{fig:compare-bicycle-speed}
@@
   the mean speed of the trial. The lightest colour dots are strollers (4 km/h) and the
-  remaining are cargo bicycles (8-24 km/h).}
+  remaining are cargo bicycles (8-24 km/h). ALT TEXT: Vertical acceleration for
+  each repetition grouped by dummy age representation.}
   \label{fig:compare-baby-mass}
@@
   road surface with colour indicating the mean speed of the repetition. The
-  lightest colour dots are strollers (4 km/h), and the rest are cargo bicycles (8-24 km/h).}
+  lightest colour dots are strollers (4 km/h), and the rest are cargo bicycles
+  (8-24 km/h). ALT TEXT: Vertical acceleration for each repetition grouped by
+  road surface.}
   \label{fig:compare-road-surface}
@@
   \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Tarmac.png}}
-  \caption{Tukey Comparison Plots for the Strollers}
+  \caption{Tukey comparison plots for the strollers. ALT TEXT: Tukey comparison
+  plots for the strollers.}
   \label{fig:tukey-stroller}
@@
   \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-High.png}}
-  \caption{Tukey Comparison Plots for the Cargo Bicycles}
+  \caption{Tukey comparison plots for the cargo bicycles. ALT TEXT: Tukey
+  comparison plots for the cargo bicycles.}
   \label{fig:tukey-bicycle}
@@
   \centering
+  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-maxicosi-0-SeatBotacc_ver-rep0.png}
+  \caption{Raw seat pan vertical acceleration versus time from session 015:
+  Keiler tricycle during the shock test. ALT TEXT: Vertical acceleration versus
+  time during an example shock test.}
+  \label{fig:shock_time-history}
+\end{figure}
+
+\begin{figure}
+  \centering
   \includegraphics[width=160mm]{fig/SeatBotacc_ver-shock-test-compare.png}
@@
   per each trial, grouped by vehicles. The colour indicates the mean speed of
-  the trial. The lighter the colour the lower the speed.}
+  the trial. The lighter the colour the lower the speed. ALT TEXT: Peak vertical
+  acceleration during shock tests grouped by vehicle.}
   \label{fig:shock_vehicle_comparison}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-maxicosi-0-SeatBotacc_ver-rep0.png}
-  \caption{Raw seat pan vertical acceleration versus time from session 015:
-  Keiler tricycle during the shock test.}
-  \label{fig:shock_time-history}
 \end{figure}
@@
   sensor supports are visible in (a) and (c). The last figure (d) shows how the
-  sensors were taped to the seat pan and backrest.}
+  sensors were taped to the seat pan and backrest. ALT TEXT: Photos of extra IMU
+  mounting locations.}
   \label{fig:sensors_UA2}
@@
   \caption{IMU locations on the Urban Arrow, equipped with
-  Pebble.}
+  Pebble. ALT TEXT: Photos of the Urban Arrow with Pebble seat.}
   \label{fig:tech_drawing_UA_Joolz}
@@
   \subcaptionbox{Front view}{\includegraphics[width=80mm]{fig/TechDraw_UA-Melia_front.pdf}}
-  \caption{IMU locations on the Urban Arrow, equipped with
-  Melia.}
+  \caption{IMU locations on the Urban Arrow, equipped with Melia. ALT TEXT:
+  Photos of the Urban Arrow with Melia seat.}
   \label{fig:tech_drawing_UA_Melia}
@@
   \caption{IMU locations on the Keiler, equipped with
-  Pebble.}
+  Pebble. ALT TEXT: Photos of the Keiler with the Pebble seat.}
   \label{fig:tech_drawing_Trike_Joolz}
@@
   \caption{IMU locations on the Keiler, equipped with
-  Melia.}
+  Melia. ALT TEXT: Photos of the Keiler with the Melia seat.}
   \label{fig:tech_drawing_Trike_Melia}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo0_front.pdf}}
-  \caption{IMU locations on the Bugaboo, configured for a 0-month-old baby.}
+  \caption{IMU locations on the Bugaboo, configured for a 0-month-old baby. ALT
+  TEXT: Photos of the Bugaboo with cot.}
   \label{fig:tech_drawing_Bugaboo0}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Bugaboo9_front.pdf}}
-  \caption{IMU locations on the Bugaboo, configured for a 9-month-old baby.}
+  \caption{IMU locations on the Bugaboo, configured for a 9-month-old baby. ALT
+  TEXT: Photos of the Bugaboo with seat.}
   \label{fig:tech_drawing_Bugaboo9}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_Maxicosi0_front.pdf}}
-  \caption{IMU locations on the Maxi-Cosi, configured for a 0-month-old baby.}
+  \caption{IMU locations on the Maxi-Cosi, configured for a 0-month-old baby.
+  ALT TEXT: Photos of the Maxi-Cosi with cot.}
   \label{fig:tech_drawing_Maxicosi0}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm,angle=-90]{fig/TechDraw_Maxicosi9_front.pdf}}
-  \caption{IMU locations on the Maxi-Cosi, configured for a 9-month-old baby.}
+  \caption{IMU locations on the Maxi-Cosi, configured for a 9-month-old baby.
+  ALT TEXT: Photos of the Maxi-Cosi with seat.}
   \label{fig:tech_drawing_Maxicosi9}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO0_front.pdf}}
-  \caption{IMU locations on the Stokke, configured for a 0-month-old baby.}
+  \caption{IMU locations on the Stokke, configured for a 0-month-old baby. ALT
+  TEXT: Photos of the Stokke with cot.}
   \label{fig:tech_drawing_YOYO0}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_YOYO9_front.pdf}}
-  \caption{IMU locations on the Stokke, configured for a 9-month-old baby.}
+  \caption{IMU locations on the Stokke, configured for a 9-month-old baby. ALT
+  TEXT: Photos of the Stokke with seat.}
   \label{fig:tech_drawing_YOYO9}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_GreenM0_front.pdf}}
-  \caption{IMU locations on the Green Machine, configured for a 0-month-old baby.}
+  \caption{IMU locations on the Green Machine, configured for a 0-month-old
+  baby. ALT TEXT: Photos of the Green Machine.}
   \label{fig:tech_drawing_GreenM0}
@@
   \subcaptionbox{Front view}{\includegraphics[width=70mm]{fig/TechDraw_OldR9_front.pdf}}
-  \caption{IMU locations on the Old Rusty, configured for a 9-month-old baby.}
+  \caption{IMU locations on the Old Rusty, configured for a 9-month-old baby.
+  ALT TEXT: Photos of the Old Rusty.}
   \label{fig:tech_drawing_OldR9}
@@
   {\includegraphics[width=70mm, angle=-90]{fig/Tarmac_bicycle.pdf}}
-  \caption{Tarmac surface where we tested bicycles.}
+  \caption{Tarmac surface where we tested bicycles. ALT TEXT: Photo of tarmac
+  for cargo bicycles.}
   \label{fig:tarmac_bicycle}
@@
  {\includegraphics[width=70mm, angle=-90]{fig/Paver_bricks_bicycle.pdf}}
-  \caption{Paver bricks surface where we tested bicycles.}
+  \caption{Paver bricks surface where we tested bicycles. ALT TEXT: Photo of paver bricks for cargo bicycles.}
   \label{fig:paver_bricks_bicycle}
@@
   \includegraphics[width=70mm, angle=0]{fig/Shock_bicycle.pdf}
-  \caption{We performed a shock test with bicycles riding over a 30x30~\si{\mm} square section bar.}
+  \caption{We performed a shock test with bicycles riding over a 30x30~\si{\mm}
+  square section bar. ALT TEXT: Photo of cargo bicycle shock test.}
   \label{fig:shock_bicycle}
@@
     \includegraphics[width=70mm, angle=-90]{fig/Tarmac_stroller.pdf}
-  \caption{Tarmac test area.}
+  \caption{Tarmac test area. ALT TEXT: Photo of tarmac for strollers.}
   \label{fig:tarmac_stroller}
@@
   \includegraphics[width=60mm, angle=-90]{fig/Cobblestone_stroller.pdf}
-  \caption{Cobblestone surface where we tested strollers.}
+  \caption{Cobblestone surface where we tested strollers. ALT TEXT: Photo of
+  cobblestone for strollers.}
   \label{fig:cobblestone_area_stroller}
@@
     \includegraphics[width=60mm, angle=-90]{fig/Sidewalk_pavers_stroller.pdf}
-  \caption{Sidewalk pavers test area for strollers.}
+  \caption{Sidewalk pavers test area for strollers. ALT TEXT: Photo of sidewalk
+  pavers for strollers.}
   \label{fig:sidewalkpavers_area_stroller}
@@
     \includegraphics[width=70mm, angle=-90]{fig/Sidewalk_slabs_stroller.pdf}
-  \caption{Sidewalk slab test area where we conducted the test with strollers.}
+  \caption{Sidewalk slab test area where we conducted the test with strollers.
+  ALT TEXT: Photo of sidewalk slabs for strollers.}
   \label{fig:sidewalkslabs_area_stroller}
@@
   \includegraphics[width=50mm, angle=-90]{fig/Paver_bricks_stroller.pdf}
-  \caption{Details of the paver bricks test area.}
+  \caption{Details of the paver bricks test area. ALT TEXT: Photo of paver
+  bricks for strollers.}
   \label{fig:paverbrick_area_stroller}
@@
   \includegraphics[width=60mm, angle=-90]{fig/Shock_stroller.pdf}
-  \caption{Area where we tested strollers during the shock experiment.}
+  \caption{Area where we tested strollers during the shock experiment. ALT TEXT:
+  Photo of shock test for strollers.}
   \label{fig:shock_area_stroller}

### 2025-11-20 src/functions.py
Updated the data directory path and made instructions more general.

@@ -164,8 +164,7 @@ def load_session_files(session_label):
     file_names = sessions[session_label]['imu_files']
     data_frames = {}
     for label, filename in file_names.items():
-        path_to_file = os.path.join(PATH_TO_SESSION_DATA, 'Raw_data_csv',
-                                    filename)
+        path_to_file = os.path.join(PATH_TO_SESSION_DATA, filename)
         data_frames[label] = load_shimmer_file(path_to_file)
     return data_frames
 

### 2025-11-20 main.tex
Update tex file with overleaf.

@@
 \title{
-  DRAFT: v8 \\
+  DRAFT: v9.dev \\
   Vibration Characterisation of Strollers and\\
@@
 bandwidth. We investigated the influence of vehicle, seat, body size, speed, and
-road surface and provided recommendations to users, designers, and for future
-research. Furthermore, as an example of how such measurements could be used for
-assessing discomfort and health effects, we discuss these in the light of
-thresholds suggested by ISO~2631-1 and Gao~et.~al~\cite{Gao2018}.
+road surface and provided recommendations for users, designers, and researchers.
+Furthermore, as an example of how such measurements could be used for assessing
+discomfort and health effects, we discuss these in the light of thresholds
+suggested by ISO~2631-1 and Gao~et.~al~\cite{Gao2018}.
 
@@
 %
-Neil Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, and Aernout
-Dijkstra-Hellinga all provided important feedback on the preprint that helped
-improve the paper. This work was financially supported by VeiligheidNL under the
-``Project Trillingen bakfiets en wandelwagen'' and we thank VeiligheidNL
-employee Mieke Cotterink for advice, support, and review of our work.
+Neil Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, Darek
+Wieckowksi, and Aernout Dijkstra-Hellinga all provided important feedback on the
+preprint that helped improve the paper. This work was financially supported by
+VeiligheidNL under the ``Project Trillingen bakfiets en wandelwagen'' and we
+thank VeiligheidNL employee Mieke Cotterink for advice, support, and review of
+our work.
 
@@
   \centering
-  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-maxicosi-0-SeatBotacc_ver-rep0.png}
+  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-pebble-0-SeatBotacc_ver-rep0.png}
   \caption{Raw seat pan vertical acceleration versus time from session 015:

### 2025-12-17 review/review-response.tex
Added initial commit of the review response letter.

\documentclass{letter}
\usepackage[margin=25mm]{geometry}
\usepackage{csquotes}

\date{17 December 2025}
\title{Ergonomics Review Response}

\begin{document}
Dear Reviewers,

Thank you for the careful review of our work. We have revised the paper to
address your comments both for clarification of various methods and details as
well as providing background and support for some of our choices. The revision
is an improved version based on your feedback.

\begin{displayquote}
  \textbf{Editor}: I have now received replies from reviewers regarding your
  manuscript and their comments are appended at the end of this email.  You
  will see that although the reviewers judge there to be some merit in the
  paper, they advise that substantial revisions are required.  The reviewers’
  comments appear reasonable and you are invited to consider these and modify
  your paper accordingly.
\end{displayquote}

TODO

\begin{displayquote}
  \textbf{Reviewer 1}: This paper evaluates vibrations with dummies
  representing infants aged 0, 3, and 9 months lying or sitting in five
  strollers and two cargo bicycles with baby seats on 6 road surfaces using the
  ISO 2631 standard. Vibration measurements were conducted using five different
  strollers and two cargo bicycles with two baby seats. In addition to
  reporting the vibration related variables such as RMS acceleration and VDV,
  the authors also conducted health and discomfort assessment. Studying the
  effects of vibrations on children/infants is extremely difficult because
  testing on real individuals is not acceptable.

  The title ``Vibration Characterisation of Strollers and Cargo Bicycles for
  Transporting Infants Including Recommendations for Users, Designers,
  Manufacturers, and Researchers'' seems a little big long with too much
  details. The authors may consider to truncate the ``including
  recommendations….''.
\end{displayquote}

TODO

\begin{displayquote}
  It is not clear why the authors included the age 0 (newborn) infants.
  Newborns are either in hospitals or at home. It is unbelievable and is very
  rare that people taking a newborn out using a stroller or cargo bicycles.
\end{displayquote}

Parents do transport newborns by bicycle in The Netherlands and it may also
occur in other countries. An extremely common question parents have is what the
minimum age for transporting an infant by bicycle is (as shown by the abudance
of internet articles). We want to characterize the full range of infant ages so
that this question can be answered definitiely in the future. For these two
reasons, we measured newborn dummies.

\begin{displayquote}
  This paper is much longer than ordinary submission. It is unbelievable that
  even the appendixes have cover 20 pages. The authors should check the word
  count limitations (A typical paper for this journal should be no more than
  8000 words) to determine if the word count is acceptable.
\end{displayquote}

The paper has 8193 words, which we disclosed at submission. The appendices are
intended to be electronic supplementary materials and not word counted. We
provide this supplementary material to ensure the reproducibility and
completeness of our work.

\begin{displayquote}
  Unrelevant issues should be deleted to make the paper concise. An example is
  on P3, Ln 24 ``Cycling is beneficial for health…. leisure.'' There is no need
  to talk about the benefits of bicycling. Another example is the details of
  the dummies, bicycles/strollers, and pavements of the test roads. The
  Appendix E should be deleted, at least. The Effect of Road Surface in A.3 may
  also have little and very limited information.
\end{displayquote}

We desire to keep the appendices as electronic supplementary material to ensure
reproducibilty and completeness of our work.

\begin{displayquote}
  Paver bricks and tarmac were tested for all vehicles, but only strollers were
  tested on cobblestones, sidewalk pavers, and sidewalk slabs. Even with the
  pavements of the same materials, road surface conditions could be quite
  different (high variations) due to the installation, years of usage, traffic,
  and many other conditions.  The road surfaces adopted in this study may
  represent very small samples of all road surfaces.
\end{displayquote}

Yes, the road surfaces we selected do not represent a large quality and
maintenance variation of that surface. We choose surfaces that were at typical
maintenance levels observed The Netherlands. We traveled various lengths, at
least kilometer in the case of the bicycles,  on these surfaces to encounter
some variation in surface quality.

TODO: add a sentence in the paper that states "these surfaces do not represent
large variation in road surface quality"

\begin{displayquote}
  The authors have mentioned that ISO 2631 considers the effects of vibration
  on adults, not on children/infants. Yet, they still perform ISO 2631-1
  weighted vertical RMS acceleration extensively to discuss the effects of the
  vibration on children/infants. The There is no way to validate whether this
  is appropriate or not because there is no ISO vibration standard issued for
  children/infants. The dummies, even with similar size and mass, probably
  don’t have the same biomechanical and phychophysical characteristics of the
  children/infants.
\end{displayquote}

We have stated these limitations in the study, some more than once. We also
recommend that the standards be improved to address its deficiencies. We decide
to report our findings in reference to the current standard and other
references because we want to benchmark against something rather than nothing.
We believe that conservative conclusions can be made via the standards such as
``We did measure vibrations that would not be permitted for adults to maintain
long-term occupational health, and it is reasonable to believe we should not
subject our infants to the same.''

\begin{displayquote}
  \textbf{Reviewer 2}: Authors have chosen an interesting topic in the field of
  vibrations and ergonomics especially for infants. Overall, the work is well
  conducted and explained. To make it more interesting to readers, I have some
  suggestions/ comments.

  1. The title looks very general, it should be improved and include the targeted age or location from where the data of infants are considered.
\end{displayquote}

TODO

\begin{displayquote}
2. The abstract starts with "We" that should be avoided.
\end{displayquote}

Active voice is not prohibited by Ergonomics and is our preferred writing style
for scientific writing. The six most recent papers published in Ergonimics
checked on December 17, 2025 were all written with active voice. Thus, we have
kept active voice as it was in the paper.

\begin{displayquote}
3. Abstract needs revision and include the novelty/ objective/ findings of the
work.
\end{displayquote}

TODO

\begin{displayquote}
4. Authors are recommended to avoid "we" in the content.
\end{displayquote}

Active voice is not prohibited by Ergonomics and is our preferred writing style
for scientific writing. The six most recent papers published in Ergonimics
checked on December 17, 2025 were all written with active voice. Thus, we have
kept active voice as it was in the paper.

\begin{displayquote}
5. In keywords, only ISO is written, but not mentioned the full standard of ISO.
\end{displayquote}

TODO

\begin{displayquote}
6. The starting paragraph of the introduction can be deleted as it only consists of the facts that is not related to the technical aspects of the work.
\end{displayquote}

TODO

\begin{displayquote}
7. The introduction can be reduced and should be focused on the previous literature, novelty not on the mechanism of bicycle or other general topics.
\end{displayquote}

TODO

\begin{displayquote}
8. The citations are starting with [4] , [20] etc. It should start with [1] [2] etc.
\end{displayquote}

TODO

\begin{displayquote}
9. The materials and methods are well explained.
\end{displayquote}

Thank you for the compliment.

\begin{displayquote}
10. The results and discussion are also well explained but it shall be better
if authors can compare the results with any previous studies.
\end{displayquote}

TODO: add some comparisons to values from prior studies in the dicussion

\begin{displayquote}
Overall, the work done by authors is appreciable.
\end{displayquote}

Thank you, we are happy you appreciate the work.

\begin{displayquote}
  \textbf{Reviewer 3}: The manuscript presents a valuable and methodologically
  solid experimental characterization of vibrations transmitted to infants in
  strollers and cargo bicycles, based on extensive field measurements and ISO
  2631-1–based analyses; however, several issues weaken its scientific
  contribution.

  The structure, while detailed, is not always clear: the manuscript is long,
  sometimes repetitive, and sections such as Results, Discussion, and
  Recommendations partially overlap.
\end{displayquote}

\begin{displayquote}
  The Introduction provides background on
  whole-body vibration but does not clearly articulate the research gap,
  particularly why the adult-oriented ISO 2631-1 standard is used despite its
  known limitations for infants, nor does it situate the work adequately within
  infant-specific vibration literature.
\end{displayquote}

TODO

\begin{displayquote}
  Although the study cites relevant works (e.g., vibration transmissibility,
  comfort studies, bicycle vibration references), it lacks a deeper comparison
  with previous findings and does not analyze how its results confirm, extend,
  or contradict existing knowledge.
\end{displayquote}

TODO

\begin{displayquote}
  The statistical analysis does not include verification of key model
  assumptions. Although ordinary least squares regression is used, the authors
  do not test whether the residuals meet the homoscedasticity requirement.
  Given the clear variability across surfaces, speeds, and vehicle types,
  unequal variance is likely and may affect the reliability of the reported
  significance levels. Including basic diagnostic checks would strengthen the
  robustness of the statistical conclusions (e.g., Levene’s test, Breusch–Pagan
  test, or residual plots)
\end{displayquote}

TODO

\begin{displayquote}
  The Discussion, while rich in engineering insights, does not critically
  reflect on methodological constraints such as the validity of using dummies
  instead of human infants, the lack of physiological correlates, potential
  bias from specific road surfaces tested in one geographical area, unvalidated
  comfort thresholds.
\end{displayquote}

TODO

\begin{displayquote}
  The key limitation concerns the applicability of the ISO 2631-1 standard used
  throughout the analysis. This standard was developed for ``healthy adults''
  in occupational and transportation contexts, which implicitly excludes
  infants and young children, whose anatomy, vibration sensitivity, postural
  constraints, and developmental vulnerability differ substantially from those
  of adults. As a result, applying adult-derived thresholds to infant transport
  systems may lead to misinterpretation of comfort or health risk levels. While
  the authors acknowledge this to some extent, a deeper reflection on the
  implications of using a non-validated standard for this population would
  strengthen the methodological transparency and contextual accuracy of the
  study.
\end{displayquote}

TODO

\begin{displayquote}
  Overall, the non-applicability of the ISO 2631-1 standard to infants and
  young children substantially limits the strength and impact of the
  conclusions. Given these limitations, the results are ultimately valid only
  in a comparative sense between the different stroller and cargo-bike models
  tested.
\end{displayquote}

Increase in vibration intensity undoutedly correlates to larger internal forces
in the vibrated object. It should be undisputed, in general, that adults can
endure larger forces than infants for equivalent injury or discomfort. This
then implies that health and comfort thresholds for infants are lower than
those for adults. So stating that we shouldn't subject infants to vibrations
known to cause discomfort and health issues to adults should not be
controversial and referencing the standards for adults at least provides an
extreme limit that if exceeded is most certainly not good for the infant. This
standard is the only substatinal benchmarkable reference we can use to put the
values we measure into some context. We believe that providing this context is
better than providing no context because infants are also made of flesh and
bones as adults are. We hope our work prompts future researchers to seek the
thresholds for infants so these thresholds are not exceeded if they are lower
than the adult thresholds. We believe that placing our results relative to some
known, is preferrable providing them only in relative comparison among the
tested scenarios. We have stated our conclusions and recommendations ``in spite
of the standard's limitations`` based on this reasoning.

\closing{Sincerely, \\
The Authors}
\end{document}

### 2025-12-17 review/review-response.tex
Add some of Gabriele's wording to the review letter.

@@
 
-Parents do transport newborns by bicycle in The Netherlands and it may also
-occur in other countries. An extremely common question parents have is what the
-minimum age for transporting an infant by bicycle is (as shown by the abudance
-of internet articles). We want to characterize the full range of infant ages so
-that this question can be answered definitiely in the future. For these two
-reasons, we measured newborn dummies.
+We are aware that newborns are less frequently carried outdoors compared to
+older infants. However, in daily routine, strollers are used for short trips
+(medical appointments, brief walks, going with older siblings to school,
+sports, and so on), particularly in urban environments. Parents also transport
+newborns by bicycle in The Netherlands and also likely in other countries.
+
+An extremely common question parents have is what the minimum age for
+transporting an infant by stroller or bicycle is (as shown by the abudance of
+internet articles). We want to characterize the full range of infant ages so
+that this question can be answered definitiely in the future.
+
+Including newborns allowed us to consider the worst-case scenario: newborns
+have the least developed musculoskeletal system, making them potentially the
+most vulnerable group. It is a conservative approach of our study, that does
+not exclude tests with older infants (9 months).
+
+For these reasons, we measured newborn sized dummies.
+
+TODO : Add a short statement in the paper that states this?
 
@@
 
-The paper has 8193 words, which we disclosed at submission. The appendices are
-intended to be electronic supplementary materials and not word counted. We
-provide this supplementary material to ensure the reproducibility and
-completeness of our work.
+The paper has 8193 words, which we disclosed to the editor at submission. The
+appendices are intended to be electronic supplementary materials and not word
+counted. We provide this supplementary material to ensure the reproducibility
+and completeness of our work.
+
+TODO : Separate appendices into a new PDF and name it supplementary materials.
 
@@
 long-term occupational health, and it is reasonable to believe we should not
-subject our infants to the same.''
+subject our infants to the same.'' Our aim in using ISO 2631-1 was not to claim
+direct applicability to infants, but rather to provide a well-known framework,
+widely used in vibration research.
 

### 2025-12-18 src/plots.py
Added a linear regression diagnostic plotting class taken from statsmodels (bsd 3-clause).

@@ -1,4 +1,11 @@
+from statsmodels.graphics.gofplots import ProbPlot
+from statsmodels.stats.outliers_influence import variance_inflation_factor
+from statsmodels.tools.tools import maybe_unwrap_results
 import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import seaborn as sns
+import statsmodels
 
 
 def plot_frequency_spectrum(freq, amp, ax=None, plot_kw={}):
@@ -19,3 +26,396 @@ def plot_iso_weights(iso_filter_df_01, iso_filter_df_02):
     ax2 = iso_filter_df_02.plot(subplots=True)
     ax2[0].set_title('iso_filter_02')
     return ax1, ax2
+
+
+"""
+All lines below this sentence were taken from the software package statsmodels
+and the specific file:
+
+https://github.com/statsmodels/statsmodels/blob/main/examples/notebooks/linear_regression_diagnostics_plots.ipynb
+
+which is licensed under the modified BSD 3-clause license and reproduced here
+as per the terms:
+
+Copyright (C) 2006, Jonathan E. Taylor
+All rights reserved.
+
+Copyright (c) 2006-2008 Scipy Developers.
+All rights reserved.
+
+Copyright (c) 2009-2018 statsmodels Developers.
+All rights reserved.
+
+
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are met:
+
+  a. Redistributions of source code must retain the above copyright notice,
+     this list of conditions and the following disclaimer.
+  b. Redistributions in binary form must reproduce the above copyright
+     notice, this list of conditions and the following disclaimer in the
+     documentation and/or other materials provided with the distribution.
+  c. Neither the name of statsmodels nor the names of its contributors
+     may be used to endorse or promote products derived from this software
+     without specific prior written permission.
+
+
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
+AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+ARE DISCLAIMED. IN NO EVENT SHALL STATSMODELS OR CONTRIBUTORS BE LIABLE FOR
[…]

### 2025-12-18 src/website.py
Added residual plots and the Breusch Pagan homoscadascity test.

@@ -7,6 +7,7 @@ import subprocess
 
 # external dependencies
 from statsmodels.stats.multicomp import pairwise_tukeyhsd
+from statsmodels.stats.diagnostic import het_breuschpagan
 import matplotlib.pyplot as plt
 import matplotlib.ticker as ticker
 import numpy as np
@@ -17,6 +18,7 @@ import statsmodels.formula.api as smf
 
 # local
 from functions import print_header, eval_health
+from plots import LinearRegDiagnostic
 from html_templates import INDEX, H2, H4, P, IMG
 from paths import (PATH_TO_REPO, PATH_TO_DATA_DIR, PATH_TO_FIG_DIR,
                    PATH_TO_TABLE_DIR)
@@ -187,6 +189,23 @@ mod = smf.ols(formula=f, data=bicycle_df)
 bicycle_res = mod.fit()
 print_header("Bicycle OLS Results (Vertical ISO Weigthed RMS)")
 print(bicycle_res.summary())
+fig, ax = plt.subplots()
+sns.residplot(
+    x=bicycle_res.fittedvalues,
+    y=bicycle_res.resid,
+    lowess=True,
+    ax=ax,
+)
+fname = '{}-residual-variance-bicycle.png'.format(SIGNAL)
+fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
+fig = sma.qqplot(bicycle_res.resid, line='s')
+fname = '{}-qqplot-bicycle.png'.format(SIGNAL)
+fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
+breuschpagan_labels = ["Lagrange multiplier statistic", "p-value", "f-value",
+                       "f p-value"]
+pprint.pprint(dict(zip(breuschpagan_labels,
+                       het_breuschpagan(bicycle_res.resid,
+                                        bicycle_res.model.exog))))
 with open(os.path.join(PATH_TO_TABLE_DIR, 'bicycle-ols.tex'), 'w') as f:
     f.write(bicycle_res.summary().as_latex())
 bicycle_comp_tables = []
@@ -225,6 +244,25 @@ mod = smf.ols(formula=f, data=stroller_df)
 stroller_res = mod.fit()
 print_header("Stroller OLS Results (Vertical ISO Weigthed RMS)")
 print(stroller_res.summary())
+diag = LinearRegDiagnostic(stroller_res)
[…]

### 2025-12-18 src/plots.py
Regression diagnostics plots working.

@@ -35,7 +35,7 @@ and the specific file:
 https://github.com/statsmodels/statsmodels/blob/main/examples/notebooks/linear_regression_diagnostics_plots.ipynb
 
 which is licensed under the modified BSD 3-clause license and reproduced here
-as per the terms:
+as per the terms. Some lines have been modifed post copy.
 
 Copyright (C) 2006, Jonathan E. Taylor
 All rights reserved.
@@ -189,7 +189,7 @@ class LinearRegDiagnostic:
         if plot_context not in plt.style.available:
             plot_context = "default"
         with plt.style.context(plot_context):
-            fig, ax = plt.subplots(nrows=2, ncols=2, figsize=(10, 10))
+            fig, ax = plt.subplots(nrows=2, ncols=2, layout='constrained')
             self.residual_plot(ax=ax[0, 0])
             self.qq_plot(ax=ax[0, 1])
             self.scale_location_plot(ax=ax[1, 0])
@@ -198,7 +198,6 @@ class LinearRegDiagnostic:
                 high_leverage_threshold=kwargs.get("high_leverage_threshold"),
                 cooks_threshold=kwargs.get("cooks_threshold"),
             )
-            plt.show()
 
         return (
             self.vif_table(),

### 2025-12-18 src/website.py

@@ -189,17 +189,9 @@ mod = smf.ols(formula=f, data=bicycle_df)
 bicycle_res = mod.fit()
 print_header("Bicycle OLS Results (Vertical ISO Weigthed RMS)")
 print(bicycle_res.summary())
-fig, ax = plt.subplots()
-sns.residplot(
-    x=bicycle_res.fittedvalues,
-    y=bicycle_res.resid,
-    lowess=True,
-    ax=ax,
-)
-fname = '{}-residual-variance-bicycle.png'.format(SIGNAL)
-fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
-fig = sma.qqplot(bicycle_res.resid, line='s')
-fname = '{}-qqplot-bicycle.png'.format(SIGNAL)
+diag = LinearRegDiagnostic(bicycle_res)
+_, fig, ax = diag()  # returns panel plot of all diagnostics
+fname = '{}-regression-diagnostics-bicycle.png'.format(SIGNAL)
 fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
 breuschpagan_labels = ["Lagrange multiplier statistic", "p-value", "f-value",
                        "f p-value"]
@@ -246,17 +238,7 @@ print_header("Stroller OLS Results (Vertical ISO Weigthed RMS)")
 print(stroller_res.summary())
 diag = LinearRegDiagnostic(stroller_res)
 _, fig, ax = diag()  # returns panel plot of all diagnostics
-fig, ax = plt.subplots()
-sns.residplot(
-    x=stroller_res.fittedvalues,
-    y=stroller_res.resid,
-    lowess=True,
-    ax=ax,
-)
-fname = '{}-residual-variance-stroller.png'.format(SIGNAL)
-fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
-fig = sma.qqplot(stroller_res.resid, line='s')
-fname = '{}-qqplot-stroller.png'.format(SIGNAL)
+fname = '{}-regression-diagnostics-stroller.png'.format(SIGNAL)
 fig.savefig(os.path.join(PATH_TO_FIG_DIR, fname), dpi=300)
 breuschpagan_labels = ["Lagrange multiplier statistic", "p-value", "f-value",
                        "f p-value"]
